### 2018-10-19 reports/manuscript/paper.tex
Add manuscript skeleton

\documentclass[11pt,twoside,a4paper]{article}
\usepackage{authblk}  % For author affiliations with the basic article class
\usepackage{booktabs}  % For formal tables
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathtools}  % for \shortintertext{} and PairedDelimiter
\usepackage{xcolor}

\graphicspath{ {../figures/} }

\DeclarePairedDelimiter\p{(}{)}
\DeclarePairedDelimiter\brkt{[}{]}

\newcommand{\ariel}[1]{{\color{blue} Ariel: [{#1}]}}
\newcommand{\adam}[1]{{\color{green} Adam: [{#1}]}}
\newcommand{\strike}[1]{{\color{red} Strikeout: [{#1}]}}
\newcommand{\authoremail}[1]{\href{mailto:{#1}}{\textnormal{\texttt{{#1}}}}}

% Set the affiliation font and the affiliation separation
\renewcommand\Affilfont{\itshape\small}
\setlength{\affilsep}{1em}
\setcounter{Maxaffil}{3}

\begin{document}

\title{AFQ-Insight}
\title{Multidimensional analysis and detection of informative features in diffusion MRI measurements of human white matter}
\date{\today}

\author[1]{Adam Richie-Halford\thanks{Corresponding author: \authoremail{richford@uw.edu}}}
\author[2]{Jason Yeatman}
\author[3]{Noah Simon}
\author[4]{Ariel Rokem}

\affil[1]{University of Washington Department of Physics, Seattle, WA 98105}
\affil[2]{University of Washington Department of Speech and Hearing Sciences, Seattle, WA 98105}
\affil[3]{University of Washington Department of Biostatistics, Seattle, WA 98105}
\affil[4]{University of Washington e{S}cience Institute, Seattle, WA 98105}

\input{abstract}

\maketitle
\tableofcontents

\input{sections}

\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}

### 2018-10-19 reports/manuscript/sections/methods.tex
Add manuscript skeleton

\section{Methods}

\begin{itemize}
  \item Data
    \begin{itemize}
      \item Raw measurement sources
      \item AFQ pipeline
      \item Insight preprocessing
    \end{itemize}
  \item Sparse Group Lasso
    \begin{itemize}
      \item Regression case
      \item Classification with logistic regression
    \end{itemize}
  \item Computational implementation
    \begin{itemize}
      \item Insert Figure for pipeline
      \item Proximal gradient methods
      \item Meta-parameter optimization
      \item Cross-validation scheme
        \begin{itemize}
          \item Insert Figure for cross-validation scheme
        \end{itemize}
    \end{itemize}
\end{itemize}

### 2018-10-19 reports/manuscript/sections/results.tex
Add manuscript skeleton

\section{Results}

\begin{itemize}
  \item Regression
    \begin{itemize}
      \item HCP Reading Scores
      \item Insert figure showing sparsity pattern
      \item Insert figure showing weights as they relate to tract differences visible in the browser
    \end{itemize}
  \item Classification
    \begin{itemize}
      \item ALS Classification (Sarica)
      \item Insert figure showing sparsity pattern
      \item Insert figure showing weights as they relate to tract differences visible in the browser
    \end{itemize}
  \item Failures
    \begin{itemize}
      \item Hopefully, the failures are common to both regression
        and classification so we can include them here in there own
        subsection.
      \item Insert figure demonstrating failure cases
    \end{itemize}
\end{itemize}

### 2018-10-26 reports/manuscript/abstract.tex
Update permissions

\begin{abstract}

\adam{This is a copy of the abstract submitted for SfN 2018}

The white matter contains long-range connections between different brain regions. Tractometry uses diffusion-weighted magnetic resonance imaging (dMRI) data to quantify tissue properties along the trajectories of these connections in the human brain in vivo\cite{yeatman2012tract}. In previous work, the results of tractometry were usually analyzed using mass univariate approaches: group comparisons or regression models computed separately for each point along every one of the tracts.  Alternatively, tissue properties such as fractional anisotropy (FA) and mean diffusivity (MD) were computed for a specific tract of interest based on an a priori hypothesis. In the present work, we developed a method based on the sparse group lasso\cite{simon2013sparse} that takes into account all of the tissue properties measured in all of the tracts, and selects informative features by enforcing sparsity, both at the level of individual tracts and tissue properties, but also across the entire set of tracts and all of the measured tissue properties. The sparsity penalties for each of these constraints is identified using a nested cross-validation scheme. Using data from a previous study that measured dMRI in patients with amyotrophic lateral sclerosis (ALS) and matched controls\cite{sarica2017corticospinal}, we demonstrate that this method is accurate, exceeding the previous results, that were based on a priori feature selection, in classifying patients and controls, with ~84\% accuracy, an area under the receiver operating characteristic curve of 0.93, and an average precision of 0.95. Moreover, our method automatically identifies as important for this classification the parts of the white matter known to be affected by ALS within the corticospinal tract. In a regression setting, data from another previous study\cite{yeatman2014lifespan} can be used to accurately predict ``brain age''. Thus, this multivariate analysis approach both (a) achieves high cross-validated accuracy for precision medicine applications of dMRI data and (b) identifies relevant features of brain anatomy to further our neuroscientific understanding of clinical disorders.

\end{abstract}

### 2018-10-26 reports/manuscript/sections.tex
Update permissions

\input{sections/introduction}
\input{sections/methods}
\input{sections/results}
\input{sections/conclusion}

\section{Acknowledgements}

Here are some amazing acknowledgements.

### 2018-10-26 reports/manuscript/sections/conclusion.tex
Update permissions

\section{Conclusion}

\begin{itemize}
  \item Feature selection + prediction
  \item Part of the AFQ ecosystem
  \item Open source, reproducibility
\end{itemize}

### 2018-10-26 reports/manuscript/sections/introduction.tex
Update permissions

\section{Introduction}

\begin{itemize}
  \item Tractometry vs averaging over tracts \\
    (see AFQ-Browser paper for inspiration and political correctness)
  \item Existing methods
    \begin{itemize}
      \item Cite profilometry\cite{dayan2016profilometry}
      \item Cite Sarica\cite{sarica2017corticospinal}
      \item Discuss mass univariate approaches\cite{yeatman2014lifespan}
    \end{itemize}
\end{itemize}

### 2018-10-27 src/data/get_data.py
Remove reading data from get_data.py

@@ -33,12 +33,12 @@ def download_url_to_file(url, output_fn, encoding='utf-8'):
 def main():
     description = 'Download datasets to test AFQ-Insight.'
     parser = argparse.ArgumentParser(description=description)
-    parser.add_argument('-d', '--dataset', required=True, type=str, choices={'all', 'als', 'reading'})
+    parser.add_argument('-d', '--dataset', required=True, type=str, choices={'all', 'als'})
     results = parser.parse_args() # collect cmd line args
 
     datasets = results.dataset
     if datasets == 'all':
-        datasets = ['als', 'reading']
+        datasets = ['als']
     else:
         datasets = [datasets]
 
@@ -53,7 +53,6 @@ def main():
                 'file': './data/raw/als_data/subjects.csv'
             },
         ],
-        'reading': []
     }
 
     for dset_key in datasets:

### 2019-02-07 reports/manuscript/paper.tex
Remove maxAfill line in paper.tex preamble
Add methods section to manuscript

@@
-\documentclass[11pt,twoside,a4paper]{article}
-\usepackage{authblk}  % For author affiliations with the basic article class
-\usepackage{booktabs}  % For formal tables
-\usepackage[margin=1in]{geometry}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
+
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
+\usepackage{listings}
 
@@
 \DeclarePairedDelimiter\brkt{[}{]}
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}
 
@@
 
-% Set the affiliation font and the affiliation separation
-\renewcommand\Affilfont{\itshape\small}
-\setlength{\affilsep}{1em}
-\setcounter{Maxaffil}{3}
+\begin{document}
+\vspace*{0.2in}
 
-\begin{document}
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{AFQ-Insight: multidimenstional analysis and detection of informative features in diffusion MRI measurements of human white matter} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Adam Richie-Halford\textsuperscript{1,*},
+Jason Yeatman\textsuperscript{2},
+Noah Simon\textsuperscript{3},
+Ariel Rokem\textsuperscript{4},
+\\
+\bigskip
+\textbf{1} Department of Physics, University of Washington, Seattle, WA, 98105, USA
+\\
+\textbf{2} Department of Speech and Hearing Sciences, University of Washington, Seattle, WA, 98105, USA
+\\
+\textbf{3} Department of Biostatistics, University of Washington, Seattle, WA, 98105, USA
+\\
+\textbf{4} e{S}cience Institute, University of Washington, Seattle, WA, 98105, USA
+\\
+\bigskip
 
-\title{AFQ-Insight}
-\title{Multidimensional analysis and detection of informative features in diffusion MRI measurements of human white matter}
-\date{\today}
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* richford@uw.edu
 
-\author[1]{Adam Richie-Halford\thanks{Corresponding author: \authoremail{richford@uw.edu}}}
-\author[2]{Jason Yeatman}
-\author[3]{Noah Simon}
-\author[4]{Ariel Rokem}
+\end{flushleft}
 
-\affil[1]{University of Washington Department of Physics, Seattle, WA 98105}
-\affil[2]{University of Washington Department of Speech and Hearing Sciences, Seattle, WA 98105}
-\affil[3]{University of Washington Department of Biostatistics, Seattle, WA 98105}
-\affil[4]{University of Washington e{S}cience Institute, Seattle, WA 98105}
-
+% Please keep the abstract below 300 words
 \input{abstract}
 
-\maketitle
-\tableofcontents
+\input{author_summary}
+
+\linenumbers
 
@@
 
-\bibliographystyle{abbrv}
+\nolinenumbers
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
 \bibliography{paper}

### 2019-02-07 reports/manuscript/sections/methods.tex
Add methods section to manuscript

@@
-\section{Methods}
+\section*{Materials and methods}
+
+\subsection*{Data}
+
+We tested AFQ-Insight in a classification setting using data from a previous study of the corticospinal tract profile in patients with amyotrophic lateral sclerosis (ALS)\cite{sarica2017corticospinal}.
+This study collected dMRI data from 24 ALS patients and 24 demographically matched healthy controls.
+In the regression setting, we used dMRI data from a previous study of properties of the white matter across the lifespan\cite{yeatman2014lifespan}, containing dMRI data from 76 subjects with ages 6-50.
+In both cases, the authors of these previous studies made their imaging data available through\ldots \adam{How?
+Through neurovault?
+Private correspondence?}.
+
+The ``raw'' dMRI data from the ALS and lifespan maturation studies were then analyzed using the Automated Fiber-Tract Quantification tractometry pipeline\cite{yeatman2012tract} with the pyAFQ package\cite{pyAFQ} \adam{Or was it the MATLAB implementation?}.
+This creates tract profiles, in which diffusion measures are quantified and averaged along twenty major fiber tracts.
+These tract profiles, along with the phenotypical data we wish to explain or predict, form the input to AFQ-Insight.
+In a domain-agnostic machine learning context, the phenotypical data comprise the target variables while the tract profiles form the feature or predictor variables.
+
+AFQ-Insight reads the target and feature data from comma separated value (CSV) files conforming to the AFQ-Browser data format\cite{yeatman2018browser} \adam{Should we cite the specific page in the online documentation} and represents them internally as \lstinline{DataFrame} objects from the pandas Python library\cite{mckinney2010data}.
+We leave imputation of the target data to the user and automatically impute missing data only in the feature matrix.
+Missing interior nodes are imputed using linear interpolation.
+For missing exteriod nodes, the user may choose between linear extrapolation and constant forward(back)-fill.
+The data imputation uses only values from adjacent nodes in the same white matter tract in the same subject so there is no danger of data leakage from other subjects.
+
+Lastly, like most learning algorithms, AFQ-Insight benefits from standardization of the input dataset.
+Some diffusion metrics will have naturally larger variance than others and may therefore dominate the objective function and make the sparse group lasso estimator unable to learn from the lower variance metrics.
+For example, fractional anisotropy (FA) is bounded between zero and one and could be overwhelmed by an unscaled higher-variance metric like the mean diffusivity (MD).
+To prevent this, AFQ-Insight uses the \lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}, to remove each feature's mean and scale it to unit variance.
+Scaling is performed separately within each cross-validation set's training or testing data to prevent leakage of information between the testing and training sets\cite{kaufman2012leakage}.
+
+\subsection*{Sparse Group Lasso}
+
+After scaling and imputation, the tractometry data and target phenotypical data can be organized in a linear model, $y = \mathbf{X} \cdot \beta$, where $y$ is the phenotype -- categorical, such as a clinical diagnosis, or numerical, such as the subject's age.
+The tractometry data is represented in the feature matrix $\mathbf{X}$, with rows corresponding to different subjects, and columns corresponding to diffusion measures at different nodes within each tract.
+The relationship between tractometric features and the phenotypic target is characterized by the coefficients in $\beta$.
+The feature matrix $\mathbf{X}$ has dimensions $N_s \times (N_t \cdot N_n \cdot N_m)$, where $N_s$ is the number of subjects, $N_t$ is the number of white matter tracts, $N_n$ is the number of nodes in each tract, and $N_m$ is the number of diffusion metrics calculated at each node.
+Typically, $N_t = 20$, $N_n = 100$, and $2 \le N_m \le 8$, resulting in $\mathcal{O}(10^4)$ features.
+Conversely, most dMRI studies have $\mathcal{O}(10^2)$ participants, yielding a feature matrix that is wide and short.
+The high dimensionality of this data requires regularization to avoid overfitting and generate interpretable results.
+
+In addition to regularizing the coefficients in $\beta$, we also wish to capitalize upon our knowledge of the group structure of the tract profile features in $\mathbf{X}$.
+The tract-metric combinations form a natural grouping.
+For example, we expect that MD features within the left arcuate fasciculus will be correlated.
+Likewise for FA values within the right corticospinal tract (CST) and so on.
+This group structure is represented in Fig~\ref{fig:group-structure}, which depicts the linear model $y = \mathbf{X} \cdot \beta$.
+The target vector $y$ is sorted into patients (p) and controls (c), while the different colors encode the group structure of the feature matrix $\mathbf{X}$, with one group for each unique tract-metric combination.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.65\textwidth]{dMRI_group_structure.pdf}
+    \caption{{\bf dMRI group structure.}
+        The phenotypical target data and tractometric features can be organized into a linear model, $y = \mathbf{X} \cdot \beta$.
+Here, the target array $y$ is suggestively sorted into patients (p) and controls (c), while the feature matrix $\mathbf{X}$ is color-coded to reveal a natural group structure.
+In this example, the left (orange) group contains $k$ features from the inferior fronto-occipital fascicle (IFOF), the middle (green) group contains $k$ features from the corpus callosum, and the right (blue) group contains $k$ features from the uncinate.
+The coefficients in $\beta$ follow the same natural grouping.
+Fascicle images taken with permission from Ref~\cite{yeatman2012tract}.
+    }
+    \label{fig:group-structure}
+\end{figure}
+
+Thus, we seek a regularization approach that will fit a linear model with anatomically-grouped covariates, where we expect to observe sparse coefficients at both the group level and the within-group level.
+The sparse group lasso (SGL) is a penalized regression technique that satisfies exactly these criteria\cite{simon2013sparse}.
+It solves for a coefficient vector $\widehat{\beta}$ that satisfies
+\begin{equation}
+    \widehat{\beta} = \min_\beta \frac{1}{2}
+    \norm*{y - \displaystyle \sum_{\ell = 1}^{m} \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
+    + \lambda_1 \displaystyle \sum_{\ell = 1}^{m} \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
+    + \lambda_2 \norm*{\beta}_1,
+    \label{eq:sgl}
+\end{equation}
+where $m$ is the number of anatomical groups, $\mathbf{X}^{(\ell)}$ is the submatrix of $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the coefficient vector for group $\ell$ and $p_\ell$ is the length of $\beta^{(\ell)}$.
+The first term is the mean square error loss, $L_{mse}$, as in the standard linear regression framework.
+The second and third terms encourage groupwise sparsity and overall sparsity, respectively.
+If $\lambda_1 = 0$ and $\lambda_2 = 1$, the SGL reduces to the traditional lasso\cite{tibshirani1996regression}.
+Conversely, if $\lambda_1 = 1$ and $\lambda_2 = 0$, the SGL reduces to the group lasso\cite{yuan2006model}.
+
+When the phenotypical target variable are categorical, as in the case of predicting a clinical diagnosis, the SGL is readily adapted to logistic regression, where the probability of a target variable belonging to an arbitrary defined ``true'' class is the logistic function of the result of the linear model,
+\begin{equation}
+    p(y = 1) = \frac{1}{1 + \exp(\mathbf{X}\cdot \beta)},
+    \label{eq:logit}
+\end{equation}
+or equivalently, the mean squared error loss function in Eq~\eqref{eq:sgl} is replaced with the cross-entropy loss, which for binary classification is the negative log likelihood of the SGL classifier giving the ``true'' label:
+\begin{equation}
+    L_{mse} \rightarrow L_{\log} = -\left(y \log(p) + (1 - y) \log(1 - p)\right).
+    \label{eq:logloss}
+\end{equation}
 
 \begin{itemize}
-  \item Data
-    \begin{itemize}
-      \item Raw measurement sources
-      \item AFQ pipeline
-      \item Insight preprocessing
-    \end{itemize}
-  \item Sparse Group Lasso
-    \begin{itemize}
-      \item Regression case
-      \item Classification with logistic regression
-    \end{itemize}
   \item Computational implementation

### 2019-02-07 reports/manuscript/sections/results.tex
Add methods section to manuscript

@@
-\section{Results}
+\section*{Results and discussion}
+
+Using data from a previous study of the corticospinal tract profile and ALS\cite{sarica2017corticospinal}, we tested the performance of AFQ-Insight in a classification setting.
+The previous study predicted ALS status with a mean accuracy of 80\% using a random forest algorithm based on a priori selection of features within the corticospinal tract.
+\adam{slight caveat here: not really a priori feature selection but rather a feature selection based on a mean decrease gini cutoff that seems a little bit like peaking.
+But anyway, I don't really want to recapitulate the entire Sarica paper here so perhaps saying a priori feature selection is a good shorthand}.
+AFQ-Insight delivers competitive predictive performance (mean 84\% accuracy, 0.93 ROC AUC) without the need for a priori feature engineering.
+The results of the classification prediction are shown in Fig~\ref{fig:class-results}.
+
+\begin{figure}[!h]
+    \centering
+    %\includegraphics[width=0.65\textwidth]{classification_results.pdf}
+    \caption{{\bf Prediction of ALS status.}
+        Classification probabilities for each subject's ALS diagnosis.
+Controls are on the left while patients are on the right.
+Predicted controls are in blue and predicted patients are in red.
+Thus, false positive are represented as red dots on the left, while false negatives are represented as blue dots on the right.
+AFQ-Insight achieves 84\% accuracy with an ROC area under the curve of 0.93.
+    }
+    \label{fig:class-results}
+\end{figure}
+
+\begin{itemize}
+  \item Classification
+    \begin{itemize}
+      \item Insert figure showing sparsity pattern
+      \item Insert figure showing weights as they relate to tract differences visible in the browser
+    \end{itemize}
+\end{itemize}
+
+In a regression setting, we attempted to accurately predict ``brain age''.
 
@@
     \begin{itemize}
-      \item HCP Reading Scores
-      \item Insert figure showing sparsity pattern
-      \item Insert figure showing weights as they relate to tract differences visible in the browser
-    \end{itemize}
-  \item Classification
-    \begin{itemize}
-      \item ALS Classification (Sarica)
+      \item Lifespan maturation age regression
       \item Insert figure showing sparsity pattern

### 2019-02-08 reports/manuscript/sections/introduction.tex
Add methods section to manuscript
First pass of several sections of the Introduction.
Haven't quite gotten to the point where I describe what/why we're doing here.

But it's a start.

@@
-\section{Introduction}
+\section*{Introduction}
 
 \begin{itemize}
-  \item Tractometry vs averaging over tracts \\
-    (see AFQ-Browser paper for inspiration and political correctness)
-  \item Existing methods
-    \begin{itemize}
-      \item Cite profilometry\cite{dayan2016profilometry}
-      \item Cite Sarica\cite{sarica2017corticospinal}
-      \item Discuss mass univariate approaches\cite{yeatman2014lifespan}
-    \end{itemize}
-\end{itemize}
+
+Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into
+the physical properties of the connections that comprise the brain white matter
+\cite{wandell2016clarifying}. Among the benefits of the method are the fact that
+it is non-invasive, and feasible to conduct in clinical scanners, and in wide
+variety of populations: healthy adults, but also clinical populations, as well
+as young or elderly subjects. While the measurements are usually conducted with
+voxels at the millimeter scale, within the diffusion time usually used, water
+molecules within each voxel can probe the structure of white matter at the
+micrometer scale, providing important information about the physical structure
+of the white matter, such as the distribution of fiber orientations within each
+voxel \cite{Frank2002-iz, Frank2001-xf}. With more sophisticated measurements
+that include several diffusion-weightings, more information can be extracted
+about the composition of different tissue type in the voxel
+\cite{Jeurissen2014-ab, Kaden2016-ho}. In addition, phenomenological
+descriptions of the diffusion properties, such as its mean diffusivity or
+fractional anisotropy can be derived from dMRI measurements
+\cite{Pierpaoli1996-vj}. Some of these descriptions are ambiguous in terms of
+their interpretation, as variance in these properties can relate to several
+different underlying physical causes. For example, fractional anisotropy can
+decrease both because of demyelination, but also because of decreased density,
+or because of partial volume with other tissue types or between crossing fiber
+populations \cite{Beaulieu1996-fn, Beaulieu2002-tl}. Even so, these descriptions
+have proven useful in characterizing individual differences or differences
+between populations \cite{}.
+
+To relate the diffusion in each voxel to the underlying macro-structure of
+long-range connections between different brain regions, methods for
+computational tract-tracing from diffusion MRI, or tractography combine the
+estimates of fiber orientations in each voxel to form streamlines that traverse
+the volume of the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods
+have been under increased scrutiny and several lines of investigation have
+raised critiques of their validity \cite{Maier-Hein2017-vb, Thomas2014-ki}. On
+the other hand, there have been efforts to shore up the inferences made with
+these methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc,
+Smith2015-cx, Smith2015-zt, Rheault2018-wk}. Importantly, though discovering
+novel fiber bundles requires extraordinary evidence, and delineating the exact
+location of the termination of the streamlines in the gray matter, there is
+little dispute that tractography can accurately delineate major white matter
+bundles that are known to exist within the core of the white matter
+\ariel{citation needed}.
+
+Using this fact, one of the most powerful methods currently available to put
+macro- and micro-structure together is \emph{tractometry} (also known as
+tract-based morphometry): assessment of the physical properties of the white
+matter along specific tracts \cite{Bells2011-cf}. Though there are several
+different available implementations of this overall idea, the principles are
+similar \cite{yeatman2012, Yendiki2011-ay, Wassermann2016-iv, ODonnell2009-uu}:
+tractometry begins by delineating the parts of the white matter that belong to
+different major tracts and axonal fiber bundles, such as the corticospinal tract
+or arcuate fasciculus, and samples the biophysical properties (such as
+fractional anisotropy or mean diffusivity) along the length of these bundles. In
+some cases, tissue properties along the length of each bundle are summarized by
+taking the mean along each bundle, but there is a large body of evidence showing
+that there is systematic variability within each bundle. This justifies
+retaining the individual samples along the length of each fiber
+\cite{yeatman2012, colby2012, ODonnell2009-uu}. However, while this retains
+important information about each individual's white matter, it also presents
+statistical challenges due to the dimensionality of the data. Based on
+tractometry, researchers may choose to compare different individuals to each
+other. This is usually done following one of the following approaches:
+
+\begin{enumerate}
+\item Mass univariate approaches: In this approach comparisons between groups or
+across individuals are done at each node of each tract, for each one of the
+diffusion metrics available at that point. This approach is exhaustive, but the
+challenge with this approach is that the are multiple points to compare, and
+statistical power is compromised by a multiple comparison problem. Different
+approaches can be taken to resolving this challenge. For example, Colby and
+colleagues \cite{colby2012} used a non-parametric resmapling approach to correct
+for family-wise error across the universe of different comparisons available in
+the mass univariate approach \cite{Nichols2002-zu, Nichols2003-yy}.
+\item ROI-based approach: An alternative is using an ROI based approach. In this
+approach, the multiple comparison problem is circumvented by selecting just a
+few tracts to compare in each individual, or even focusing on particular
+segments of these tracts. This approach is very powerful when the biological
+basis of the process of interest is relatively well understood (for a recent
+example, see \cite{huber2018rapid}).
+\item ROI-based selection, followed by multivariate analysis. Here, an ROI is
+selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
+ROI are used together to fit a model that can predict differences between
+individuals.
+\end{enumerate}
+
+In the present work, we present a novel framework for analysis of tractometry
+that simultaneously selects the features for analysis, and fits a model to these
+features. Rather than a comparative approach, this framework takes a predictive
+approach to analysis \cite{Yarkoni2017-bi}. Using this approach, we need to
+first deal with the large and asymmetric dimensionality of the data: tractometry
+data usually has many more features (i.e., number of measurements per
+individual) than samples (number of subjects). This regime is the target of
+several statistical learning techniques, and is often solved by various forms of
+regularization. For example, Tikhonov regularization shrinks the solution such that
+each feature. The Lasso. One of the enabling

### 2019-02-09 reports/manuscript/sections/introduction.tex
Remove cruft.
A bit more about what we're doing here.

@@
 \section*{Introduction}
-
-\begin{itemize}
 
@@
 \begin{enumerate}
+
 \item Mass univariate approaches: In this approach comparisons between groups or
@@
 the mass univariate approach \cite{Nichols2002-zu, Nichols2003-yy}.
+
 \item ROI-based approach: An alternative is using an ROI based approach. In this
@@
 example, see \cite{huber2018rapid}).
+
 \item ROI-based selection, followed by multivariate analysis. Here, an ROI is
@@
 individuals.
+
 \end{enumerate}
@@
 features. Rather than a comparative approach, this framework takes a predictive
-approach to analysis \cite{Yarkoni2017-bi}. Using this approach, we need to
-first deal with the large and asymmetric dimensionality of the data: tractometry
-data usually has many more features (i.e., number of measurements per
-individual) than samples (number of subjects). This regime is the target of
-several statistical learning techniques, and is often solved by various forms of
-regularization. For example, Tikhonov regularization shrinks the solution such that
-each feature. The Lasso. One of the enabling
+approach to analysis \cite{Yarkoni2017-bi}. We use a linear modeling approach,
+which aims to predict phenotypical variance in a group of subjects, based on a
+linear combination of the features estimated with tractometry. Using this
+approach, we need to first deal with the large and asymmetric dimensionality of
+the data: tractometry data usually has many more features (i.e., number of
+measurements per individual) than samples (number of subjects), which makes
+inferences from the data about phenotypical differences between individuals
+ill-posed. This regime is the target of several statistical learning techniques,
+and is often solved by various forms of regularization. For example, Tikhonov
+regularization shrinks the solution such that the sum of squared contributions
+from the individual features are minimized \cite{Hoerl2000-ij}. Another solution
+to the problem is provided by the Lasso algorithm, which instead minimizes the
+sum of the absolute values of contributions of each feature
+\cite{Tibshirani1996-qs}. This tends to shrink to zero the contributions of many
+of the features, providing results that are both accurate and interpretable.
+When additional structure is available in the organization of the data,
+regularization algorithms can take advantage of this structure. For example, if
+the features lend themselves to a natural division into different groups, the
+group lasso (GL) can be used to select groups of features, rather than
+individual features \cite{Yuan2006-ky}. The Sparse Group Lasso (SGL) elaborates
+on this idea by providing control both of group sparsity, as well as overall
+sparsity of the solutions \cite{simon2013sgl}. Because the features measured
+with tractomery lend themselves to grouping based on the tracts from which each
+measurement is taken, GL and SGL provide a useful tool linear model fitting in
+problems of this form.

### 2019-02-09 reports/manuscript/sections/introduction.tex
Adds a little bit more about multivariate analysis.

@@
 ROI are used together to fit a model that can predict differences between
-individuals.
+individuals. An example of that is the ``profilometry'' framework, in which
+different diffusion metrics from a single tract are combined together to provide
+input to a multivariate analysis of covariance, and linear discriminant analysis
+\cite{dayan2016profilometry}. Other work has used random forests algorithms
+applied to the corticospinal tract to discriminate between patients with ALS and
+matched controls \cite{sarica2017corticospinal}
 

### 2019-02-09 reports/manuscript/sections/results.tex
Remove comment about Sarica paper

@@
 The previous study predicted ALS status with a mean accuracy of 80\% using a random forest algorithm based on a priori selection of features within the corticospinal tract.
-\adam{slight caveat here: not really a priori feature selection but rather a feature selection based on a mean decrease gini cutoff that seems a little bit like peaking.
-But anyway, I don't really want to recapitulate the entire Sarica paper here so perhaps saying a priori feature selection is a good shorthand}.
 AFQ-Insight delivers competitive predictive performance (mean 84\% accuracy, 0.93 ROC AUC) without the need for a priori feature engineering.

### 2019-02-11 reports/manuscript/sections/introduction.tex
These are better references for predictive model "culture".

@@
 have proven useful in characterizing individual differences or differences
-between populations \cite{}.
+between populations \ariel{citation needed}.
 
-To relate the diffusion in each voxel to the underlying macro-structure of
-long-range connections between different brain regions, methods for
-computational tract-tracing from diffusion MRI, or tractography combine the
-estimates of fiber orientations in each voxel to form streamlines that traverse
-the volume of the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods
-have been under increased scrutiny and several lines of investigation have
-raised critiques of their validity \cite{Maier-Hein2017-vb, Thomas2014-ki}. On
-the other hand, there have been efforts to shore up the inferences made with
-these methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc,
-Smith2015-cx, Smith2015-zt, Rheault2018-wk}. Importantly, though discovering
-novel fiber bundles requires extraordinary evidence, and delineating the exact
-location of the termination of the streamlines in the gray matter, there is
-little dispute that tractography can accurately delineate major white matter
-bundles that are known to exist within the core of the white matter
-\ariel{citation needed}.
+To relate the diffusion in each voxel to the macro-structure of long-range
+connections between different brain regions, methods for computational
+tract-tracing from diffusion MRI, or tractography, combine the estimates of
+fiber orientations in each voxel to form streamlines that traverse the volume of
+the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods have been
+under increased scrutiny and several lines of investigation have raised
+critiques of their validity \cite{Maier-Hein2017-vb, Thomas2014-ki}. On the
+other hand, there have been efforts to shore up the inferences made with these
+methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
+Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel fiber
+bundles requires extraordinary evidence, and delineating the exact location of
+the termination of the streamlines in the gray matter, there is little dispute
+that tractography can accurately delineate major white matter bundles that are
+known to exist within the core of the white matter \cite{Maier-Hein2017-vb}.
 
@@
 features. Rather than a comparative approach, this framework takes a predictive
-approach to analysis \cite{Yarkoni2017-bi}. We use a linear modeling approach,
+approach to inference \cite{Breiman2001}. We use a linear modeling approach,
 which aims to predict phenotypical variance in a group of subjects, based on a
@@
 measurement is taken, GL and SGL provide a useful tool linear model fitting in
-problems of this form.
+problems of this form. Using linear regression as the basis for analysis is
+useful for both regression tasks, in which a continuous measure (e.g., age) is
+modeled, as well as for classification tasks, where a discrete property is
+modeled (e.g., ). Moreover, use of SGL in particular helps derive informative
+properties of the human white matter, both in cases where the underlying causes
+of variance are sparsely concentrated (e.g., in one particular white matter
+tract) and in cases where biological substrates of differences between
+individuals are more widespread. This is because SGL is controlled by
+meta-parameters that set the degree to  which and that can be set empirically,
+based on the data, in a process of nested cross-validation. We demonstrate these
+properties of the algorithm in data from previously published studies
+\cite{sarica2017corticospinal, yeatman2014lifespan}.

### 2019-02-20 reports/manuscript/sections/results.tex
Add results figures and text

@@
 AFQ-Insight delivers competitive predictive performance (mean 84\% accuracy, 0.93 ROC AUC) without the need for a priori feature engineering.
-The results of the classification prediction are shown in Fig~\ref{fig:class-results}.
+The results of the classification prediction are shown in Fig~\ref{fig:class-results}, with ``ground-truth'' ALS status separated into columns, and predicted ALS status encoded by color.
+In addition to this classification performance, AFQ Insight also identifies the white matter tracts most important for the ALS classification.
+The relative importance of white matter features is captured in the $\beta$ coefficients from Eq~\eqref{eq:sgl}.
+Fig~\ref{fig:class-beta} depicts these coefficients ``unfolded'' across the brain.
+The $x$-axis organizes white matter tracts starting with left distal tracts, progressing toward the center of the brain and then outward toward the right distal tracts.
+Fig~\ref{fig:class-beta} shows that AFQ-Insight selects FA metrics in the right corticospinal tract as most important to ALS classification, confirming previous findings\cite{van2011upper, toosy2003diffusion, sarica2014tractography, sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and identifying exactly the portions of the brain that were selected \emph{a priori} in the previous study from which we collected our data\cite{sarica2017corticospinal}.
 
@@
     \centering
-    %\includegraphics[width=0.65\textwidth]{classification_results.pdf}
+    \includegraphics[width=0.65\textwidth]{classification_results.png}
     \caption{{\bf Prediction of ALS status.}
@@
 
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{classification_unfolded_beta.png}
+    \caption{{\bf Feature importance for prediction of ALS status.}
+        Classification probabilities for each subject's ALS diagnosis.
+Controls are on the left while patients are on the right.
+Predicted controls are in blue and predicted patients are in red.
+Thus, false positive are represented as red dots on the left, while false negatives are represented as blue dots on the right.
+AFQ-Insight achieves 84\% accuracy with an ROC area under the curve of 0.93.
+    }
+    \label{fig:class-beta}
+\end{figure}
+
 \begin{itemize}
@@
     \begin{itemize}
-      \item Insert figure showing sparsity pattern
       \item Insert figure showing weights as they relate to tract differences visible in the browser
@@
 In a regression setting, we attempted to accurately predict ``brain age''.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.65\textwidth]{regression_results.png}
+    \caption{{\bf Prediction of brain age.}
+    }
+    \label{fig:class-results}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{regression_unfolded_beta.png}
+    \caption{{\bf Feature importance for brain age.}
+    }
+    \label{fig:class-beta}
+\end{figure}
 
@@
     \end{itemize}
+\end{itemize}
+\begin{itemize}
   \item Failures

### 2019-11-15 reports/manuscript/sections/methods.tex
Add notebooks and requirements.txt
New figures (from OHBM poster). Lots of changes everywhere.

@@
 
-We tested AFQ-Insight in a classification setting using data from a previous study of the corticospinal tract profile in patients with amyotrophic lateral sclerosis (ALS)\cite{sarica2017corticospinal}.
-This study collected dMRI data from 24 ALS patients and 24 demographically matched healthy controls.
-In the regression setting, we used dMRI data from a previous study of properties of the white matter across the lifespan\cite{yeatman2014lifespan}, containing dMRI data from 76 subjects with ages 6-50.
-In both cases, the authors of these previous studies made their imaging data available through\ldots \adam{How?
-Through neurovault?
-Private correspondence?}.
+Two different previously-published datasets were used here:
 
-The ``raw'' dMRI data from the ALS and lifespan maturation studies were then analyzed using the Automated Fiber-Tract Quantification tractometry pipeline\cite{yeatman2012tract} with the pyAFQ package\cite{pyAFQ} \adam{Or was it the MATLAB implementation?}.
-This creates tract profiles, in which diffusion measures are quantified and averaged along twenty major fiber tracts.
-These tract profiles, along with the phenotypical data we wish to explain or predict, form the input to AFQ-Insight.
-In a domain-agnostic machine learning context, the phenotypical data comprise the target variables while the tract profiles form the feature or predictor variables.
+\begin{enumerate}
 
-AFQ-Insight reads the target and feature data from comma separated value (CSV) files conforming to the AFQ-Browser data format\cite{yeatman2018browser} \adam{Should we cite the specific page in the online documentation} and represents them internally as \lstinline{DataFrame} objects from the pandas Python library\cite{mckinney2010data}.
-We leave imputation of the target data to the user and automatically impute missing data only in the feature matrix.
-Missing interior nodes are imputed using linear interpolation.
-For missing exteriod nodes, the user may choose between linear extrapolation and constant forward(back)-fill.
-The data imputation uses only values from adjacent nodes in the same white matter tract in the same subject so there is no danger of data leakage from other subjects.
+\item Diffusion MRI data from a previous study of properties of the white matter
+across the lifespan\cite{yeatman2014lifespan}, containing dMRI data from 76
+subjects with ages 6-50. These data were measured in a GE Discovery 750 3T MRI
+scanner at the Stanford Center for Cognitive and Neurobiological Imaging. The
+Stanford University IRB approved the procedures of this study. Informed consent
+was obtained from each adult participant, and assent for participation was
+provided by by parents/guardians for children. Voxel resolution was 2x2x2 $mm^3$
+96 non-colinear directions of measurement were measured with a b=2,000 $s/mm^2$
+and 30 non-colinear directions of measurement were measured with a b=1,000
+$s/mm^2$. Data was preprocessed to correct for subject motion and the diffusion
+tensor model \cite{basser1994mr} was fit in every voxel, using a robust fit
+\cite{chang2005restore}. These data were acquired using a dual spin echo
+sequence, in which there is sufficient time for eddy currents to subside between
+the application of the gradients and the image acquisition, so no eddy current
+correction was appliced. We will refer to this dataset as WH.
 
-Lastly, like most learning algorithms, AFQ-Insight benefits from standardization of the input dataset.
-Some diffusion metrics will have naturally larger variance than others and may therefore dominate the objective function and make the sparse group lasso estimator unable to learn from the lower variance metrics.
-For example, fractional anisotropy (FA) is bounded between zero and one and could be overwhelmed by an unscaled higher-variance metric like the mean diffusivity (MD).
-To prevent this, AFQ-Insight uses the \lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}, to remove each feature's mean and scale it to unit variance.
-Scaling is performed separately within each cross-validation set's training or testing data to prevent leakage of information between the testing and training sets\cite{kaufman2012leakage}.
+\item Diffusion MRI from from a previous study of the corticospinal tract
+profile in patients with amyotrophic lateral sclerosis
+(ALS)\cite{sarica2017corticospinal}, containing data from 24 ALS patients and 24
+demographically matched healthy controls. These data were measured in a GE
+Discovery 750 3T MRI scanner at the Institute of Bioimaging and Molecular
+Physiology in Catanzaro. Informed consent was provided as approved by the
+Ethical Committee of the University ``Magna Graecia'' of Catanzaro. Voxel
+resolution was 2x2x2 $mm^3$ and 27 non-colinear directions were measured with a
+b=1,000 $s/mm^2$. Here, both motion correction and eddy current correction were
+applied before modeling the diffusioon tensor in each voxel. We will refer to
+this dataset as ALS.
+
+\end{enumerate}
+
+Data from both of these studies was processed in a similar manner, using the
+Matlab Automated Fiber Quantification toolbox (AFQ) \cite{yeatman2012tract}:
+streamlines representing fascicles of white matter nerve fibers were generated
+using a determinstic tractography algorithm that follows the prinicpal diffusion
+direction of the diffusion tensor in each voxel (STT \cite{basser2000vivo}).
+Major tracts were identified using multiple criteria: streamlines are selected
+as candidates for inclusion in a bundle of streamlines that represents a tract
+if they pass through known inclusion ROIs and do not pass through exclusion ROIs
+\cite{wakana2007reproducibility}. In addition, a probabilistic atlas is used to
+exclude streamlines which are unlikely to be part of a tract \cite{Hua2008-sh}.
+Each streamline is resampled to 100 nodes and the robust mean at each location
+is calculated by estimating the 3D covariance of the location of each node and
+excluding streamlines that are more than 5 standard deviations from the mean
+location in any node. Finally, a tract profile of tissue properties in each
+tract was created by interpolating the value of MRI maps of these tissue
+properties to the location of the nodes of the resampled streamlines designated
+to each tract. In each of 100 nodes, the values are summed across streamlines,
+weighting the contribution of each streamline by the inverse of the mahalnobis
+distance of the node from the average  of that node across streamlines. This
+means that streamlines that are more representative of the tract contribute more
+to the tract profile, relative to streamlines that are on the edge of the tract.
+
+This process creates tract profiles, in which diffusion measures are quantified
+and averaged along twenty major fiber tracts. Here, we use only the mean
+diffusivity (MD) and the fractional anisotropy (FA) of the diffusion tensor, but
+additional dMRI-based maps or maps based on other quantitative MRI measurements
+can also be used. These tract profiles, along with the phenotypical data we wish
+to explain or predict, form the input to the SGL algorithm. In a domain-agnostic
+machine learning context, the phenotypical data comprise the target variables
+while the tract profiles form the feature or predictor variables (See
+Fig~\ref{fig:group-structure}).
 
@@
 
-After scaling and imputation, the tractometry data and target phenotypical data can be organized in a linear model, $y = \mathbf{X} \cdot \beta$, where $y$ is the phenotype -- categorical, such as a clinical diagnosis, or numerical, such as the subject's age.
-The tractometry data is represented in the feature matrix $\mathbf{X}$, with rows corresponding to different subjects, and columns corresponding to diffusion measures at different nodes within each tract.
-The relationship between tractometric features and the phenotypic target is characterized by the coefficients in $\beta$.
-The feature matrix $\mathbf{X}$ has dimensions $N_s \times (N_t \cdot N_n \cdot N_m)$, where $N_s$ is the number of subjects, $N_t$ is the number of white matter tracts, $N_n$ is the number of nodes in each tract, and $N_m$ is the number of diffusion metrics calculated at each node.
-Typically, $N_t = 20$, $N_n = 100$, and $2 \le N_m \le 8$, resulting in $\mathcal{O}(10^4)$ features.
-Conversely, most dMRI studies have $\mathcal{O}(10^2)$ participants, yielding a feature matrix that is wide and short.
-The high dimensionality of this data requires regularization to avoid overfitting and generate interpretable results.
+Before fitting a model to the data, imputation and standardization are
+performed. Missing node values (e.g., in cases where AFQ designates a node as
+not-a-number) are imputed via linear interpolation. Care is taken not to
+interpolate across the boundaries between different tracts. Some diffusion
+metrics will have naturally larger variance than others and may therefore
+dominate the objective function and make the SGL estimator unable to learn from
+the lower variance metrics. For example, fractional anisotropy (FA) is bounded
+between zero and one and could be overwhelmed by an unscaled higher-variance
+metric like the mean diffusivity (MD). To prevent this, we use the
+\lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}, to remove each
+feature's mean and scale it to unit variance. Scaling is performed separately
+within each cross-validation set's training or testing data to prevent leakage
+of information between the testing and training sets\cite{kaufman2012leakage}.
 
-In addition to regularizing the coefficients in $\beta$, we also wish to capitalize upon our knowledge of the group structure of the tract profile features in $\mathbf{X}$.
-The tract-metric combinations form a natural grouping.
-For example, we expect that MD features within the left arcuate fasciculus will be correlated.
-Likewise for FA values within the right corticospinal tract (CST) and so on.
-This group structure is represented in Fig~\ref{fig:group-structure}, which depicts the linear model $y = \mathbf{X} \cdot \beta$.
-The target vector $y$ is sorted into patients (p) and controls (c), while the different colors encode the group structure of the feature matrix $\mathbf{X}$, with one group for each unique tract-metric combination.
+After scaling and imputation, the tractometry data and target phenotypical data
+can be organized in a linear model, $y = \mathbf{X} \cdot \beta$, where $y$ is
+the phenotype -- categorical, such as a clinical diagnosis, or numerical, such
+as the subject's age. The tractometry data is represented in the feature matrix
+$\mathbf{X}$, with rows corresponding to different subjects, and columns
+corresponding to diffusion measures at different nodes within each tract. The
+relationship between tractometric features and the phenotypic target is
+characterized by the coefficients in $\beta$. The feature matrix $\mathbf{X}$
+has dimensions $N_s \times (N_t \cdot N_n \cdot N_m)$, where $N_s$ is the number
+of subjects, $N_t$ is the number of white matter tracts, $N_n$ is the number of
+nodes in each tract, and $N_m$ is the number of diffusion metrics calculated at
+each node. Typically, $N_t = 20$, $N_n = 100$, and $2 \le N_m \le 8$, resulting
+in $\mathcal{O}(10^4)$ features. Conversely, most dMRI studies have
+$\mathcal{O}(10^2)$ participants, yielding a feature matrix that is wide and
+short. The high dimensionality of this data requires regularization to avoid
+overfitting and generate interpretable results.
 
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.65\textwidth]{dMRI_group_structure.pdf}
-    \caption{{\bf dMRI group structure.}
-        The phenotypical target data and tractometric features can be organized into a linear model, $y = \mathbf{X} \cdot \beta$.
-Here, the target array $y$ is suggestively sorted into patients (p) and controls (c), while the feature matrix $\mathbf{X}$ is color-coded to reveal a natural group structure.
-In this example, the left (orange) group contains $k$ features from the inferior fronto-occipital fascicle (IFOF), the middle (green) group contains $k$ features from the corpus callosum, and the right (blue) group contains $k$ features from the uncinate.
-The coefficients in $\beta$ follow the same natural grouping.
-Fascicle images taken with permission from Ref~\cite{yeatman2012tract}.
-    }
-    \label{fig:group-structure}
-\end{figure}
-
-Thus, we seek a regularization approach that will fit a linear model with anatomically-grouped covariates, where we expect to observe sparse coefficients at both the group level and the within-group level.
-The sparse group lasso (SGL) is a penalized regression technique that satisfies exactly these criteria\cite{simon2013sparse}.
-It solves for a coefficient vector $\widehat{\beta}$ that satisfies
+In addition to regularizing the coefficients in $\beta$, we also wish to
+capitalize on our knowledge of the group structure of the tract profile features
+in $\mathbf{X}$. The tract-metric combinations form a natural grouping. For
+example, we expect that MD features within the left arcuate fasciculus will be
+correlated. Likewise for FA values within the right corticospinal tract (CST)
+and so on. This group structure is represented in Fig~\ref{fig:group-structure},
+which depicts the linear model $y = \mathbf{X} \cdot \beta$. Thus, we seek a
+regularization approach that will fit a linear model with anatomically-grouped
+covariates, where we expect to observe sparse coefficients at both the group
+level and the within-group level. The sparse group lasso (SGL) is a penalized
+regression technique that satisfies exactly these
+criteria\cite{simon2013sparse}. It solves for a coefficient vector
+$\widehat{\beta}$ that satisfies
 \begin{equation}
@@
 \end{equation}
-where $m$ is the number of anatomical groups, $\mathbf{X}^{(\ell)}$ is the submatrix of $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the coefficient vector for group $\ell$ and $p_\ell$ is the length of $\beta^{(\ell)}$.
-The first term is the mean square error loss, $L_{mse}$, as in the standard linear regression framework.
-The second and third terms encourage groupwise sparsity and overall sparsity, respectively.
-If $\lambda_1 = 0$ and $\lambda_2 = 1$, the SGL reduces to the traditional lasso\cite{tibshirani1996regression}.
-Conversely, if $\lambda_1 = 1$ and $\lambda_2 = 0$, the SGL reduces to the group lasso\cite{yuan2006model}.
 
-When the phenotypical target variable are categorical, as in the case of predicting a clinical diagnosis, the SGL is readily adapted to logistic regression, where the probability of a target variable belonging to an arbitrary defined ``true'' class is the logistic function of the result of the linear model,
+where $m$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
+$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the coefficient
+vector for group $\ell$ and $p_\ell$ is the length of $\beta^{(\ell)}$. The
+first term is the mean square error loss, $L_{mse}$, as in the standard linear
+regression framework. The second and third terms encourage groupwise sparsity
+and overall sparsity, respectively. If $\lambda_1 = 0$ and $\lambda_2 = 1$, the
+SGL reduces to the traditional lasso\cite{tibshirani1996regression}. Conversely,
+if $\lambda_1 = 1$ and $\lambda_2 = 0$, the SGL reduces to the group
+lasso\cite{yuan2006model}.
+
+When the phenotypical target variable are categorical, as in the case of
+predicting a clinical diagnosis, the SGL is readily adapted to logistic
+regression, where the probability of a target variable belonging to an arbitrary
+defined ``true'' class is the logistic function of the result of the linear
+model,
+
 \begin{equation}
@@
 \end{equation}
-or equivalently, the mean squared error loss function in Eq~\eqref{eq:sgl} is replaced with the cross-entropy loss, which for binary classification is the negative log likelihood of the SGL classifier giving the ``true'' label:
+
+or equivalently, the mean squared error loss function in Eq~\eqref{eq:sgl} is
+replaced with the cross-entropy loss, which for binary classification is the
+negative log likelihood of the SGL classifier giving the ``true'' label:
+
 \begin{equation}
@@
 \end{equation}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.65\textwidth]{dMRI_group_structure.png}
+    \caption{{\bf dMRI group structure.}
+        The phenotypical target data and tractometric features can be organized
+    into a linear model, $y = \mathbf{X} \cdot \beta$. The feature matrix
+    $\mathbf{X}$ is color-coded to reveal a natural group structure: the left
+    (orange) group contains $k$ features from the inferior fronto-occipital
+    fascicle (IFOF), the middle (green) group contains $k$ features from the
+    corpus callosum, and the right (blue) group contains $k$ features from the
+    uncinate. The coefficients in $\beta$ follow the same natural grouping.
+    Fascicle images taken from Ref~\cite{yeatman2012tract}.}
+    \label{fig:group-structure}
+\end{figure}
+
+\subsection*{Metaparameter optimization}
+
+To select the values of the metaparameters $\lambda$
 
@@
 \end{itemize}
+
+\subsection*{Software implementation}
+
+The full software implementation of the SGL approach presented here is available
+in a Python software package called AFQ-Insight, which is developed publicly in
+\url{https://github.com/richford/afq-insight}. The version of the code used to
+produce the results herein is also available in XXX Zenodo DOI. AFQ-Insight
+reads the target and feature data that has been processed by AFQ from comma
+separated value (CSV) files conforming to the AFQ-Browser data
+format\cite{yeatman2018browser} and represents them internally as
+\lstinline{DataFrame} objects from the pandas Python
+library\cite{mckinney2010data}. The software provides different options for
+imputing missing data in the feature matrix. Missing interior nodes are imputed
+using linear interpolation. For missing exterior nodes, the user may choose
+between linear extrapolation and constant forward(back)-fill. Imputation uses
+only values from adjacent nodes in the same white matter tract in the same
+subject so there is no danger of data leakage from other subjects.

### 2019-11-15 reports/manuscript/sections/results.tex
Add style file
New figures (from OHBM poster). Lots of changes everywhere.

@@
 
-Using data from a previous study of the corticospinal tract profile and ALS\cite{sarica2017corticospinal}, we tested the performance of AFQ-Insight in a classification setting.
-The previous study predicted ALS status with a mean accuracy of 80\% using a random forest algorithm based on a priori selection of features within the corticospinal tract.
-AFQ-Insight delivers competitive predictive performance (mean 84\% accuracy, 0.93 ROC AUC) without the need for a priori feature engineering.
-The results of the classification prediction are shown in Fig~\ref{fig:class-results}, with ``ground-truth'' ALS status separated into columns, and predicted ALS status encoded by color.
-In addition to this classification performance, AFQ Insight also identifies the white matter tracts most important for the ALS classification.
-The relative importance of white matter features is captured in the $\beta$ coefficients from Eq~\eqref{eq:sgl}.
-Fig~\ref{fig:class-beta} depicts these coefficients ``unfolded'' across the brain.
-The $x$-axis organizes white matter tracts starting with left distal tracts, progressing toward the center of the brain and then outward toward the right distal tracts.
-Fig~\ref{fig:class-beta} shows that AFQ-Insight selects FA metrics in the right corticospinal tract as most important to ALS classification, confirming previous findings\cite{van2011upper, toosy2003diffusion, sarica2014tractography, sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and identifying exactly the portions of the brain that were selected \emph{a priori} in the previous study from which we collected our data\cite{sarica2017corticospinal}.
+The WH dataset used for continuous regression contains data from 76 healthy
+subjects, ranging between 6 years and 50 years of age
+\cite{yeatman2014lifespan}. SGL fit to tractometry-extracted features in these
+subjects accurately predicts the age of the subjects. The model reaches a mean
+absolute error of 3.6 years (Figure \ref{fig:regress-results}), which is lower
+than the results of a recent study that predicted age in a large sample, based
+on TBSS-extracted diffusion features \cite{Richard2018-ux}. The model weights
+in this case are distributed over many different tracts and dMRI tissue
+properties (Figure \ref{}) This demonstrates that SGL is not coerced to produce overly sparse
+results when a more accurate model requires a dense selection of features.
 
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{classification_results.png}
+    \includegraphics[width=0.65\textwidth]{regression_residuals.png}
+    \caption{{\bf Prediction of brain age.}
+    }
+    \label{fig:regress-results}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{regression_beta_annotated.pdf}
+    \caption{{\bf Feature importance for brain age.}
+    }
+    \label{fig:regress-beta}
+\end{figure}
+
+\begin{itemize}
+  \item Regression
+    \begin{itemize}
+      \item Lifespan maturation age regression
+      \item Insert figure showing sparsity pattern
+      \item Insert figure showing weights as they relate to tract differences visible in the browser
+    \end{itemize}
+\end{itemize}
+\begin{itemize}
+  \item Failures
+    \begin{itemize}
+      \item Hopefully, the failures are common to both regression
+        and classification so we can include them here in there own
+        subsection.
+      \item Insert figure demonstrating failure cases
+    \end{itemize}
+\end{itemize}
+
+Using data from a previous study of the corticospinal tract profile and
+ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
+classification setting. The previous study predicted ALS status with a mean
+accuracy of 80\% using a random forest algorithm based on a priori selection of
+features within the corticospinal tract. AFQ-Insight delivers competitive
+predictive performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC
+AUC) without the need for a priori feature engineering. The results of the
+classification prediction are shown in Fig~\ref{fig:class-results}, with
+``ground-truth'' ALS status separated into columns, and predicted ALS status
+encoded by color. In addition to this classification performance, AFQ Insight
+also identifies the white matter tracts most important for the ALS
+classification. The relative importance of white matter features is captured in
+the $\beta$ coefficients from Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-beta}
+depicts these coefficients ``unfolded'' across the brain. The $x$-axis organizes
+white matter tracts starting with left distal tracts, progressing toward the
+center of the brain and then outward toward the right distal tracts.
+Fig~\ref{fig:class-beta} shows that AFQ-Insight selects FA metrics in the right
+corticospinal tract as most important to ALS classification, confirming previous
+findings\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
+sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
+ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
+abe2010voxel} and identifying exactly the portions of the brain that were
+selected \emph{a priori} in the previous study from which we collected our
+data\cite{sarica2017corticospinal}.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.65\textwidth]{classification_probs.png}
     \caption{{\bf Prediction of ALS status.}
@@
 \end{itemize}
-
-In a regression setting, we attempted to accurately predict ``brain age''.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.65\textwidth]{regression_results.png}
-    \caption{{\bf Prediction of brain age.}
-    }
-    \label{fig:class-results}
-\end{figure}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{regression_unfolded_beta.png}
-    \caption{{\bf Feature importance for brain age.}
-    }
-    \label{fig:class-beta}
-\end{figure}
-
-\begin{itemize}
-  \item Regression
-    \begin{itemize}
-      \item Lifespan maturation age regression
-      \item Insert figure showing sparsity pattern
-      \item Insert figure showing weights as they relate to tract differences visible in the browser
-    \end{itemize}
-\end{itemize}
-\begin{itemize}
-  \item Failures
-    \begin{itemize}
-      \item Hopefully, the failures are common to both regression
-        and classification so we can include them here in there own
-        subsection.
-      \item Insert figure demonstrating failure cases
-    \end{itemize}
-\end{itemize}

### 2019-11-16 reports/manuscript/sections/results.tex
Inserting all the figures into the paper.

@@
 
+\subsection*{Regression for age prediction}
 The WH dataset used for continuous regression contains data from 76 healthy
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{regression_residuals.png}
+    \includegraphics[width=1\textwidth]{regression_residuals.png}
     \caption{{\bf Prediction of brain age.}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{regression_beta_annotated.pdf}
+    \includegraphics[width=0.5\textwidth]{regression_beta_annotated.pdf}
     \caption{{\bf Feature importance for brain age.}
@@
     \label{fig:regress-beta}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\textwidth]{regression_tract_profiles.pdf}
+    \caption{{\bf Coefficients in context}
+    It makes sense
+    }
+    \label{fig:regress-profiles}
 \end{figure}
@@
 
+\subsection*{Classification for ALS detection}
+
 Using data from a previous study of the corticospinal tract profile and
@@
 accuracy of 80\% using a random forest algorithm based on a priori selection of
-features within the corticospinal tract. AFQ-Insight delivers competitive
-predictive performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC
-AUC) without the need for a priori feature engineering. The results of the
-classification prediction are shown in Fig~\ref{fig:class-results}, with
-``ground-truth'' ALS status separated into columns, and predicted ALS status
-encoded by color. In addition to this classification performance, AFQ Insight
-also identifies the white matter tracts most important for the ALS
-classification. The relative importance of white matter features is captured in
-the $\beta$ coefficients from Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-beta}
-depicts these coefficients ``unfolded'' across the brain. The $x$-axis organizes
-white matter tracts starting with left distal tracts, progressing toward the
-center of the brain and then outward toward the right distal tracts.
-Fig~\ref{fig:class-beta} shows that AFQ-Insight selects FA metrics in the right
+features within the corticospinal tract. SGL delivers competitive predictive
+performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC AUC) without
+the need for a priori feature engineering. The results of the classification
+prediction are shown in Fig~\ref{fig:class-results}, with ``ground-truth'' ALS
+status separated into columns, and predicted ALS status encoded by color. In
+addition to this classification performance, SGL also identifies the white
+matter tracts most important for ALS classification. The relative importance of
+white matter features is captured in the $\beta$ coefficients from
+Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-beta} depicts these coefficients across
+the brain, laid out on a skeleton of the major tracts. We find that SGL selects
+FA metrics in the corticospinal tract and particualrly in the right
 corticospinal tract as most important to ALS classification, confirming previous
@@
     \caption{{\bf Prediction of ALS status.}
-        Classification probabilities for each subject's ALS diagnosis.
-Controls are on the left while patients are on the right.
-Predicted controls are in blue and predicted patients are in red.
-Thus, false positive are represented as red dots on the left, while false negatives are represented as blue dots on the right.
-AFQ-Insight achieves 84\% accuracy with an ROC area under the curve of 0.93.
-    }
+        Classification probabilities for each subject's ALS diagnosis. Controls
+        are on the left while patients are on the right. Predicted controls are in blue
+        and predicted patients are in red. Thus, false positive are represented as red
+        dots on the left, while false negatives are represented as blue dots on the
+        right. The SGL algorithm achieves 93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006
+        ROC AUC}
     \label{fig:class-results}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{classification_unfolded_beta.png}
+    \includegraphics[width=0.95\textwidth]{classification_beta_bupu.png}
     \caption{{\bf Feature importance for prediction of ALS status.}
-        Classification probabilities for each subject's ALS diagnosis.
-Controls are on the left while patients are on the right.
-Predicted controls are in blue and predicted patients are in red.
-Thus, false positive are represented as red dots on the left, while false negatives are represented as blue dots on the right.
-AFQ-Insight achieves 84\% accuracy with an ROC area under the curve of 0.93.
+        SGL coefficients are presented on a skeleton of the major tracts. The
+    brain is oriented with the right hemisphere to our left and anterior out of
+    the page. As expected large negative coefficients are in the FA of the
+    corticospinal tract (and particularly right CST, here to the left)}
+    \label{fig:class-beta}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
+    \caption{{\bf Coefficients with FA tract profiles}
        }
-    \label{fig:class-beta}
+    \label{fig:class-profiles}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
+    \caption{{\bf Mis-classifications}
+       They make sense}
+    \label{fig:class-errors}
 \end{figure}

### 2019-11-16 reports/manuscript/abstract.tex
Add methods section to manuscript

@@
-\begin{abstract}
+\section*{Abstract}
 
-\adam{This is a copy of the abstract submitted for SfN 2018}
-
-The white matter contains long-range connections between different brain regions.
-Tractometry uses diffusion-weighted magnetic resonance imaging (dMRI) data to quantify tissue properties along the trajectories of these connections in the human brain in vivo\cite{yeatman2012tract}.
-In previous work, the results of tractometry were usually analyzed using mass univariate approaches: group comparisons or regression models computed separately for each point along every one of the tracts.
-Alternatively, tissue properties such as fractional anisotropy (FA) and mean diffusivity (MD) were computed for a specific tract of interest based on an a priori hypothesis.
-In the present work, we developed a method based on the sparse group lasso\cite{simon2013sparse} that takes into account all of the tissue properties measured in all of the tracts, and selects informative features by enforcing sparsity, both at the level of individual tracts and tissue properties, but also across the entire set of tracts and all of the measured tissue properties.
-The sparsity penalties for each of these constraints is identified using a nested cross-validation scheme.
-Using data from a previous study that measured dMRI in patients with amyotrophic lateral sclerosis (ALS) and matched controls\cite{sarica2017corticospinal}, we demonstrate that this method is accurate, exceeding the previous results, that were based on a priori feature selection, in classifying patients and controls, with ~84\% accuracy, an area under the receiver operating characteristic curve of 0.93, and an average precision of 0.95.
-Moreover, our method automatically identifies as important for this classification the parts of the white matter known to be affected by ALS within the corticospinal tract.
-In a regression setting, data from another previous study\cite{yeatman2014lifespan} can be used to accurately predict ``brain age''.
-Thus, this multivariate analysis approach both (a) achieves high cross-validated accuracy for precision medicine applications of dMRI data and (b) identifies relevant features of brain anatomy to further our neuroscientific understanding of clinical disorders.
-
-\end{abstract}
+The white matter contains long-range connections between different brain
+regions. Tractometry uses diffusion-weighted magnetic resonance imaging (dMRI)
+data to quantify tissue properties along the trajectories of these connections
+in the human brain in vivo\cite{yeatman2012tract}. In previous work, the results
+of tractometry were usually analyzed using mass univariate approaches: group
+comparisons or regression models computed separately for each point along every
+one of the tracts.  Alternatively, tissue properties such as fractional
+anisotropy (FA) and mean diffusivity (MD) were computed for a specific tract of
+interest based on an a priori hypothesis. In the present work, we developed a
+method based on the sparse group lasso\cite{simon2013sparse} that takes into
+account tissue properties measured in all of the tracts, and selects informative
+features by enforcing sparsity, both at the level of individual tracts and
+tissue properties, but also across the entire set of tracts and all of the
+measured tissue properties. The sparsity penalties for each of these constraints
+is identified using a nested cross-validation scheme. Using data from a previous
+study that measured dMRI in patients with amyotrophic lateral sclerosis (ALS)
+and matched controls\cite{sarica2017corticospinal}, we demonstrate that this
+method is accurate, exceeding the previous results, that were based on a priori
+feature selection, in classifying patients and controls, with ~84\% accuracy, an
+area under the receiver operating characteristic curve of 0.93, and an average
+precision of 0.95. Moreover, our method automatically identifies as important
+for this classification the parts of the white matter known to be affected by
+ALS within the corticospinal tract. In a regression setting, data from another
+previous study\cite{yeatman2014lifespan} can be used to accurately predict
+``brain age''. Thus, this multivariate analysis approach both (a) achieves high
+cross-validated accuracy for precision medicine applications of dMRI data and
+(b) identifies relevant features of brain anatomy to further our neuroscientific
+understanding of clinical disorders.

### 2019-11-16 reports/manuscript/paper.tex
First pass of several sections of the Introduction.
Haven't quite gotten to the point where I describe what/why we're doing here.

But it's a start.

@@
 {\Large
-\textbf\newline{AFQ-Insight: multidimenstional analysis and detection of informative features in diffusion MRI measurements of human white matter} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Multidimensional analysis and detection of informative features in diffusion MRI measurements of human white matter} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \\
-\textbf{2} Department of Speech and Hearing Sciences, University of Washington, Seattle, WA, 98105, USA
+\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, CA, 94305, USA
 \\

### 2019-11-16 reports/manuscript/sections/conclusion.tex
Add methods section to manuscript

@@
-\section{Conclusion}
+\section*{Conclusion}
+
+We present here a novel method for analysis of dMRI tractometry data. This
+method relies on the Sparse Group Lasso \cite{simon2013sparse} to provide both
+acurate prediction of the phenotypic properties of individual subjects based on
+their dMRI data, but also provides interpretable results by identifying the
+features that are important across subjects to make these predictions. The
+method is broadly applicable: it performs well in predicting both continuous
+variables, such as biological age, as well as discrete variable, such as whether
+a person is a patient or a healthy control. In both of these cases, SGL
+out-performs previous algorithms that have been developed for these tasks. In
+addition, the nested cross-validation approach that we have developed tunes the
+degree of sparseness required by the algorithm, such that both very local
+phenomena, as well as widely distributed phenomena are accurately captured.
+
+Specifically, we demonstrated that the algorithm correctly detects the fact that
+ ALS, which is a disease of lower motor neurons, is localized to the
+ cortico-spinal tract. This recapitulates the results of previous analysis of
+ these same data, using a targetted ROI-based approach. In contrast, in analysis
+ of biological age, the coefficients identified by the algorithm are very widely
+ distributed.
+
+Taken together, these results demonstrate the promise of a group regularized
+regression approach. Even at the scale of dozens of subjects, the results
+provided by SGL are both accurate and interpretable. We expect that additional
+data will improve the performance of these algorithms. Neuroscience has entered
+an era in which large consortium efforts are putting together large datasets
+that can be analyzed using this approach. Future work will apply this method to
+these datasets. For example, to the Human Connectome Project dataset
+\cite{VanEssen2012}
+
+These results also motivate extensions of the method using more sophisticated
+cost functions. For example, the fused sparse group lasso (FSGL)
+\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
+in the variation of diffusion metrics along the tracts. As brain measurements
+include additional structure (for example, bilateral symmetry), future work
+could also incorporate overlapping group membership for each entry in the tract
+profiles. For example, a measurement could come from the corpus callosum, but
+also from the right hemipshere. This would also require extending the cost
+function used here to incorporate these constraints.
+
+The method is packaged as open-source software called AFQ-Insight that is openly
+available. The sofware integrates within a broader automated fiber
+quantification software ecosystem: AFQ \cite{yeatman2012tract}, which extracts
+tractometry data from raw dMRI, as well as AFQ-Browser, which visualizes
+tractometry data and facilitates sharing of the results of dMRI studies
+\cite{yeatman2018browser}.
 

### 2019-11-16 reports/manuscript/sections/introduction.tex

@@
 have proven useful in characterizing individual differences or differences
-between populations \ariel{citation needed}.
+between populations \cite{}.
 
@@
 features. Rather than a comparative approach, this framework takes a predictive
-approach to inference \cite{Breiman2001}. We use a linear modeling approach,
+approach to analysis \cite{Yarkoni2017-bi}. We use a linear modeling approach,
 which aims to predict phenotypical variance in a group of subjects, based on a

### 2019-11-16 reports/manuscript/sections/results.tex

@@
 \subsection*{Regression for age prediction}
+
 The WH dataset used for continuous regression contains data from 76 healthy
@@
 than the results of a recent study that predicted age in a large sample, based
-on TBSS-extracted diffusion features \cite{Richard2018-ux}. The model weights
-in this case are distributed over many different tracts and dMRI tissue
-properties (Figure \ref{}) This demonstrates that SGL is not coerced to produce overly sparse
-results when a more accurate model requires a dense selection of features.
+on TBSS-extracted diffusion features \cite{Richard2018-ux}. The model weights in
+this case are distributed over many different tracts and dMRI tissue properties
+(Figure \ref{fig:regress-beta}) This demonstrates that SGL is not coerced to
+produce overly sparse results when a more accurate model requires a dense
+selection of features.
 

### 2019-11-22 reports/manuscript/sections/conclusion.tex
More edits -- especially in methods, and a new section in conclusions.

@@
 
+SGL has many other potential applications in neuroscience, because of the
+hierarchical and grouped nature of many of the data -- that are collected in
+multiple sample points within anatomically-defined areas. For example, this
+method may be useful to understand the relationship between fMRI recordings and
+behavior, where activity in each voxel may co-vary with voxels within the same
+anatomical region and form features and groups of features. Similarly,
+large-scale multi-electrode recordings of neural activity in awake behaving
+animals are becoming increasingly feasible \cite{steinmetz2018distributed,
+Jun2017-gv} and these recordings can form features (neurons) and groups (neurons
+within an anatomical region). More ambitiously perhaps, this approach may be
+used to understand the role of correlations in so-called resting-state fMRI
+time-series and behavior, where pairwise correlations between voxels in
+different anatomical regions are features in the matrix and features may be
+grouped by pairs of anatomical regions. Given the large number of voxels in the
+surface of the gray matter, and given that correlations increase the number of
+features by a factor of $n^2$ this would be a challenging problem to solve using
+SGL.
+
 \begin{itemize}

### 2019-11-22 reports/manuscript/sections/methods.tex

@@
 \section*{Materials and methods}
+
+TODO:
+
+\begin{itemize}
+  \item Computational implementation
+    \begin{itemize}
+      \item Insert Figure for pipeline
+      \item Proximal gradient methods
+      \item Meta-parameter optimization
+      \item Cross-validation scheme
+        \begin{itemize}
+          \item Insert Figure for cross-validation scheme
+        \end{itemize}
+    \end{itemize}
+\end{itemize}
 
@@
 After scaling and imputation, the tractometry data and target phenotypical data
-can be organized in a linear model, $y = \mathbf{X} \cdot \beta$, where $y$ is
-the phenotype -- categorical, such as a clinical diagnosis, or numerical, such
-as the subject's age. The tractometry data is represented in the feature matrix
-$\mathbf{X}$, with rows corresponding to different subjects, and columns
-corresponding to diffusion measures at different nodes within each tract. The
-relationship between tractometric features and the phenotypic target is
-characterized by the coefficients in $\beta$. The feature matrix $\mathbf{X}$
-has dimensions $N_s \times (N_t \cdot N_n \cdot N_m)$, where $N_s$ is the number
-of subjects, $N_t$ is the number of white matter tracts, $N_n$ is the number of
-nodes in each tract, and $N_m$ is the number of diffusion metrics calculated at
-each node. Typically, $N_t = 20$, $N_n = 100$, and $2 \le N_m \le 8$, resulting
-in $\mathcal{O}(10^4)$ features. Conversely, most dMRI studies have
-$\mathcal{O}(10^2)$ participants, yielding a feature matrix that is wide and
-short. The high dimensionality of this data requires regularization to avoid
-overfitting and generate interpretable results.
+can be organized in a linear model:
 
-In addition to regularizing the coefficients in $\beta$, we also wish to
-capitalize on our knowledge of the group structure of the tract profile features
-in $\mathbf{X}$. The tract-metric combinations form a natural grouping. For
-example, we expect that MD features within the left arcuate fasciculus will be
-correlated. Likewise for FA values within the right corticospinal tract (CST)
-and so on. This group structure is represented in Fig~\ref{fig:group-structure},
-which depicts the linear model $y = \mathbf{X} \cdot \beta$. Thus, we seek a
-regularization approach that will fit a linear model with anatomically-grouped
-covariates, where we expect to observe sparse coefficients at both the group
-level and the within-group level. The sparse group lasso (SGL) is a penalized
-regression technique that satisfies exactly these
+\begin{equation}
+y = \mathbf{X} \cdot \beta,
+\label{eq:lm}
+\end{equation}
+
+where $y$ is the phenotype -- categorical, such as a clinical diagnosis, or
+continuous numerical, such as the subject's age. The tractometry data is
+represented in the feature matrix $\mathbf{X}$, with rows corresponding to
+different subjects, and columns corresponding to diffusion measures at different
+nodes within each tract. The relationship between tractometric features and the
+phenotypic target is characterized by the coefficients in $\beta$. In general,
+the feature matrix $\mathbf{X}$ has dimensions $S \times (T \cdot N \cdot M)$,
+where $S$ is the number of subjects, $T$ is the number of white matter tracts,
+$N$ is the number of nodes in each tract, and $M$ is the number of diffusion
+metrics calculated at each node. Typically, $T = 20$, $N = 100$, and $2 \le M
+\le 8$, resulting in $\sim 4,000 - 16,000$  features. Conversely, many dMRI
+studies have between a few dozen and a few hundred subjects, yielding a feature
+matrix that is wide and short. Even in cases where more than a thousand subjects
+are measured (e.g., in the Human Connectome Project, where 1,200 subjects were
+measured \cite{VanEssen2012}), the problem is ill-posed: The high dimensionality
+of this data requires regularization to avoid overfitting and generate
+interpretable results.
+
+Here, we propose that in addition to regularizing the coefficients in $\beta$,
+we can also capitalize on our knowledge of the group structure of the tract
+profile features in $\mathbf{X}$. The tract-metric combinations form a natural
+grouping. For example, we expect that MD features within the left arcuate
+fasciculus to co-vary across individuals. Likewise for FA values within the
+right corticospinal tract (CST) and so on. This group structure is represented
+in Fig~\ref{fig:group-structure}, which depicts the linear model $y = \mathbf{X}
+\cdot \beta$. Thus, we seek a regularization approach that will fit a linear
+model with anatomically-grouped covariates, where we expect to observe both
+groupwise sparsity: the number of groups (tract/metric combinations) with at
+least one non-zero coefficients as well as within-group sparsity: the number of
+non-zero coefficients within each non-zero groups. The sparse group lasso (SGL)
+is a penalized regression technique that satisfies exactly these
 criteria\cite{simon2013sparse}. It solves for a coefficient vector
@@
     \widehat{\beta} = \min_\beta \frac{1}{2}
-    \norm*{y - \displaystyle \sum_{\ell = 1}^{m} \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
-    + \lambda_1 \displaystyle \sum_{\ell = 1}^{m} \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
+    \norm*{y - \displaystyle \sum_{\ell = 1}^{G} \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
+    + \lambda_1 \displaystyle \sum_{\ell = 1}^{G} \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
     + \lambda_2 \norm*{\beta}_1,
@@
 
-where $m$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
+where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
 $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the coefficient
-vector for group $\ell$ and $p_\ell$ is the length of $\beta^{(\ell)}$. The
+vector for group $\ell$ and $p_\ell$ is the length of $\beta^{(\ell)}$. In the
+tractomtetry setting, $G = T \cdot M$ and $\forall \ell: p_\ell = 100$. The
 first term is the mean square error loss, $L_{mse}$, as in the standard linear
@@
 
-When the phenotypical target variable are categorical, as in the case of
-predicting a clinical diagnosis, the SGL is readily adapted to logistic
-regression, where the probability of a target variable belonging to an arbitrary
-defined ``true'' class is the logistic function of the result of the linear
-model,
+\subsection*{Implementation, cross-validation and metaparameter optimization}
+
+For given values of $\lambda_1$ and $\lambda_2$, the cost function in equation
+\ref{eq:sgl} can be optimized using proximal gradient descent methods
+\cite{parikh2014proximal} here implemented as a custom proximal operator that is
+then optimized using the COPT library \cite{fabian_pedregosa_2018_1473584}. To
+find the values of the metaparameters $\lambda_1$ and $\lambda_2$, we used a
+hyperoptimization procedure, implemented using the hyperopt software
+\cite{Bergstra_2015}. XXX We need more details here.
+
+To objectively evaluate the model and guard against over-fitting, we used
+cross-validation. XXX More here.
+
+\subsubsection*{Incorporating transformations on $y$}
+
+Often, the target variable $y$ is not in the domain in which the linear model
+can be best fit to it. Equation \ref{eq:lm} can be slightly modified as:
+
+\begin{equation}
+y = f^-1(\mathbf{X} \cdot \beta),
+\label{eq:lm}
+\end{equation}
+
+where the transformation function $f^-1$ characterizes the transform applied to
+the data before fitting the linear coefficients. For example, an often-used
+transform is the logarithmic transform:
+
+\begin{equation}
+f(y) = log_n(y)
+\label{eq:log_nonlinearity}
+\end{equation}
+
+In this case, the model is parametrized by one additional fit parameter, $n$.
+
+\subsubsection*{Categorical $y$}
+When the phenotypical target variable is categorical, as in the case of
+explaining or predicting the presence of a clinical diagnosis, the SGL is
+readily adapted to logistic regression, where the probability of a target
+variable belonging to an arbitrary defined ``true'' class is the logistic
+function of the result of the linear model,
 
@@
     uncinate. The coefficients in $\beta$ follow the same natural grouping.
-    Fascicle images taken from Ref~\cite{yeatman2012tract}.}
+    Fascicle image reproduced with permission from Ref~\cite{yeatman2012tract}
+    Figure 1.}
     \label{fig:group-structure}
 \end{figure}
-
-\subsection*{Metaparameter optimization}
-
-To select the values of the metaparameters $\lambda$
-
-\begin{itemize}
-  \item Computational implementation
-    \begin{itemize}
-      \item Insert Figure for pipeline
-      \item Proximal gradient methods
-      \item Meta-parameter optimization
-      \item Cross-validation scheme
-        \begin{itemize}
-          \item Insert Figure for cross-validation scheme
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
 

### 2019-11-22 reports/manuscript/sections/methods.tex
Fixes up various merge issues from the rebase.

@@
 \cite{parikh2014proximal} here implemented as a custom proximal operator that is
-then optimized using the COPT library \cite{fabian_pedregosa_2018_1473584}. To
+then optimized using the COPT library \ariel{citation needed here}. To
 find the values of the metaparameters $\lambda_1$ and $\lambda_2$, we used a

### 2019-11-22 reports/manuscript/sections/introduction.tex

--- 2019-02-11 reports/manuscript/sections/introduction.tex
@@
 different available implementations of this overall idea, the principles are
-similar \cite{yeatman2012, Yendiki2011-ay, Wassermann2016-iv, ODonnell2009-uu}:
+similar \cite{yeatman2012tract, Yendiki2011-ay, Wassermann2016-iv, ODonnell2009-uu}:
 tractometry begins by delineating the parts of the white matter that belong to
@@
 retaining the individual samples along the length of each fiber
-\cite{yeatman2012, colby2012, ODonnell2009-uu}. However, while this retains
+\cite{yeatman2012tract, colby2012, ODonnell2009-uu}. However, while this retains
 important information about each individual's white matter, it also presents
@@
 features. Rather than a comparative approach, this framework takes a predictive
-approach to inference \cite{Breiman2001}. We use a linear modeling approach,
+approach to inference \cite{Breiman2001-uz}. We use a linear modeling approach,
 which aims to predict phenotypical variance in a group of subjects, based on a

### 2019-11-25 reports/manuscript/sections.tex
Add methods section to manuscript

@@
 
-\section{Acknowledgements}
+\section*{Acknowledgments}
 
-Here are some amazing acknowledgements.
+This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
+National Institutes for Mental Health and by a grant from the Gordon \& Betty
+Moore Foundation and the Alfred P. Sloan Foundation to the University of
+Washington eScience Institute Data Science Environment. We would like to thank
+Scott Murray for a useful discussion of the SGL method.

### 2019-11-25 reports/manuscript/sections/results.tex

@@
 subjects, ranging between 6 years and 50 years of age
-\cite{yeatman2014lifespan}. SGL fit to tractometry-extracted features in these
-subjects accurately predicts the age of the subjects. The model reaches a mean
-absolute error of 3.6 years (Figure \ref{fig:regress-results}), which is lower
-than the results of a recent study that predicted age in a large sample, based
-on TBSS-extracted diffusion features \cite{Richard2018-ux}. The model weights in
-this case are distributed over many different tracts and dMRI tissue properties
-(Figure \ref{fig:regress-beta}) This demonstrates that SGL is not coerced to
-produce overly sparse results when a more accurate model requires a dense
-selection of features.
+\cite{yeatman2014lifespan}. SGL was fit to tractometry-extracted features: FA
+and MD in 20 major brain tracts, with each tract divided into 100 nodes. To
+evaluate the fit of the model, we used a nested cross-validation procedure. In
+this procedure, batches of subjects are held out. For each batch (or fold), the
+model is fully fit without this data. Then, once the parameters are fixed, the
+model is inverted to predict the ages of held out subjects based on the linear
+coeffiecients and the static non-linearity. data is held out, and a model age
+was predicted using a model that was fit without that subject. This scheme
+automatically finds the right level of regularization and fits the coefficients
+to the ill-posed linear model, while guarding against overfitting. SGL
+accurately predicts the age of the subjects in this procedure, with procedure,
+with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}),
+which is lower than the results of a recent study that predicted age in a large
+sample, based on TBSS-extracted diffusion features \cite{Richard2018-ux}. The
+model weights in this case are distributed over many different tracts and dMRI
+tissue properties (Figure \ref{fig:regress-beta}) This demonstrates that SGL is
+not coerced to produce overly sparse results when a more accurate model requires
+a dense selection of features.
 

### 2019-12-01 reports/manuscript/sections/conclusion.tex
Starting to work on figure captions.

@@
 method relies on the Sparse Group Lasso \cite{simon2013sparse} to provide both
-acurate prediction of the phenotypic properties of individual subjects based on
+accurate prediction of the phenotypic properties of individual subjects based on
 their dMRI data, but also provides interpretable results by identifying the

### 2019-12-01 reports/manuscript/sections/results.tex
Starting to work on figure captions.

@@
 
-\subsection*{Regression for age prediction}
+\subsection*{SGL of tractometry data in a regression setting}
 
@@
 subjects, ranging between 6 years and 50 years of age
-\cite{yeatman2014lifespan}. SGL was fit to tractometry-extracted features: FA
-and MD in 20 major brain tracts, with each tract divided into 100 nodes. To
-evaluate the fit of the model, we used a nested cross-validation procedure. In
-this procedure, batches of subjects are held out. For each batch (or fold), the
-model is fully fit without this data. Then, once the parameters are fixed, the
-model is inverted to predict the ages of held out subjects based on the linear
-coeffiecients and the static non-linearity. data is held out, and a model age
-was predicted using a model that was fit without that subject. This scheme
-automatically finds the right level of regularization and fits the coefficients
-to the ill-posed linear model, while guarding against overfitting. SGL
-accurately predicts the age of the subjects in this procedure, with procedure,
-with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}),
-which is lower than the results of a recent study that predicted age in a large
-sample, based on TBSS-extracted diffusion features \cite{Richard2018-ux}. The
-model weights in this case are distributed over many different tracts and dMRI
-tissue properties (Figure \ref{fig:regress-beta}) This demonstrates that SGL is
-not coerced to produce overly sparse results when a more accurate model requires
-a dense selection of features.
+\cite{yeatman2014lifespan}. In this case, biological age was used as the
+predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
+tractometry-extracted features: FA and MD in 20 major brain tracts, with each
+tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
+cross-validation procedure. In this procedure, batches of subjects are held out.
+For each batch (or fold), the model is fully fit without this data. Then, once
+the parameters are fixed, the model is inverted to predict the ages of held out
+subjects based on the linear coeffiecients and the static non-linearity. data is
+held out, and a model age was predicted using a model that was fit without that
+subject. This scheme automatically finds the right level of regularization and
+fits the coefficients to the ill-posed linear model, while guarding against
+overfitting. SGL accurately predicts the age of the subjects in this procedure,
+with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}). This
+is lower than the results of a recent study that predicted age in a large
+sample, based on diffusion MRI features \cite{Richard2018-ux}. The model weights
+in this case are distributed over many different tracts and dMRI tissue
+properties (Figure \ref{fig:regress-beta}). This demonstrates that SGL is not
+coerced to produce overly sparse results when a more accurate model requires a
+dense selection of features.
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{regression_residuals.png}
-    \caption{{\bf Prediction of brain age.}
+    \includegraphics[width=0.8\textwidth]{regression_residuals.png}
+    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), an accurate prediction falls close to the $y=x$ line (dashed).
+The mean absolute error in this case  is 3.6 years and, the coefficient of determination $R^2=0.3$.
+Right: Standardized residuals (on the abscissa) as a function of the true age (on the ordinate).
+Predictions are generally more accurate for younger individuals.
     }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{regression_beta_annotated.pdf}
-    \caption{{\bf Feature importance for brain age.}
+    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
+    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
+    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with the anterior up.
+The left cingulum cingulate (A) and forceps minor (B) are highlighted.
+Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
     }
     \label{fig:regress-beta}
-\end{figure}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=1\textwidth]{regression_tract_profiles.pdf}
-    \caption{{\bf Coefficients in context}
-    It makes sense
-    }
-    \label{fig:regress-profiles}
 \end{figure}

### 2019-12-01 reports/manuscript/sections/results.tex
Reorganizing plots a bit.

@@
 
-The WH dataset used for continuous regression contains data from 76 healthy
-subjects, ranging between 6 years and 50 years of age
-\cite{yeatman2014lifespan}. In this case, biological age was used as the
-predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
-tractometry-extracted features: FA and MD in 20 major brain tracts, with each
-tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
-cross-validation procedure. In this procedure, batches of subjects are held out.
-For each batch (or fold), the model is fully fit without this data. Then, once
-the parameters are fixed, the model is inverted to predict the ages of held out
-subjects based on the linear coeffiecients and the static non-linearity. data is
-held out, and a model age was predicted using a model that was fit without that
-subject. This scheme automatically finds the right level of regularization and
-fits the coefficients to the ill-posed linear model, while guarding against
-overfitting. SGL accurately predicts the age of the subjects in this procedure,
-with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}). This
-is lower than the results of a recent study that predicted age in a large
-sample, based on diffusion MRI features \cite{Richard2018-ux}. The model weights
-in this case are distributed over many different tracts and dMRI tissue
-properties (Figure \ref{fig:regress-beta}). This demonstrates that SGL is not
-coerced to produce overly sparse results when a more accurate model requires a
-dense selection of features.
+To test the performance of SGL in tractometry data in a continuous regression
+task, we focus here on the prediction of biological age from the tractometry
+data. Prediction of ``brain age'' is a commonly undertaken task. This is both
+because it operates on a natural scale, with meaningful and easily understood
+units, as well as because predictions of brain age, and deviations from accurate
+prediction are diagnostic of overall brain age \ariel{citation needed}. The WH
+dataset used here contains data from 76 healthy subjects, ranging between 6
+years and 50 years of age \cite{yeatman2014lifespan}. In this case, biological
+age was used as the predicted variable ($y$ in equation \ref{eq:lm}). SGL was
+fit to tractometry-extracted features: FA and MD in 20 major brain tracts, with
+each tract divided into 100 nodes. To evaluate the fit of the model, we used a
+nested cross-validation procedure. In this procedure, batches of subjects are
+held out. For each batch (or fold), the model is fully fit without this data.
+Then, once the parameters are fixed, the model is inverted to predict the ages
+of held out subjects based on the linear coeffiecients and the static
+non-linearity. data is held out, and a model age was predicted using a model
+that was fit without that subject. This scheme automatically finds the right
+level of regularization and fits the coefficients to the ill-posed linear model,
+while guarding against overfitting. SGL accurately predicts the age of the
+subjects in this procedure, with a mean absolute error of 3.6 years (Figure
+\ref{fig:regress-results}, left panel). This is lower than the results of a
+recent study that predicted age in a large sample, based on diffusion MRI
+features \cite{Richard2018-ux}. Nevertheless, older subjects have higher
+residual variance, reflecting the automatically-chosen log-transformation and
+implying that brain age becomes more difficult to predict as we age
+chronologically (\ref{fig:regress-result}, right panel). The model weights are
+distributed over many different tracts and dMRI tissue properties (Figure
+\ref{fig:regress-beta} left). This demonstrates that SGL is not coerced to
+produce overly sparse results when a more accurate model requires a dense
+selection of features. Furthermore, looking closer at a selection of tracts
+where high coefficients are found demonstrates that diffusion properties (FA, in
+this case) are different in different age groups in parts of the tracts where
+these higher coefficients are found (Figure \ref{regress-beta} right).
 
@@
     \includegraphics[width=0.8\textwidth]{regression_residuals.png}
-    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), an accurate prediction falls close to the $y=x$ line (dashed).
+    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), from the test splits (i.e., when each subject's data was held out in fitting the model); an accurate prediction falls close to the $y=x$ line (dashed).
 The mean absolute error in this case is 3.6 years and, the coefficient of determination $R^2=0.3$.
@@
     \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
-    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with the anterior up.
+    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with anterior facing up, and right hemisphere on the right.
+The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the tracts.
 The left cingulum cingulate (A) and forceps minor (B) are highlighted.
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{classification_probs.png}
+    \includegraphics[width=0.45\textwidth]{classification_probs.png}
+    \includegraphics[width=0.45\textwidth]{classification_beta_bupu.png}
+
     \caption{{\bf Prediction of ALS status.}
-        Classification probabilities for each subject's ALS diagnosis. Controls
-        are on the left while patients are on the right. Predicted controls are in blue
-        and predicted patients are in red. Thus, false positive are represented as red
-        dots on the left, while false negatives are represented as blue dots on the
-        right. The SGL algorithm achieves 93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006
-        ROC AUC}
-    \label{fig:class-results}
-\end{figure}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{classification_beta_bupu.png}
-    \caption{{\bf Feature importance for prediction of ALS status.}
-        SGL coefficients are presented on a skeleton of the major tracts. The
-    brain is oriented with the right hemisphere to our left and anterior out of
+        Left: Classification probabilities for each subject's ALS diagnosis.
+        Controls are on the left while patients are on the right. Predicted
+        controls are in blue and predicted patients are in red. Thus, false
+        positive are represented as red dots on the left, while false negatives
+        are represented as blue dots on the right. The SGL algorithm achieves
+        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
+        coefficients are presented on a skeleton of the major tracts. The brain
+        is oriented with the right hemisphere to our left and anterior out of
         the page. As expected large negative coefficients are in the FA of the
         corticospinal tract (and particularly right CST, here to the left)}
-    \label{fig:class-beta}
+    \label{fig:class-results}
 \end{figure}
@@
 \end{figure}
-
-\begin{itemize}
-  \item Classification
-    \begin{itemize}
-      \item Insert figure showing weights as they relate to tract differences visible in the browser
-    \end{itemize}
-\end{itemize}

### 2019-12-01 reports/manuscript/sections/results.tex
More figure captions. Section titles.

@@
 
-\subsection*{SGL of tractometry data in a regression setting}
+\subsection*{SGL accurately predicts age from tractometry data in a regression setting}
 
@@
     \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with anterior facing up, and right hemisphere on the right.
-The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the tracts.
+The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the length of the tracts.
 The left cingulum cingulate (A) and forceps minor (B) are highlighted.
@@
 
-\subsection*{Classification for ALS detection}
+\subsection*{SGL accurately detects ALS in tractometry data in a classification setting}
 
@@
 
-    \caption{{\bf Prediction of ALS status.}
+    \caption{{\bf SGL accurately predicts ALS.}
         Left: Classification probabilities for each subject's ALS diagnosis.
@@
     \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
-    \caption{{\bf Coefficients with FA tract profiles}
-       }
+    \caption{{\bf Model coefficients mirror FA differences}. The places along the
+       length of the corticospinal tract where $\hat{\beta}$ coefficients for FA
+       (dashed line, right axis) have large negative values correspond to the
+       locations of substantial differences between the ALS (green) and control
+       (orange) FA (shaded area indicates standard error of the mean).}
     \label{fig:class-profiles}
@@
         \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
-    \caption{{\bf Mis-classifications}
+    \caption{{\bf Model mis-classifications correspond to features identified by the model}.
        They make sense}

### 2019-12-01 reports/manuscript/sections/results.tex
Small things.

@@
 
-Using data from a previous study of the corticospinal tract profile and
+Using data from a previous study of the corticospinal tract (CST) profile and
 ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
@@
         the page. As expected large negative coefficients are in the FA of the
-        corticospinal tract (and particularly right CST, here to the left)}
+        CST (and particularly in the right hemisphere, here to the left)}
     \label{fig:class-results}
@@
     \caption{{\bf Model coefficients mirror FA differences}. The places along the
-       length of the corticospinal tract where $\hat{\beta}$ coefficients for FA
+       length of the CST  where $\hat{\beta}$ coefficients for FA
        (dashed line, right axis) have large negative values correspond to the
@@
         \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
-    \caption{{\bf Model mis-classifications correspond to features identified by the model}.
-       They make sense}
+    \caption{{\bf Model mis-classifications correspond to features identified by
+       the model}. The FA in CST of individuals that are mis-classified by the
+       model is compared the group FA (with shaded are indicating standard error
+       of the mean). False negative classifications (individuals that have ALS,
+       but are classified as patients have) correspond to high FA either in the
+       more inferior part of the CST}
     \label{fig:class-errors}

### 2019-12-01 reports/manuscript/sections/methods.tex
Removes todo list already addressed.

@@
 
-\subsubsection*{Categorical $y$}
+\subsubsection*{Classification of categorical $y$}
 When the phenotypical target variable is categorical, as in the case of

### 2019-12-01 reports/manuscript/abstract.tex
More references and edits throughout.

@@
 regions. Tractometry uses diffusion-weighted magnetic resonance imaging (dMRI)
-data to quantify tissue properties along the trajectories of these connections
-in the human brain in vivo\cite{yeatman2012tract}. In previous work, the results
-of tractometry were usually analyzed using mass univariate approaches: group
-comparisons or regression models computed separately for each point along every
-one of the tracts.  Alternatively, tissue properties such as fractional
-anisotropy (FA) and mean diffusivity (MD) were computed for a specific tract of
-interest based on an a priori hypothesis. In the present work, we developed a
-method based on the sparse group lasso\cite{simon2013sparse} that takes into
-account tissue properties measured in all of the tracts, and selects informative
-features by enforcing sparsity, both at the level of individual tracts and
-tissue properties, but also across the entire set of tracts and all of the
-measured tissue properties. The sparsity penalties for each of these constraints
-is identified using a nested cross-validation scheme. Using data from a previous
-study that measured dMRI in patients with amyotrophic lateral sclerosis (ALS)
-and matched controls\cite{sarica2017corticospinal}, we demonstrate that this
-method is accurate, exceeding the previous results, that were based on a priori
-feature selection, in classifying patients and controls, with ~84\% accuracy, an
-area under the receiver operating characteristic curve of 0.93, and an average
-precision of 0.95. Moreover, our method automatically identifies as important
-for this classification the parts of the white matter known to be affected by
-ALS within the corticospinal tract. In a regression setting, data from another
-previous study\cite{yeatman2014lifespan} can be used to accurately predict
-``brain age''. Thus, this multivariate analysis approach both (a) achieves high
-cross-validated accuracy for precision medicine applications of dMRI data and
-(b) identifies relevant features of brain anatomy to further our neuroscientific
-understanding of clinical disorders.
+data to quantify tissue properties, such as fractional anisotropy (FA) and mean
+diffusivity (MD), along the trajectories of these connections in the human brain
+\emph{in vivo}\cite{yeatman2012tract}. Statistical inference from tractometry
+data usually either averages these quantities along the length of the tract in
+each individual, or performs analysis point-by-point along each tract, with
+group comparisons or regression models computed separately for each point along
+every one of the tracts. Alternatively, tissue properties are computed for a
+specific tract of interest based on an a priori hypothesis. In the present work,
+we developed a method based on the sparse group lasso (SGL)
+\cite{simon2013sparse} that takes into account tissue properties measured along
+the tracts, and selects informative features by enforcing sparsity, both at the
+level of individual tracts and tissue properties, but also across the entire set
+of tracts and all of the measured tissue properties. The sparsity penalties for
+each of these constraints is identified using a nested cross-validation scheme
+that guards against over-fitting and simultaneously identifies the correct level
+of sparsity, both at the group level and overall. We demonstrate the accuracy of
+the method in two settings: In a regression setting, dMRI is used to accurately
+predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In a
+classification setting, patients with amyotrophic lateral sclerosis (ALS) are
+accurately distinguished from matched controls\cite{sarica2017corticospinal}. In
+addition, SGL automatically identifies FA in the corticospinal tract as
+important for this classification -- correctly finding the parts of the white
+matter known to be affected by ALS. \ariel{Still need a punchy ending sentence
+here}

### 2019-12-01 reports/manuscript/sections/results.tex
Removes todo list already addressed.
More references and edits throughout.

@@
 units, as well as because predictions of brain age, and deviations from accurate
-prediction are diagnostic of overall brain age \ariel{citation needed}. The WH
-dataset used here contains data from 76 healthy subjects, ranging between 6
-years and 50 years of age \cite{yeatman2014lifespan}. In this case, biological
-age was used as the predicted variable ($y$ in equation \ref{eq:lm}). SGL was
-fit to tractometry-extracted features: FA and MD in 20 major brain tracts, with
-each tract divided into 100 nodes. To evaluate the fit of the model, we used a
-nested cross-validation procedure. In this procedure, batches of subjects are
-held out. For each batch (or fold), the model is fully fit without this data.
-Then, once the parameters are fixed, the model is inverted to predict the ages
-of held out subjects based on the linear coeffiecients and the static
-non-linearity. data is held out, and a model age was predicted using a model
-that was fit without that subject. This scheme automatically finds the right
-level of regularization and fits the coefficients to the ill-posed linear model,
-while guarding against overfitting. SGL accurately predicts the age of the
-subjects in this procedure, with a mean absolute error of 3.6 years (Figure
-\ref{fig:regress-results}, left panel). This is lower than the results of a
-recent study that predicted age in a large sample, based on diffusion MRI
-features \cite{Richard2018-ux}. Nevertheless, older subjects have higher
-residual variance, reflecting the automatically-chosen log-transformation and
-implying that brain age becomes more difficult to predict as we age
-chronologically (\ref{fig:regress-result}, right panel). The model weights are
-distributed over many different tracts and dMRI tissue properties (Figure
-\ref{fig:regress-beta} left). This demonstrates that SGL is not coerced to
-produce overly sparse results when a more accurate model requires a dense
-selection of features. Furthermore, looking closer at a selection of tracts
-where high coefficients are found demonstrates that diffusion properties (FA, in
-this case) are different in different age groups in parts of the tracts where
-these higher coefficients are found (Figure \ref{regress-beta} right).
+prediction are diagnostic of overall brain health (for a recent review, see
+\cite{Cole2019-rz}). The WH dataset used here contains data from 76 healthy
+subjects, ranging between 6 years and 50 years of age
+\cite{yeatman2014lifespan}. In this case, biological age was used as the
+predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
+tractometry-extracted features: FA and MD in 20 major brain tracts, with each
+tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
+cross-validation procedure. In this procedure, batches of subjects are held out.
+For each batch (or fold), the model is fully fit without this data. Then, once
+the parameters are fixed, the model is inverted to predict the ages of held out
+subjects based on the linear coeffiecients and the static non-linearity. data is
+held out, and a model age was predicted using a model that was fit without that
+subject. This scheme automatically finds the right level of regularization and
+fits the coefficients to the ill-posed linear model, while guarding against
+overfitting. SGL accurately predicts the age of the subjects in this procedure,
+with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}, left
+panel). This is lower than the results of a recent study that predicted age in a
+large sample, based on diffusion MRI features \cite{Richard2018-ux}.
+Nevertheless, older subjects have higher residual variance, reflecting the
+automatically-chosen log-transformation and implying that brain age becomes more
+difficult to predict as we age chronologically (\ref{fig:regress-results}, right
+panel). The model weights are distributed over many different tracts and dMRI
+tissue properties (Figure \ref{fig:regress-beta} left). This demonstrates that
+SGL is not coerced to produce overly sparse results when a more accurate model
+requires a dense selection of features. Furthermore, looking closer at a
+selection of tracts where high coefficients are found demonstrates that
+diffusion properties (FA, in this case) are different in different age groups in
+parts of the tracts where these higher coefficients are found (Figure
+\ref{fig:regress-beta} right).
 
@@
     \includegraphics[width=0.8\textwidth]{regression_residuals.png}
-    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), from the test splits (i.e., when each subject's data was held out in fitting the model); an accurate prediction falls close to the $y=x$ line (dashed).
-The mean absolute error in this case is 3.6 years and, the coefficient of determination $R^2=0.3$.
-Right: Standardized residuals (on the abscissa) as a function of the true age (on the ordinate).
-Predictions are generally more accurate for younger individuals.
-    }
+    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted
+    age of each individual (on the abscissa) and true age (on the ordinate),
+    from the test splits (i.e., when each subject's data was held out in fitting
+    the model); an accurate prediction falls close to the $y=x$ line (dashed).
+    The mean absolute error in this case is 3.6 years and, the coefficient of
+    determination $R^2=0.3$. Right: Standardized residuals (on the abscissa) as
+    a function of the true age (on the ordinate). Predictions are generally more
+    accurate for younger individuals.}
     \label{fig:regress-results}
@@
     \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
-    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with anterior facing up, and right hemisphere on the right.
-The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the length of the tracts.
-The left cingulum cingulate (A) and forceps minor (B) are highlighted.
-Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
-    }
+    \caption{{\bf Feature importance for predicting age from tractometry.} Left:
+    A skeletonized display of the main brain tracts analyzed, with anterior
+    facing up, and right hemisphere on the right. The $\hat{\beta}$ coefficients
+    displayed in blue (negative) to red (positive) are for measurements of FA
+    along the length of the tracts. The left cingulum cingulate (A) and forceps
+    minor (B) are highlighted. Right: the FA (in shades of blue and green) and
+    the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps
+    minor.}
     \label{fig:regress-beta}
 \end{figure}
-
-\begin{itemize}
-  \item Regression
-    \begin{itemize}
-      \item Lifespan maturation age regression
-      \item Insert figure showing sparsity pattern
-      \item Insert figure showing weights as they relate to tract differences visible in the browser
-    \end{itemize}
-\end{itemize}
-\begin{itemize}
-  \item Failures
-    \begin{itemize}
-      \item Hopefully, the failures are common to both regression
-        and classification so we can include them here in there own
-        subsection.
-      \item Insert figure demonstrating failure cases
-    \end{itemize}
-\end{itemize}
 

### 2019-12-01 reports/manuscript/sections/conclusion.tex

@@
 a person is a patient or a healthy control. In both of these cases, SGL
-out-performs previous algorithms that have been developed for these tasks. In
-addition, the nested cross-validation approach that we have developed tunes the
-degree of sparseness required by the algorithm, such that both very local
-phenomena, as well as widely distributed phenomena are accurately captured.
+out-performs previous algorithms that have been developed for these tasks
+\cite{sarica2017corticospinal, Richard2018-ux}. The nested cross-validation
+approach used to fit the model and make both predictioons and inferences from it
+guards against overfitting and tunes the degree of sparseness required by the
+algorithm, such that both phenomena that are locally focused in a particular
+anatomical location and a particular property of diffusion (e.g., FA in the
+CST), as well as widely distributed phenomena can be accurately captured.
 
@@
 cortico-spinal tract. This recapitulates the results of previous analysis of
- these same data, using a targetted ROI-based approach. In contrast, in analysis
- of biological age, the coefficients identified by the algorithm are very widely
- distributed.
+these same data, using a targetted ROI-based approach
+\cite{sarica2017corticospinal}. In contrast, in analysis of biological age, the
+coefficients identified by the algorithm are very widely distributed in many
+parts of the white matter, mirroring previous results with this dataset that
+show a large and continuous distribution of life-span changes in white matter
+properties \cite{yeatman2014lifespan}.
 
-Taken together, these results demonstrate the promise of a group regularized
+Taken together, these results demonstrate the promise of the group-regularized
 regression approach. Even at the scale of dozens of subjects, the results
-provided by SGL are both accurate and interpretable. We expect that additional
-data will improve the performance of these algorithms. Neuroscience has entered
-an era in which large consortium efforts are putting together large datasets
-that can be analyzed using this approach. Future work will apply this method to
-these datasets. For example, to the Human Connectome Project dataset
-\cite{VanEssen2012}
+provided by SGL are both accurate and interpretable. Thus, this multivariate
+analysis approach both (a) achieves high cross-validated accuracy for precision
+medicine applications of dMRI data and (b) identifies relevant features of brain
+anatomy that can further our neuroscientific understanding of clinical
+disorders.
 
-These results also motivate extensions of the method using more sophisticated
-cost functions. For example, the fused sparse group lasso (FSGL)
-\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
-in the variation of diffusion metrics along the tracts. As brain measurements
-include additional structure (for example, bilateral symmetry), future work
-could also incorporate overlapping group membership for each entry in the tract
-profiles. For example, a measurement could come from the corpus callosum, but
-also from the right hemipshere. This would also require extending the cost
-function used here to incorporate these constraints.
-
-The method is packaged as open-source software called AFQ-Insight that is openly
-available. The sofware integrates within a broader automated fiber
-quantification software ecosystem: AFQ \cite{yeatman2012tract}, which extracts
-tractometry data from raw dMRI, as well as AFQ-Browser, which visualizes
-tractometry data and facilitates sharing of the results of dMRI studies
-\cite{yeatman2018browser}.
+Meanwhile, neuroscience has entered an era in which consortium efforts are
+putting together large datasets of high-quality dMRI data to address a variety
+of scientific questions \cite{jernigan2016ping, jernigan2018abcd,
+alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
+these data pose a substantial challenge. Dimensionality reduction with
+tractometry, followed by analysis with the approach we present here promises to
+capitalize on the wealth of data and on the co-measurement of interesting and
+important phenotypical data about brain health and about the participants'
+cognitive abilities. We also expect the group-regularized approach to improve
+with larger datasets.
 
@@
 
-\begin{itemize}
-  \item Feature selection + prediction
-  \item Part of the AFQ ecosystem
-  \item Open source, reproducibility
-\end{itemize}
+The results we present here also motivate extensions of the method using more
+sophisticated cost functions. For example, the fused sparse group lasso (FSGL)
+\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
+in the variation of diffusion metrics along the tracts. As brain measurements
+include additional structure (for example, bilateral symmetry), future work
+could also incorporate overlapping group membership for each entry in the tract
+profiles \ariel{citation needed}. For example, a measurement could come from the
+corpus callosum, but also from the right hemipshere. This would also require
+extending the cost function used here to incorporate these constraints.
+
+The method is packaged as open-source software called AFQ-Insight that is openly
+available, and this also where extensions of the method will be developed. The
+sofware integrates within a broader automated fiber quantification software
+ecosystem: AFQ \cite{yeatman2012tract}, which extracts tractometry data from raw
+and processed dMRI datasets, as well as AFQ-Browser, which visualizes
+tractometry data and facilitates sharing of the results of dMRI studies
+\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
+software, the results presented in this paper are also provided in
+\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
+notebooks
+\cite{kluyver2016jupyter}

### 2019-12-01 reports/manuscript/sections/introduction.tex

@@
 modeled, as well as for classification tasks, where a discrete property is
-modeled (e.g., ). Moreover, use of SGL in particular helps derive informative
-properties of the human white matter, both in cases where the underlying causes
-of variance are sparsely concentrated (e.g., in one particular white matter
-tract) and in cases where biological substrates of differences between
-individuals are more widespread. This is because SGL is controlled by
-meta-parameters that set the degree to  which and that can be set empirically,
-based on the data, in a process of nested cross-validation. We demonstrate these
-properties of the algorithm in data from previously published studies
-\cite{sarica2017corticospinal, yeatman2014lifespan}.
+modeled (e.g., whether an individual has a particular disease). Moreover, use of
+SGL in particular helps derive informative properties of the human white matter,
+both in cases where the underlying causes of variance are sparsely concentrated
+(e.g., in one particular white matter tract) and in cases where biological
+substrates of differences between individuals are more widespread. This is
+because SGL is controlled by meta-parameters that set the degree to  which and
+that can be set empirically, based on the data, in a process of nested
+cross-validation. We demonstrate these properties of the algorithm in data from
+previously published studies \cite{sarica2017corticospinal,
+yeatman2014lifespan}.

### 2019-12-03 reports/manuscript/abstract.tex
Add details to cross-validation section and software implementation. Update some references and minor edits to other sections

@@
 of sparsity, both at the group level and overall. We demonstrate the accuracy of
-the method in two settings: In a regression setting, dMRI is used to accurately
+the method in two settings: in a regression setting, dMRI is used to accurately
 predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In a

### 2019-12-03 reports/manuscript/sections/methods.tex
More references and edits throughout.
Add details to cross-validation section and software implementation. Update some references and minor edits to other sections

@@
 \section*{Materials and methods}
-
-TODO:
-
-\begin{itemize}
-  \item Computational implementation
-    \begin{itemize}
-      \item Insert Figure for pipeline
-      \item Proximal gradient methods
-      \item Meta-parameter optimization
-      \item Cross-validation scheme
-        \begin{itemize}
-          \item Insert Figure for cross-validation scheme
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
 
@@
 was obtained from each adult participant, and assent for participation was
-provided by by parents/guardians for children. Voxel resolution was 2x2x2 $mm^3$
-96 non-colinear directions of measurement were measured with a b=2,000 $s/mm^2$
-and 30 non-colinear directions of measurement were measured with a b=1,000
-$s/mm^2$. Data was preprocessed to correct for subject motion and the diffusion
+provided by parents/guardians for children. Voxel resolution was
+\num{2x2x2}\si{\milli\meter^3} with 96 non-colinear directions measured with a
+$b= \SI{2000}{\second\per\milli\meter^2}$ and 30 non-colinear directions
+measured with a $b=\SI{1000}{\second\per\milli\meter^2}$.
+Data was preprocessed to correct for subject motion and the diffusion
 tensor model \cite{basser1994mr} was fit in every voxel, using a robust fit
@@
 Ethical Committee of the University ``Magna Graecia'' of Catanzaro. Voxel
-resolution was 2x2x2 $mm^3$ and 27 non-colinear directions were measured with a
-b=1,000 $s/mm^2$. Here, both motion correction and eddy current correction were
+resolution was \num{2x2x2}\si{\milli\meter^3} and 27 non-colinear directions
+were measured with a $b=\SI{1000}{\second\per\milli\meter^2}$.
+Here, both motion correction and eddy current correction were
 applied before modeling the diffusioon tensor in each voxel. We will refer to
@@
 are measured (e.g., in the Human Connectome Project, where 1,200 subjects were
-measured \cite{VanEssen2012}), the problem is ill-posed: The high dimensionality
+measured \cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
 of this data requires regularization to avoid overfitting and generate
@@
 grouping. For example, we expect that MD features within the left arcuate
-fasciculus to co-vary across individuals. Likewise for FA values within the
+fasciculus will co-vary across individuals. Likewise for FA values within the
 right corticospinal tract (CST) and so on. This group structure is represented
@@
 model with anatomically-grouped covariates, where we expect to observe both
-groupwise sparsity: the number of groups (tract/metric combinations) with at
-least one non-zero coefficients as well as within-group sparsity: the number of
-non-zero coefficients within each non-zero groups. The sparse group lasso (SGL)
+groupwise sparsity, where the number of groups (tract/metric combinations) with
+at least one non-zero coefficients is small, as well as within-group sparsity,
+where the number of non-zero coefficients within each non-zero group is small.
+The sparse group lasso (SGL)
 is a penalized regression technique that satisfies exactly these
@@
     \widehat{\beta} = \min_\beta \frac{1}{2}
-    \norm*{y - \displaystyle \sum_{\ell = 1}^{G} \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
-    + \lambda_1 \displaystyle \sum_{\ell = 1}^{G} \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
+    \norm*{y - \displaystyle \sum_{\ell = 1}^{G}
+    \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
+    + \lambda_1 \displaystyle \sum_{\ell = 1}^{G}
+    \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
     + \lambda_2 \norm*{\beta}_1,
@@
 
-where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
-$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the coefficient
-vector for group $\ell$ and $p_\ell$ is the length of $\beta^{(\ell)}$. In the
-tractomtetry setting, $G = T \cdot M$ and $\forall \ell: p_\ell = 100$. The
-first term is the mean square error loss, $L_{mse}$, as in the standard linear
-regression framework. The second and third terms encourage groupwise sparsity
-and overall sparsity, respectively. If $\lambda_1 = 0$ and $\lambda_2 = 1$, the
-SGL reduces to the traditional lasso\cite{tibshirani1996regression}. Conversely,
-if $\lambda_1 = 1$ and $\lambda_2 = 0$, the SGL reduces to the group
-lasso\cite{yuan2006model}.
+where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix
+of $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is
+the coefficient vector for group $\ell$ and $p_\ell$ is the length of
+$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \cdot M$ and
+$\forall \ell: p_\ell = 100$. The first term is the mean square error
+loss, $L_{\text{mse}}$, as in the standard linear regression framework.
+The second and third terms encourage groupwise sparsity and overall
+sparsity, respectively. If $\lambda_1 = 0$ and $\lambda_2 = 1$, the
+SGL reduces to the traditional lasso\cite{tibshirani1996regression}.
+Conversely, if $\lambda_1 = 1$ and $\lambda_2 = 0$, the SGL reduces to
+the group lasso\cite{yuan2006model}.
 
@@
 \cite{parikh2014proximal} here implemented as a custom proximal operator that is
-then optimized using the COPT library \ariel{citation needed here}. To
-find the values of the metaparameters $\lambda_1$ and $\lambda_2$, we used a
-hyperoptimization procedure, implemented using the hyperopt software
-\cite{Bergstra_2015}. XXX We need more details here.
+then optimized using the C-OPT library\cite{copt}. This supplies an estimate
+of the optimal $\widehat{\beta}$ given a particular set of values for the
+regulation parameters $\lambda_1$ and $\lambda_2$. We then find the optimal
+values for $\lambda_1$ and $\lambda_2$ using the hyperopt library's \verb|fmin|
+function\cite{Bergstra_2015} with a tree of Parzen estimators search
+algorithm\cite{bergstra2011algorithms}. For the WH dataset, where the target
+variable is continuous numerical, \verb|fmin| searches for metaparameters that
+minimize the median absolute error, though in general a user may also
+choose to minimize the root-mean-square-error or to maximize the
+coefficient of determination ($R^2$). For the ALS dataset, where the
+target variable is binary categorical, \verb|fmin| seeks to maximize the
+classification accuracy, though in general the user may also choose to
+maximize the area under the receiver operating curve (ROC AUC) or the
+average precision. \adam{Enough detail provided?}
 
-To objectively evaluate the model and guard against over-fitting, we used
-cross-validation. XXX More here.
+To objectively evaluate the model and guard against over-fitting,
+we used a nested cross-validation scheme, depicted in
+Fig~\ref{fig:cross-val} for the categorical classification case. The
+input data is shuffled and then decomposed into $k$ batches, hereafter
+referred to as folds. For the ALS dataset, $k=10$, while for the WH
+dataset, $k=5$. For each unique fold, we hold that fold out as the
+test\textsubscript{outer} set and let the remaining data comprise
+the train\textsubscript{outer} set, with the subscript indicating
+the depth of the nested decomposition. We further decompose each
+train\textsubscript{outer} set into three folds, and again for each
+unique fold, we hold out that fold as the test\textsubscript{inner}
+set and let the remaining data comprise the train\textsubscript{inner}
+set. At level-1 of the decomposition, we fit an SGL model using
+arbitrary fixed regularization parameters $\lambda_1$ and $\lambda_2$,
+training the model using train\textsubscript{inner} and evaluating
+the fit using the appropriate metric on test\textsubscript{inner}.
+The optimal regularization parameters are determined using the
+aforementioned hyperopt library at level-0 of the decomposition. We
+find optimal regularization parameters and $\widehat{\beta}$ for each
+train\textsubscript{outer} set and then use those to predict values for
+data in test\textsubscript{outer}. Thus each subject in the dataset has
+a predicted phenotype derived from a model that never saw its particular
+subject's data.
+
+The above procedure describes $k$-fold cross validation. In fact,
+we use repeated $k$-fold cross validation on the outer level of the
+decomposition, so that the input data is decomposed into $k$ folds,
+three times. Thus, each subject has three predicted phenotypes. We then
+take the mean predicted value to summarize the skill of the model.
+In the classification case, the shuffling into folds is stratified such
+that each fold has a population that preserves the percentage of each
+class found in the larger input data.
+\adam{Clear as mud?}.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.55\textwidth]{nested-cross-validation.pdf}
+    \caption{{\bf Nested $k$-fold cross-validation scheme.}
+        We evaluate model quality using a nested $k$-fold cross
+        validation scheme. At level-0, the input data is decomposed
+        three times into $k$ shuffled groups and optimal hyperparameters
+        are found for the level-0 training set. Optimization of these
+        hyperparameters requires the use of the hyperopt library and
+        many repeated evaluations of an SGL model over a search space
+        of possible regularization parameters. These evaluations take
+        place at level-1 of the decomposition, where the level-0 training
+        set is further decomposed into three shuffled groups.
+        For the ALS data, $k=10$. For the WH data, $k=5$.
+    }
+    \label{fig:cross-val}
+\end{figure}
 
@@
 can be best fit to it. Equation \ref{eq:lm} can be slightly modified as:
-
 \begin{equation}
@@
 \end{equation}
-
-where the transformation function $f^-1$ characterizes the transform applied to
-the data before fitting the linear coefficients. For example, an often-used
+where the transformation function $f^{-1}$ characterizes the transform applied
+to the data before fitting the linear coefficients. For example, an often-used
 transform is the logarithmic transform:
-
 \begin{equation}
-f(y) = log_n(y)
+f(y) = \log_n(y)
 \label{eq:log_nonlinearity}
 \end{equation}
-
 In this case, the model is parametrized by one additional fit parameter, $n$.
@@
 function of the result of the linear model,
-
 \begin{equation}
@@
 \end{equation}
-
 or equivalently, the mean squared error loss function in Eq~\eqref{eq:sgl} is
@@
 negative log likelihood of the SGL classifier giving the ``true'' label:
-
 \begin{equation}
-    L_{mse} \rightarrow L_{\log} = -\left(y \log(p) + (1 - y) \log(1 - p)\right).
+    L_{\text{mse}} \rightarrow L_{\log} =
+    -\left(y \log(p) + (1 - y) \log(1 - p)\right).
     \label{eq:logloss}
@@
 \url{https://github.com/richford/afq-insight}. The version of the code used to
-produce the results herein is also available in XXX Zenodo DOI. AFQ-Insight
-reads the target and feature data that has been processed by AFQ from comma
-separated value (CSV) files conforming to the AFQ-Browser data
+produce the results herein is also available in \ariel{Need to add Zenodo DOI}.
+AFQ-Insight reads the target and feature data that has been processed by AFQ
+from comma separated value (CSV) files conforming to the AFQ-Browser data
 format\cite{yeatman2018browser} and represents them internally as
@@
 only values from adjacent nodes in the same white matter tract in the same
-subject so there is no danger of data leakage from other subjects.
+subject so there is no danger of data leakage from other subjects. It uses the
+scikit-learn\cite{scikit-learn} library to decompose input data into separate
+test and train datasets, to scale each feature to have zero mean and
+unit variance, and to evaluate each fit in the hyperparameter search using
+appropriate classification and regression metrics such as accuracy, area
+under the receiver operating curve (AUC ROC), and coefficient of determination
+($R^2$). For each set of hyperparameters, we solve the SGL using a custom
+proximal operator supplied to the C-OPT library\cite{copt}. Appropriate
+hyperparameters are found using the hyperopt library\cite{Bergstra_2015}.

### 2019-12-03 reports/manuscript/sections/results.tex
Add details to cross-validation section and software implementation. Update some references and minor edits to other sections

@@
 the parameters are fixed, the model is inverted to predict the ages of held out
-subjects based on the linear coeffiecients and the static non-linearity. data is
-held out, and a model age was predicted using a model that was fit without that
-subject. This scheme automatically finds the right level of regularization and
+subjects based on the linear coeffiecients and the static non-linearity.
+This scheme automatically finds the right level of regularization and
 fits the coefficients to the ill-posed linear model, while guarding against
@@
 
-\begin{figure}[!h]
+\begin{figure}[h]
     \centering
@@
 the need for a priori feature engineering. The results of the classification
-prediction are shown in Fig~\ref{fig:class-results}, with ``ground-truth'' ALS
+prediction are shown in Fig~\ref{fig:class-results} with ``ground-truth'' ALS
 status separated into columns, and predicted ALS status encoded by color. In
@@
 white matter features is captured in the $\beta$ coefficients from
-Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-beta} depicts these coefficients across
-the brain, laid out on a skeleton of the major tracts. We find that SGL selects
+Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-profiles} depicts these coefficients along
+the right CST, plotted over the FA values for the control and ALS subject
+groups. We find that SGL selects
 FA metrics in the corticospinal tract and particualrly in the right
@@
 
-\begin{figure}[!h]
+We also find that mislabelled subjects correspond to outlying features in the
+CST. Fig~\ref{fig:class-errors} depicts the group FA values along with
+FA values of mislabelled subjects, two false negatives and one false-positive.
+The false negative classifications have high FA in one of the two sections of
+the CST where $\norm{\widehat{\beta}} > 0$ in Fig~\ref{fig:class-profiles}.
+The false positive subject has an FA that oscillates between the two group
+means. Thus, the SGL method fails comprehensibly.
+
+\begin{figure}[h]
     \centering
@@
        of the mean). False negative classifications (individuals that have ALS,
-       but are classified as patients have) correspond to high FA either in the
-       more inferior part of the CST}
+       but are classified as patients) correspond to high FA either in one of
+       the two regions of large $\norm{\widehat{\beta}}$ in
+       Fig~\ref{fig:class-profiles}. The false positive classification has
+       an FA profile that oscillates between the two group means.
+   }
     \label{fig:class-errors}

### 2019-12-03 reports/manuscript/abstract.tex
Massaging the methods and reordering things.
A few small edits in the abstract and introduction as well.

Added citation for SOG, addressing #10.

@@
 every one of the tracts. Alternatively, tissue properties are computed for a
-specific tract of interest based on an a priori hypothesis. In the present work,
-we developed a method based on the sparse group lasso (SGL)
+specific tract of interest based on an \emph{a priori} hypothesis. In the
+present work, we developed a method based on the sparse group lasso (SGL)
 \cite{simon2013sparse} that takes into account tissue properties measured along
-the tracts, and selects informative features by enforcing sparsity, both at the
-level of individual tracts and tissue properties, but also across the entire set
-of tracts and all of the measured tissue properties. The sparsity penalties for
-each of these constraints is identified using a nested cross-validation scheme
-that guards against over-fitting and simultaneously identifies the correct level
-of sparsity, both at the group level and overall. We demonstrate the accuracy of
-the method in two settings: in a regression setting, dMRI is used to accurately
+all of the tracts, and selects informative features by enforcing sparsity, both
+at the level of individual tracts and tissue properties, but also across the
+entire set of tracts and all of the measured tissue properties. The sparsity
+penalties for each of these constraints is identified using a nested
+cross-validation scheme that guards against over-fitting and simultaneously
+identifies the correct levels of sparsity. We demonstrate the accuracy of the
+method in two settings: in a regression setting, dMRI is used to accurately
 predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In a
@@
 important for this classification -- correctly finding the parts of the white
-matter known to be affected by ALS. \ariel{Still need a punchy ending sentence
-here}
+matter known to be affected by ALS.
+\ariel{Still need a punchy ending sentence here}

### 2019-12-06 reports/manuscript/sections/methods.tex
Convert to docx using pandoc. Simplify some of the math used to allow that.

@@
 provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}\si{\milli\meter^3} with 96 non-colinear directions measured with a
-$b= \SI{2000}{\second\per\milli\meter^2}$ and 30 non-colinear directions
-measured with a $b=\SI{1000}{\second\per\milli\meter^2}$.
-Data was preprocessed to correct for subject motion and the diffusion
-tensor model \cite{basser1994mr} was fit in every voxel, using a robust fit
-\cite{chang2005restore}. These data were acquired using a dual spin echo
-sequence, in which there is sufficient time for eddy currents to subside between
-the application of the gradients and the image acquisition, so no eddy current
-correction was appliced. We will refer to this dataset as WH.
+\num{2x2x2}$mm^3$ with 96 non-colinear directions measured with a $b=2000$
+$\frac{sec}{mm^2}$ and 30 non-colinear directions measured with a $b=1000$
+$\frac{sec}{mm^2}$. Data was preprocessed to correct for subject motion and the
+diffusion tensor model \cite{basser1994mr} was fit in every voxel, using a
+robust fit \cite{chang2005restore}. These data were acquired using a dual spin
+echo sequence, in which there is sufficient time for eddy currents to subside
+between the application of the gradients and the image acquisition, so no eddy
+current correction was appliced. We will refer to this dataset as WH.
 
@@
 Ethical Committee of the University ``Magna Graecia'' of Catanzaro. Voxel
-resolution was \num{2x2x2}\si{\milli\meter^3} and 27 non-colinear directions
-were measured with a $b=\SI{1000}{\second\per\milli\meter^2}$.
-Here, both motion correction and eddy current correction were
-applied before modeling the diffusioon tensor in each voxel. We will refer to
-this dataset as ALS.
+resolution was \num{2x2x2} $mm^3$ and 27 non-colinear directions were
+measured with a $b=1000$ $\frac{sec}{mm^2}$. Here, both motion correction and
+eddy current correction were applied before modeling the diffusioon tensor in
+each voxel. We will refer to this dataset as ALS.
 
@@
 criteria\cite{simon2013sparse}. It solves for a coefficient vector
-$\widehat{\beta}$ that satisfies
+$\hat{\beta}$ that satisfies
 \begin{equation}
-    \widehat{\beta} = \min_\beta \frac{1}{2}
-    \norm*{y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
+    \hat{\beta} = \min_\beta \frac{1}{2}
+    ||y - \displaystyle \sum_{\ell = 1}^{G}
+    \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}||_2^2
     + \lambda_1 \displaystyle \sum_{\ell = 1}^{G}
-    \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
-    + \lambda_2 \norm*{\beta}_1,
+    \sqrt{p_\ell} ||\beta^{(\ell)}||_2
+    + \lambda_2 ||\beta||_1,
     \label{eq:sgl}
@@
 
-\subsection*{Implementation, cross-validation and metaparameter optimization}
-
-For given values of $\lambda_1$ and $\lambda_2$, the cost function in equation
-\ref{eq:sgl} can be optimized using proximal gradient descent methods
-\cite{parikh2014proximal} here implemented as a custom proximal operator that is
-then optimized using the C-OPT library\cite{copt}. This supplies an estimate
-of the optimal $\widehat{\beta}$ given a particular set of values for the
-regulation parameters $\lambda_1$ and $\lambda_2$. We then find the optimal
-values for $\lambda_1$ and $\lambda_2$ using the hyperopt library's \verb|fmin|
-function\cite{Bergstra_2015} with a tree of Parzen estimators search
-algorithm\cite{bergstra2011algorithms}. For the WH dataset, where the target
-variable is continuous numerical, \verb|fmin| searches for metaparameters that
-minimize the median absolute error, though in general a user may also
-choose to minimize the root-mean-square-error or to maximize the
-coefficient of determination ($R^2$). For the ALS dataset, where the
-target variable is binary categorical, \verb|fmin| seeks to maximize the
-classification accuracy, though in general the user may also choose to
-maximize the area under the receiver operating curve (ROC AUC) or the
-average precision. \adam{Enough detail provided?}
-
-To objectively evaluate the model and guard against over-fitting,
-we used a nested cross-validation scheme, depicted in
-Fig~\ref{fig:cross-val} for the categorical classification case. The
-input data is shuffled and then decomposed into $k$ batches, hereafter
-referred to as folds. For the ALS dataset, $k=10$, while for the WH
-dataset, $k=5$. For each unique fold, we hold that fold out as the
-test\textsubscript{outer} set and let the remaining data comprise
-the train\textsubscript{outer} set, with the subscript indicating
-the depth of the nested decomposition. We further decompose each
-train\textsubscript{outer} set into three folds, and again for each
-unique fold, we hold out that fold as the test\textsubscript{inner}
-set and let the remaining data comprise the train\textsubscript{inner}
-set. At level-1 of the decomposition, we fit an SGL model using
-arbitrary fixed regularization parameters $\lambda_1$ and $\lambda_2$,
-training the model using train\textsubscript{inner} and evaluating
-the fit using the appropriate metric on test\textsubscript{inner}.
-The optimal regularization parameters are determined using the
-aforementioned hyperopt library at level-0 of the decomposition. We
-find optimal regularization parameters and $\widehat{\beta}$ for each
-train\textsubscript{outer} set and then use those to predict values for
-data in test\textsubscript{outer}. Thus each subject in the dataset has
-a predicted phenotype derived from a model that never saw its particular
-subject's data.
-
-The above procedure describes $k$-fold cross validation. In fact,
-we use repeated $k$-fold cross validation on the outer level of the
-decomposition, so that the input data is decomposed into $k$ folds,
-three times. Thus, each subject has three predicted phenotypes. We then
-take the mean predicted value to summarize the skill of the model.
-In the classification case, the shuffling into folds is stratified such
-that each fold has a population that preserves the percentage of each
-class found in the larger input data.
-\adam{Clear as mud?}.
-
 \begin{figure}[!h]
     \centering
-    \includegraphics[width=0.55\textwidth]{nested-cross-validation.pdf}
-    \caption{{\bf Nested $k$-fold cross-validation scheme.}
-        We evaluate model quality using a nested $k$-fold cross
-        validation scheme. At level-0, the input data is decomposed
-        three times into $k$ shuffled groups and optimal hyperparameters
-        are found for the level-0 training set. Optimization of these
-        hyperparameters requires the use of the hyperopt library and
-        many repeated evaluations of an SGL model over a search space
-        of possible regularization parameters. These evaluations take
-        place at level-1 of the decomposition, where the level-0 training
-        set is further decomposed into three shuffled groups.
-        For the ALS data, $k=10$. For the WH data, $k=5$.
-    }
-    \label{fig:cross-val}
+    \includegraphics[width=0.65\textwidth]{dMRI_group_structure.png}
+    \caption{{\bf dMRI group structure.}
+        The phenotypical target data and tractometric features can be organized
+    into a linear model, $y = \mathbf{X} \cdot \beta$. The feature matrix
+    $\mathbf{X}$ is color-coded to reveal a natural group structure: the left
+    (orange) group contains $k$ features from the inferior fronto-occipital
+    fascicle (IFOF), the middle (green) group contains $k$ features from the
+    corpus callosum, and the right (blue) group contains $k$ features from the
+    uncinate. The coefficients in $\beta$ follow the same natural grouping.
+    Fascicle image reproduced with permission from Ref~\cite{yeatman2012tract}
+    Figure 1.}
+    \label{fig:group-structure}
 \end{figure}
@@
 
+\subsection*{Implementation, cross-validation and metaparameter optimization}
+
+For given values of $\lambda_1$ and $\lambda_2$, the cost function in equation
+\ref{eq:sgl} can be optimized using proximal gradient descent methods
+\cite{parikh2014proximal} here implemented as a custom proximal operator that is
+then optimized using the C-OPT library\cite{copt}. This supplies an estimate of
+the optimal $\hat{\beta}$ given a particular set of values for the
+meta-parameters $\lambda_1$ and $\lambda_2$.
+
+To objectively evaluate the model and guard against over-fitting, we used a
+nested cross-validation scheme, depicted in Fig~\ref{fig:cross-val} for the
+categorical classification case. The input data is shuffled and then decomposed
+into $k$ batches, hereafter referred to as folds. For the ALS dataset we used
+$k=10$ and for the WH dataset $k=5$. For each unique fold, we hold that fold out
+as the test\textsubscript{outer} set and let the remaining data comprise the
+train\textsubscript{outer} set, with the subscript indicating the depth of the
+nested decomposition. We further decompose each train\textsubscript{outer} set
+into three folds, and again for each unique fold, we hold out that fold as the
+test\textsubscript{inner} set and let the remaining data comprise the
+train\textsubscript{inner} set. At level-1 of the decomposition, we fit an SGL
+model using fixed regularization meta-parameters $\lambda_1$ and $\lambda_2$,
+training the model using train\textsubscript{inner} and evaluating the fit on
+test\textsubscript{inner}. We find the optimal values for $\lambda_1$ and
+$\lambda_2$ using hyperoptimizatin. This is implemented using the hyperopt
+library's \verb|fmin| function\cite{Bergstra_2015} with a tree of Parzen
+estimators search algorithm\cite{bergstra2011algorithms}. For continuous
+numerical $y$, \verb|fmin| searches for meta-parameter values that minimize the
+median absolute error. This can also be done minimizing the root of the mean
+squared error (RMSE) or to maximizing the coefficient of determination ($R^2$).
+For binary categorical $y$ \verb|fmin| seeks to maximize the classification
+accuracy. This can also be done maximizing the area under the receiver operating
+curve (ROC AUC) or the average precision. Using hyperoptimization, we find
+optimal regularization parameters and $\hat{\beta}$ for each
+train\textsubscript{outer} set and then use those to predict values for data in
+test\textsubscript{outer}. Thus each subject in the dataset has a predicted
+phenotype derived from a model that never saw its particular subject's data.
+
+The above procedure describes $k$-fold cross validation. In fact, we use
+repeated $k$-fold cross validation on the outer level of the decomposition, so
+that the input data is decomposed into $k$ folds, three times. Thus, each
+subject has three predicted phenotypes. We then take the mean predicted value to
+summarize the performance of the model. In the classification case, the
+shuffling into folds is stratified such that each fold has a population that
+preserves the percentage of each class found in the larger input data.
+
 \begin{figure}[!h]
     \centering
-    \includegraphics[width=0.65\textwidth]{dMRI_group_structure.png}
-    \caption{{\bf dMRI group structure.}
-        The phenotypical target data and tractometric features can be organized
-    into a linear model, $y = \mathbf{X} \cdot \beta$. The feature matrix
-    $\mathbf{X}$ is color-coded to reveal a natural group structure: the left
-    (orange) group contains $k$ features from the inferior fronto-occipital
-    fascicle (IFOF), the middle (green) group contains $k$ features from the
-    corpus callosum, and the right (blue) group contains $k$ features from the
-    uncinate. The coefficients in $\beta$ follow the same natural grouping.
-    Fascicle image reproduced with permission from Ref~\cite{yeatman2012tract}
-    Figure 1.}
-    \label{fig:group-structure}
+    \includegraphics[width=0.55\textwidth]{nested-cross-validation.pdf}
+    \caption{{\bf Nested $k$-fold cross-validation scheme.}
+        We evaluate model quality using a nested $k$-fold cross
+        validation scheme. At level-0, the input data is decomposed
+        three times into $k$ shuffled groups and optimal hyperparameters
+        are found for the level-0 training set. Optimization of these
+        hyperparameters requires the use of the hyperopt library and
+        many repeated evaluations of an SGL model over a search space
+        of possible regularization parameters. These evaluations take
+        place at level-1 of the decomposition, where the level-0 training
+        set is further decomposed into three shuffled groups.
+        For the ALS data, $k=10$. For the WH data, $k=5$.
+    }
+    \label{fig:cross-val}
 \end{figure}

### 2019-12-06 reports/manuscript/sections/results.tex
Convert to docx using pandoc. Simplify some of the math used to allow that.

@@
 The false negative classifications have high FA in one of the two sections of
-the CST where $\norm{\widehat{\beta}} > 0$ in Fig~\ref{fig:class-profiles}.
+the CST where $||\hat{\beta}|| > 0$ in Fig~\ref{fig:class-profiles}.
 The false positive subject has an FA that oscillates between the two group
@@
        but are classified as patients) correspond to high FA either in one of
-       the two regions of large $\norm{\widehat{\beta}}$ in
+       the two regions of large $||\hat{\beta}||$ in
        Fig~\ref{fig:class-profiles}. The false positive classification has

### 2019-12-06 reports/manuscript/abstract.tex
Incorporate Jason's edits to the abstract

@@
 
-The white matter contains long-range connections between different brain
-regions. Tractometry uses diffusion-weighted magnetic resonance imaging (dMRI)
-data to quantify tissue properties, such as fractional anisotropy (FA) and mean
-diffusivity (MD), along the trajectories of these connections in the human brain
-\emph{in vivo}\cite{yeatman2012tract}. Statistical inference from tractometry
-data usually either averages these quantities along the length of the tract in
-each individual, or performs analysis point-by-point along each tract, with
-group comparisons or regression models computed separately for each point along
-every one of the tracts. Alternatively, tissue properties are computed for a
-specific tract of interest based on an \emph{a priori} hypothesis. In the
-present work, we developed a method based on the sparse group lasso (SGL)
-\cite{simon2013sparse} that takes into account tissue properties measured along
-all of the tracts, and selects informative features by enforcing sparsity, both
-at the level of individual tracts and tissue properties, but also across the
-entire set of tracts and all of the measured tissue properties. The sparsity
-penalties for each of these constraints is identified using a nested
-cross-validation scheme that guards against over-fitting and simultaneously
-identifies the correct levels of sparsity. We demonstrate the accuracy of the
-method in two settings: in a regression setting, dMRI is used to accurately
-predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In a
-classification setting, patients with amyotrophic lateral sclerosis (ALS) are
-accurately distinguished from matched controls\cite{sarica2017corticospinal}. In
-addition, SGL automatically identifies FA in the corticospinal tract as
-important for this classification -- correctly finding the parts of the white
-matter known to be affected by ALS.
-\ariel{Still need a punchy ending sentence here}
+The white matter contains long-range connections between different
+brain regions. Tractometry uses diffusion-weighted magnetic resonance
+imaging (dMRI) data to quantify tissue properties (e.g. fractional
+anisotropy (FA), mean diffusivity (MD), etc.), along the trajectories
+of these connections\cite{yeatman2012tract}. Statistical inference from
+tractometry data usually either (a) averages these quantities along
+the length of the tract in each individual, or (b) performs analysis
+point-by-point along each tract, with group comparisons or regression
+models computed separately for each point along every one of the tracts.
+In the present work, we developed a method based on the sparse group
+lasso (SGL) \cite{simon2013sparse} that takes into account tissue
+properties measured along all of the tracts, and selects informative
+features by enforcing sparsity, not only at the level of individual
+tracts and tissue properties, but also across the entire set of tracts
+and all of the measured tissue properties. The sparsity penalties for
+each of these constraints is identified using a nested cross-validation
+scheme that guards against over-fitting and simultaneously identifies
+the correct level of sparsity. We demonstrate the accuracy of the method
+in two settings: in a regression setting, dMRI is used to accurately
+predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In this
+case, the weights are distributed throughout the white matter indicating
+that many different regions of the white matter change with development
+and contribute to the prediction of age. In a classification setting,
+patients with amyotrophic lateral sclerosis (ALS) are accurately
+distinguished from matched controls\cite{sarica2017corticospinal} and
+SGL automatically identifies FA in the corticospinal tract as important
+for this classification -- correctly finding the parts of the white
+matter known to be affected by the disease. Thus, SGL makes it possible
+to leverage the multivariate relationship between diffusion properties
+measured along multiple tracts to make accurate predictions of subject
+characteristics while simultaneously discovering the most relevant
+features of the white matter for the characteristic of interest.

### 2019-12-06 reports/manuscript/sections/conclusion.tex

@@
 could also incorporate overlapping group membership for each entry in the tract
-profiles \ariel{citation needed}. For example, a measurement could come from the
+profiles \cite{Rao2014-xm}. For example, a measurement could come from the
 corpus callosum, but also from the right hemipshere. This would also require

### 2019-12-06 reports/manuscript/sections/introduction.tex

@@
 bundles requires extraordinary evidence, and delineating the exact location of
-the termination of the streamlines in the gray matter, there is little dispute
-that tractography can accurately delineate major white matter bundles that are
-known to exist within the core of the white matter \cite{Maier-Hein2017-vb}.
+the termination of the streamlines in the gray matter is still prone to error,
+there is little dispute that tractography can accurately delineate major white
+matter bundles that are known to exist within the core of the white matter
+\cite{Maier-Hein2017-vb}.
 
@@
 retaining the individual samples along the length of each fiber
-\cite{yeatman2012tract, colby2012, ODonnell2009-uu}. However, while this retains
+\cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this retains
 important information about each individual's white matter, it also presents
@@
 input to a multivariate analysis of covariance, and linear discriminant analysis
-\cite{dayan2016profilometry}. Other work has used random forests algorithms
-applied to the corticospinal tract to discriminate between patients with ALS and
-matched controls \cite{sarica2017corticospinal}
+\cite{dayan2016profilometry}.
 
@@
 
-In the present work, we present a novel framework for analysis of tractometry
+In the present work, we developed a novel framework for analysis of tractometry
 that simultaneously selects the features for analysis, and fits a model to these
@@
 modeled (e.g., whether an individual has a particular disease). Moreover, use of
-SGL in particular helps derive informative properties of the human white matter,
-both in cases where the underlying causes of variance are sparsely concentrated
-(e.g., in one particular white matter tract) and in cases where biological
-substrates of differences between individuals are more widespread. This is
-because SGL is controlled by meta-parameters that set the degree to  which and
-that can be set empirically, based on the data, in a process of nested
-cross-validation. We demonstrate these properties of the algorithm in data from
-previously published studies \cite{sarica2017corticospinal,
-yeatman2014lifespan}.
+SGL helps derive informative properties of the human white matter, both in cases
+where the underlying causes of variance are sparsely concentrated (e.g., in one
+particular white matter tract) and in cases where biological substrates of
+differences between individuals are more widespread. This is because SGL is
+controlled by meta-parameters that set the degree to which group sparsity and
+overall sparsity are applied. These metaparameters can be set empirically, based
+on the data, through a process of nested cross-validation. We demonstrate these
+properties of the algorithm in data from previously published studies
+\cite{sarica2017corticospinal, yeatman2014lifespan}.

### 2019-12-06 reports/manuscript/sections/methods.tex

@@
 provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$mm^3$ with 96 non-colinear directions measured with a $b=2000$
-$\frac{sec}{mm^2}$ and 30 non-colinear directions measured with a $b=1000$
-$\frac{sec}{mm^2}$. Data was preprocessed to correct for subject motion and the
-diffusion tensor model \cite{basser1994mr} was fit in every voxel, using a
-robust fit \cite{chang2005restore}. These data were acquired using a dual spin
-echo sequence, in which there is sufficient time for eddy currents to subside
-between the application of the gradients and the image acquisition, so no eddy
-current correction was appliced. We will refer to this dataset as WH.
+\num{2x2x2}\si{\milli\meter^3} with 96 non-colinear directions measured with a
+$b= \SI{2000}{\second\per\milli\meter^2}$ and 30 non-colinear directions
+measured with a $b=\SI{1000}{\second\per\milli\meter^2}$.
+Data was preprocessed to correct for subject motion and the diffusion
+tensor model \cite{basser1994mr} was fit in every voxel, using a robust fit
+\cite{chang2005restore}. These data were acquired using a dual spin echo
+sequence, in which there is sufficient time for eddy currents to subside between
+the application of the gradients and the image acquisition, so no eddy current
+correction was appliced. We will refer to this dataset as WH.
 
@@
 Ethical Committee of the University ``Magna Graecia'' of Catanzaro. Voxel
-resolution was \num{2x2x2} $mm^3$ and 27 non-colinear directions were
-measured with a $b=1000$ $\frac{sec}{mm^2}$. Here, both motion correction and
-eddy current correction were applied before modeling the diffusioon tensor in
-each voxel. We will refer to this dataset as ALS.
+resolution was \num{2x2x2}\si{\milli\meter^3} and 27 non-colinear directions
+were measured with a $b=\SI{1000}{\second\per\milli\meter^2}$.
+Here, both motion correction and eddy current correction were
+applied before modeling the diffusioon tensor in each voxel. We will refer to
+this dataset as ALS.
 
@@
 criteria\cite{simon2013sparse}. It solves for a coefficient vector
-$\hat{\beta}$ that satisfies
+$\widehat{\beta}$ that satisfies
 \begin{equation}
-    \hat{\beta} = \min_\beta \frac{1}{2}
-    ||y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}||_2^2
+    \widehat{\beta} = \min_\beta \frac{1}{2}
+    \norm*{y - \displaystyle \sum_{\ell = 1}^{G}
+    \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}}_2^2
     + \lambda_1 \displaystyle \sum_{\ell = 1}^{G}
-    \sqrt{p_\ell} ||\beta^{(\ell)}||_2
-    + \lambda_2 ||\beta||_1,
+    \sqrt{p_\ell} \norm*{\beta^{(\ell)}}_2
+    + \lambda_2 \norm*{\beta}_1,
     \label{eq:sgl}
@@
 then optimized using the C-OPT library\cite{copt}. This supplies an estimate of
-the optimal $\hat{\beta}$ given a particular set of values for the
+the optimal $\widehat{\beta}$ given a particular set of values for the
 meta-parameters $\lambda_1$ and $\lambda_2$.
@@
 curve (ROC AUC) or the average precision. Using hyperoptimization, we find
-optimal regularization parameters and $\hat{\beta}$ for each
+optimal regularization parameters and $\widehat{\beta}$ for each
 train\textsubscript{outer} set and then use those to predict values for data in

### 2019-12-10 reports/manuscript/sections/methods.tex
Add error term to definition of linear model and use y-hat, beta-hat afterward to represent predictions

--- 2019-12-06 reports/manuscript/sections/methods.tex
@@
 
-After scaling and imputation, the tractometry data and target phenotypical data
-can be organized in a linear model:
-
+After scaling and imputation, the tractometry data and target
+phenotypical data can be organized in a linear model:
 \begin{equation}
-y = \mathbf{X} \cdot \beta,
+    y = \mathbf{X} \beta + \epsilon,
     \label{eq:lm}
 \end{equation}
-
-where $y$ is the phenotype -- categorical, such as a clinical diagnosis, or
-continuous numerical, such as the subject's age. The tractometry data is
-represented in the feature matrix $\mathbf{X}$, with rows corresponding to
-different subjects, and columns corresponding to diffusion measures at different
-nodes within each tract. The relationship between tractometric features and the
-phenotypic target is characterized by the coefficients in $\beta$. In general,
-the feature matrix $\mathbf{X}$ has dimensions $S \times (T \cdot N \cdot M)$,
-where $S$ is the number of subjects, $T$ is the number of white matter tracts,
-$N$ is the number of nodes in each tract, and $M$ is the number of diffusion
-metrics calculated at each node. Typically, $T = 20$, $N = 100$, and $2 \le M
-\le 8$, resulting in $\sim 4,000 - 16,000$  features. Conversely, many dMRI
-studies have between a few dozen and a few hundred subjects, yielding a feature
-matrix that is wide and short. Even in cases where more than a thousand subjects
-are measured (e.g., in the Human Connectome Project, where 1,200 subjects were
-measured \cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
+where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
+or continuous numerical, such as the subject's age. The tractometry
+data is represented in the feature matrix $\mathbf{X}$, with rows
+corresponding to different subjects, and columns corresponding
+to diffusion measures at different nodes within each tract. The
+relationship between tractometric features and the phenotypic target is
+characterized by the coefficients in $\beta$. The error term, $\epsilon$
+is an unobserved random variable that captures the error in the model.
+We denote our prediction of the targer phenotype as $\hat{y}$ and the
+coefficients that produce this prediction as $\hat{\beta}$, so that
+\begin{equation}
+    \hat{y} = \mathbf{X} \hat{\beta},
+    \label{eq:lm-approx}
+\end{equation}
+without the error term, $\epsilon$. In general, the feature matrix
+$\mathbf{X}$ has dimensions $S \times (T \times N \times M)$, where $S$
+is the number of subjects, $T$ is the number of white matter tracts,
+$N$ is the number of nodes in each tract, and $M$ is the number of
+diffusion metrics calculated at each node. Typically, $T = 20$, $N =
+100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 16,000$ features.
+Conversely, many dMRI studies have between a few dozen and a few
+hundred subjects, yielding a feature matrix that is wide and short.
+Even in cases where more than a thousand subjects are measured (e.g.,
+in the Human Connectome Project, where 1,200 subjects were measured
+\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
 of this data requires regularization to avoid overfitting and generate
@@
 
-Here, we propose that in addition to regularizing the coefficients in $\beta$,
-we can also capitalize on our knowledge of the group structure of the tract
-profile features in $\mathbf{X}$. The tract-metric combinations form a natural
-grouping. For example, we expect that MD features within the left arcuate
-fasciculus will co-vary across individuals. Likewise for FA values within the
-right corticospinal tract (CST) and so on. This group structure is represented
-in Fig~\ref{fig:group-structure}, which depicts the linear model $y = \mathbf{X}
-\cdot \beta$. Thus, we seek a regularization approach that will fit a linear
-model with anatomically-grouped covariates, where we expect to observe both
-groupwise sparsity, where the number of groups (tract/metric combinations) with
-at least one non-zero coefficients is small, as well as within-group sparsity,
-where the number of non-zero coefficients within each non-zero group is small.
-The sparse group lasso (SGL)
-is a penalized regression technique that satisfies exactly these
-criteria\cite{simon2013sparse}. It solves for a coefficient vector
+Here, we propose that in addition to regularizing the coefficients
+in $\hat{\beta}$, we can also capitalize on our knowledge of the
+group structure of the tract profile features in $\mathbf{X}$. The
+tract-metric combinations form a natural grouping. For example, we
+expect that MD features within the left arcuate fasciculus will
+co-vary across individuals. Likewise for FA values within the right
+corticospinal tract (CST) and so on. This group structure is represented
+in Fig~\ref{fig:group-structure}, which depicts the linear model
+$\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a regularization
+approach that will fit a linear model with anatomically-grouped
+covariates, where we expect to observe both groupwise sparsity, where
+the number of groups (tract/metric combinations) with at least one
+non-zero coefficients is small, as well as within-group sparsity, where
+the number of non-zero coefficients within each non-zero group is small.
+The sparse group lasso (SGL) is a penalized regression technique that
+satisfies exactly these criteria\cite{simon2013sparse}. It solves for a
+coefficient vector
 $\hat{\beta}$ that satisfies
@@
     ||y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \cdot \beta^{(\ell)}||_2^2
+    \mathbf{X}^{(\ell)} \beta^{(\ell)}||_2^2
     + \lambda_1 \displaystyle \sum_{\ell = 1}^{G}
@@
 \end{equation}
-
 where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix
@@
 the coefficient vector for group $\ell$ and $p_\ell$ is the length of
-$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \cdot M$ and
+$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and
 $\forall \ell: p_\ell = 100$. The first term is the mean square error
@@
     \caption{{\bf dMRI group structure.}
-        The phenotypical target data and tractometric features can be organized
-    into a linear model, $y = \mathbf{X} \cdot \beta$. The feature matrix
-    $\mathbf{X}$ is color-coded to reveal a natural group structure: the left
-    (orange) group contains $k$ features from the inferior fronto-occipital
-    fascicle (IFOF), the middle (green) group contains $k$ features from the
-    corpus callosum, and the right (blue) group contains $k$ features from the
-    uncinate. The coefficients in $\beta$ follow the same natural grouping.
-    Fascicle image reproduced with permission from Ref~\cite{yeatman2012tract}
-    Figure 1.}
+        The phenotypical target data and tractometric features can
+        be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the inferior fronto-occipital
+        fascicle (IFOF), the middle (green) group contains $k$ features
+        from the corpus callosum, and the right (blue) group
+        contains $k$ features from the uncinate. The coefficients in
+        $\hat{\beta}$ follow the same natural grouping. Fascicle image
+        reproduced with permission from Ref~\cite{yeatman2012tract}
+        Figure 1.
+    }
     \label{fig:group-structure}
@@
 
-Often, the target variable $y$ is not in the domain in which the linear model
-can be best fit to it. Equation \ref{eq:lm} can be slightly modified as:
+Often, the target variable $y$ is not in the domain in which the linear
+model can be best fit to it. Equation \ref{eq:lm-approx} can be slightly
+modified as:
 \begin{equation}
-y = f^-1(\mathbf{X} \cdot \beta),
-\label{eq:lm}
+    \hat{y} = f^-1(\mathbf{X} \hat{\beta}),
+    \label{eq:lm-transform}
 \end{equation}
-where the transformation function $f^{-1}$ characterizes the transform applied
-to the data before fitting the linear coefficients. For example, an often-used
-transform is the logarithmic transform:
+where the transformation function $f^{-1}$ characterizes the transform
+applied to the data before fitting the linear coefficients. For example,
+an often-used transform is the logarithmic transform:
 \begin{equation}
-f(y) = \log_n(y)
-\label{eq:log_nonlinearity}
+    f(\hat{y}) = \log_n(\hat{y})
+    \label{eq:log-nonlinearity}
 \end{equation}
-In this case, the model is parametrized by one additional fit parameter, $n$.
+In this case, the model is parametrized by one additional fit parameter,
+$n$.
 
@@
 \begin{equation}
-    p(y = 1) = \frac{1}{1 + \exp(\mathbf{X}\cdot \beta)},
+    p(\hat{y} = 1) = \frac{1}{1 + \exp(\mathbf{X} \hat{\beta})},
     \label{eq:logit}
@@
 test\textsubscript{inner}. We find the optimal values for $\lambda_1$ and
-$\lambda_2$ using hyperoptimizatin. This is implemented using the hyperopt
+$\lambda_2$ using hyperoptimization, implemented using the hyperopt
 library's \verb|fmin| function\cite{Bergstra_2015} with a tree of Parzen

### 2019-12-11 reports/manuscript/sections/conclusion.tex
Incorporates some of Jason's comments/suggestions.

@@
 
-We present here a novel method for analysis of dMRI tractometry data. This
-method relies on the Sparse Group Lasso \cite{simon2013sparse} to provide both
-accurate prediction of the phenotypic properties of individual subjects based on
-their dMRI data, but also provides interpretable results by identifying the
-features that are important across subjects to make these predictions. The
-method is broadly applicable: it performs well in predicting both continuous
-variables, such as biological age, as well as discrete variable, such as whether
-a person is a patient or a healthy control. In both of these cases, SGL
-out-performs previous algorithms that have been developed for these tasks
-\cite{sarica2017corticospinal, Richard2018-ux}. The nested cross-validation
-approach used to fit the model and make both predictioons and inferences from it
-guards against overfitting and tunes the degree of sparseness required by the
-algorithm, such that both phenomena that are locally focused in a particular
-anatomical location and a particular property of diffusion (e.g., FA in the
-CST), as well as widely distributed phenomena can be accurately captured.
+We present here a novel method for analysis of dMRI tractometry data that relies
+on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
+predictions of phenotypic properties of individual subjects while,
+simultaneously, (b) identifying the most important features of the white matter
+in a completely data-driven approach. Importantly, through the use of a nested
+cross-validation procedure, the method adapts to the constraints of small
+datasets while also leveraging the power of larger datasets. Moreover, the
+method is broadly applicable to a wide range of research questions: it performs
+well in predicting both continuous variables, such as biological age, as well as
+categorical variables, such as whether a person is a patient or a healthy control.
+In both of these cases, SGL out-performs previous algorithms that have been
+developed for these tasks \cite{sarica2017corticospinal, Richard2018-ux}. The
+nested cross-validation approach used to fit the model and make both predictions
+and inferences from it guards against overfitting and tunes the degree of
+sparseness required by the algorithm. This means that both phenomena that are
+locally focused in a particular anatomical location and a particular property of
+diffusion (e.g., FA in the CST), as well as widely distributed phenomena can be
+accurately captured.
 
@@
 \cite{sarica2017corticospinal}. In contrast, in analysis of biological age, the
-coefficients identified by the algorithm are very widely distributed in many
+coefficients identified by the algorithm are very widely distributed across many
 parts of the white matter, mirroring previous results with this dataset that
@@
 
-Meanwhile, neuroscience has entered an era in which consortium efforts are
-putting together large datasets of high-quality dMRI data to address a variety
-of scientific questions \cite{jernigan2016ping, jernigan2018abcd,
-alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
-these data pose a substantial challenge. Dimensionality reduction with
-tractometry, followed by analysis with the approach we present here promises to
-capitalize on the wealth of data and on the co-measurement of interesting and
-important phenotypical data about brain health and about the participants'
-cognitive abilities. We also expect the group-regularized approach to improve
-with larger datasets.
+Neuroscience has entered an era in which consortium efforts are putting together
+large datasets of high-quality dMRI data to address a variety of scientific
+questions \cite{jernigan2016ping, jernigan2018abcd, alexander2017open,
+Miller2016-hw, VanEssen2012}. The volume and complexity of these data pose a
+substantial challenge. Dimensionality reduction with tractometry, followed by
+analysis with the approach we present here promises to capitalize on the wealth
+of data and on the co-measurement of interesting and important phenotypical data
+about brain health and about the participants' cognitive abilities. We also
+expect the group-regularized approach to improve with larger datasets.
 
@@
 The method is packaged as open-source software called AFQ-Insight that is openly
-available, and this also where extensions of the method will be developed. The
+available, and provides a clear API to allow for extensions of the method. The
 sofware integrates within a broader automated fiber quantification software

### 2019-12-11 reports/manuscript/sections/introduction.tex
Incorporates some of Jason's comments/suggestions.

@@
 Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into
-the physical properties of the connections that comprise the brain white matter
-\cite{wandell2016clarifying}. Among the benefits of the method are the fact that
-it is non-invasive, and feasible to conduct in clinical scanners, and in wide
-variety of populations: healthy adults, but also clinical populations, as well
-as young or elderly subjects. While the measurements are usually conducted with
-voxels at the millimeter scale, within the diffusion time usually used, water
-molecules within each voxel can probe the structure of white matter at the
-micrometer scale, providing important information about the physical structure
-of the white matter, such as the distribution of fiber orientations within each
-voxel \cite{Frank2002-iz, Frank2001-xf}. With more sophisticated measurements
-that include several diffusion-weightings, more information can be extracted
-about the composition of different tissue type in the voxel
-\cite{Jeurissen2014-ab, Kaden2016-ho}. In addition, phenomenological
-descriptions of the diffusion properties, such as its mean diffusivity or
-fractional anisotropy can be derived from dMRI measurements
-\cite{Pierpaoli1996-vj}. Some of these descriptions are ambiguous in terms of
-their interpretation, as variance in these properties can relate to several
-different underlying physical causes. For example, fractional anisotropy can
-decrease both because of demyelination, but also because of decreased density,
-or because of partial volume with other tissue types or between crossing fiber
-populations \cite{Beaulieu1996-fn, Beaulieu2002-tl}. Even so, these descriptions
-have proven useful in characterizing individual differences or differences
-between populations \ariel{citation needed}.
+the physical properties of the connections that comprise the brain white matter.
+While the measurements are usually conducted with voxels at the millimeter
+scale, water molecules within each voxel probe the structure of white matter at
+the micrometer scale providing important information about the physical
+structure of the white matter, including  the distribution of fiber orientations
+and density of axons within each voxel \cite{wandell2016clarifying}. Even though
+metrics derived from diffusion measurements are ambiguous in terms of their
+underlying biological interpretation, analyzing the variance in these properties
+has proven useful in characterizing individual differences in cognitive
+function, characterizing differences between populations and detecting
+abnormalities associated with disease \cite{Thomason2011-qn}
 
@@
 Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel fiber
-bundles requires extraordinary evidence, and delineating the exact location of
-the termination of the streamlines in the gray matter is still prone to error,
-there is little dispute that tractography can accurately delineate major white
-matter bundles that are known to exist within the core of the white matter
+bundles requires extraordinary evidence, and delineating the exact cortical
+termination of the streamlines in the gray matter is still prone to error, there
+is little dispute that tractography can accurately define the location of major
+white matter bundles that are known to exist within the core of the white matter
 \cite{Maier-Hein2017-vb}.
@@
 tractometry begins by delineating the parts of the white matter that belong to
-different major tracts and axonal fiber bundles, such as the corticospinal tract
+different major tracts or axonal fiber bundles, such as the corticospinal tract
 or arcuate fasciculus, and samples the biophysical properties (such as
@@
 few tracts to compare in each individual, or even focusing on particular
-segments of these tracts. This approach is very powerful when the biological
-basis of the process of interest is relatively well understood (for a recent
-example, see \cite{huber2018rapid}).
+segments of these tracts based on \emph{a priori} hypotheses. This approach is
+very powerful when the biological basis of the process of interest is relatively
+well understood (for a recent example, see \cite{huber2018rapid}).
 
@@
 
-In the present work, we developed a novel framework for analysis of tractometry
-that simultaneously selects the features for analysis, and fits a model to these
-features. Rather than a comparative approach, this framework takes a predictive
-approach to inference \cite{Breiman2001-uz}. We use a linear modeling approach,
-which aims to predict phenotypical variance in a group of subjects, based on a
-linear combination of the features estimated with tractometry. Using this
-approach, we need to first deal with the large and asymmetric dimensionality of
-the data: tractometry data usually has many more features (i.e., number of
-measurements per individual) than samples (number of subjects), which makes
-inferences from the data about phenotypical differences between individuals
-ill-posed. This regime is the target of several statistical learning techniques,
-and is often solved by various forms of regularization. For example, Tikhonov
-regularization shrinks the solution such that the sum of squared contributions
-from the individual features are minimized \cite{Hoerl2000-ij}. Another solution
-to the problem is provided by the Lasso algorithm, which instead minimizes the
-sum of the absolute values of contributions of each feature
-\cite{Tibshirani1996-qs}. This tends to shrink to zero the contributions of many
-of the features, providing results that are both accurate and interpretable.
-When additional structure is available in the organization of the data,
-regularization algorithms can take advantage of this structure. For example, if
-the features lend themselves to a natural division into different groups, the
-group lasso (GL) can be used to select groups of features, rather than
-individual features \cite{Yuan2006-ky}. The Sparse Group Lasso (SGL) elaborates
-on this idea by providing control both of group sparsity, as well as overall
-sparsity of the solutions \cite{simon2013sgl}. Because the features measured
-with tractomery lend themselves to grouping based on the tracts from which each
-measurement is taken, GL and SGL provide a useful tool linear model fitting in
-problems of this form. Using linear regression as the basis for analysis is
-useful for both regression tasks, in which a continuous measure (e.g., age) is
-modeled, as well as for classification tasks, where a discrete property is
-modeled (e.g., whether an individual has a particular disease). Moreover, use of
-SGL helps derive informative properties of the human white matter, both in cases
-where the underlying causes of variance are sparsely concentrated (e.g., in one
-particular white matter tract) and in cases where biological substrates of
-differences between individuals are more widespread. This is because SGL is
-controlled by meta-parameters that set the degree to which group sparsity and
-overall sparsity are applied. These metaparameters can be set empirically, based
-on the data, through a process of nested cross-validation. We demonstrate these
-properties of the algorithm in data from previously published studies
-\cite{sarica2017corticospinal, yeatman2014lifespan}.
+Ideally, we would like a method that simultaneously capitalizes on all the data
+across all tracts to make the best possible prediction, while also retaining and
+surfacing spatial information about the locations that are most informative for
+a prediction. In the present work, we developed a novel framework for analysis
+of tractometry that simultaneously selects the features for analysis, and fits a
+model to these features. Rather than a comparative approach, this framework
+takes a predictive approach to inference \cite{Breiman2001-uz}. We use a linear
+modeling approach, which aims to predict phenotypical variance in a group of
+subjects, based on a linear combination of the features estimated with
+tractometry. Using this approach, we need to first deal with the large and
+asymmetric dimensionality of the data: tractometry data usually has many more
+features (i.e., number of measurements per individual) than samples (number of
+subjects), which makes inferences from the data about phenotypical differences
+between individuals ill-posed. This regime is the target of several statistical
+learning techniques, and is often solved by various forms of regularization. For
+example, Tikhonov regularization shrinks the solution such that the sum of
+squared contributions from the individual features are minimized
+\cite{Hoerl2000-ij}. Another solution to the problem is provided by the Lasso
+algorithm, which instead minimizes the sum of the absolute values of
+contributions of each feature \cite{Tibshirani1996-qs}. This tends to shrink to
+zero the contributions of many of the features, providing results that are both
+accurate and interpretable. When additional structure is available in the
+organization of the data, regularization algorithms can take advantage of this
+structure. For example, if the features lend themselves to a natural division
+into different groups, the group lasso (GL) can be used to select groups of
+features, rather than individual features \cite{Yuan2006-ky}. The Sparse Group
+Lasso (SGL) elaborates on this idea by providing control both of group sparsity,
+as well as overall sparsity of the solutions \cite{simon2013sgl}. Because the
+features measured with tractomery lend themselves to grouping based on the
+tracts from which each measurement is taken, GL and SGL provide a useful tool
+linear model fitting in problems of this form. Using linear regression as the
+basis for analysis is useful for both regression tasks, in which a continuous
+measure (e.g., age) is modeled, as well as for classification tasks, where a
+discrete property is modeled (e.g., whether an individual has a particular
+disease). Moreover, use of SGL helps derive informative properties of the human
+white matter, both in cases where the underlying causes of variance are sparsely
+concentrated (e.g., in one particular white matter tract) and in cases where
+biological substrates of differences between individuals are more widespread.
+This is because SGL is controlled by meta-parameters that set the degree to
+which group sparsity and overall sparsity are applied. These metaparameters can
+be set empirically, based on the data, through a process of nested
+cross-validation. We demonstrate these properties of the algorithm in data from
+previously published studies \cite{sarica2017corticospinal,
+yeatman2014lifespan}.

### 2019-12-11 reports/manuscript/sections/methods.tex
Incorporates some of Jason's comments/suggestions.

@@
 Matlab Automated Fiber Quantification toolbox (AFQ) \cite{yeatman2012tract}:
-streamlines representing fascicles of white matter nerve fibers were generated
+streamlines representing fascicles of white matter tracts were generated
 using a determinstic tractography algorithm that follows the prinicpal diffusion
@@
 between zero and one and could be overwhelmed by an unscaled higher-variance
-metric like the mean diffusivity (MD). To prevent this, we use the
-\lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}, to remove each
-feature's mean and scale it to unit variance. Scaling is performed separately
-within each cross-validation set's training or testing data to prevent leakage
-of information between the testing and training sets\cite{kaufman2012leakage}.
+metric like the mean diffusivity (MD). To prevent this we remove each feature's
+mean and scale it to unit variance (z-score) using the
+\lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}. Scaling is
+performed separately within each cross-validation set's training or testing data
+to prevent leakage of information between the testing and training
+sets\cite{kaufman2012leakage}.
 

### 2019-12-11 reports/manuscript/sections/results.tex
Incorporates some of Jason's comments/suggestions.

@@
 
-To test the performance of SGL in tractometry data in a continuous regression
-task, we focus here on the prediction of biological age from the tractometry
+To test the performance of SGL with tractometry data in a continuous regression
+task, we focus here on the prediction of biological age based on tractometry
 data. Prediction of ``brain age'' is a commonly undertaken task. This is both
@@
 the parameters are fixed, the model is inverted to predict the ages of held out
-subjects based on the linear coeffiecients and the static non-linearity.
-This scheme automatically finds the right level of regularization and
-fits the coefficients to the ill-posed linear model, while guarding against
+subjects based on the linear coeffiecients and the static non-linearity. This
+scheme automatically finds the right level of regularization (i.e., sparseness)
+and fits the coefficients to the ill-posed linear model, while guarding against
 overfitting. SGL accurately predicts the age of the subjects in this procedure,

### 2019-12-11 reports/manuscript/sections/conclusion.tex
Adds a cite to Chamberland's work.
Anticipates future work on unsupervised methods.
Add a period at the end of the last sentence.

@@
 extending the cost function used here to incorporate these constraints.
+Similarly, unsupervised dimensionality reduction \cite{Chamberland2019-mu} could
+also benefit from constraints based on grouping.
 
@@
 \url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
-notebooks
-\cite{kluyver2016jupyter}
+notebooks \cite{kluyver2016jupyter}.

### 2019-12-12 reports/manuscript/sections/conclusion.tex
One more pass through

@@
 predictions of phenotypic properties of individual subjects while,
-simultaneously, (b) identifying the most important features of the white matter
-in a completely data-driven approach. Importantly, through the use of a nested
-cross-validation procedure, the method adapts to the constraints of small
-datasets while also leveraging the power of larger datasets. Moreover, the
-method is broadly applicable to a wide range of research questions: it performs
-well in predicting both continuous variables, such as biological age, as well as
-categorical variables, such as whether a person is a patient or a healthy control.
-In both of these cases, SGL out-performs previous algorithms that have been
-developed for these tasks \cite{sarica2017corticospinal, Richard2018-ux}. The
-nested cross-validation approach used to fit the model and make both predictions
-and inferences from it guards against overfitting and tunes the degree of
-sparseness required by the algorithm. This means that both phenomena that are
-locally focused in a particular anatomical location and a particular property of
-diffusion (e.g., FA in the CST), as well as widely distributed phenomena can be
-accurately captured.
+simultaneously, (b) identifying the features of the white matter that are most
+important for this prediction in a completely data-driven approach. The method
+is broadly applicable to a wide range of research questions: it performs well in
+predicting both continuous variables, such as biological age, as well as
+categorical variables, such as whether a person is a patient or a healthy
+control. In both of these cases, SGL out-performs previous algorithms that have
+been developed for these tasks \cite{sarica2017corticospinal, Richard2018-ux}.
+The nested cross-validation approach used to fit the model and make both
+predictions and inferences from the model guards against overfitting and tunes
+the degree of sparseness required by the algorithm. This means that SGL can
+accurately describe phenomena that are locally confined to a particular
+anatomical location or diffusion property (e.g., FA in the CST) as well as
+phenomena that are widely distributed amongst brain regions and measured
+diffusion properties.
 
@@
 cortico-spinal tract. This recapitulates the results of previous analysis of
-these same data, using a targetted ROI-based approach
+these same data, using a targeted ROI-based approach
 \cite{sarica2017corticospinal}. In contrast, in analysis of biological age, the
@@
 regression approach. Even at the scale of dozens of subjects, the results
-provided by SGL are both accurate and interpretable. Thus, this multivariate
-analysis approach both (a) achieves high cross-validated accuracy for precision
-medicine applications of dMRI data and (b) identifies relevant features of brain
-anatomy that can further our neuroscientific understanding of clinical
-disorders.
+provided by SGL are both accurate, as well as interpretable
+\cite{Murdoch2019-ax}: tractometry capitalizes on domain knowledge to engineer
+meaningful features; SGL scores these features based on their relative
+importance; enables a visualization of these feature importance scores in the
+anatomical coordinate frame of the tracts (e.g., Figures \ref{fig:class-results}
+and fig:regress-beta) and provides a means to understand model errors (e.g.,
+Figure \ref{fig:class-errors}) . Thus, this multivariate analysis approach both
+(a) achieves high cross-validated accuracy for precision medicine applications
+of dMRI data and (b) identifies relevant features of brain anatomy that can
+further our neuroscientific understanding of clinical disorders.
 
 Neuroscience has entered an era in which consortium efforts are putting together
-large datasets of high-quality dMRI data to address a variety of scientific
-questions \cite{jernigan2016ping, jernigan2018abcd, alexander2017open,
-Miller2016-hw, VanEssen2012}. The volume and complexity of these data pose a
-substantial challenge. Dimensionality reduction with tractometry, followed by
-analysis with the approach we present here promises to capitalize on the wealth
-of data and on the co-measurement of interesting and important phenotypical data
-about brain health and about the participants' cognitive abilities. We also
-expect the group-regularized approach to improve with larger datasets.
+large datasets of high-quality dMRI measurments to address a variety of
+scientific questions \cite{jernigan2016ping, jernigan2018abcd,
+alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
+these data pose a substantial challenge. Dimensionality reduction with
+tractometry, followed by analysis with the approach we present here promises to
+capitalize on the wealth of data and on the co-measurement of interesting and
+important phenotypical data about brain health and about the participants'
+cognitive abilities. We also expect the group-regularized approach to improve
+with larger datasets.
 
@@
 extending the cost function used here to incorporate these constraints.
-Similarly, unsupervised dimensionality reduction \cite{Chamberland2019-mu} could
-also benefit from constraints based on grouping.
+Similarly, unsupervised dimensionality reduction of tractometry data (e.g.,
+\cite{Chamberland2019-mu}) could also benefit from constraints based on
+grouping.
 

### 2019-12-12 reports/manuscript/sections/conclusion.tex

@@
 Neuroscience has entered an era in which consortium efforts are putting together
-large datasets of high-quality dMRI measurments to address a variety of
+large datasets of high-quality dMRI measurements to address a variety of
 scientific questions \cite{jernigan2016ping, jernigan2018abcd,

### 2019-12-12 reports/manuscript/sections/introduction.tex

@@
 the micrometer scale providing important information about the physical
-structure of the white matter, including  the distribution of fiber orientations
-and density of axons within each voxel \cite{wandell2016clarifying}. Even though
-metrics derived from diffusion measurements are ambiguous in terms of their
-underlying biological interpretation, analyzing the variance in these properties
-has proven useful in characterizing individual differences in cognitive
-function, characterizing differences between populations and detecting
-abnormalities associated with disease \cite{Thomason2011-qn}
+structure of the white matter, including the density of axons and distribution
+of nerve fascicle orientations within each voxel \cite{wandell2016clarifying}.
+Even though metrics derived from diffusion measurements are ambiguous in terms
+of their underlying biological interpretation \cite{Jones2013-xv}, analyzing the
+variance in these properties has proven useful in characterizing individual
+differences in cognitive function, characterizing differences between
+populations and detecting brain abnormalities associated with disease
+\cite{Thomason2011-qn}.
 
@@
 tract-tracing from diffusion MRI, or tractography, combine the estimates of
-fiber orientations in each voxel to form streamlines that traverse the volume of
-the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods have been
+fascicle orientations in each voxel to form streamlines that traverse the volume
+of the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods have been
 under increased scrutiny and several lines of investigation have raised
@@
 methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
-Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel fiber
+Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel nerve fiber
 bundles requires extraordinary evidence, and delineating the exact cortical
 termination of the streamlines in the gray matter is still prone to error, there
-is little dispute that tractography can accurately define the location of major
-white matter bundles that are known to exist within the core of the white matter
-\cite{Maier-Hein2017-vb}.
+is little dispute that tractography can accurately define the location of
+several major white matter bundles that are known to exist within the core of
+the white matter \cite{Maier-Hein2017-vb}.
 
@@
 different available implementations of this overall idea, the principles are
-similar \cite{yeatman2012tract, Yendiki2011-ay, Wassermann2016-iv, ODonnell2009-uu}:
-tractometry begins by delineating the parts of the white matter that belong to
-different major tracts or axonal fiber bundles, such as the corticospinal tract
-or arcuate fasciculus, and samples the biophysical properties (such as
-fractional anisotropy or mean diffusivity) along the length of these bundles. In
-some cases, tissue properties along the length of each bundle are summarized by
-taking the mean along each bundle, but there is a large body of evidence showing
-that there is systematic variability within each bundle. This justifies
-retaining the individual samples along the length of each fiber
-\cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this retains
+similar \cite{yeatman2012tract, Yendiki2011-ay, Wassermann2016-iv,
+ODonnell2009-uu}: tractometry begins by delineating the parts of the white
+matter that belong to different major tracts or axonal nerve fiber bundles, such
+as the corticospinal tract or arcuate fasciculus, and samples the biophysical
+properties (such as fractional anisotropy or mean diffusivity) along the length
+of these bundles. In some cases, tissue properties along the length of each
+bundle are summarized by taking the mean along each bundle, but there is a large
+body of evidence showing that there is systematic variability within each
+bundle. This justifies retaining the individual samples along the length of each
+bundle \cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this retains
 important information about each individual's white matter, it also presents
@@
 across individuals are done at each node of each tract, for each one of the
-diffusion metrics available at that point. This approach is exhaustive, but the
-challenge with this approach is that the are multiple points to compare, and
+diffusion metrics available at that point. This approach is exhaustive, but
 statistical power is compromised by a multiple comparison problem. Different
@@
 colleagues \cite{colby2012} used a non-parametric resmapling approach to correct
-for family-wise error across the universe of different comparisons available in
-the mass univariate approach \cite{Nichols2002-zu, Nichols2003-yy}.
+for family-wise error across the different possible comparisons
+\cite{Nichols2002-zu, Nichols2003-yy}.
 
-\item ROI-based approach: An alternative is using an ROI based approach. In this
-approach, the multiple comparison problem is circumvented by selecting just a
-few tracts to compare in each individual, or even focusing on particular
-segments of these tracts based on \emph{a priori} hypotheses. This approach is
-very powerful when the biological basis of the process of interest is relatively
-well understood (for a recent example, see \cite{huber2018rapid}).
+\item Region of interest(ROI)-based approaches: An alternative that circumvents
+the multiple comparison problem is to select just a few tracts to compare in
+each individual, or even focusing on particular segments of these tracts based
+on \emph{a priori} hypotheses. This approach is very powerful when the
+biological basis of the process of interest is relatively well understood (for a
+recent example, see \cite{huber2018rapid}).
 
-\item ROI-based selection, followed by multivariate analysis. Here, an ROI is
+\item ROI-based selection, followed by multivariate analysis: Here, an ROI is
 selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
@@
 
-Ideally, we would like a method that simultaneously capitalizes on all the data
-across all tracts to make the best possible prediction, while also retaining and
-surfacing spatial information about the locations that are most informative for
-a prediction. In the present work, we developed a novel framework for analysis
-of tractometry that simultaneously selects the features for analysis, and fits a
-model to these features. Rather than a comparative approach, this framework
-takes a predictive approach to inference \cite{Breiman2001-uz}. We use a linear
-modeling approach, which aims to predict phenotypical variance in a group of
-subjects, based on a linear combination of the features estimated with
-tractometry. Using this approach, we need to first deal with the large and
-asymmetric dimensionality of the data: tractometry data usually has many more
-features (i.e., number of measurements per individual) than samples (number of
-subjects), which makes inferences from the data about phenotypical differences
-between individuals ill-posed. This regime is the target of several statistical
-learning techniques, and is often solved by various forms of regularization. For
-example, Tikhonov regularization shrinks the solution such that the sum of
-squared contributions from the individual features are minimized
-\cite{Hoerl2000-ij}. Another solution to the problem is provided by the Lasso
-algorithm, which instead minimizes the sum of the absolute values of
-contributions of each feature \cite{Tibshirani1996-qs}. This tends to shrink to
-zero the contributions of many of the features, providing results that are both
-accurate and interpretable. When additional structure is available in the
-organization of the data, regularization algorithms can take advantage of this
-structure. For example, if the features lend themselves to a natural division
-into different groups, the group lasso (GL) can be used to select groups of
-features, rather than individual features \cite{Yuan2006-ky}. The Sparse Group
-Lasso (SGL) elaborates on this idea by providing control both of group sparsity,
-as well as overall sparsity of the solutions \cite{simon2013sgl}. Because the
-features measured with tractomery lend themselves to grouping based on the
-tracts from which each measurement is taken, GL and SGL provide a useful tool
-linear model fitting in problems of this form. Using linear regression as the
-basis for analysis is useful for both regression tasks, in which a continuous
-measure (e.g., age) is modeled, as well as for classification tasks, where a
-discrete property is modeled (e.g., whether an individual has a particular
-disease). Moreover, use of SGL helps derive informative properties of the human
-white matter, both in cases where the underlying causes of variance are sparsely
-concentrated (e.g., in one particular white matter tract) and in cases where
-biological substrates of differences between individuals are more widespread.
-This is because SGL is controlled by meta-parameters that set the degree to
-which group sparsity and overall sparsity are applied. These metaparameters can
-be set empirically, based on the data, through a process of nested
-cross-validation. We demonstrate these properties of the algorithm in data from
-previously published studies \cite{sarica2017corticospinal,
-yeatman2014lifespan}.
+Generally speaking analysis methods should balance predictive accuracy with
+descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}. Accordingly,
+tractometry analysis should simultaneously capitalize on all the data across all
+tracts to make the best possible prediction, while also retaining and surfacing
+spatial information about the locations that are most informative for a
+prediction. In the present work, we developed a novel framework for analysis of
+tractometry that simultaneously selects the features for analysis, and fits a
+model to these features. We use a linear modeling approach, which aims to
+predict phenotypical variance in a group of subjects, based on a linear
+combination of the features estimated with tractometry. Using this approach, we
+need to first deal with the large and asymmetric dimensionality of the data:
+tractometry data usually has many more features (i.e., number of measurements
+per individual) than samples (number of subjects), which makes inferences from
+the data about phenotypical differences between individuals ill-posed. This
+regime is the target of several statistical learning techniques, and is often
+solved by various forms of regularization. For example, Tikhonov regularization
+shrinks the solution such that the sum of squared contributions from the
+individual features are minimized \cite{Hoerl2000-ij}. Another solution to the
+problem is provided by the Lasso algorithm, which instead minimizes the sum of
+the absolute values of contributions of each feature \cite{Tibshirani1996-qs}.
+This tends to shrink to zero the contributions of many of the features,
+providing results that are both accurate and interpretable. When additional
+structure is available in the organization of the data, regularization
+algorithms can take advantage of this structure. For example, if the features
+lend themselves to a natural division into different groups, the group lasso
+(GL) can be used to select groups of features, rather than individual features
+\cite{Yuan2006-ky}. The Sparse Group Lasso (SGL) elaborates on this idea by
+providing control both of group sparsity, as well as overall sparsity of the
+solutions \cite{simon2013sgl}. Because the features measured with tractomery
+lend themselves to grouping based on the tracts from which each measurement is
+taken, GL and SGL provide a useful tool linear model fitting in problems of this
+form. Using linear regression as the basis for analysis is useful for both
+regression tasks, in which a continuous measure (e.g., age) is modeled, as well
+as for classification tasks, where a discrete property is modeled (e.g., whether
+an individual has a particular disease). Moreover, use of SGL helps derive
+informative properties of the human white matter, both in cases where the
+underlying causes of variance are sparsely concentrated (e.g., in one particular
+white matter tract) and in cases where biological substrates of differences
+between individuals are more widespread. This is because SGL is controlled by
+meta-parameters that set the degree to which group sparsity and overall sparsity
+are applied. These metaparameters can be set empirically, based on the data,
+through a process of nested cross-validation. We demonstrate these properties of
+the algorithm in data from previously published studies
+\cite{sarica2017corticospinal, yeatman2014lifespan}.

### 2019-12-12 reports/manuscript/sections/results.tex

@@
 \section*{Results and discussion}
+
+We developed a method for analyzing dMRI tractometry data with SGL. We
+demonstrate the use of this method on two previously published datasets in both
+a classification setting and a regression setting.
+
+\subsection*{SGL accurately detects ALS in tractometry data in a classification setting}
+
+Using data from a previous study of the corticospinal tract (CST) profile and
+ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
+classification setting. The previous study predicted ALS status with a mean
+accuracy of 80\% using a random forest algorithm based on a priori selection of
+features within the corticospinal tract. SGL delivers competitive predictive
+performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC AUC) without
+the need for a priori feature engineering. The results of the classification
+prediction are shown in Figure \ref{fig:class-results} with ``ground-truth'' ALS
+status separated into columns, and predicted ALS status encoded by color. In
+addition to this classification performance, SGL also identifies the white
+matter tracts most important for ALS classification. The relative importance of
+white matter features is captured in the $\beta$ coefficients from
+Eq~\eqref{eq:sgl}. Figure \ref{fig:class-profiles} depicts these coefficients along
+the right CST, plotted over the FA values for the control and ALS subject
+groups. We find that SGL selects FA metrics in the corticospinal tract and
+particularly in the right corticospinal tract as most important to ALS
+classification, confirming previous findings\cite{van2011upper,
+toosy2003diffusion, sarica2014tractography, sage2007quantitative,
+sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
+cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
+identifying the portions of the brain that were selected \emph{a priori} in the
+previous study from which we collected our data\cite{sarica2017corticospinal}.
+
+Analyzing the ways in which the model mislabels individuals may also provide
+insight. We found that mislabelled subjects are outliers relative to their group
+with respect to diffusion features of the CST. Figure \ref{fig:class-errors}
+depicts the group FA values along with FA values of mislabelled subjects, two
+false negatives and one false-positive. The false negative classifications have
+high FA in one of the two sections of the CST where $||\hat{\beta}|| > 0$ in
+Figure \ref{fig:class-profiles}. The false positive subject has an FA that
+oscillates between the two group means. Thus, the SGL method fails
+comprehensibly.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.45\textwidth]{classification_probs.png}
+    \includegraphics[width=0.45\textwidth]{classification_beta_bupu.png}
+
+    \caption{{\bf SGL accurately predicts ALS.}
+        Left: Classification probabilities for each subject's ALS diagnosis.
+        Controls are on the left while patients are on the right. Predicted
+        controls are in blue and predicted patients are in red. Thus, false
+        positive are represented as red dots on the left, while false negatives
+        are represented as blue dots on the right. The SGL algorithm achieves
+        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
+        coefficients are presented on a skeleton of the major tracts. The brain
+        is oriented with the right hemisphere to our left and anterior out of
+        the page. As expected large negative coefficients are in the FA of the
+        CST (and particularly in the right hemisphere, here to the left)}
+    \label{fig:class-results}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
+    \caption{{\bf Model coefficients mirror FA differences}. The places along the
+       length of the CST  where $\hat{\beta}$ coefficients for FA
+       (dashed line, right axis) have large negative values correspond to the
+       locations of substantial differences between the ALS (green) and control
+       (orange) FA (shaded area indicates standard error of the mean).}
+    \label{fig:class-profiles}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
+    \caption{{\bf Model mis-classifications correspond to features identified by
+       the model}. The FA in CST of individuals that are mis-classified by the
+       model is compared the group FA (with shaded are indicating standard error
+       of the mean). False negative classifications (individuals that have ALS,
+       but are classified as patients) correspond to high FA either in one of
+       the two regions of large $||\hat{\beta}||$ in
+       Figure \ref{fig:class-profiles}. The false positive classification has
+       an FA profile that oscillates between the two group means.
+   }
+    \label{fig:class-errors}
+\end{figure}
 
@@
 \end{figure}
-
-\subsection*{SGL accurately detects ALS in tractometry data in a classification setting}
-
-Using data from a previous study of the corticospinal tract (CST) profile and
-ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
-classification setting. The previous study predicted ALS status with a mean
-accuracy of 80\% using a random forest algorithm based on a priori selection of
-features within the corticospinal tract. SGL delivers competitive predictive
-performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC AUC) without
-the need for a priori feature engineering. The results of the classification
-prediction are shown in Fig~\ref{fig:class-results} with ``ground-truth'' ALS
-status separated into columns, and predicted ALS status encoded by color. In
-addition to this classification performance, SGL also identifies the white
-matter tracts most important for ALS classification. The relative importance of
-white matter features is captured in the $\beta$ coefficients from
-Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-profiles} depicts these coefficients along
-the right CST, plotted over the FA values for the control and ALS subject
-groups. We find that SGL selects
-FA metrics in the corticospinal tract and particualrly in the right
-corticospinal tract as most important to ALS classification, confirming previous
-findings\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
-sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
-ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
-abe2010voxel} and identifying exactly the portions of the brain that were
-selected \emph{a priori} in the previous study from which we collected our
-data\cite{sarica2017corticospinal}.
-
-We also find that mislabelled subjects correspond to outlying features in the
-CST. Fig~\ref{fig:class-errors} depicts the group FA values along with
-FA values of mislabelled subjects, two false negatives and one false-positive.
-The false negative classifications have high FA in one of the two sections of
-the CST where $||\hat{\beta}|| > 0$ in Fig~\ref{fig:class-profiles}.
-The false positive subject has an FA that oscillates between the two group
-means. Thus, the SGL method fails comprehensibly.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.45\textwidth]{classification_probs.png}
-    \includegraphics[width=0.45\textwidth]{classification_beta_bupu.png}
-
-    \caption{{\bf SGL accurately predicts ALS.}
-        Left: Classification probabilities for each subject's ALS diagnosis.
-        Controls are on the left while patients are on the right. Predicted
-        controls are in blue and predicted patients are in red. Thus, false
-        positive are represented as red dots on the left, while false negatives
-        are represented as blue dots on the right. The SGL algorithm achieves
-        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
-        coefficients are presented on a skeleton of the major tracts. The brain
-        is oriented with the right hemisphere to our left and anterior out of
-        the page. As expected large negative coefficients are in the FA of the
-        CST (and particularly in the right hemisphere, here to the left)}
-    \label{fig:class-results}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
-    \caption{{\bf Model coefficients mirror FA differences}. The places along the
-       length of the CST  where $\hat{\beta}$ coefficients for FA
-       (dashed line, right axis) have large negative values correspond to the
-       locations of substantial differences between the ALS (green) and control
-       (orange) FA (shaded area indicates standard error of the mean).}
-    \label{fig:class-profiles}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
-    \caption{{\bf Model mis-classifications correspond to features identified by
-       the model}. The FA in CST of individuals that are mis-classified by the
-       model is compared the group FA (with shaded are indicating standard error
-       of the mean). False negative classifications (individuals that have ALS,
-       but are classified as patients) correspond to high FA either in one of
-       the two regions of large $||\hat{\beta}||$ in
-       Fig~\ref{fig:class-profiles}. The false positive classification has
-       an FA profile that oscillates between the two group means.
-   }
-    \label{fig:class-errors}
-\end{figure}

### 2019-12-12 reports/manuscript/abstract.tex
Incorporate Jason's round 2 edits

@@
 The white matter contains long-range connections between different
-brain regions. Tractometry uses diffusion-weighted magnetic resonance
-imaging (dMRI) data to quantify tissue properties (e.g. fractional
-anisotropy (FA), mean diffusivity (MD), etc.), along the trajectories
-of these connections\cite{yeatman2012tract}. Statistical inference from
+brain regions and the organization of these connections hold important
+implications for brain function in health and disease. Tractometry
+uses diffusion-weighted magnetic resonance imaging (dMRI) data
+to quantify tissue properties (e.g. fractional anisotropy (FA),
+mean diffusivity (MD), etc.), along the trajectories of these
+connections\cite{yeatman2012tract}. Statistical inference from
 tractometry data usually either (a) averages these quantities along
@@
 features by enforcing sparsity, not only at the level of individual
-tracts and tissue properties, but also across the entire set of tracts
-and all of the measured tissue properties. The sparsity penalties for
-each of these constraints is identified using a nested cross-validation
-scheme that guards against over-fitting and simultaneously identifies
-the correct level of sparsity. We demonstrate the accuracy of the method
-in two settings: in a regression setting, dMRI is used to accurately
-predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In this
-case, the weights are distributed throughout the white matter indicating
-that many different regions of the white matter change with development
+tracts, but also across the entire set of tracts and all of the measured
+tissue properties. The sparsity penalties for each of these constraints
+is identified using a nested cross-validation scheme that guards
+against over-fitting and simultaneously identifies the correct level of
+sparsity. We demonstrate the accuracy of the method in two settings:
+in a regression setting, dMRI is used to accurately predict ``brain
+age'' \cite{yeatman2014lifespan, Brown2012-so}. In this case, the
+weights are distributed throughout the white matter indicating that
+many different regions of the white matter change with development
 and contribute to the prediction of age. In a classification setting,

### 2019-12-12 reports/manuscript/sections/conclusion.tex
Incorporate Jason's round 2 edits

@@
 
-Specifically, we demonstrated that the algorithm correctly detects the fact that
-ALS, which is a disease of lower motor neurons, is localized to the
-cortico-spinal tract. This recapitulates the results of previous analysis of
-these same data, using a targeted ROI-based approach
-\cite{sarica2017corticospinal}. In contrast, in analysis of biological age, the
-coefficients identified by the algorithm are very widely distributed across many
-parts of the white matter, mirroring previous results with this dataset that
-show a large and continuous distribution of life-span changes in white matter
-properties \cite{yeatman2014lifespan}.
+Specifically, we demonstrated that the algorithm correctly detects
+the fact that ALS, which is a disease of lower motor neurons, is
+localized to the cortico-spinal tract. This recapitulates the results
+of previous analysis of these same data, using a targeted ROI-based
+approach \cite{sarica2017corticospinal}. In contrast, for the analysis
+of biological age, the coefficients identified by the algorithm are very
+widely distributed across many parts of the white matter, mirroring
+previous results with this dataset (and others) that show a large and
+continuous distribution of life-span changes in white matter properties
+\cite{yeatman2014lifespan}.
 
@@
 
-SGL has many other potential applications in neuroscience, because of the
-hierarchical and grouped nature of many of the data -- that are collected in
-multiple sample points within anatomically-defined areas. For example, this
-method may be useful to understand the relationship between fMRI recordings and
-behavior, where activity in each voxel may co-vary with voxels within the same
-anatomical region and form features and groups of features. Similarly,
-large-scale multi-electrode recordings of neural activity in awake behaving
-animals are becoming increasingly feasible \cite{steinmetz2018distributed,
-Jun2017-gv} and these recordings can form features (neurons) and groups (neurons
-within an anatomical region). More ambitiously perhaps, this approach may be
-used to understand the role of correlations in so-called resting-state fMRI
-time-series and behavior, where pairwise correlations between voxels in
-different anatomical regions are features in the matrix and features may be
-grouped by pairs of anatomical regions. Given the large number of voxels in the
-surface of the gray matter, and given that correlations increase the number of
-features by a factor of $n^2$ this would be a challenging problem to solve using
-SGL.
+SGL has many other potential applications in neuroscience, because
+of the hierarchical and grouped nature of many data types that are
+collected in multiple sample points within anatomically-defined areas.
+For example, this method may be useful to understand the relationship
+between fMRI recordings and behavior, where activity in each voxel
+may co-vary with voxels within the same anatomical region and form
+features and groups of features. Similarly, large-scale multi-electrode
+recordings of neural activity in awake behaving animals are becoming
+increasingly feasible \cite{steinmetz2018distributed, Jun2017-gv} and
+these recordings can form features (neurons) and groups (neurons within
+an anatomical region). More ambitiously perhaps, this approach may be
+used to understand the role of correlations in so-called resting-state
+fMRI time-series and behavior, where pairwise correlations between
+voxels in different anatomical regions are features in the matrix and
+features may be grouped by pairs of anatomical regions. Given the large
+number of voxels in the surface of the gray matter and given that
+correlations increase the number of features by a factor of $n^2$, this
+would pose a challenging problem to solve using SGL.
 
@@
 
-The method is packaged as open-source software called AFQ-Insight that is openly
-available, and provides a clear API to allow for extensions of the method. The
-sofware integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract}, which extracts tractometry data from raw
-and processed dMRI datasets, as well as AFQ-Browser, which visualizes
+The method is packaged as open-source software called AFQ-Insight
+that is openly available, and provides a clear API to allow
+for extensions of the method. The sofware integrates within a
+broader automated fiber quantification software ecosystem: AFQ
+\cite{yeatman2012tract}, which extracts tractometry data from raw and
+processed dMRI datasets, as well as AFQ-Browser, which visualizes
 tractometry data and facilitates sharing of the results of dMRI studies
-\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
-software, the results presented in this paper are also provided in
-\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
-notebooks \cite{kluyver2016jupyter}.
+\cite{yeatman2018browser}. To facilitate reproducibility and ease use
+of the software, the results presented in this paper are also provided
+in \url{https://github.com/richford/afq-insight-paper} as a series of
+Jupyter notebooks \cite{kluyver2016jupyter}.

### 2019-12-12 reports/manuscript/sections/introduction.tex
Incorporate Jason's round 2 edits

@@
 
-Using this fact, one of the most powerful methods currently available to put
-macro- and micro-structure together is \emph{tractometry} (also known as
-tract-based morphometry): assessment of the physical properties of the white
-matter along specific tracts \cite{Bells2011-cf}. Though there are several
-different available implementations of this overall idea, the principles are
-similar \cite{yeatman2012tract, Yendiki2011-ay, Wassermann2016-iv,
-ODonnell2009-uu}: tractometry begins by delineating the parts of the white
-matter that belong to different major tracts or axonal nerve fiber bundles, such
-as the corticospinal tract or arcuate fasciculus, and samples the biophysical
-properties (such as fractional anisotropy or mean diffusivity) along the length
-of these bundles. In some cases, tissue properties along the length of each
-bundle are summarized by taking the mean along each bundle, but there is a large
-body of evidence showing that there is systematic variability within each
-bundle. This justifies retaining the individual samples along the length of each
-bundle \cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this retains
-important information about each individual's white matter, it also presents
+Leveraging this fact, one of the most powerful methods currently
+available to put macro- and micro-structure together is
+\emph{tractometry}: assessment of the physical properties of the white
+matter along specific tracts \cite{Bells2011-cf}. Though there are
+several different available implementations of this overall idea,
+the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
+Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
+the parts of the white matter that belong to different major tracts or
+axonal nerve fiber bundles, such as the corticospinal tract or arcuate
+fasciculus, and samples the biophysical properties (such as fractional
+anisotropy or mean diffusivity) along the length of these bundles.
+In some cases, tissue properties along the length of each bundle are
+summarized by taking the mean along each bundle, but there is a large
+body of evidence showing that there is systematic variability along
+the trajectory of each bundle. This justifies retaining the individual
+samples along the length of each bundle \cite{yeatman2012tract,
+colby2012, ODonnell2009-uu}. However, while this retains important
+information about each individual's white matter, it also presents
 statistical challenges due to the dimensionality of the data. Based on
-tractometry, researchers may choose to compare different individuals to each
-other. This is usually done following one of the following approaches:
+tractometry, researchers may choose to compare different individuals
+to each other. This is usually done following one of the following
+approaches:
 
@@
 
-\item Mass univariate approaches: In this approach comparisons between groups or
-across individuals are done at each node of each tract, for each one of the
-diffusion metrics available at that point. This approach is exhaustive, but
-statistical power is compromised by a multiple comparison problem. Different
-approaches can be taken to resolving this challenge. For example, Colby and
-colleagues \cite{colby2012} used a non-parametric resmapling approach to correct
-for family-wise error across the different possible comparisons
+\item Mass univariate approaches: In this approach comparisons between
+groups or across individuals are done independently at each node
+of each tract, for each one of the diffusion metrics available at
+that point. This approach is exhaustive, but statistical power is
+compromised by a multiple comparison problem. Different approaches
+can be taken to resolving this challenge. For example, Colby and
+colleagues \cite{colby2012} used a non-parametric resmapling approach to
+correct for family-wise error across the different possible comparisons
 \cite{Nichols2002-zu, Nichols2003-yy}.
 
-\item Region of interest(ROI)-based approaches: An alternative that circumvents
-the multiple comparison problem is to select just a few tracts to compare in
-each individual, or even focusing on particular segments of these tracts based
-on \emph{a priori} hypotheses. This approach is very powerful when the
-biological basis of the process of interest is relatively well understood (for a
-recent example, see \cite{huber2018rapid}).
+\item Region of interest(ROI)-based approaches: An alternative that
+circumvents the multiple comparison problem is to select just a few
+tracts to compare in each individual, or even focusing on particular
+segments of these tracts based on \emph{a priori} hypotheses. This
+approach is very powerful when the biological basis of the process
+of interest is relatively well understood (for a recent example, see
+\cite{huber2018rapid}).
 
-\item ROI-based selection, followed by multivariate analysis: Here, an ROI is
-selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
-ROI are used together to fit a model that can predict differences between
-individuals. An example of that is the ``profilometry'' framework, in which
-different diffusion metrics from a single tract are combined together to provide
-input to a multivariate analysis of covariance, and linear discriminant analysis
+\item ROI-based selection, followed by multivariate analysis: Here,
+an ROI is selected based on \emph{a priori} knowledge, and all the
+nodes or voxels in the ROI are used together to fit a model that can
+predict differences between individuals. An example of that is the
+``profilometry'' framework, in which different diffusion metrics
+from a single tract are combined together to provide input to a
+multivariate analysis of covariance, and linear discriminant analysis
 \cite{dayan2016profilometry}.
@@
 
-Generally speaking analysis methods should balance predictive accuracy with
-descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}. Accordingly,
-tractometry analysis should simultaneously capitalize on all the data across all
-tracts to make the best possible prediction, while also retaining and surfacing
-spatial information about the locations that are most informative for a
-prediction. In the present work, we developed a novel framework for analysis of
-tractometry that simultaneously selects the features for analysis, and fits a
-model to these features. We use a linear modeling approach, which aims to
+Generally speaking, analysis methods should balance predictive
+accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}.
+Accordingly, tractometry analysis should simultaneously capitalize on
+all the data across all tracts to make the best possible prediction,
+while also retaining and elucidating spatial information about the
+locations that are most informative for a prediction. In the present
+work, we developed a novel framework for analysis of tractometry that
+simultaneously selects the features for analysis, and fits a model
+to these features. We use a linear modeling approach, which aims to
 predict phenotypical variance in a group of subjects, based on a linear
-combination of the features estimated with tractometry. Using this approach, we
-need to first deal with the large and asymmetric dimensionality of the data:
-tractometry data usually has many more features (i.e., number of measurements
-per individual) than samples (number of subjects), which makes inferences from
-the data about phenotypical differences between individuals ill-posed. This
-regime is the target of several statistical learning techniques, and is often
-solved by various forms of regularization. For example, Tikhonov regularization
-shrinks the solution such that the sum of squared contributions from the
-individual features are minimized \cite{Hoerl2000-ij}. Another solution to the
-problem is provided by the Lasso algorithm, which instead minimizes the sum of
-the absolute values of contributions of each feature \cite{Tibshirani1996-qs}.
-This tends to shrink to zero the contributions of many of the features,
-providing results that are both accurate and interpretable. When additional
-structure is available in the organization of the data, regularization
-algorithms can take advantage of this structure. For example, if the features
-lend themselves to a natural division into different groups, the group lasso
-(GL) can be used to select groups of features, rather than individual features
-\cite{Yuan2006-ky}. The Sparse Group Lasso (SGL) elaborates on this idea by
-providing control both of group sparsity, as well as overall sparsity of the
-solutions \cite{simon2013sgl}. Because the features measured with tractomery
-lend themselves to grouping based on the tracts from which each measurement is
-taken, GL and SGL provide a useful tool linear model fitting in problems of this
-form. Using linear regression as the basis for analysis is useful for both
-regression tasks, in which a continuous measure (e.g., age) is modeled, as well
-as for classification tasks, where a discrete property is modeled (e.g., whether
-an individual has a particular disease). Moreover, use of SGL helps derive
-informative properties of the human white matter, both in cases where the
-underlying causes of variance are sparsely concentrated (e.g., in one particular
-white matter tract) and in cases where biological substrates of differences
-between individuals are more widespread. This is because SGL is controlled by
-meta-parameters that set the degree to which group sparsity and overall sparsity
-are applied. These metaparameters can be set empirically, based on the data,
-through a process of nested cross-validation. We demonstrate these properties of
-the algorithm in data from previously published studies
-\cite{sarica2017corticospinal, yeatman2014lifespan}.
+combination of the features estimated with tractometry.
+
+Using this approach, we first need to deal with the large and
+asymmetric dimensionality of the data: tractometry data usually has
+many more features (i.e., number of measurements per individual) than
+samples (number of subjects), which makes inferences from the data
+about phenotypical differences between individuals ill-posed. This
+regime is the target of several statistical learning techniques, and
+is often solved by various forms of regularization. For example,
+Tikhonov regularization shrinks the solution such that the sum of
+squared contributions from the individual features are minimized
+\cite{Hoerl2000-ij}. Another solution to the problem is provided by
+the Lasso algorithm, which instead minimizes the sum of the absolute
+values of contributions of each feature \cite{Tibshirani1996-qs}. This
+tends to shrink to zero the contributions of many of the features,
+providing results that are both accurate and interpretable. When
+additional structure is available in the organization of the data,
+regularization algorithms can take advantage of this structure. For
+example, if the features lend themselves to a natural division into
+different groups, the group lasso (GL) can be used to select groups
+of features, rather than individual features \cite{Yuan2006-ky}.
+The Sparse Group Lasso (SGL) elaborates on this idea by providing
+control both of group sparsity, as well as overall sparsity of the
+solutions \cite{simon2013sgl}. Because the features measured with
+tractomery lend themselves to grouping based on the tracts from which
+each measurement is taken, GL and SGL could provide a useful tool
+for linear model fitting in problems of this form. Here we, first,
+develop an implementation of SGL that is well suited to the analysis of
+tractometry data and, second, demonstrate the power and flexibility of
+this approach by applying it to both classification (disease diagnosis)
+and continuous prediction (age) problems from previously published
+studies \cite{sarica2017corticospinal, yeatman2014lifespan}.

### 2019-12-12 reports/manuscript/abstract.tex
Change order of ALS and aging studies to match the order used in the results section

@@
 is identified using a nested cross-validation scheme that guards
-against over-fitting and simultaneously identifies the correct level of
-sparsity. We demonstrate the accuracy of the method in two settings:
-in a regression setting, dMRI is used to accurately predict ``brain
-age'' \cite{yeatman2014lifespan, Brown2012-so}. In this case, the
-weights are distributed throughout the white matter indicating that
-many different regions of the white matter change with development
-and contribute to the prediction of age. In a classification setting,
-patients with amyotrophic lateral sclerosis (ALS) are accurately
-distinguished from matched controls\cite{sarica2017corticospinal} and
-SGL automatically identifies FA in the corticospinal tract as important
-for this classification -- correctly finding the parts of the white
-matter known to be affected by the disease. Thus, SGL makes it possible
+against over-fitting and simultaneously identifies the correct
+level of sparsity. We demonstrate the accuracy of the method in two
+settings: in a classification setting, patients with amyotrophic
+lateral sclerosis (ALS) are accurately distinguished from matched
+controls\cite{sarica2017corticospinal} and SGL automatically identifies
+FA in the corticospinal tract as important for this classification --
+correctly finding the parts of the white matter known to be affected
+by the disease. In a regression setting, dMRI is used to accurately
+predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In this
+case, the weights are distributed throughout the white matter indicating
+that many different regions of the white matter change with development
+and contribute to the prediction of age. Thus, SGL makes it possible
 to leverage the multivariate relationship between diffusion properties

### 2019-12-13 reports/manuscript/abstract.tex
Respond to Mareike's edits, misc.

@@
 level of sparsity. We demonstrate the accuracy of the method in two
-settings: in a classification setting, patients with amyotrophic
+settings: i) In a classification setting, patients with amyotrophic
 lateral sclerosis (ALS) are accurately distinguished from matched
-controls\cite{sarica2017corticospinal} and SGL automatically identifies
-FA in the corticospinal tract as important for this classification --
-correctly finding the parts of the white matter known to be affected
-by the disease. In a regression setting, dMRI is used to accurately
-predict ``brain age'' \cite{yeatman2014lifespan, Brown2012-so}. In this
-case, the weights are distributed throughout the white matter indicating
-that many different regions of the white matter change with development
-and contribute to the prediction of age. Thus, SGL makes it possible
-to leverage the multivariate relationship between diffusion properties
-measured along multiple tracts to make accurate predictions of subject
-characteristics while simultaneously discovering the most relevant
-features of the white matter for the characteristic of interest.
+controls \cite{sarica2017corticospinal}. Furthermore, SGL automatically
+identifies FA in the corticospinal tract as important for this
+classification -- correctly finding the parts of the white matter known
+to be affected by the disease. ii) In a regression setting, dMRI is
+used to accurately predict ``brain age'' \cite{yeatman2014lifespan,
+Brown2012-so}. In this case, the weights are distributed throughout the
+white matter indicating that many different regions of the white matter
+change with development and contribute to the prediction of age. Thus,
+SGL makes it possible to leverage the multivariate relationship between
+diffusion properties measured along multiple tracts to make accurate
+predictions of subject characteristics while simultaneously discovering
+the most relevant features of the white matter for the characteristic of
+interest.

### 2019-12-13 reports/manuscript/sections/introduction.tex
Respond to Mareike's edits, misc.

@@
 Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
-the parts of the white matter that belong to different major tracts or
-axonal nerve fiber bundles, such as the corticospinal tract or arcuate
+the parts of the white matter that belong to different major tracts
+(i.e. bundles of streamlines), such as the corticospinal tract or arcuate
 fasciculus, and samples the biophysical properties (such as fractional

### 2019-12-13 reports/manuscript/sections/methods.tex
One more pass through
Respond to Mareike's edits, misc.

@@
 
-\item Diffusion MRI data from a previous study of properties of the white matter
-across the lifespan\cite{yeatman2014lifespan}, containing dMRI data from 76
-subjects with ages 6-50. These data were measured in a GE Discovery 750 3T MRI
-scanner at the Stanford Center for Cognitive and Neurobiological Imaging. The
-Stanford University IRB approved the procedures of this study. Informed consent
-was obtained from each adult participant, and assent for participation was
-provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$mm^3$ with 96 non-colinear directions measured with a $b=2000$
-$\frac{sec}{mm^2}$ and 30 non-colinear directions measured with a $b=1000$
-$\frac{sec}{mm^2}$. Data was preprocessed to correct for subject motion and the
-diffusion tensor model \cite{basser1994mr} was fit in every voxel, using a
-robust fit \cite{chang2005restore}. These data were acquired using a dual spin
-echo sequence, in which there is sufficient time for eddy currents to subside
-between the application of the gradients and the image acquisition, so no eddy
-current correction was appliced. We will refer to this dataset as WH.
+\item Diffusion MRI from a previous study of the corticospinal
+tract profile in patients with amyotrophic lateral sclerosis
+(ALS \cite{sarica2017corticospinal}), containing data from 24 ALS
+patients and 24 demographically matched healthy controls. These data
+were measured in a GE Discovery 750 3T MRI scanner at the Institute
+of Bioimaging and Molecular Physiology in Catanzaro. Informed consent
+was provided as approved by the Ethical Committee of the University
+``Magna Graecia'' of Catanzaro. Voxel resolution was \num{2x2x2}
+$\text{mm}^3$ and 27 non-colinear directions were measured with a
+$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Here, both motion correction
+and eddy current correction were applied before modeling the diffusion
+tensor in each voxel. We will refer to this dataset as ALS.
 
-\item Diffusion MRI from from a previous study of the corticospinal tract
-profile in patients with amyotrophic lateral sclerosis
-(ALS)\cite{sarica2017corticospinal}, containing data from 24 ALS patients and 24
-demographically matched healthy controls. These data were measured in a GE
-Discovery 750 3T MRI scanner at the Institute of Bioimaging and Molecular
-Physiology in Catanzaro. Informed consent was provided as approved by the
-Ethical Committee of the University ``Magna Graecia'' of Catanzaro. Voxel
-resolution was \num{2x2x2} $mm^3$ and 27 non-colinear directions were
-measured with a $b=1000$ $\frac{sec}{mm^2}$. Here, both motion correction and
-eddy current correction were applied before modeling the diffusioon tensor in
-each voxel. We will refer to this dataset as ALS.
+\item Diffusion MRI data from a previous study of properties of
+the white matter across the lifespan \cite{yeatman2014lifespan},
+containing dMRI data from 76 subjects with ages 6-50. These data were
+measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
+for Cognitive and Neurobiological Imaging. The Stanford University
+IRB approved the procedures of this study. Informed consent was
+obtained from each adult participant, and assent for participation
+was provided by parents/guardians for children. Voxel resolution was
+\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
+$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
+measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was
+preprocessed to correct for subject motion and the diffusion tensor
+model \cite{basser1994mr} was fit in every voxel, using a robust fit
+\cite{chang2005restore}. These data were acquired using a dual spin echo
+sequence, in which there is sufficient time for eddy currents to subside
+between the application of the gradients and the image acquisition, so
+no eddy current correction was appliced. We will refer to this dataset
+as WH.
 
@@
 
-Data from both of these studies was processed in a similar manner, using the
-Matlab Automated Fiber Quantification toolbox (AFQ) \cite{yeatman2012tract}:
-streamlines representing fascicles of white matter tracts were generated
-using a determinstic tractography algorithm that follows the prinicpal diffusion
-direction of the diffusion tensor in each voxel (STT \cite{basser2000vivo}).
-Major tracts were identified using multiple criteria: streamlines are selected
-as candidates for inclusion in a bundle of streamlines that represents a tract
-if they pass through known inclusion ROIs and do not pass through exclusion ROIs
-\cite{wakana2007reproducibility}. In addition, a probabilistic atlas is used to
-exclude streamlines which are unlikely to be part of a tract \cite{Hua2008-sh}.
-Each streamline is resampled to 100 nodes and the robust mean at each location
-is calculated by estimating the 3D covariance of the location of each node and
-excluding streamlines that are more than 5 standard deviations from the mean
-location in any node. Finally, a tract profile of tissue properties in each
-tract was created by interpolating the value of MRI maps of these tissue
-properties to the location of the nodes of the resampled streamlines designated
-to each tract. In each of 100 nodes, the values are summed across streamlines,
-weighting the contribution of each streamline by the inverse of the mahalnobis
-distance of the node from the average  of that node across streamlines. This
-means that streamlines that are more representative of the tract contribute more
-to the tract profile, relative to streamlines that are on the edge of the tract.
+Data from both of these studies was processed in a similar manner,
+using the Matlab Automated Fiber Quantification toolbox (AFQ)
+\cite{yeatman2012tract}: streamlines representing fascicles of white
+matter tracts were generated using a determinstic tractography algorithm
+that follows the prinicpal diffusion direction of the diffusion tensor
+in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
+using multiple criteria: streamlines are selected as candidates for
+inclusion in a bundle of streamlines that represents a tract if they
+pass through known inclusion ROIs and do not pass through exclusion
+ROIs \cite{wakana2007reproducibility}. In addition, a probabilistic
+atlas is used to exclude streamlines which are unlikely to be part of
+a tract \cite{Hua2008-sh}. Each streamline is resampled to 100 nodes
+and the robust mean at each location is calculated by estimating the 3D
+covariance of the location of each node and excluding streamlines that
+are more than 5 standard deviations from the mean location in any node.
+Finally, a tract profile of tissue properties in each tract was created
+by interpolating the value of MRI maps of these tissue properties to the
+location of the nodes of the resampled streamlines designated to each
+tract. In each of 100 nodes, the values are summed across streamlines,
+weighting the contribution of each streamline by the inverse of the
+mahalnobis distance of the node from the average of that node across
+streamlines. This means that streamlines that are more representative of
+the tract contribute more to the tract profile, relative to streamlines
+that are on the edge of the tract.
 
-This process creates tract profiles, in which diffusion measures are quantified
-and averaged along twenty major fiber tracts. Here, we use only the mean
-diffusivity (MD) and the fractional anisotropy (FA) of the diffusion tensor, but
-additional dMRI-based maps or maps based on other quantitative MRI measurements
-can also be used. These tract profiles, along with the phenotypical data we wish
-to explain or predict, form the input to the SGL algorithm. In a domain-agnostic
-machine learning context, the phenotypical data comprise the target variables
-while the tract profiles form the feature or predictor variables (See
-Fig~\ref{fig:group-structure}).
+This process creates tract profiles, in which diffusion measures
+are quantified and averaged along twenty major fiber tracts. Here,
+we use only the mean diffusivity (MD) and the fractional anisotropy
+(FA) of the diffusion tensor, but additional dMRI-based maps or maps
+based on other quantitative MRI measurements can also be used. These
+tract profiles, along with the phenotypical data we wish to explain
+or predict, form the input to the SGL algorithm. In a domain-agnostic
+machine learning context, the phenotypical data comprise the target
+variables while the tract profiles form the feature or predictor
+variables (See Fig~\ref{fig:group-structure}).
 
@@
 mean and scale it to unit variance (z-score) using the
-\lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}. Scaling is
+\lstinline{StandardScaler} from scikit-learn \cite{scikit-learn}. Scaling is
 performed separately within each cross-validation set's training or testing data
@@
 Often, the target variable $y$ is not in the domain in which the linear
-model can be best fit to it. Equation \ref{eq:lm-approx} can be slightly
+model can be best fit to it. Equation \eqref{eq:lm-approx} can be slightly
 modified as:
@@
 
-For given values of $\lambda_1$ and $\lambda_2$, the cost function in equation
-\ref{eq:sgl} can be optimized using proximal gradient descent methods
+For given values of $\lambda_1$ and $\lambda_2$, the cost function in Eq~\eqref{eq:sgl} can be optimized using proximal gradient descent methods
 \cite{parikh2014proximal} here implemented as a custom proximal operator that is
@@
 
-To objectively evaluate the model and guard against over-fitting, we used a
-nested cross-validation scheme, depicted in Fig~\ref{fig:cross-val} for the
-categorical classification case. The input data is shuffled and then decomposed
-into $k$ batches, hereafter referred to as folds. For the ALS dataset we used
-$k=10$ and for the WH dataset $k=5$. For each unique fold, we hold that fold out
-as the test\textsubscript{outer} set and let the remaining data comprise the
-train\textsubscript{outer} set, with the subscript indicating the depth of the
-nested decomposition. We further decompose each train\textsubscript{outer} set
-into three folds, and again for each unique fold, we hold out that fold as the
+To objectively evaluate the model and guard against over-fitting,
+we used a nested cross-validation scheme, depicted in
+Fig~\ref{fig:cross-val} for the categorical classification case.
+The subjects (i.e. rows of the feature matrix $\mathbf{X}$ in
+Fig~\ref{fig:group-structure} and Eq~\eqref{eq:lm}) are shuffled and
+then decomposed into $k$ batches, hereafter referred to as folds. For
+the ALS dataset we used $k=10$ and for the WH dataset $k=5$. For each
+unique fold, we hold that fold out as the test\textsubscript{outer} set
+and let the remaining data comprise the train\textsubscript{outer} set,
+with the subscript indicating the depth of the nested decomposition.
+We further decompose each train\textsubscript{outer} set into three
+folds, and again for each unique fold, we hold out that fold as the
 test\textsubscript{inner} set and let the remaining data comprise the
-train\textsubscript{inner} set. At level-1 of the decomposition, we fit an SGL
-model using fixed regularization meta-parameters $\lambda_1$ and $\lambda_2$,
-training the model using train\textsubscript{inner} and evaluating the fit on
-test\textsubscript{inner}. We find the optimal values for $\lambda_1$ and
-$\lambda_2$ using hyperoptimization, implemented using the hyperopt
-library's \verb|fmin| function\cite{Bergstra_2015} with a tree of Parzen
-estimators search algorithm\cite{bergstra2011algorithms}. For continuous
-numerical $y$, \verb|fmin| searches for meta-parameter values that minimize the
-median absolute error. This can also be done minimizing the root of the mean
-squared error (RMSE) or to maximizing the coefficient of determination ($R^2$).
-For binary categorical $y$ \verb|fmin| seeks to maximize the classification
-accuracy. This can also be done maximizing the area under the receiver operating
-curve (ROC AUC) or the average precision. Using hyperoptimization, we find
-optimal regularization parameters and $\hat{\beta}$ for each
-train\textsubscript{outer} set and then use those to predict values for data in
-test\textsubscript{outer}. Thus each subject in the dataset has a predicted
-phenotype derived from a model that never saw its particular subject's data.
+train\textsubscript{inner} set. At level-1 of the decomposition, we fit
+an SGL model using fixed regularization meta-parameters $\lambda_1$
+and $\lambda_2$, training the model using train\textsubscript{inner}
+and evaluating the fit on test\textsubscript{inner}. We find
+the optimal values for $\lambda_1$ and $\lambda_2$ using
+hyperoptimization, implemented using the hyperopt library's \verb|fmin|
+function\cite{Bergstra_2015} with a tree of Parzen estimators search
+algorithm\cite{bergstra2011algorithms}. For continuous numerical $y$,
+\verb|fmin| searches for meta-parameter values that minimize the median
+absolute error. This can also be done minimizing the root of the mean
+squared error (RMSE) or to maximizing the coefficient of determination
+($R^2$). For binary categorical $y$ \verb|fmin| seeks to maximize the
+classification accuracy. This can also be done maximizing the area
+under the receiver operating curve (ROC AUC) or the average precision.
+Using hyperoptimization, we find optimal regularization parameters and
+$\hat{\beta}$ for each train\textsubscript{outer} set and then use those
+to predict values for data in test\textsubscript{outer}. Thus each
+subject in the dataset has a predicted phenotype derived from a model
+that never saw its particular subject's data.
 

### 2019-12-16 reports/manuscript/sections/introduction.tex
Clarify voxel size vs diffusion lengths in first paragraph of introduction

@@
 
-Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into
-the physical properties of the connections that comprise the brain white matter.
-While the measurements are usually conducted with voxels at the millimeter
-scale, water molecules within each voxel probe the structure of white matter at
-the micrometer scale providing important information about the physical
-structure of the white matter, including the density of axons and distribution
-of nerve fascicle orientations within each voxel \cite{wandell2016clarifying}.
-Even though metrics derived from diffusion measurements are ambiguous in terms
-of their underlying biological interpretation \cite{Jones2013-xv}, analyzing the
-variance in these properties has proven useful in characterizing individual
-differences in cognitive function, characterizing differences between
-populations and detecting brain abnormalities associated with disease
-\cite{Thomason2011-qn}.
+Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique
+view into the physical properties of the connections that comprise
+the brain white matter. While the measurements are usually conducted
+with voxels at the millimeter scale, water molecules within each voxel
+diffuse with characteristic lengths at the micrometer scale, providing
+aggregate information about the physical structure of the white matter,
+including the density of axons and distribution of nerve fascicle
+orientations within each voxel \cite{wandell2016clarifying}. Even though
+metrics derived from diffusion measurements are ambiguous in terms
+of their underlying biological interpretation \cite{Jones2013-xv},
+analyzing the variance in these properties has proven useful in
+characterizing individual differences in cognitive function,
+characterizing differences between populations and detecting brain
+abnormalities associated with disease \cite{Thomason2011-qn}.
 

### 2019-12-16 reports/manuscript/sections/introduction.tex
Use tract and bundle consistently. Add sentence to introduction arguing that bundles, not streamlines, are the appropriate degrees of freedom for studying dMRI

@@
 
-To relate the diffusion in each voxel to the macro-structure of long-range
-connections between different brain regions, methods for computational
-tract-tracing from diffusion MRI, or tractography, combine the estimates of
-fascicle orientations in each voxel to form streamlines that traverse the volume
-of the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods have been
-under increased scrutiny and several lines of investigation have raised
-critiques of their validity \cite{Maier-Hein2017-vb, Thomas2014-ki}. On the
-other hand, there have been efforts to shore up the inferences made with these
-methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
-Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel nerve fiber
-bundles requires extraordinary evidence, and delineating the exact cortical
-termination of the streamlines in the gray matter is still prone to error, there
-is little dispute that tractography can accurately define the location of
-several major white matter bundles that are known to exist within the core of
-the white matter \cite{Maier-Hein2017-vb}.
+To relate the diffusion in each voxel to the macro-structure of
+long-range connections between different brain regions, methods for
+computational tract-tracing from diffusion MRI, or tractography, combine
+the estimates of fascicle orientations in each voxel to form streamlines
+that traverse the volume of the white matter \cite{Conturo1999-je,
+Mori2002-qi}. These methods have been under increased scrutiny and
+several lines of investigation have raised critiques of their validity
+\cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
+have been efforts to shore up the inferences made with these methods
+\cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
+Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
+nerve fiber tracts requires extraordinary evidence, and delineating
+the exact cortical termination of the streamlines in the gray matter
+is still prone to error, there is little dispute that tractography
+can accurately define the location of several major white matter
+tracts that are known to exist within the core of the white matter
+\cite{Maier-Hein2017-vb}.
 
@@
 Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
-the parts of the white matter that belong to different major tracts
-(i.e. bundles of streamlines), such as the corticospinal tract or arcuate
-fasciculus, and samples the biophysical properties (such as fractional
-anisotropy or mean diffusivity) along the length of these bundles.
-In some cases, tissue properties along the length of each bundle are
-summarized by taking the mean along each bundle, but there is a large
-body of evidence showing that there is systematic variability along
-the trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}. However, while this retains important
-information about each individual's white matter, it also presents
-statistical challenges due to the dimensionality of the data. Based on
-tractometry, researchers may choose to compare different individuals
-to each other. This is usually done following one of the following
-approaches:
+the parts of the white matter that belong to different major ``tracts''
+(i.e. anatomical or functional groups of white matter fibers),
+such as the corticospinal tract or arcuate fasciculus, assigning
+tractography generated streamlines to ``bundles,'' which approximate
+the anatomical tracts, and sampling biophysical properties (such
+as fractional anisotropy or mean diffusivity) along the length
+of these bundles. Whereas the identification of the anatomical
+correlates of tractography-generated streamlines is an open problem,
+the correspondence between tractometry's bundles and anatomical tracts
+is well supported. Tract-based diffusion metrics are therefore
+appropriate degrees of freedom with which to understand the
+white-matter correlates of cognitive function or disease.
+
+In some previous tractometry-based studies, tissue properties along
+the length of each tract were summarized by taking the mean along
+each bundle, but there is a large body of evidence showing that there
+is systematic variability along the trajectory of each bundle. This
+justifies retaining the individual samples along the length of each
+bundle \cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this
+retains important information about each individual's white matter, it
+also presents statistical challenges due to the dimensionality of the
+data. Based on tractometry, researchers may choose to compare different
+individuals to each other. This is usually done according to one of the
+following approaches:
 

### 2019-12-16 reports/manuscript/sections/methods.tex
Use tract and bundle consistently. Add sentence to introduction arguing that bundles, not streamlines, are the appropriate degrees of freedom for studying dMRI

@@
 are more than 5 standard deviations from the mean location in any node.
-Finally, a tract profile of tissue properties in each tract was created
+Finally, a tract profile of tissue properties in each bundle was created
 by interpolating the value of MRI maps of these tissue properties to the

### 2019-12-16 reports/manuscript/sections/introduction.tex
Add catani reference to introduction to support correspondence between bundles/tracts.

@@
 tractography generated streamlines to ``bundles,'' which approximate
-the anatomical tracts, and sampling biophysical properties (such
-as fractional anisotropy or mean diffusivity) along the length
-of these bundles. Whereas the identification of the anatomical
-correlates of tractography-generated streamlines is an open problem,
-the correspondence between tractometry's bundles and anatomical tracts
-is well supported. Tract-based diffusion metrics are therefore
-appropriate degrees of freedom with which to understand the
+the anatomical tracts, and sampling biophysical properties (such as
+fractional anisotropy or mean diffusivity) along the length of these
+bundles. Whereas the identification of the anatomical correlates
+of tractography-generated streamlines is an open problem, the
+correspondence between tractometry's bundles and anatomical tracts is
+well supported \cite{Catani2002-vu}. Tract-based diffusion metrics are
+therefore appropriate degrees of freedom with which to understand the
 white-matter correlates of cognitive function or disease.

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

@@
 aggregate information about the physical structure of the white matter,
-including the density of axons and distribution of nerve fascicle
+including the density of axons and distribution of fiber
 orientations within each voxel \cite{wandell2016clarifying}. Even though

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

@@
 computational tract-tracing from diffusion MRI, or tractography, combine
-the estimates of fascicle orientations in each voxel to form streamlines
+the estimates of fiber orientations in each voxel to form streamlines
 that traverse the volume of the white matter \cite{Conturo1999-je,

### 2019-12-16 reports/manuscript/sections/methods.tex
More tract/bundle disambiguation in methods

--- 2019-12-13 reports/manuscript/sections/methods.tex
@@
 \item Diffusion MRI from a previous study of the corticospinal
-tract profile in patients with amyotrophic lateral sclerosis
+tract (CST) in patients with amyotrophic lateral sclerosis
 (ALS \cite{sarica2017corticospinal}), containing data from 24 ALS
@@
 are more than 5 standard deviations from the mean location in any node.
-Finally, a tract profile of tissue properties in each tract was created
+Finally, a bundle profile of tissue properties in each bundle was created
 by interpolating the value of MRI maps of these tissue properties to the
 location of the nodes of the resampled streamlines designated to each
-tract. In each of 100 nodes, the values are summed across streamlines,
+bundle. In each of 100 nodes, the values are summed across streamlines,
 weighting the contribution of each streamline by the inverse of the
@@
 streamlines. This means that streamlines that are more representative of
-the tract contribute more to the tract profile, relative to streamlines
+the tract contribute more to the bundle profile, relative to streamlines
 that are on the edge of the tract.
 
-This process creates tract profiles, in which diffusion measures
+This process creates bundle profiles, in which diffusion measures
 are quantified and averaged along twenty major fiber tracts. Here,
@@
 based on other quantitative MRI measurements can also be used. These
-tract profiles, along with the phenotypical data we wish to explain
+bundle profiles, along with the phenotypical data we wish to explain
 or predict, form the input to the SGL algorithm. In a domain-agnostic
 machine learning context, the phenotypical data comprise the target
-variables while the tract profiles form the feature or predictor
+variables while the bundle profiles form the feature or predictor
 variables (See Fig~\ref{fig:group-structure}).
@@
 not-a-number) are imputed via linear interpolation. Care is taken not to
-interpolate across the boundaries between different tracts. Some diffusion
+interpolate across the boundaries between different bundles. Some diffusion
 metrics will have naturally larger variance than others and may therefore
@@
 corresponding to different subjects, and columns corresponding
-to diffusion measures at different nodes within each tract. The
+to diffusion measures at different nodes within each bundle. The
 relationship between tractometric features and the phenotypic target is
@@
 without the error term, $\epsilon$. In general, the feature matrix
-$\mathbf{X}$ has dimensions $S \times (T \times N \times M)$, where $S$
-is the number of subjects, $T$ is the number of white matter tracts,
-$N$ is the number of nodes in each tract, and $M$ is the number of
-diffusion metrics calculated at each node. Typically, $T = 20$, $N =
+$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
+is the number of subjects, $B$ is the number of white matter bundles,
+$N$ is the number of nodes in each bundle, and $M$ is the number of
+diffusion metrics calculated at each node. Typically, $B = 20$, $N =
 100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 16,000$ features.
@@
 in $\hat{\beta}$, we can also capitalize on our knowledge of the
-group structure of the tract profile features in $\mathbf{X}$. The
-tract-metric combinations form a natural grouping. For example, we
+group structure of the bundle profile features in $\mathbf{X}$. The
+bundle-metric combinations form a natural grouping. For example, we
 expect that MD features within the left arcuate fasciculus will
@@
 covariates, where we expect to observe both groupwise sparsity, where
-the number of groups (tract/metric combinations) with at least one
+the number of groups (bundle/metric combinations) with at least one
 non-zero coefficients is small, as well as within-group sparsity, where
@@
 between linear extrapolation and constant forward(back)-fill. Imputation uses
-only values from adjacent nodes in the same white matter tract in the same
+only values from adjacent nodes in the same white matter bundle in the same
 subject so there is no danger of data leakage from other subjects. It uses the

### 2019-12-16 reports/manuscript/sections/introduction.tex

@@
 Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
-nerve fiber tracts requires extraordinary evidence, and delineating
+tracts requires extraordinary evidence, and delineating
 the exact cortical termination of the streamlines in the gray matter

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

@@
 Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
-the parts of the white matter that belong to different major ``tracts''
+the parts of the white matter that belong to different major tracts
 (i.e. anatomical or functional groups of white matter fibers),

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex
Remove two lines from introduction the talked about degrees of freedom.

--- 2019-12-16 reports/manuscript/sections/introduction.tex
@@
 the parts of the white matter that belong to different major ``tracts''
-(i.e. anatomical or functional groups of white matter fibers),
-such as the corticospinal tract or arcuate fasciculus, assigning
-tractography generated streamlines to ``bundles,'' which approximate
-the anatomical tracts, and sampling biophysical properties (such as
-fractional anisotropy or mean diffusivity) along the length of these
-bundles. Whereas the identification of the anatomical correlates
-of tractography-generated streamlines is an open problem, the
-correspondence between tractometry's bundles and anatomical tracts is
-well supported \cite{Catani2002-vu}. Tract-based diffusion metrics are
-therefore appropriate degrees of freedom with which to understand the
-white-matter correlates of cognitive function or disease.
-
+(i.e. anatomical or functional groups of white matter fibers), such as
+the corticospinal tract or arcuate fasciculus, assigning tractography
+generated streamlines to ``bundles,'' which approximate the anatomical
+tracts, and sampling biophysical properties (such as fractional
+anisotropy or mean diffusivity) along the length of these bundles.
 In some previous tractometry-based studies, tissue properties along

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

--- 2019-12-16 reports/manuscript/sections/introduction.tex
@@
 tracts that are known to exist within the core of the white matter
-\cite{Maier-Hein2017-vb}.
+\cite{Maier-Hein2017-vb, Catani2002-vu}.
 
@@
 each bundle, but there is a large body of evidence showing that there
-is systematic variability along the trajectory of each bundle. This
+is systematic variability in the values of diffusion metrics along the trajectory of each bundle. This
 justifies retaining the individual samples along the length of each

### 2019-12-16 reports/manuscript/sections/introduction.tex

--- 2019-12-16 reports/manuscript/sections/introduction.tex
@@
 anisotropy or mean diffusivity) along the length of these bundles.
-In some previous tractometry-based studies, tissue properties along
-the length of each tract were summarized by taking the mean along
-each bundle, but there is a large body of evidence showing that there
-is systematic variability along the trajectory of each bundle. This
-justifies retaining the individual samples along the length of each
-bundle \cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this
-retains important information about each individual's white matter, it
-also presents statistical challenges due to the dimensionality of the
-data. Based on tractometry, researchers may choose to compare different
-individuals to each other. This is usually done according to one of the
-following approaches:
+the parts of the white matter that belong to different major tracts
+(i.e. anatomical or functional groups of white matter fibers), such as
+the corticospinal tract or arcuate fasciculus, assigning tractography
+generated streamlines to ``bundles,'' which approximate the anatomical
+tracts, and sampling biophysical properties (such as fractional
+anisotropy or mean diffusivity) along the length of these bundles. In
+some previous tractometry-based studies, tissue properties along the
+length of each tract were summarized by taking the mean along each
+bundle, but there is a large body of evidence showing that there is
+systematic variability in the values of diffusion metrics along the
+trajectory of each bundle. This justifies retaining the individual
+samples along the length of each bundle \cite{yeatman2012tract,
+colby2012, ODonnell2009-uu}. While this retains important information
+about each individual's white matter, it also presents statistical
+challenges due to the dimensionality of the data. Based on tractometry,
+researchers may choose to compare different individuals to each other.
+This is usually done according to one of the following approaches:
 

### 2019-12-16 reports/manuscript/sections/methods.tex
Update reports/manuscript/sections/methods.tex
Co-Authored-By: Ariel Rokem <arokem@gmail.com>

@@
 between the application of the gradients and the image acquisition, so
-no eddy current correction was appliced. We will refer to this dataset
+no eddy current correction was applied. We will refer to this dataset
 as WH.

### 2019-12-16 reports/manuscript/abstract.tex

@@
 tractometry data usually either (a) averages these quantities along
-the length of the tract in each individual, or (b) performs analysis
-point-by-point along each tract, with group comparisons or regression
-models computed separately for each point along every one of the tracts.
+the length of the bundle in each individual, or (b) performs analysis
+point-by-point along each bundle, with group comparisons or regression
+models computed separately for each point along every one of the bundles.
 In the present work, we developed a method based on the sparse group
 lasso (SGL) \cite{simon2013sparse} that takes into account tissue
-properties measured along all of the tracts, and selects informative
+properties measured along all of the bundles, and selects informative
 features by enforcing sparsity, not only at the level of individual
-tracts, but also across the entire set of tracts and all of the measured
+bundles, but also across the entire set of bundles and all of the measured
 tissue properties. The sparsity penalties for each of these constraints
@@
 SGL makes it possible to leverage the multivariate relationship between
-diffusion properties measured along multiple tracts to make accurate
+diffusion properties measured along multiple bundles to make accurate
 predictions of subject characteristics while simultaneously discovering

### 2019-12-16 reports/manuscript/sections/conclusion.tex

@@
 importance; enables a visualization of these feature importance scores in the
-anatomical coordinate frame of the tracts (e.g., Figures \ref{fig:class-results}
+anatomical coordinate frame of the bundles (e.g., Figures \ref{fig:class-results}
 and fig:regress-beta) and provides a means to understand model errors (e.g.,
@@
 \cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
-in the variation of diffusion metrics along the tracts. As brain measurements
+in the variation of diffusion metrics along the bundles. As brain measurements
 include additional structure (for example, bilateral symmetry), future work

### 2019-12-16 reports/manuscript/sections/introduction.tex

@@
 groups or across individuals are done independently at each node
-of each tract, for each one of the diffusion metrics available at
+of each bundle, for each one of the diffusion metrics available at
 that point. This approach is exhaustive, but statistical power is

### 2019-12-16 reports/manuscript/sections/methods.tex
Update reports/manuscript/sections/methods.tex
Co-Authored-By: Ariel Rokem <arokem@gmail.com>
Add more detail to the ALS dataset description.

@@
 $\text{mm}^3$ and 27 non-colinear directions were measured with a
-$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Here, both motion correction
-and eddy current correction were applied before modeling the diffusion
-tensor in each voxel. We will refer to this dataset as ALS.
+$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was preprocessed to 
+correct for subject motion and for eddy currents. The diffusion tensor
+model \cite{basser1994mr} was fit in every voxel.
+We will refer to this dataset as ALS.
 
@@
 $b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
-measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was
-preprocessed to correct for subject motion and the diffusion tensor
-model \cite{basser1994mr} was fit in every voxel, using a robust fit
-\cite{chang2005restore}. These data were acquired using a dual spin echo
-sequence, in which there is sufficient time for eddy currents to subside
-between the application of the gradients and the image acquisition, so
-no eddy current correction was applied. We will refer to this dataset
-as WH.
+measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. These data
+were acquired using a dual spin echo sequence, in which there is
+sufficient time for eddy currents to subside between the application of
+the gradients and the image acquisition, so no eddy current correction
+was applied, but motion correction was applied before fitting the
+diffusion tensor model \cite{basser1994mr} in every voxel using a robust
+fit \cite{chang2005restore}. We will refer to this dataset as WH.
 

### 2019-12-17 reports/manuscript/abstract.tex
Small edits in abstract.

@@
 The white matter contains long-range connections between different
-brain regions and the organization of these connections hold important
+brain regions and the organization of these connections holds important
 implications for brain function in health and disease. Tractometry
@@
 connections\cite{yeatman2012tract}. Statistical inference from
-tractometry data usually either (a) averages these quantities along
-the length of the bundle in each individual, or (b) performs analysis
+tractometry usually either (a) averages these quantities along
+the length of each bundle in each individual, or performs analysis
 point-by-point along each bundle, with group comparisons or regression
 models computed separately for each point along every one of the bundles.
+These approaches are limited in their sensitivity, on the one hand (a), or
+in their statistical power, on the other (b).
 In the present work, we developed a method based on the sparse group

### 2019-12-19 reports/manuscript/abstract.tex
Edit abstract for style

@@
 tractometry usually either (a) averages these quantities along
-the length of each bundle in each individual, or performs analysis
+the length of each bundle in each individual, or (b) performs analysis
 point-by-point along each bundle, with group comparisons or regression
 models computed separately for each point along every one of the bundles.
-These approaches are limited in their sensitivity, on the one hand (a), or
-in their statistical power, on the other (b).
+These approaches are limited in their sensitivity, in the former case, or
+in their statistical power, in the latter.
 In the present work, we developed a method based on the sparse group

### 2019-12-19 reports/manuscript/sections/conclusion.tex
Add zenodo DOI

@@
 \cite{yeatman2018browser}. To facilitate reproducibility and ease use
-of the software, the results presented in this paper are also provided
-in \url{https://github.com/richford/afq-insight-paper} as a series of
-Jupyter notebooks \cite{kluyver2016jupyter}.
+of the software, the results presented
+in this paper are also provided in
+\url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks} as a series of Jupyter notebooks
+\cite{kluyver2016jupyter}.

### 2021-01-21 reports/manuscript/abstract.tex
ENH: update paper and figures

@@
-\section*{Abstract}
-
+\begin{abstract}
     The white matter contains long-range connections between different
@@
     interest.
+\end{abstract}

### 2021-01-21 reports/manuscript/paper.tex
Add details to cross-validation section and software implementation. Update some references and minor edits to other sections
ENH: update paper and figures

--- 2018-10-19 reports/manuscript/paper.tex
@@
-\documentclass[11pt,twoside,a4paper]{article}
-\usepackage{authblk}  % For author affiliations with the basic article class
-\usepackage{booktabs}  % For formal tables
-\usepackage[margin=1in]{geometry}
+%% ****** Start of file apstemplate.tex ****** %
+%%
+%%   This file is part of the APS files in the REVTeX 4 distribution.
+%%   Version 4.1r of REVTeX, August 2010
+%%
+%%
+%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
+%%
+%%   See the REVTeX 4 README file for restrictions and more information.
+%%
+%
+% This is a template for producing manuscripts for use with REVTEX 4.0
+% Copy this file to another name and then work on that file.
+% That way, you always have this original template file to use.
+%
+% Group addresses by affiliation; use superscriptaddress for long
+% author lists, or if there are many overlapping affiliations.
+% For Phys. Rev. appearance, change preprint to twocolumn.
+% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
+%  Add 'draft' option to mark overfull boxes with black boxes
+%  Add 'showpacs' option to make PACS codes appear
+%  Add 'showkeys' option to make keywords appear
+\documentclass[10pt,%
+               aps,%
+               prl,%
+               preprint,%
+               superscriptaddress,%
+               preprintnumbers,%
+               amsmath,%
+               floatfix,%
+               endfloats*]{revtex4-2}
+\usepackage[T1]{fontenc}
+\usepackage[utf8x]{inputenc} 
+\usepackage[export]{adjustbox}  % Used to adjust figure frames
+\usepackage{subcaption}
+\usepackage{url}
+\usepackage{color}
+\usepackage{xcolor}
+\usepackage{listings}
+\usepackage{float}
+\usepackage{amsfonts}
+\usepackage{mathtools}
+\usepackage{dcolumn}
+\usepackage{wrapfig}
+\usepackage{physics}
+\usepackage[inline]{enumitem}
+\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
+\usepackage{todonotes}
 \usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{mathtools}  % for \shortintertext{} and PairedDelimiter
-\usepackage{xcolor}
+\graphicspath{ {../paper_figures} }
 
-\graphicspath{ {../figures/} }
+%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
+\usepackage{xr-hyper}
+\usepackage[pdftex,%
+            colorlinks=true,%
+            linkcolor=blue,%
+            citecolor=blue,%
+            urlcolor=blue,%
+            bookmarksnumbered=true,%
+            bookmarksopen=true]{hyperref}
+\usepackage[capitalize]{cleveref}
+\makeatletter
+\newcommand*{\addFileDependency}[1]{
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
 
-\DeclarePairedDelimiter\p{(}{)}
-\DeclarePairedDelimiter\brkt{[}{]}
+\newcommand*{\myexternaldocument}[2][ext:]{
+    \externaldocument[#1]{#2}
+    \addFileDependency{#2.tex}
+    \addFileDependency{#2.aux}
+}
+%%% END HELPER CODE
 
-\newcommand{\ariel}[1]{{\color{blue} Ariel: [{#1}]}}
-\newcommand{\adam}[1]{{\color{green} Adam: [{#1}]}}
-\newcommand{\strike}[1]{{\color{red} Strikeout: [{#1}]}}
-\newcommand{\authoremail}[1]{\href{mailto:{#1}}{\textnormal{\texttt{{#1}}}}}
-
-% Set the affiliation font and the affiliation separation
-\renewcommand\Affilfont{\itshape\small}
-\setlength{\affilsep}{1em}
-\setcounter{Maxaffil}{3}
+% put all the external documents here!
+\myexternaldocument[supp:]{supplemental}
 
@@
 
-\title{AFQ-Insight}
-\title{Multidimensional analysis and detection of informative features in diffusion MRI measurements of human white matter}
+\title{Multidimensional analysis and detection of informative features in human white matter}
+
+\author{Adam \surname{Richie-Halford}}%
+\email{richford@uw.edu}%
+\affiliation{%
+    eScience Institute,%
+    University of Washington, Seattle,%
+    Washington 98195--1560, USA
+}
+
+\author{Jason \surname{Yeatman}}%
+\affiliation{%
+    Graduate School of Education and Division of Developmental and Behavioral Pediatrics,%
+    Stanford University,%
+    Stanford, CA, 94305, USA
+}
+
+\author{Noah \surname{Simon}}%
+\affiliation{%
+    Department of Biostatistics,%
+    University of Washington, Seattle,%
+    Washington 98195--1560, USA
+}
+
+\author{Ariel \surname{Rokem}}%
+\affiliation{%
+    Department of Psychology,%
+    University of Washington, Seattle,%
+    Washington 98195--1560, USA
+}
+
 \date{\today}
 
-\author[1]{Adam Richie-Halford\thanks{Corresponding author: \authoremail{richford@uw.edu}}}
-\author[2]{Jason Yeatman}
-\author[3]{Noah Simon}
-\author[4]{Ariel Rokem}
-
-\affil[1]{University of Washington Department of Physics, Seattle, WA 98105}
-\affil[2]{University of Washington Department of Speech and Hearing Sciences, Seattle, WA 98105}
-\affil[3]{University of Washington Department of Biostatistics, Seattle, WA 98105}
-\affil[4]{University of Washington e{S}cience Institute, Seattle, WA 98105}
-
+% Please keep the abstract below 300 words
+\input{output}
 \input{abstract}
@@
 \maketitle
-\tableofcontents
 
-\input{sections}
+\input{sections/introduction}
+\input{sections/results}
+\input{sections/conclusion}
+\input{sections/methods}
 
-\bibliographystyle{abbrv}
+\begin{acknowledgments}
+    {\it Acknowledgments.-}
+    This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
+    National Institutes for Mental Health and by a grant from the Gordon \& Betty
+    Moore Foundation and the Alfred P. Sloan Foundation to the University of
+    Washington eScience Institute Data Science Environment. We would like to thank
+    Scott Murray for a useful discussion of the SGL method and Mareike Grotheer for
+    helpful comments on the manuscript.
+\end{acknowledgments}
+
+\printfigures
+
+\bibliographystyle{naturemag}
 \bibliography{paper}

### 2021-01-21 reports/manuscript/sections/__latexindent_temp.tex
ENH: update paper and figures

--- 2019-12-16 reports/manuscript/sections/introduction.tex
@@
-\section*{Introduction}
+\subsection*{Introduction}
+
+\begin{figure}[!h]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{0.5em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-9.75cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{{\bf Tractometry data lineage}
+        \label{fig:methods}
+        {\bf (a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CST\_L) over a mid-saggital
+        anatomical slice.
+        {\bf (c)} Tractometry further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (fa)
+        profile for CST\_L.
+        {\bf (d)} the phenotypical target data and tractometric features can
+        be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CST\_L, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGC\_L),
+        and the right (blue) group
+        contains $k$ features from the left arcuate (ARC\_L). The coefficients in
+        $\hat{\beta}$ follow the same natural grouping.
+        % Cross-validation:
+        % we evaluate model quality using a nested $k$-fold cross validation
+        % scheme. At level-0, the input data is decomposed into $k$
+        % shuffled groups and optimal hyperparameters are found for the level-0
+        % training set.
+        % To avoid overfitting, the optimal hyperparameters are themselves
+        % evaluated using a cross-validation scheme taking place
+        % at level-1 of the decomposition, where each
+        % level-0 training set is further decomposed into five shuffled
+        % groups. For the ALS and WH data, $k=10$, while for the HBN and
+        % Cam-CAN data, $k=5$.
+    }
+\end{figure}
+
+\todo[inline]{The introduction section should be shortened for Nature methods
+I think.}
 

### 2021-01-21 reports/manuscript/sections/conclusion.tex
ENH: update paper and figures

@@
-\section*{Conclusion}
+\subsection*{Discussion}
 
@@
 
-Taken together, these results demonstrate the promise of the group-regularized
-regression approach. Even at the scale of dozens of subjects, the results
-provided by SGL are both accurate, as well as interpretable
-\cite{Murdoch2019-ax}: tractometry capitalizes on domain knowledge to engineer
-meaningful features; SGL scores these features based on their relative
-importance; enables a visualization of these feature importance scores in the
-anatomical coordinate frame of the bundles (e.g., Figures \ref{fig:class-results}
-and fig:regress-beta) and provides a means to understand model errors (e.g.,
-Figure \ref{fig:class-errors}) . Thus, this multivariate analysis approach both
-(a) achieves high cross-validated accuracy for precision medicine applications
-of dMRI data and (b) identifies relevant features of brain anatomy that can
-further our neuroscientific understanding of clinical disorders.
+One drawback of our approach is also evident in the age regression results.
+There are portions of the bundle profiles in
+\cref{fig:age-results:wh-profile,fig:age-results:hbn-profile,fig:age-results:cc-profile}
+for which the $\hat{\beta}$ coefficients are zero but for which the bundle
+profiles clearly contain an age differentiating signal. While SGL correctly
+identifies certain features as important, it is not guaranteed to identify
+\emph{all} of the important features. It will identify a parsimonious set of
+important features, dense enough to predict the phenotype and sparse enough
+(at either the group or global level) to satisfy the sparsity constraints.
+
+Taken together, these results demonstrate the promise of the
+group-regularized regression approach. Even at the scale of dozens of
+subjects, the results provided by SGL are both accurate, as well as
+interpretable \cite{Murdoch2019-ax}: tractometry capitalizes on domain
+knowledge to engineer meaningful features; SGL scores these features based on
+their relative importance; enables a visualization of these feature
+importance scores in the anatomical coordinate frame of the bundles (e.g.,
+\cref{fig:class-results:coefs3d,fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d})
+and provides a means to understand model errors (e.g.,
+\cref{fig:class-results:false-positives,fig:class-results:false-negatives}) .
+Thus, this multivariate analysis approach both (a) achieves high
+cross-validated accuracy for precision medicine applications of dMRI data and
+(b) identifies relevant features of brain anatomy that can further our
+neuroscientific understanding of clinical disorders.
 

### 2021-01-21 reports/manuscript/sections/methods.tex
Add zenodo DOI
ENH: update paper and figures

--- 2019-12-16 reports/manuscript/sections/methods.tex
@@
-\section*{Materials and methods}
+\subsection*{Methods}
 
-\subsection*{Data}
-
-Two different previously-published datasets were used here:
-
-\begin{enumerate}
-
-\item Diffusion MRI from a previous study of the corticospinal
-tract (CST) in patients with amyotrophic lateral sclerosis
-(ALS \cite{sarica2017corticospinal}), containing data from 24 ALS
-patients and 24 demographically matched healthy controls. These data
-were measured in a GE Discovery 750 3T MRI scanner at the Institute
-of Bioimaging and Molecular Physiology in Catanzaro. Informed consent
-was provided as approved by the Ethical Committee of the University
-``Magna Graecia'' of Catanzaro. Voxel resolution was \num{2x2x2}
-$\text{mm}^3$ and 27 non-colinear directions were measured with a
-$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Here, both motion correction
-and eddy current correction were applied before modeling the diffusion
-tensor in each voxel. We will refer to this dataset as ALS.
-
-\item Diffusion MRI data from a previous study of properties of
-the white matter across the lifespan \cite{yeatman2014lifespan},
-containing dMRI data from 76 subjects with ages 6-50. These data were
-measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
-for Cognitive and Neurobiological Imaging. The Stanford University
-IRB approved the procedures of this study. Informed consent was
-obtained from each adult participant, and assent for participation
-was provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
-$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
-measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was
-preprocessed to correct for subject motion and the diffusion tensor
-model \cite{basser1994mr} was fit in every voxel, using a robust fit
-\cite{chang2005restore}. These data were acquired using a dual spin echo
-sequence, in which there is sufficient time for eddy currents to subside
-between the application of the gradients and the image acquisition, so
-no eddy current correction was applied. We will refer to this dataset
-as WH.
-
-\end{enumerate}
-
-Data from both of these studies was processed in a similar manner,
-using the Matlab Automated Fiber Quantification toolbox (AFQ)
-\cite{yeatman2012tract}: streamlines representing fascicles of white
-matter tracts were generated using a determinstic tractography algorithm
-that follows the prinicpal diffusion direction of the diffusion tensor
-in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
-using multiple criteria: streamlines are selected as candidates for
-inclusion in a bundle of streamlines that represents a tract if they
-pass through known inclusion ROIs and do not pass through exclusion
-ROIs \cite{wakana2007reproducibility}. In addition, a probabilistic
-atlas is used to exclude streamlines which are unlikely to be part of
-a tract \cite{Hua2008-sh}. Each streamline is resampled to 100 nodes
-and the robust mean at each location is calculated by estimating the 3D
-covariance of the location of each node and excluding streamlines that
-are more than 5 standard deviations from the mean location in any node.
-Finally, a bundle profile of tissue properties in each bundle was created
-by interpolating the value of MRI maps of these tissue properties to the
-location of the nodes of the resampled streamlines designated to each
-bundle. In each of 100 nodes, the values are summed across streamlines,
-weighting the contribution of each streamline by the inverse of the
-mahalnobis distance of the node from the average of that node across
-streamlines. This means that streamlines that are more representative of
-the tract contribute more to the bundle profile, relative to streamlines
-that are on the edge of the tract.
-
-This process creates bundle profiles, in which diffusion measures
-are quantified and averaged along twenty major fiber tracts. Here,
-we use only the mean diffusivity (MD) and the fractional anisotropy
-(FA) of the diffusion tensor, but additional dMRI-based maps or maps
-based on other quantitative MRI measurements can also be used. These
-bundle profiles, along with the phenotypical data we wish to explain
-or predict, form the input to the SGL algorithm. In a domain-agnostic
-machine learning context, the phenotypical data comprise the target
-variables while the bundle profiles form the feature or predictor
-variables (See Fig~\ref{fig:group-structure}).
-
-\subsection*{Sparse Group Lasso}
-
-Before fitting a model to the data, imputation and standardization are
-performed. Missing node values (e.g., in cases where AFQ designates a node as
-not-a-number) are imputed via linear interpolation. Care is taken not to
-interpolate across the boundaries between different bundles. Some diffusion
-metrics will have naturally larger variance than others and may therefore
-dominate the objective function and make the SGL estimator unable to learn from
-the lower variance metrics. For example, fractional anisotropy (FA) is bounded
-between zero and one and could be overwhelmed by an unscaled higher-variance
-metric like the mean diffusivity (MD). To prevent this we remove each feature's
-mean and scale it to unit variance (z-score) using the
-\lstinline{StandardScaler} from scikit-learn \cite{scikit-learn}. Scaling is
-performed separately within each cross-validation set's training or testing data
-to prevent leakage of information between the testing and training
-sets\cite{kaufman2012leakage}.
-
-After scaling and imputation, the tractometry data and target
-phenotypical data can be organized in a linear model:
-\begin{equation}
-    y = \mathbf{X} \beta + \epsilon,
-    \label{eq:lm}
-\end{equation}
-where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
-or continuous numerical, such as the subject's age. The tractometry
-data is represented in the feature matrix $\mathbf{X}$, with rows
-corresponding to different subjects, and columns corresponding
-to diffusion measures at different nodes within each bundle. The
-relationship between tractometric features and the phenotypic target is
-characterized by the coefficients in $\beta$. The error term, $\epsilon$
-is an unobserved random variable that captures the error in the model.
-We denote our prediction of the targer phenotype as $\hat{y}$ and the
-coefficients that produce this prediction as $\hat{\beta}$, so that
-\begin{equation}
-    \hat{y} = \mathbf{X} \hat{\beta},
-    \label{eq:lm-approx}
-\end{equation}
-without the error term, $\epsilon$. In general, the feature matrix
-$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
-is the number of subjects, $B$ is the number of white matter bundles,
-$N$ is the number of nodes in each bundle, and $M$ is the number of
-diffusion metrics calculated at each node. Typically, $B = 20$, $N =
-100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 16,000$ features.
-Conversely, many dMRI studies have between a few dozen and a few
-hundred subjects, yielding a feature matrix that is wide and short.
-Even in cases where more than a thousand subjects are measured (e.g.,
-in the Human Connectome Project, where 1,200 subjects were measured
-\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
-of this data requires regularization to avoid overfitting and generate
-interpretable results.
-
-Here, we propose that in addition to regularizing the coefficients
-in $\hat{\beta}$, we can also capitalize on our knowledge of the
-group structure of the bundle profile features in $\mathbf{X}$. The
-bundle-metric combinations form a natural grouping. For example, we
-expect that MD features within the left arcuate fasciculus will
-co-vary across individuals. Likewise for FA values within the right
-corticospinal tract (CST) and so on. This group structure is represented
-in Fig~\ref{fig:group-structure}, which depicts the linear model
-$\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a regularization
-approach that will fit a linear model with anatomically-grouped
-covariates, where we expect to observe both groupwise sparsity, where
-the number of groups (bundle/metric combinations) with at least one
-non-zero coefficients is small, as well as within-group sparsity, where
-the number of non-zero coefficients within each non-zero group is small.
-The sparse group lasso (SGL) is a penalized regression technique that
-satisfies exactly these criteria\cite{simon2013sparse}. It solves for a
-coefficient vector
-$\hat{\beta}$ that satisfies
-\begin{equation}
-    \hat{\beta} = \min_\beta \frac{1}{2}
-    ||y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \beta^{(\ell)}||_2^2
-    + \lambda_1 \displaystyle \sum_{\ell = 1}^{G}
-    \sqrt{p_\ell} ||\beta^{(\ell)}||_2
-    + \lambda_2 ||\beta||_1,
-    \label{eq:sgl}
-\end{equation}
-where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix
-of $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is
-the coefficient vector for group $\ell$ and $p_\ell$ is the length of
-$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and
-$\forall \ell: p_\ell = 100$. The first term is the mean square error
-loss, $L_{\text{mse}}$, as in the standard linear regression framework.
-The second and third terms encourage groupwise sparsity and overall
-sparsity, respectively. If $\lambda_1 = 0$ and $\lambda_2 = 1$, the
-SGL reduces to the traditional lasso\cite{tibshirani1996regression}.
-Conversely, if $\lambda_1 = 1$ and $\lambda_2 = 0$, the SGL reduces to
-the group lasso\cite{yuan2006model}.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.65\textwidth]{dMRI_group_structure.png}
-    \caption{{\bf dMRI group structure.}
-        The phenotypical target data and tractometric features can
-        be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the inferior fronto-occipital
-        fascicle (IFOF), the middle (green) group contains $k$ features
-        from the corpus callosum, and the right (blue) group
-        contains $k$ features from the uncinate. The coefficients in
-        $\hat{\beta}$ follow the same natural grouping. Fascicle image
-        reproduced with permission from Ref~\cite{yeatman2012tract}
-        Figure 1.
-    }
-    \label{fig:group-structure}
-\end{figure}
-
-\subsubsection*{Incorporating transformations on $y$}
-
-Often, the target variable $y$ is not in the domain in which the linear
-model can be best fit to it. Equation \eqref{eq:lm-approx} can be slightly
-modified as:
-\begin{equation}
-    \hat{y} = f^-1(\mathbf{X} \hat{\beta}),
-    \label{eq:lm-transform}
-\end{equation}
-where the transformation function $f^{-1}$ characterizes the transform
-applied to the data before fitting the linear coefficients. For example,
-an often-used transform is the logarithmic transform:
-\begin{equation}
-    f(\hat{y}) = \log_n(\hat{y})
-    \label{eq:log-nonlinearity}
-\end{equation}
-In this case, the model is parametrized by one additional fit parameter,
-$n$.
-
-\subsubsection*{Classification of categorical $y$}
-When the phenotypical target variable is categorical, as in the case of
-explaining or predicting the presence of a clinical diagnosis, the SGL is
-readily adapted to logistic regression, where the probability of a target
-variable belonging to an arbitrary defined ``true'' class is the logistic
-function of the result of the linear model,
-\begin{equation}
-    p(\hat{y} = 1) = \frac{1}{1 + \exp(\mathbf{X} \hat{\beta})},
-    \label{eq:logit}
-\end{equation}
-or equivalently, the mean squared error loss function in Eq~\eqref{eq:sgl} is
-replaced with the cross-entropy loss, which for binary classification is the
-negative log likelihood of the SGL classifier giving the ``true'' label:
-\begin{equation}
-    L_{\text{mse}} \rightarrow L_{\log} =
-    -\left(y \log(p) + (1 - y) \log(1 - p)\right).
-    \label{eq:logloss}
-\end{equation}
-
-\subsection*{Implementation, cross-validation and metaparameter optimization}
-
-For given values of $\lambda_1$ and $\lambda_2$, the cost function in Eq~\eqref{eq:sgl} can be optimized using proximal gradient descent methods
-\cite{parikh2014proximal} here implemented as a custom proximal operator that is
-then optimized using the C-OPT library\cite{copt}. This supplies an estimate of
-the optimal $\hat{\beta}$ given a particular set of values for the
-meta-parameters $\lambda_1$ and $\lambda_2$.
-
-To objectively evaluate the model and guard against over-fitting,
-we used a nested cross-validation scheme, depicted in
-Fig~\ref{fig:cross-val} for the categorical classification case.
-The subjects (i.e. rows of the feature matrix $\mathbf{X}$ in
-Fig~\ref{fig:group-structure} and Eq~\eqref{eq:lm}) are shuffled and
-then decomposed into $k$ batches, hereafter referred to as folds. For
-the ALS dataset we used $k=10$ and for the WH dataset $k=5$. For each
-unique fold, we hold that fold out as the test\textsubscript{outer} set
-and let the remaining data comprise the train\textsubscript{outer} set,
-with the subscript indicating the depth of the nested decomposition.
-We further decompose each train\textsubscript{outer} set into three
-folds, and again for each unique fold, we hold out that fold as the
-test\textsubscript{inner} set and let the remaining data comprise the
-train\textsubscript{inner} set. At level-1 of the decomposition, we fit
-an SGL model using fixed regularization meta-parameters $\lambda_1$
-and $\lambda_2$, training the model using train\textsubscript{inner}
-and evaluating the fit on test\textsubscript{inner}. We find
-the optimal values for $\lambda_1$ and $\lambda_2$ using
-hyperoptimization, implemented using the hyperopt library's \verb|fmin|
-function\cite{Bergstra_2015} with a tree of Parzen estimators search
-algorithm\cite{bergstra2011algorithms}. For continuous numerical $y$,
-\verb|fmin| searches for meta-parameter values that minimize the median
-absolute error. This can also be done minimizing the root of the mean
-squared error (RMSE) or to maximizing the coefficient of determination
-($R^2$). For binary categorical $y$ \verb|fmin| seeks to maximize the
-classification accuracy. This can also be done maximizing the area
-under the receiver operating curve (ROC AUC) or the average precision.
-Using hyperoptimization, we find optimal regularization parameters and
-$\hat{\beta}$ for each train\textsubscript{outer} set and then use those
-to predict values for data in test\textsubscript{outer}. Thus each
-subject in the dataset has a predicted phenotype derived from a model
-that never saw its particular subject's data.
-
-The above procedure describes $k$-fold cross validation. In fact, we use
-repeated $k$-fold cross validation on the outer level of the decomposition, so
-that the input data is decomposed into $k$ folds, three times. Thus, each
-subject has three predicted phenotypes. We then take the mean predicted value to
-summarize the performance of the model. In the classification case, the
-shuffling into folds is stratified such that each fold has a population that
-preserves the percentage of each class found in the larger input data.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.55\textwidth]{nested-cross-validation.pdf}
-    \caption{{\bf Nested $k$-fold cross-validation scheme.}
-        We evaluate model quality using a nested $k$-fold cross
-        validation scheme. At level-0, the input data is decomposed
-        three times into $k$ shuffled groups and optimal hyperparameters
-        are found for the level-0 training set. Optimization of these
-        hyperparameters requires the use of the hyperopt library and
-        many repeated evaluations of an SGL model over a search space
-        of possible regularization parameters. These evaluations take
-        place at level-1 of the decomposition, where the level-0 training
-        set is further decomposed into three shuffled groups.
-        For the ALS data, $k=10$. For the WH data, $k=5$.
-    }
-    \label{fig:cross-val}
-\end{figure}
-
-\subsection*{Software implementation}
-
-The full software implementation of the SGL approach presented here is available
-in a Python software package called AFQ-Insight, which is developed publicly in
-\url{https://github.com/richford/afq-insight}. The version of the code used to
-produce the results herein is also available in \ariel{Need to add Zenodo DOI}.
-AFQ-Insight reads the target and feature data that has been processed by AFQ
-from comma separated value (CSV) files conforming to the AFQ-Browser data
-format\cite{yeatman2018browser} and represents them internally as
-\lstinline{DataFrame} objects from the pandas Python
-library\cite{mckinney2010data}. The software provides different options for
-imputing missing data in the feature matrix. Missing interior nodes are imputed
-using linear interpolation. For missing exterior nodes, the user may choose
-between linear extrapolation and constant forward(back)-fill. Imputation uses
-only values from adjacent nodes in the same white matter bundle in the same
-subject so there is no danger of data leakage from other subjects. It uses the
-scikit-learn\cite{scikit-learn} library to decompose input data into separate
-test and train datasets, to scale each feature to have zero mean and
-unit variance, and to evaluate each fit in the hyperparameter search using
-appropriate classification and regression metrics such as accuracy, area
-under the receiver operating curve (AUC ROC), and coefficient of determination
-($R^2$). For each set of hyperparameters, we solve the SGL using a custom
-proximal operator supplied to the C-OPT library\cite{copt}. Appropriate
-hyperparameters are found using the hyperopt library\cite{Bergstra_2015}.
+Methods and associated references are available in \cref{supp:sec:methods} of
+the supplemental material \cite{supplement}.

### 2021-01-21 reports/manuscript/sections/results.tex
ENH: update paper and figures

@@
-\section*{Results and discussion}
+\subsection*{Results}
+
+\begin{figure*}
+    \vspace{3cm}
+    \rlap{
+        \includegraphics[width=0.33\textwidth]{als_coefs.pdf}
+    }
+    \vspace{-8.4cm}
+    \includegraphics[width=\textwidth]{als_results.pdf}
+    {\phantomsubcaption\label{fig:class-results:probs}}
+    {\phantomsubcaption\label{fig:class-results:coefs3d}}
+    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
+    {\phantomsubcaption\label{fig:class-results:false-positives}}
+    {\phantomsubcaption\label{fig:class-results:false-negatives}}
+    \caption{%
+        {\bf SGL accurately and interpretably predicts ALS diagnosis.}
+        \label{fig:class-results}
+        {\bf (a)} Classification probabilities for ALS diagnosis, with
+        controls on the left, patients on the right, predicted controls in
+        blue, and predicted patients in orange. So orange dots on the left
+        represent false positives, while blue dots on the right represent
+        false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
+        ROC AUC of {\protect\alsRocAuc}.
+        {\bf (b)} SGL coefficients are presented on the core fibers of major
+        fiber bundles. They exhibit high group sparsity and are concentrated
+        in the fa of the CST. The brain is oriented with the right hemisphere
+        in the foreground and anterior to the right of the page. The CST\_L,
+        CST\_R, and CF\_A bundles are indicated for orientation.
+        {\bf (c)} SGL identifies three portions of the CST as important,
+        where $\hat{\beta}$ (dashed line, right axis) has large values. These
+        are centered around nodes 30, 65, and 90, corresponding to locations
+        of substantial differences in FA between the ALS and control groups
+        (shaded areas indicates standard error of the mean).
+        {\bf (d)} Bundle profiles for false positive classifications. Line
+        colors correspond to the marker edge color in the top left plot.
+        These individuals have reduced FA in the CST portions which SGL
+        identified as important. Their misclassification is coherent with the
+        feature importance and the group differences in FA.
+        {\bf (e)} Individual bundle profiles for false negative
+        classifications. These individuals have bundle profiles which
+        oscillate between the group means.
+    }
+\end{figure*}
 
 We developed a method for analyzing dMRI tractometry data with SGL. We
-demonstrate the use of this method on two previously published datasets in both
-a classification setting and a regression setting.
+demonstrate the use of this method on four previously published datasets in
+both a classification setting and a regression setting.
 
-\subsection*{SGL accurately detects ALS in tractometry data in a classification setting}
+\subsubsection*{SGL accurately detects ALS from tractometry data}
 
 Using data from a previous study of the corticospinal tract (CST) profile and
-ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
+ALS \cite{sarica2017corticospinal}, we tested the performance of SGL in a
 classification setting. The previous study predicted ALS status with a mean
-accuracy of 80\% using a random forest algorithm based on a priori selection of
-features within the corticospinal tract. SGL delivers competitive predictive
-performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC AUC) without
-the need for a priori feature engineering. The results of the classification
-prediction are shown in Figure \ref{fig:class-results} with ``ground-truth'' ALS
-status separated into columns, and predicted ALS status encoded by color. In
-addition to this classification performance, SGL also identifies the white
-matter tracts most important for ALS classification. The relative importance of
-white matter features is captured in the $\beta$ coefficients from
-Eq~\eqref{eq:sgl}. Figure \ref{fig:class-profiles} depicts these coefficients along
-the right CST, plotted over the FA values for the control and ALS subject
-groups. We find that SGL selects FA metrics in the corticospinal tract and
-particularly in the right corticospinal tract as most important to ALS
-classification, confirming previous findings\cite{van2011upper,
-toosy2003diffusion, sarica2014tractography, sage2007quantitative,
-sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
-cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
-identifying the portions of the brain that were selected \emph{a priori} in the
-previous study from which we collected our data\cite{sarica2017corticospinal}.
+accuracy of 80\% using a random forest algorithm based on a priori selection
+of features within the corticospinal tract. SGL delivers competitive
+predictive performance (mean {\alsAccuracy}\% accuracy, {\alsRocAuc} ROC AUC)
+without the need for a priori feature engineering. The results of the
+classification prediction are shown in \cref{fig:class-results:probs} with
+``ground-truth'' ALS status separated into columns, and predicted ALS status
+encoded by color. In addition to this classification performance, SGL also
+identifies the white matter tracts most important for ALS classification. The
+relative importance of white matter features is captured in the $\beta$
+coefficients from \cref{supp:eq:sgl}. \Cref{fig:class-results:tract-profiles}
+depicts these coefficients along the right CST, plotted over the FA values
+for the control and ALS subject groups. We find that SGL selects FA metrics
+in the corticospinal tract and particularly in the right corticospinal tract
+as most important to ALS classification, confirming previous findings
+\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
+sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
+ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
+abe2010voxel} and identifying the portions of the brain that were selected
+\emph{a priori} in the previous study from which we collected our data
+\cite{sarica2017corticospinal}.
 
-Analyzing the ways in which the model mislabels individuals may also provide
-insight. We found that mislabelled subjects are outliers relative to their group
-with respect to diffusion features of the CST. Figure \ref{fig:class-errors}
-depicts the group FA values along with FA values of mislabelled subjects, two
-false negatives and one false-positive. The false negative classifications have
-high FA in one of the two sections of the CST where $||\hat{\beta}|| > 0$ in
-Figure \ref{fig:class-profiles}. The false positive subject has an FA that
-oscillates between the two group means. Thus, the SGL method fails
-comprehensibly.
+The $\beta$ coefficients exhibit high bundle level sparsity; only some
+bundles are important, which can be be confirmed by observing the value of
+$\alpha$ in \cref{supp:eq:sgl}, the regularization hyperparameter that
+controls the mixture of the group lasso and lasso penalties. If $\alpha$ is
+closer to zero, it indicates that the phenotype in question preferentially
+correlates with only a few groups of covariates. For the ALS dataset, $\alpha
+= $ \alsLRatio, confirming that the white matter correlates of ALS reside
+mostly in one bundle, namely the CST.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.45\textwidth]{classification_probs.png}
-    \includegraphics[width=0.45\textwidth]{classification_beta_bupu.png}
+Analyzing the ways in which the model mislabels individuals also provides
+insight. We found that mislabelled subjects are outliers relative to their
+group with respect to diffusion features of the CST.
+\Cref{fig:class-results:false-positives,fig:class-results:false-negatives}
+depicts the group FA values along with FA values of mislabelled subjects,
+four false negatives and three false-positives. The false positive
+classifications have reduced FA in one or more of the three sections of the
+CST where $\norm*{\hat{\beta}}$ is large
+\cref{fig:class-results:tract-profiles}. The false negative subjects have FA
+profiles that oscillate between the two group means. Thus, the SGL method
+fails comprehensibly.
 
-    \caption{{\bf SGL accurately predicts ALS.}
-        Left: Classification probabilities for each subject's ALS diagnosis.
-        Controls are on the left while patients are on the right. Predicted
-        controls are in blue and predicted patients are in red. Thus, false
-        positive are represented as red dots on the left, while false negatives
-        are represented as blue dots on the right. The SGL algorithm achieves
-        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
-        coefficients are presented on a skeleton of the major tracts. The brain
-        is oriented with the right hemisphere to our left and anterior out of
-        the page. As expected large negative coefficients are in the FA of the
-        CST (and particularly in the right hemisphere, here to the left)}
-    \label{fig:class-results}
-\end{figure}
+\begin{figure*}
+    \vspace{3.65cm}
+    \rlap{
+        \hspace{1cm}
+        \includegraphics[width=0.275\textwidth]{wh_coefs.pdf}
+        \hspace{0.25em}
+        \includegraphics[width=0.275\textwidth]{hbn_coefs.pdf}
+        \hspace{0.25em}
+        \includegraphics[width=0.275\textwidth]{camcan_coefs.pdf}
+    }
+    \vspace{-7.3cm}
+    \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
+    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
+    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
+    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:wh-profile}}
+    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
+    {\phantomsubcaption\label{fig:age-results:cc-profile}}
+    \caption{%
+        {\bf Predicting age with tractometry and SGL.}
+        \label{fig:age-results}
+        {\bf (top)} The predicted age vs. true age of each individual from the test
+        splits (i.e., when each subject's data was held out in fitting the
+        model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
+        datasets; an accurate prediction falls close to the $y=x$ line
+        (dashed). The mean absolute error (MAE) and coefficient of
+        determination $R^2$ are presented in the lower right of each scatter
+        plot.
+        {\bf (middle)} Feature importance for predicting age from tractometry in
+        the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
+        The orientation of the
+        brain is that same as in \cref{fig:class-results:coefs3d}, however because
+        the coefficients exhibit high global sparsity (as opposed to group
+        sparsity), we plot the mean of the absolute value of $\hat{\beta}$
+        for each bundle on the core fiber. The global distrubution of the
+        $\hat{\beta}$ coefficients reflects the fact that aging is not
+        confined to a single white matter bundle.
+        {\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
+        {\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
+    }
+\end{figure*}
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
-    \caption{{\bf Model coefficients mirror FA differences}. The places along the
-       length of the CST  where $\hat{\beta}$ coefficients for FA
-       (dashed line, right axis) have large negative values correspond to the
-       locations of substantial differences between the ALS (green) and control
-       (orange) FA (shaded area indicates standard error of the mean).}
-    \label{fig:class-profiles}
-\end{figure}
+\subsubsection*{SGL accurately predicts age from tractometry data}
 
-\begin{figure}[h]
-    \centering
-        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
-    \caption{{\bf Model mis-classifications correspond to features identified by
-       the model}. The FA in CST of individuals that are mis-classified by the
-       model is compared the group FA (with shaded are indicating standard error
-       of the mean). False negative classifications (individuals that have ALS,
-       but are classified as patients) correspond to high FA either in one of
-       the two regions of large $||\hat{\beta}||$ in
-       Figure \ref{fig:class-profiles}. The false positive classification has
-       an FA profile that oscillates between the two group means.
-   }
-    \label{fig:class-errors}
-\end{figure}
+To test the performance of SGL with tractometry data in a continuous
+regression task, we focus here on the prediction of biological age based on
+tractometry data in three datasets named WH, HBN, and Cam-CAN (see
+\cref{supp:sec:data} for further details). Prediction of ``brain age'' is a
+commonly undertaken task in neuroimaging machine learning, in part because
+these predictions, and deviations therefrom, may be diagnostic of overall
+brain health (for a review, see \textcite{Cole2019-rz}). However, as
+\textcite{nelson2019biomarkers} have observed, aging biomarkers are subject
+to unique challenges and tend to be noncausative. Our interest in aging here
+relies on its utility as a methodological benthmark. Biological age operates
+on a natural scale, with meaningful and easily understood units, and it's
+popularity as a machine learning target makes it valuable for comparisons
+with other studies.
 
-\subsection*{SGL accurately predicts age from tractometry data in a regression setting}
+The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
+\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
+data from 76, 978, and 640 subjects, respectively, ranging from 6-50, 5-21,
+and 18-88 years of age, respectively. In each case, biological age was used
+as the predicted variable ($y$ in \cref{supp:eq:lm}). SGL was fit to
+tractometry-extracted features in 18 major brain tracts: DTI FA and DTI MD
+for WH and DKI FA and DKI MD for HBN and Cam-CAN, with each tract divided
+into 100 nodes.
 
-To test the performance of SGL with tractometry data in a continuous regression
-task, we focus here on the prediction of biological age based on tractometry
-data. Prediction of ``brain age'' is a commonly undertaken task. This is both
-because it operates on a natural scale, with meaningful and easily understood
-units, as well as because predictions of brain age, and deviations from accurate
-prediction are diagnostic of overall brain health (for a recent review, see
-\cite{Cole2019-rz}). The WH dataset used here contains data from 76 healthy
-subjects, ranging between 6 years and 50 years of age
-\cite{yeatman2014lifespan}. In this case, biological age was used as the
-predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
-tractometry-extracted features: FA and MD in 20 major brain tracts, with each
-tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
-cross-validation procedure. In this procedure, batches of subjects are held out.
-For each batch (or fold), the model is fully fit without this data. Then, once
-the parameters are fixed, the model is inverted to predict the ages of held out
-subjects based on the linear coeffiecients and the static non-linearity. This
-scheme automatically finds the right level of regularization (i.e., sparseness)
-and fits the coefficients to the ill-posed linear model, while guarding against
-overfitting. SGL accurately predicts the age of the subjects in this procedure,
-with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}, left
-panel). This is lower than the results of a recent study that predicted age in a
-large sample, based on diffusion MRI features \cite{Richard2018-ux}.
-Nevertheless, older subjects have higher residual variance, reflecting the
-automatically-chosen log-transformation and implying that brain age becomes more
-difficult to predict as we age chronologically (\ref{fig:regress-results}, right
-panel). The model weights are distributed over many different tracts and dMRI
-tissue properties (Figure \ref{fig:regress-beta} left). This demonstrates that
-SGL is not coerced to produce overly sparse results when a more accurate model
-requires a dense selection of features. Furthermore, looking closer at a
-selection of tracts where high coefficients are found demonstrates that
-diffusion properties (FA, in this case) are different in different age groups in
-parts of the tracts where these higher coefficients are found (Figure
-\ref{fig:regress-beta} right).
+To evaluate the fit of the model, we used a nested cross-validation
+procedure. In this procedure, batches of subjects are held out. For each
+batch (or fold), the model is fully fit without this data. Then, once the
+parameters are fixed, the model is inverted to predict the ages of held out
+subjects based on the linear coeffiecients. This scheme automatically finds
+the right level of regularization (i.e., sparseness) and fits the
+coefficients to the ill-posed linear model, while guarding against
+overfitting. SGL accurately predicts the age of the subjects in this
+procedure, with a median absolute error of 2.8 years, 1.5 years, and 6.0
+years for WH, HBN, and Cam-CAN, respectively and coefficients of
+determination $R^2 = $ {\whRsq} , {\hbnRsq}, and {\camcanRsq}, respectively (see
+\cref{fig:age-results}, top panels). The predictions for Cam-CAN are
+competitive with a recent state of the art prediction
+\cite{mcpherson2020single}, which used streamline density to estimate the
+brain's structural connectivity and achieved $R^2 = 0.63$. The median
+absolute errors are also lower than the results of a recent study that
+predicted age in a large sample, based on diffusion MRI features
+\cite{Richard2018-ux}.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.8\textwidth]{regression_residuals.png}
-    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted
-    age of each individual (on the abscissa) and true age (on the ordinate),
-    from the test splits (i.e., when each subject's data was held out in fitting
-    the model); an accurate prediction falls close to the $y=x$ line (dashed).
-    The mean absolute error in this case is 3.6 years and, the coefficient of
-    determination $R^2=0.3$. Right: Standardized residuals (on the abscissa) as
-    a function of the true age (on the ordinate). Predictions are generally more
-    accurate for younger individuals.}
-    \label{fig:regress-results}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
-    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
-    \caption{{\bf Feature importance for predicting age from tractometry.} Left:
-    A skeletonized display of the main brain tracts analyzed, with anterior
-    facing up, and right hemisphere on the right. The $\hat{\beta}$ coefficients
-    displayed in blue (negative) to red (positive) are for measurements of FA
-    along the length of the tracts. The left cingulum cingulate (A) and forceps
-    minor (B) are highlighted. Right: the FA (in shades of blue and green) and
-    the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps
-    minor.}
-    \label{fig:regress-beta}
-\end{figure}
+In contrast to the ALS classification case, the selected $\alpha$ values
+indicate high global sparsity over group sparsity, with $\alpha = $
+{\whLRatio}, {\hbnLRatio}, and {\ccLRatio}, for the WH, HBN, and Cam-CAN
+datasets, respectively. The model weights are distributed over many different
+tracts and dMRI tissue properties (see
+\cref{fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d}
+and supplemental material
+\cref{supp:fig:wh-bp:md,supp:fig:wh-bp:fa,supp:fig:hbn-bp:md,supp:fig:hbn-bp:fa,supp:fig:cc-bp:md,supp:fig:cc-bp:fa}).
+This demonstrates that SGL is not coerced to produce overly sparse results
+when a more accurate model requires a dense selection of features.
+Furthermore, inspecting the portions of bundles with larger coefficients in
+\cref{fig:age-results:wh-profile,fig:age-results:hbn-profile,fig:age-results:cc-profile}
+reveals that SGL selects informative regions where diffusion properties are
+different between the age quintiles.

### 2021-01-21 reports/manuscript/supplemental.tex
ENH: update paper and figures

%% ****** Start of file apstemplate.tex ****** %
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.1r of REVTeX, August 2010
%%
%%
%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
\documentclass[10pt,%
               aps,%
               prl,%
               preprint,%
               superscriptaddress,%
               preprintnumbers,%
               amsmath,%
               floatfix,%
               endfloats*]{revtex4-2}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc} 
\usepackage[export]{adjustbox}  % Used to adjust figure frames
\usepackage{subcaption}
\usepackage{url}
\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{wrapfig}
\usepackage{physics}
\usepackage{mathtools}  % For shortintertext
\usepackage[inline]{enumitem}
\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
\usepackage{todonotes}
\usepackage{graphicx}
\graphicspath{ {../paper_figures} }
\usepackage{bibentry}

%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr-hyper}
\usepackage[pdftex,%
            colorlinks=true,%
            linkcolor=blue,%
            citecolor=blue,%
            urlcolor=blue,%
            bookmarksnumbered=true,%
            bookmarksopen=true]{hyperref}
\usepackage[capitalize]{cleveref}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[2][ext:]{
    \externaldocument[#1]{#2}
    \addFileDependency{#2.tex}
    \addFileDependency{#2.aux}
}
%%% END HELPER CODE

% put all the external documents here!
\myexternaldocument[main:]{paper}

\begin{document}

\title{Supplemental Material: Multidimensional analysis and detection of informative features in human white matter}

\author{Adam \surname{Richie-Halford}}%
\email{richford@uw.edu}%
\affiliation{%
    eScience Institute,%
    University of Washington, Seattle,%
    Washington 98195--1560, USA
}

\author{Jason \surname{Yeatman}}%
\affiliation{%
    Graduate School of Education and Division of Developmental and Behavioral Pediatrics,%
    Stanford University,%
    Stanford, CA, 94305, USA
}

\author{Noah \surname{Simon}}%
\affiliation{%
    Department of Biostatistics,%
    University of Washington, Seattle,%
    Washington 98195--1560, USA
}

\author{Ariel \surname{Rokem}}%
\affiliation{%
    Department of Psychology,%
    University of Washington, Seattle,%
    Washington 98195--1560, USA
}

\date{\today}

\preprint{NT@UW-20-21}
%\pacs{}
\begin{abstract}
In these supplemental materials we present\ldots
\end{abstract}

\maketitle

\makeatletter
\def\l@subsubsection#1#2{}
\makeatother
\tableofcontents

%\newpage
\section{Online Methods}
\label{sec:methods}

\subsection{Data}
\label{sec:data}

Four different previously-published datasets were used here:

\begin{enumerate}

\item Diffusion MRI from a previous study of the corticospinal
tract (CST) in patients with amyotrophic lateral sclerosis
(ALS \cite{sarica2017corticospinal}), containing data from 24 ALS
patients and 24 demographically matched healthy controls. These data
were measured in a GE Discovery 750 3T MRI scanner at the Institute
of Bioimaging and Molecular Physiology in Catanzaro. Informed consent
was provided as approved by the Ethical Committee of the University
``Magna Graecia'' of Catanzaro. Voxel resolution was \num{2x2x2}
$\text{mm}^3$ and 27 non-colinear directions were measured with a
$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was preprocessed to 
correct for subject motion and for eddy currents. The diffusion tensor
model \cite{basser1994mr} was fit in every voxel.
We will refer to this dataset as ALS.

\item Diffusion MRI data from a previous study of properties of
the white matter across the lifespan \cite{yeatman2014lifespan},
containing dMRI data from 76 subjects with ages 6-50. These data were
measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
for Cognitive and Neurobiological Imaging. The Stanford University
IRB approved the procedures of this study. Informed consent was
obtained from each adult participant, and assent for participation
was provided by parents/guardians for children. Voxel resolution was
\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. These data
were acquired using a dual spin echo sequence, in which there is
sufficient time for eddy currents to subside between the application of
the gradients and the image acquisition, so no eddy current correction
was applied, but motion correction was applied before fitting the
diffusion tensor model \cite{basser1994mr} in every voxel using a robust
fit \cite{chang2005restore}. We will refer to this dataset as WH.

\item Diffusion MRI data from the Healthy Brain Network pediatric mental
health study \cite{alexander2017open}, containing dMRI data from 978 subjects
with ages 5-21. These data were measured in 3T Siemens MRI scanners at three
sites in the New York area. Informed consent was obtained from each
participant aged 18 or older. For participants younger than 18, written
consent was obtained from their legal guardians and written assent was
obtained from the participant. Voxel resolution was
\num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions measured for
each of $b=1000 \frac{\text{sec}}{\text{mm}^2}$ and $b=2000
\frac{\text{sec}}{\text{mm}^2}$.
Preprocessing was performed using \emph{QSIPrep} 0.12.1, which is based on
\emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.

\begin{itemize}

\item {\it Anatomical data preprocessing}
The T1-weighted (T1w) image was corrected for intensity non-uniformity
(INU) using \texttt{N4BiasFieldCorrection} \cite[ANTs 2.3.1]{n4}, and
used as T1w-reference throughout the workflow. The T1w-reference was
then skull-stripped using \texttt{antsBrainExtraction.sh} (ANTs 2.3.1),
using OASIS as target template. Spatial normalization to the ICBM 152
Nonlinear Asymmetrical template version 2009c
\cite[RRID:SCR\_008796]{mni} was performed through nonlinear
registration with \texttt{antsRegistration} \cite[ANTs 2.3.1,
RRID:SCR\_004757]{ants}, using brain-extracted versions of both T1w
volume and template. Brain tissue segmentation of cerebrospinal fluid
(CSF), white-matter (WM) and gray-matter (GM) was performed on the
brain-extracted T1w using \texttt{FAST} \cite[FSL 6.0.3:b862cdd5,
RRID:SCR\_002823]{fsl_fast}.

\item {\it Diffusion data preprocessing}
Several confounding time-series were calculated based on the
\emph{preprocessed DWI}: framewise displacement (FD) using the
implementation in \emph{Nipype} \cite[following the definitions
by]{power_fd_dvars}. The head-motion estimates calculated in the
correction step were also placed within the corresponding confounds
file. Slicewise cross correlation was also calculated. The DWI
time-series were resampled to ACPC, generating a \emph{preprocessed DWI
run in ACPC space}.
\end{itemize}

Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
\cite[RRID:SCR\_001362]{nilearn} and \emph{Dipy} \cite{dipy}. For more
details of the pipeline, see
\href{https://qsiprep.readthedocs.io/en/latest/workflows.html}{the
section corresponding to workflows in \emph{QSIPrep}'s documentation}.
We will refer to this dataset as HBN.

\item Diffusion MRI data from the Cambridge Centre for Ageing and
Neuroscience (Cam-CAN) ``CC700'' dataset
\cite{shafto2014cambridge,taylor2017cambridge}, containing data from 640
subjects with ages 18-88. These data were measured on a 3T Siemens TIM Trio
system and written informed consent was obtained from each participant. Voxel
resolution was \num{2x2x2}$\text{mm}^3$ with 30 non-colinear directions
measured for each of $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$ and $b=2000$
$\frac{\text{sec}}{\text{mm}^2}$. The diffusion weighted images were acquired
with a twice refocused spin-echo sequence and the same preprocessing pipeline
used for the HBN dataset was applied to this data. We will refer to this
dataset as Cam-CAN.

\end{enumerate}

Data from the ALS and WH studies was processed in a similar manner,
using the Matlab Automated Fiber Quantification toolbox (\texttt{mAFQ})
\cite{yeatman2012tract}: streamlines representing fascicles of white
matter tracts were generated using a determinstic tractography algorithm
that follows the prinicpal diffusion direction of the diffusion tensor
in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
using multiple criteria: streamlines are selected as candidates for
inclusion in a bundle of streamlines that represents a tract if they
pass through known inclusion ROIs and do not pass through exclusion
ROIs \cite{wakana2007reproducibility}. In addition, a probabilistic
atlas is used to exclude streamlines which are unlikely to be part of
a tract \cite{Hua2008-sh}. Each streamline is resampled to 100 nodes
and the robust mean at each location is calculated by estimating the 3D
covariance of the location of each node and excluding streamlines that
are more than 5 standard deviations from the mean location in any node.
Finally, a bundle profile of tissue properties in each bundle was created
by interpolating the value of MRI maps of these tissue properties to the
location of the nodes of the resampled streamlines designated to each
bundle. In each of 100 nodes, the values are summed across streamlines,
weighting the contribution of each streamline by the inverse of the
mahalnobis distance of the node from the average of that node across
streamlines. This means that streamlines that are more representative of
the tract contribute more to the bundle profile, relative to streamlines
that are on the edge of the tract.

Data from the HBN and Cam-CAN studies were processed using the updated
Python Automated Fiber Quantification toolbox (\texttt{pyAFQ}).
\todo[inline]{Add pyAFQ citation} In addition to demonstrating the our
analysis pipeline is robust to changes in the platform and version number of
tractometry software, the use of the updated \texttt{pyAFQ} capitalized upon
the following three improvements over the legacy Matlab version
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item the ability to ingest data provided in the BIDS format
    \cite{gorgolewski2016brain}
    \item the calculation of diffusion kertosis imaging (DKI
    \cite{jensen2005diffusion}) metrics
    \item the exclusion of the Cingulum Hippocampus bundles, which
    demonstrated low reliability in the legacy \texttt{mAFQ}.
\end{enumerate*}
We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
as \texttt{AFQ}.

These processes create bundle profiles, in which diffusion measures
are quantified and averaged along twenty major fiber tracts. Here,
we use only the mean diffusivity (MD) and the fractional anisotropy
(FA) of the diffusion tensor, but additional dMRI-based maps or maps
based on other quantitative MRI measurements can also be used. These
bundle profiles, along with the phenotypical data we wish to explain
or predict, form the input to the SGL algorithm. In a domain-agnostic
machine learning context, the phenotypical data comprise the target
variables while the bundle profiles form the feature or predictor
variables (See \cref{main:fig:methods:group-structure} in the main text).

\subsection{Sparse Group Lasso}

Before fitting a model to the data, imputation and standardization are
performed. Missing node values (e.g., in cases where \texttt{AFQ} designates
a node as not-a-number) are imputed via linear interpolation. Care is taken
not to interpolate across the boundaries between different bundles. Some
diffusion metrics will have naturally larger variance than others and may
therefore dominate the objective function and make the SGL estimator unable
to learn from the lower variance metrics. For example, fractional anisotropy
(FA) is bounded between zero and one and could be overwhelmed by an unscaled
higher-variance metric like the mean diffusivity (MD). To prevent this we
remove each feature's mean and scale it to unit variance (z-score) using the
\lstinline{StandardScaler} from scikit-learn \cite{scikit-learn}. The scaling
parameters are learned only from the training data and then applied equally
to the training and test data in order to prevent leakage of information
between the testing and training sets \cite{kaufman2012leakage}.

After scaling and imputation, the tractometry data and target
phenotypical data can be organized in a linear model:
\begin{equation}
    y = \mathbf{X} \beta + \epsilon,
    \label{eq:lm}
\end{equation}
where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
or continuous numerical, such as the subject's age. The tractometry
data is represented in the feature matrix $\mathbf{X}$, with rows
corresponding to different subjects, and columns corresponding
to diffusion measures at different nodes within each bundle. The
relationship between tractometric features and the phenotypic target is
characterized by the coefficients in $\beta$. The error term, $\epsilon$
is an unobserved random variable that captures the error in the model.
We denote our prediction of the targer phenotype as $\hat{y}$ and the
coefficients that produce this prediction as $\hat{\beta}$, so that
\begin{equation}
    \hat{y} = \mathbf{X} \hat{\beta},
    \label{eq:lm-approx}
\end{equation}
without the error term, $\epsilon$. In general, the feature matrix
$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
is the number of subjects, $B$ is the number of white matter bundles,
$N$ is the number of nodes in each bundle, and $M$ is the number of
diffusion metrics calculated at each node. Typically, $B = 20$, $N =
100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 16,000$ features.
Conversely, many dMRI studies have between a few dozen and a few
hundred subjects, yielding a feature matrix that is wide and short.
Even in cases where more than a thousand subjects are measured (e.g.,
in the Human Connectome Project, where 1,200 subjects were measured
\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
of this data requires regularization to avoid overfitting and generate
interpretable results.

Here, we propose that in addition to regularizing the coefficients in
$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
of the bundle profile features in $\mathbf{X}$. The bundle-metric
combinations form a natural grouping. For example, we expect that MD features
within the left arcuate fasciculus will co-vary across individuals. Likewise
for FA values within the right corticospinal tract (CST) and so on. This
group structure is represented in \cref{main:fig:methods:group-structure}, which
depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
regularization approach that will fit a linear model with
anatomically-grouped covariates, where we expect to observe both groupwise
sparsity, where the number of groups (bundle/metric combinations) with at
least one non-zero coefficients is small, as well as within-group sparsity,
where the number of non-zero coefficients within each non-zero group is
small. The sparse group lasso (SGL) is a penalized regression technique that
satisfies exactly these criteria\cite{simon2013sparse}. It solves for a
coefficient vector $\hat{\beta}$ that satisfies
\begin{multline}
    \hat{\beta} = \min_\beta L_{\text{mse}}
    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
    + \alpha \lambda \norm{\beta}_1,\\%
    \text{where} \quad
    L_{\text{mse}} = \frac{1}{2}
    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2
    \label{eq:sgl}
\end{multline}
where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
coefficient vector for group $\ell$ and $p_\ell$ is the length of
$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
\ell: p_\ell = 100$. The first term is the mean square error loss,
$L_{\text{mse}}$, as in the standard linear regression framework. The second
and third terms encourage groupwise sparsity and overall sparsity,
respectively. If $\alpha = 1$ the SGL reduces to the traditional
lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
reduces to the group lasso\cite{yuan2006model}. Thus, the model
hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
The hyperparameter $\lambda$ controls the strength of the regularization.

\subsubsection{Incorporating target transformations}

Often, the target variable $y$ is not in the domain in which the linear
model can be best fit to it. \Cref{eq:lm-approx} can be slightly
modified as:
\begin{equation}
    \hat{y} = f^{-1} \left( \mathbf{X} \hat{\beta} \right),
    \label{eq:lm-transform}
\end{equation}
where the transformation function $f^{-1}$ characterizes the transform
applied to the data before fitting the linear coefficients. For example,
For the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
\begin{equation}
    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
    \label{eq:log-nonlinearity}
\end{equation}

\subsubsection{Classification of categorical targets}
When the phenotypical target variable is categorical, as in the case of
explaining or predicting the presence of a clinical diagnosis, the SGL is
readily adapted to logistic regression, where the probability of a target
variable belonging to an arbitrary defined ``true'' class is the logistic
function of the result of the linear model,
\begin{equation}
    p(\hat{y} = 1) = \frac{1}{1 + \exp(\mathbf{X} \hat{\beta})},
    \label{eq:logit}
\end{equation}
or equivalently, the mean squared error loss function in \cref{eq:sgl} is
replaced with the cross-entropy loss, which for binary classification is the
negative log likelihood of the SGL classifier giving the ``true'' label:
\begin{equation}
    L_{\text{mse}} \rightarrow L_{\log} =
    -\left(y \log(p) + (1 - y) \log(1 - p)\right).
    \label{eq:logloss}
\end{equation}

\subsection{Implementation, cross-validation and metaparameter optimization}

Because the SGL is not specific to tractometry, we implement its solution as
a separate Python package called \texttt{groupyr} \cite{groupyr}.
\texttt{Groupyr} solves the cost function in \cref{eq:sgl} using proximal
gradient descent \cite{parikh2014proximal} by implementing a custom proximal
operator and relying on the C-OPT optimization library \cite{copt}, providing
a fitted SGL model as a scikit-learn compatible estimator \cite{sklearn_api}.
\texttt{Groupyr} also selects the hyperparameters $\alpha$ and $\lambda$ that
yield the best cross-validated performance using either
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, or }}]
    \item an exhaustive grid search of hyperparameter combinations
    \item sequential model based optimization using the scikit-optimize
    library \cite{scikit_optimize}.
\end{enumerate*}

\todo[inline]{%
    Rewrite the remainder of this section to reflect \texttt{groupyr} changes.
}

To objectively evaluate the model performance and guard against over-fitting,
we used a nested cross-validation scheme, depicted in
\cref{main:fig:methods:cross-val} for the categorical classification case.
The subjects (i.e. rows of the feature matrix $\mathbf{X}$ in
\cref{main:fig:methods:group-structure} and \cref{eq:lm}) are shuffled and
then decomposed into $k$ batches, hereafter referred to as folds. For
the ALS dataset we used $k=10$ and for the WH dataset $k=5$. For each
unique fold, we hold that fold out as the test\textsubscript{outer} set
and let the remaining data comprise the train\textsubscript{outer} set,
with the subscript indicating the depth of the nested decomposition.
We further decompose each train\textsubscript{outer} set into three
folds, and again for each unique fold, we hold out that fold as the
test\textsubscript{inner} set and let the remaining data comprise the
train\textsubscript{inner} set. At level-1 of the decomposition, we fit
an SGL model using fixed regularization meta-parameters $\alpha$
and $\lambda$, training the model using train\textsubscript{inner}
and evaluating the fit on test\textsubscript{inner}. We find
the optimal values for $\alpha$ and $\lambda$ using
hyperoptimization, implemented using the hyperopt library's \verb|fmin|
function\cite{Bergstra_2015} with a tree of Parzen estimators search
algorithm\cite{bergstra2011algorithms}. For continuous numerical $y$,
\verb|fmin| searches for meta-parameter values that minimize the median
absolute error. This can also be done minimizing the root of the mean
squared error (RMSE) or to maximizing the coefficient of determination
($R^2$). For binary categorical $y$ \verb|fmin| seeks to maximize the
classification accuracy. This can also be done maximizing the area
under the receiver operating curve (ROC AUC) or the average precision.
Using hyperoptimization, we find optimal regularization parameters and
$\hat{\beta}$ for each train\textsubscript{outer} set and then use those
to predict values for data in test\textsubscript{outer}. Thus each
subject in the dataset has a predicted phenotype derived from a model
that never saw its particular subject's data.

The above procedure describes $k$-fold cross validation. In fact, we use
repeated $k$-fold cross validation on the outer level of the decomposition, so
that the input data is decomposed into $k$ folds, three times. Thus, each
subject has three predicted phenotypes. We then take the mean predicted value to
summarize the performance of the model. In the classification case, the
shuffling into folds is stratified such that each fold has a population that
preserves the percentage of each class found in the larger input data.

\subsection{Software implementation}

The full software implementation of the SGL approach presented here is available
in a Python software package called AFQ-Insight, which is developed publicly in
\url{https://github.com/richford/afq-insight}. The version of the code used to
produce the results herein is also available in
\url{https://doi.org/10.5281/zenodo.3585942}.
\todo[inline]{Update version here}
AFQ-Insight reads the target and feature data that has been processed by AFQ
from comma separated value (CSV) files conforming to the AFQ-Browser data
format \cite{yeatman2018browser} and represents them internally as
\lstinline{DataFrame} objects from the pandas Python
library \cite{mckinney2010data}. The software provides different options for
imputing missing data in the feature matrix. Missing interior nodes are imputed
using linear interpolation. For missing exterior nodes, the user may choose
between linear extrapolation and constant forward(back)-fill. Imputation uses
only values from adjacent nodes in the same white matter bundle in the same
subject so there is no danger of data leakage from other subjects. It uses the
scikit-learn \cite{scikit-learn} library to decompose input data into separate
test and train datasets, to scale each feature to have zero mean and
unit variance, and to evaluate each fit in the hyperparameter search using
appropriate classification and regression metrics such as accuracy, area
under the receiver operating curve (AUC ROC), and coefficient of determination
($R^2$). For each set of hyperparameters, we solve the SGL using a custom
proximal operator supplied to the C-OPT library\cite{copt}. Appropriate
hyperparameters are found using the hyperopt library\cite{Bergstra_2015}.

\section{Bundle and coefficient profiles}
\label{sec:bundle-profiles}

Here, we present the bundle profiles and $\hat{\beta}$ coefficients
for each dataset. Throughout this section, diffusion metrics are plotted
along the length of eighteen bundles: 
right corticospinal (CST\_R),
left corticospinal (CST\_L),
right uncinate (UNC\_R),
left uncinate (UNC\_L),
left inferior fronto-occipital fasciculus (IFO\_L),
right inferior fronto-occipital fasciculus (IFO\_R),
right arcuate (ARC\_R),
left arcuate (ARC\_L),
right thalamic radiation (ATR\_R),
left thalamic radiation (ATR\_L),
right cingulum cingulate (CGC\_R),
left cingulum cingulate (CGC\_L),
callosum forceps major (FP),
callosum forceps minor (FA),
right inferior longitudinal fasciculus (ILF\_R),
left inferior longitudinal fasciculus (ILF\_L),
right superior longitudinal fasciculus (SLF\_R),
and left superior longitudinal fasciculus (SLF\_L).
We display results for two different diffusion metrics: fractional anisotropy
(fa) and mean diffusivity (md). We use lower-case letters to abbreviate the
diffusion metrics and distinguish fractional anisotropy (fa) from the
callosum forceps minor (FA).

\subsection{ALS bundle profiles}

\begin{figure*}
    \includegraphics[width=\textwidth]{sarica_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for ALS classification.
        }
        \label{fig:als-bp:fa}
    }
\end{figure*}

\Cref{fig:als-bp:fa,fig:als-bp:md} show the bundle profiles and regression
coefficients for the ALS dataset fa and md metrics, respectively. The scale
of the $\hat{\beta}$ axes is shared between the fa and md figures to
highlight the relative importance of the fa features over the md features.

\begin{figure*}
    \includegraphics[width=\textwidth]{sarica_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) Bundle profiles and $\hat{\beta}$
            coefficients for ALS classification.
        }
        \label{fig:als-bp:md}
    }
\end{figure*}

\subsection{WH bundle profiles}

\begin{figure*}
    \includegraphics[width=\textwidth]{wh_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the WH dataset.
        }
        \label{fig:wh-bp:fa}
    }
\end{figure*}

\hspace{1em}

\begin{figure*}
    \includegraphics[width=\textwidth]{wh_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the WH dataset.
        }
        \label{fig:wh-bp:md}
    }
\end{figure*}

\subsection{HBN bundle profiles}

\begin{figure*}
    \includegraphics[width=\textwidth]{hbn_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the HBN dataset.
        }
        \label{fig:hbn-bp:fa}
    }
\end{figure*}

\hspace{1em}

\begin{figure*}
    \includegraphics[width=\textwidth]{hbn_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the HBN dataset.
        }
        \label{fig:hbn-bp:md}
    }
\end{figure*}

\subsection{Cam-CAN bundle profiles}

\begin{figure*}
    \includegraphics[width=\textwidth]{cc_coefs_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the Cam-CAN dataset.
        }
        \label{fig:cc-bp:fa}
    }
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{cc_coefs_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
            coefficients for age regression in the Cam-CAN dataset.
        }
        \label{fig:cc-bp:md}
    }
\end{figure*}

\printfigures

\bibliographystyle{naturemag}
\bibliography{paper}

\end{document}

### 2021-01-25 reports/manuscript/abstract.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

@@
     mean diffusivity (MD), etc.), along the trajectories of these
-    connections\cite{yeatman2012tract}. Statistical inference from
+    connections \cite{yeatman2012tract}. Statistical inference from
     tractometry usually either (a) averages these quantities along
@@
     bundles, but also across the entire set of bundles and all of the measured
-    tissue properties. The sparsity penalties for each of these constraints
-    is identified using a nested cross-validation scheme that guards
-    against over-fitting and simultaneously identifies the correct
-    level of sparsity. We demonstrate the accuracy of the method in two
+    tissue properties.
+    % The sparsity penalties for each of these constraints
+    % is identified using a nested cross-validation scheme that guards
+    % against over-fitting and simultaneously identifies the correct
+    % level of sparsity.
+    We demonstrate the accuracy of the method in two
     settings: i) In a classification setting, patients with amyotrophic
@@
     identifies FA in the corticospinal tract as important for this
-    classification -- correctly finding the parts of the white matter known
+    classification, correctly finding the parts of the white matter known
     to be affected by the disease. ii) In a regression setting, dMRI is

### 2021-01-25 reports/manuscript/sections/conclusion.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

@@
 
-We present here a novel method for analysis of dMRI tractometry data that relies
-on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
+We present here a novel method for analysis of dMRI tractometry data that
+relies on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
 predictions of phenotypic properties of individual subjects while,
-simultaneously, (b) identifying the features of the white matter that are most
-important for this prediction in a completely data-driven approach. The method
-is broadly applicable to a wide range of research questions: it performs well in
-predicting both continuous variables, such as biological age, as well as
-categorical variables, such as whether a person is a patient or a healthy
-control. In both of these cases, SGL out-performs previous algorithms that have
-been developed for these tasks \cite{sarica2017corticospinal, Richard2018-ux}.
-The nested cross-validation approach used to fit the model and make both
-predictions and inferences from the model guards against overfitting and tunes
-the degree of sparseness required by the algorithm. This means that SGL can
-accurately describe phenomena that are locally confined to a particular
+simultaneously, (b) identifying the features of the white matter that are
+most important for this prediction in a completely data-driven approach. The
+method is broadly applicable to a wide range of research questions: it
+performs well in predicting both continuous variables, such as biological
+age, as well as categorical variables, such as whether a person is a patient
+or a healthy control. In both of these cases, SGL out-performs previous
+algorithms that have been developed for these tasks
+\cite{sarica2017corticospinal, Richard2018-ux, mcpherson2020single}. The
+nested cross-validation approach used to fit the model and make both
+predictions and inferences from the model guards against overfitting and
+tunes the degree of sparseness required by the algorithm. This means that SGL
+can accurately describe phenomena that are locally confined to a particular
 anatomical location or diffusion property (e.g., FA in the CST) as well as
@@
 
-Specifically, we demonstrated that the algorithm correctly detects
-the fact that ALS, which is a disease of lower motor neurons, is
-localized to the cortico-spinal tract. This recapitulates the results
-of previous analysis of these same data, using a targeted ROI-based
-approach \cite{sarica2017corticospinal}. In contrast, for the analysis
-of biological age, the coefficients identified by the algorithm are very
-widely distributed across many parts of the white matter, mirroring
-previous results with this dataset (and others) that show a large and
-continuous distribution of life-span changes in white matter properties
-\cite{yeatman2014lifespan}.
+Specifically, we demonstrated that the algorithm correctly detects the fact
+that ALS, which is a disease of lower motor neurons, is localized to the
+cortico-spinal tract. This recapitulates the results of previous analysis of
+these same data, using a targeted ROI-based approach
+\cite{sarica2017corticospinal}. In contrast, for the analysis of biological
+age, the coefficients identified by the algorithm are very widely distributed
+across many parts of the white matter, mirroring previous results that show a
+large and continuous distribution of life-span changes in white matter
+properties \cite{yeatman2014lifespan}.
 
@@
 
-Neuroscience has entered an era in which consortium efforts are putting together
+Neuroscience has entered an era in which consortium efforts are amassing
 large datasets of high-quality dMRI measurements to address a variety of

### 2021-01-25 reports/manuscript/sections/introduction.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

@@
-\section*{Introduction}
+\subsection*{Introduction}
+
+\begin{figure}[!h]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{0.5em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-9.75cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{{\bf Tractometry data lineage}
+        \label{fig:methods}
+        {\bf (a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
+        anatomical slice.
+        {\bf (c)} Tractometry further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for CSTL.
+        {\bf (d)} the phenotypical target data and tractometric features can
+        be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the left arcuate (ARCL). The coefficients in
+        $\hat{\beta}$ follow the same natural grouping.
+        % Cross-validation:
+        % we evaluate model quality using a nested $k$-fold cross validation
+        % scheme. At level-0, the input data is decomposed into $k$
+        % shuffled groups and optimal hyperparameters are found for the level-0
+        % training set.
+        % To avoid overfitting, the optimal hyperparameters are themselves
+        % evaluated using a cross-validation scheme taking place
+        % at level-1 of the decomposition, where each
+        % level-0 training set is further decomposed into five shuffled
+        % groups. For the ALS and WH data, $k=10$, while for the HBN and
+        % Cam-CAN data, $k=5$.
+    }
+\end{figure}
+
+\todo[inline]{The introduction section should be shortened for Nature methods
+I think.}
 
@@
 generated streamlines to ``bundles,'' which approximate the anatomical
-tracts, and sampling biophysical properties (such as fractional
-anisotropy or mean diffusivity) along the length of these bundles.
+tracts, and sampling biophysical properties, such as fractional
+anisotropy (FA) or mean diffusivity (MD), along the length of these bundles.
 the parts of the white matter that belong to different major tracts

### 2021-01-25 reports/manuscript/sections/results.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

@@
         fiber bundles. They exhibit high group sparsity and are concentrated
-        in the fa of the CST. The brain is oriented with the right hemisphere
-        in the foreground and anterior to the right of the page. The CST\_L,
-        CST\_R, and CF\_A bundles are indicated for orientation.
+        in the FA of the CST. The brain is oriented with the right hemisphere
+        in the foreground and anterior to the right of the page. The CSTL,
+        CSTR, and CFA bundles are indicated for orientation.
         {\bf (c)} SGL identifies three portions of the CST as important,
@@
 accuracy of 80\% using a random forest algorithm based on a priori selection
-of features within the corticospinal tract. SGL delivers competitive
-predictive performance (mean {\alsAccuracy}\% accuracy, {\alsRocAuc} ROC AUC)
-without the need for a priori feature engineering. The results of the
-classification prediction are shown in \cref{fig:class-results:probs} with
-``ground-truth'' ALS status separated into columns, and predicted ALS status
-encoded by color. In addition to this classification performance, SGL also
-identifies the white matter tracts most important for ALS classification. The
-relative importance of white matter features is captured in the $\beta$
-coefficients from \cref{supp:eq:sgl}. \Cref{fig:class-results:tract-profiles}
-depicts these coefficients along the right CST, plotted over the FA values
-for the control and ALS subject groups. We find that SGL selects FA metrics
-in the corticospinal tract and particularly in the right corticospinal tract
-as most important to ALS classification, confirming previous findings
-\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
-sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
-ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
-abe2010voxel} and identifying the portions of the brain that were selected
-\emph{a priori} in the previous study from which we collected our data
+of features within the CST. SGL delivers competitive
+predictive performance, with a cross-validated accuracy of {\alsAccuracy}\%
+and an area under the receiver operating characteristic curve (ROC AUC) of
+{\alsRocAuc}, all without the need for a priori feature engineering. The
+results of the classification prediction are shown in
+\cref{fig:class-results:probs} with ``ground-truth'' ALS status separated
+into columns, and predicted ALS status encoded by color. In addition to this
+classification performance, SGL also identifies the white matter tracts most
+important for ALS classification. The relative importance of white matter
+features is captured in the $\beta$ coefficients from \cref{supp:eq:sgl} of
+the supplemental material \cite{supplement}.
+\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
+right CST, plotted over the FA values for the control and ALS subject groups.
+We find that SGL selects FA metrics in the corticospinal tract and
+particularly in the right corticospinal tract as most important to ALS
+classification, confirming previous findings \cite{van2011upper,
+toosy2003diffusion, sarica2014tractography, sage2007quantitative,
+sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
+cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
+identifying the portions of the brain that were selected \emph{a priori} in
+the previous study from which we collected our data
 \cite{sarica2017corticospinal}.
@@
 bundles are important, which can be be confirmed by observing the value of
-$\alpha$ in \cref{supp:eq:sgl}, the regularization hyperparameter that
-controls the mixture of the group lasso and lasso penalties. If $\alpha$ is
-closer to zero, it indicates that the phenotype in question preferentially
-correlates with only a few groups of covariates. For the ALS dataset, $\alpha
-= $ \alsLRatio, confirming that the white matter correlates of ALS reside
-mostly in one bundle, namely the CST.
+$\alpha$, the regularization hyperparameter that controls the mixture of the
+group lasso and lasso penalties
+(see \cref{supp:eq:sgl} of the supplemental material \cite{supplement}).
+If $\alpha$ is closer to zero, it indicates that the phenotype in question
+preferentially correlates with only a few groups of covariates. For the ALS
+dataset, $\alpha = $ \alsLRatio, confirming that the white matter correlates
+of ALS reside mostly in one bundle, namely the CST.
 
@@
 To test the performance of SGL with tractometry data in a continuous
-regression task, we focus here on the prediction of biological age based on
-tractometry data in three datasets named WH, HBN, and Cam-CAN (see
-\cref{supp:sec:data} for further details). Prediction of ``brain age'' is a
-commonly undertaken task in neuroimaging machine learning, in part because
-these predictions, and deviations therefrom, may be diagnostic of overall
-brain health (for a review, see \textcite{Cole2019-rz}). However, as
-\textcite{nelson2019biomarkers} have observed, aging biomarkers are subject
-to unique challenges and tend to be noncausative. Our interest in aging here
-relies on its utility as a methodological benthmark. Biological age operates
-on a natural scale, with meaningful and easily understood units, and it's
-popularity as a machine learning target makes it valuable for comparisons
-with other studies.
+regression task, we focus here on the prediction of biological age in three
+datasets named WH, HBN, and Cam-CAN (see supplemental material
+\cite{supplement} for a description of each dataset). Prediction of ``brain
+age'' is a commonly undertaken task in neuroimaging machine learning, in part
+because these predictions, and deviations therefrom, may be diagnostic of
+overall brain health (for a review, see Cole et al.~\cite{Cole2019-rz}).
+However, as Nelson et al.~\cite{nelson2019biomarkers} have observed, aging
+biomarkers are subject to unique challenges and tend to be noncausative. Our
+interest in aging here relies on its utility as a methodological benthmark.
+Biological age operates on a natural scale, with meaningful and easily
+understood units, and it's popularity as a machine learning target makes it
+valuable for comparisons with other studies.
 
@@
 and 18-88 years of age, respectively. In each case, biological age was used
-as the predicted variable ($y$ in \cref{supp:eq:lm}). SGL was fit to
-tractometry-extracted features in 18 major brain tracts: DTI FA and DTI MD
-for WH and DKI FA and DKI MD for HBN and Cam-CAN, with each tract divided
-into 100 nodes.
+as the predicted variable $y$. SGL was fit to the tractometry-extracted
+features FA and MD in 18 major brain tracts, with diffusion metrics extracted
+from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
+imaging (DKI) \cite{jensen2005diffusion} the HBN and Cam-CAN datasets.
 
@@
 subjects based on the linear coeffiecients. This scheme automatically finds
-the right level of regularization (i.e., sparseness) and fits the
-coefficients to the ill-posed linear model, while guarding against
-overfitting. SGL accurately predicts the age of the subjects in this
-procedure, with a median absolute error of 2.8 years, 1.5 years, and 6.0
-years for WH, HBN, and Cam-CAN, respectively and coefficients of
-determination $R^2 = $ {\whRsq} , {\hbnRsq}, and {\camcanRsq}, respectively (see
-\cref{fig:age-results}, top panels). The predictions for Cam-CAN are
-competitive with a recent state of the art prediction
-\cite{mcpherson2020single}, which used streamline density to estimate the
-brain's structural connectivity and achieved $R^2 = 0.63$. The median
-absolute errors are also lower than the results of a recent study that
+the right level of sparsity and fits the coefficients to the ill-posed linear
+model, while guarding against overfitting. SGL accurately predicts the age of
+the subjects in this procedure, with a median absolute error of {\whMae},
+{\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
+respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq},
+and {\camcanRsq}, respectively (see \cref{fig:age-results}, top panels). The
+predictions for Cam-CAN are competitive with a recent state of the art
+prediction \cite{mcpherson2020single}, which used streamline density to
+estimate the brain's structural connectivity and achieved $R^2 = 0.63$. The
+median absolute errors are also lower than the results of a recent study that
 predicted age in a large sample, based on diffusion MRI features

### 2021-01-25 reports/manuscript/supplemental.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

@@
 
-\preprint{NT@UW-20-21}
-%\pacs{}
-\begin{abstract}
-In these supplemental materials we present\ldots
-\end{abstract}
-
 \maketitle
@@
 %\newpage
-\section{Online Methods}
+\section{Methods}
 \label{sec:methods}
@@
 
-Data from the HBN and Cam-CAN studies were processed using the updated
-Python Automated Fiber Quantification toolbox (\texttt{pyAFQ}).
-\todo[inline]{Add pyAFQ citation} In addition to demonstrating the our
-analysis pipeline is robust to changes in the platform and version number of
-tractometry software, the use of the updated \texttt{pyAFQ} capitalized upon
-the following three improvements over the legacy Matlab version
+Data from the HBN and Cam-CAN studies were processed using the updated Python
+Automated Fiber Quantification toolbox (\texttt{pyAFQ})\todo{Add pyAFQ
+citation}. In addition to demonstrating the our analysis pipeline is robust
+to changes in tractometry software, the use of the updated \texttt{pyAFQ}
+capitalized upon the following improvements over the legacy Matlab version
 \begin{enumerate*}[%
@@
     \cite{jensen2005diffusion}) metrics
-    \item the exclusion of the Cingulum Hippocampus bundles, which
-    demonstrated low reliability in the legacy \texttt{mAFQ}.
 \end{enumerate*}
@@
 \subsection{Sparse Group Lasso}
+\label{sec:sgl}
 
@@
 
+\subsubsection{Bagging meta-estimators}
+
+\Cref{sec:sgl} describes a single SGL model. To further improve model
+performance, we create ensemble models composed of $m = 20$ individual SGL
+models using bootstrap aggregation (bagging) \cite{breiman1996bagging}.
+Bagging relies on the underlying assumption that some of the error in a
+single SGL model's prediction stems from a mismatch in the distributions of
+training data used to fit the model and test data used to evaluate its
+performance. To overcome this, bagging invokes the same base estimator (e.g.
+SGL) many times with different training sets, which are created by sampling
+the original training samples with replacement. The bagging meta-estimator's
+prediction is then the average of its constituent estimators' predictions.
+Likewise, when we report the hyperparameter values $\alpha$ and $\lambda$, or
+regression coefficients $\hat{\beta}$, we are refering to these values
+averaged over 20 estimators in the bagging meta-estimator.
+
 \subsubsection{Incorporating target transformations}
@@
 applied to the data before fitting the linear coefficients. For example,
-For the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
+for the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
 \begin{equation}
@@
 
+\begin{figure}[!h]
+    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
+    \caption{{\bf Nested cross-validation}
+        \label{fig:nested-cross-val}
+        We evaluate model quality using a nested $k$-fold cross validation
+        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+        groups and optimal hyperparameters are found for the level-0 training
+        set. To avoid overfitting, the optimal hyperparameters are themselves
+        evaluated using a cross-validation scheme taking place at level-1 of
+        the decomposition, where each level-0 training set is further
+        decomposed into $k_1 = 3$ shuffled groups. In the classification
+        case, the training and test splits are stratified by diagnosis. For
+        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+        $k_0 = 5$.
+    }
+\end{figure}
+
 Because the SGL is not specific to tractometry, we implement its solution as
@@
 
-\todo[inline]{%
-    Rewrite the remainder of this section to reflect \texttt{groupyr} changes.
-}
-
 To objectively evaluate the model performance and guard against over-fitting,
-we used a nested cross-validation scheme, depicted in
-\cref{main:fig:methods:cross-val} for the categorical classification case.
-The subjects (i.e. rows of the feature matrix $\mathbf{X}$ in
-\cref{main:fig:methods:group-structure} and \cref{eq:lm}) are shuffled and
-then decomposed into $k$ batches, hereafter referred to as folds. For
-the ALS dataset we used $k=10$ and for the WH dataset $k=5$. For each
-unique fold, we hold that fold out as the test\textsubscript{outer} set
-and let the remaining data comprise the train\textsubscript{outer} set,
-with the subscript indicating the depth of the nested decomposition.
-We further decompose each train\textsubscript{outer} set into three
-folds, and again for each unique fold, we hold out that fold as the
-test\textsubscript{inner} set and let the remaining data comprise the
-train\textsubscript{inner} set. At level-1 of the decomposition, we fit
-an SGL model using fixed regularization meta-parameters $\alpha$
-and $\lambda$, training the model using train\textsubscript{inner}
-and evaluating the fit on test\textsubscript{inner}. We find
-the optimal values for $\alpha$ and $\lambda$ using
-hyperoptimization, implemented using the hyperopt library's \verb|fmin|
-function\cite{Bergstra_2015} with a tree of Parzen estimators search
-algorithm\cite{bergstra2011algorithms}. For continuous numerical $y$,
-\verb|fmin| searches for meta-parameter values that minimize the median
-absolute error. This can also be done minimizing the root of the mean
-squared error (RMSE) or to maximizing the coefficient of determination
-($R^2$). For binary categorical $y$ \verb|fmin| seeks to maximize the
-classification accuracy. This can also be done maximizing the area
-under the receiver operating curve (ROC AUC) or the average precision.
-Using hyperoptimization, we find optimal regularization parameters and
-$\hat{\beta}$ for each train\textsubscript{outer} set and then use those
-to predict values for data in test\textsubscript{outer}. Thus each
-subject in the dataset has a predicted phenotype derived from a model
-that never saw its particular subject's data.
-
-The above procedure describes $k$-fold cross validation. In fact, we use
-repeated $k$-fold cross validation on the outer level of the decomposition, so
-that the input data is decomposed into $k$ folds, three times. Thus, each
-subject has three predicted phenotypes. We then take the mean predicted value to
-summarize the performance of the model. In the classification case, the
-shuffling into folds is stratified such that each fold has a population that
-preserves the percentage of each class found in the larger input data.
+we used a nested cross-validation scheme, which is depicted for the binary
+classification case in \cref{fig:nested-cross-val}. The subjects (i.e. rows
+of the feature matrix $\mathbf{X}$ in \cref{main:fig:methods:group-structure}
+and \cref{eq:lm}) are first shuffled and then decomposed into $k_0$ batches,
+hereafter referred to as folds. For the ALS and WH datasets, we used $k_0 =
+10$ and for the HBN and Cam-CAN datasets, $k_0 = 5$. For each unique fold, we
+hold that fold out as the test\textsubscript{0} set and let the remaining
+data comprise the train\textsubscript{0} set, with the subscript indicating
+the depth of the nested decomposition. We further decompose each
+train\textsubscript{0} set into three folds, and again for each unique fold,
+we hold out that fold as the test\textsubscript{1} set and let the remaining
+data comprise the train\textsubscript{1} set. At level-1 of the
+decomposition, we fit an SGL model using fixed regularization meta-parameters
+$\alpha$ and $\lambda$, training the model using train\textsubscript{1} and
+evaluating the fit on test\textsubscript{1}. We find the optimal values for
+$\alpha$ and $\lambda$ using sequential model based optimization, implemented
+using the scikit-optimize \verb|BayesSearchCV| class\cite{scikit-optimize}.
+For continuous numerical $y$, \verb|BayesSearchCV| searches for
+meta-parameter values that maximize the $R^2$ averaged over test sets. For
+binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
+classification accuracy. Using hyperoptimization, we find optimal
+regularization parameters and $\hat{\beta}$ for each train\textsubscript{0}
+set and then use those to predict values for data in test\textsubscript{0}.
+Thus each subject in the dataset has a predicted phenotype derived from a
+model that never saw its particular subject's data. In the classification
+case, the shuffling into folds is stratified such that each fold has a
+population that preserves the percentage of each class found in the larger
+input data.
 
@@
 produce the results herein is also available in
-\url{https://doi.org/10.5281/zenodo.3585942}.
-\todo[inline]{Update version here}
+\url{https://doi.org/10.5281/zenodo.3585942}\todo{Update version here}.
 AFQ-Insight reads the target and feature data that has been processed by AFQ
@@
 format \cite{yeatman2018browser} and represents them internally as
-\lstinline{DataFrame} objects from the pandas Python
-library \cite{mckinney2010data}. The software provides different options for
-imputing missing data in the feature matrix. Missing interior nodes are imputed
-using linear interpolation. For missing exterior nodes, the user may choose
-between linear extrapolation and constant forward(back)-fill. Imputation uses
-only values from adjacent nodes in the same white matter bundle in the same
-subject so there is no danger of data leakage from other subjects. It uses the
-scikit-learn \cite{scikit-learn} library to decompose input data into separate
-test and train datasets, to scale each feature to have zero mean and
+\lstinline{DataFrame} objects from the pandas Python library
+\cite{mckinney2010data}. The software provides different options for imputing
+missing data in the feature matrix. Missing interior nodes are imputed using
+linear interpolation. For missing exterior nodes, the user may choose between
+linear extrapolation and constant forward(back)-fill. Imputation uses only
+values from adjacent nodes in the same white matter bundle in the same
+subject so there is no danger of data leakage from other subjects. It uses
+the scikit-learn \cite{scikit-learn} library to decompose input data into
+separate test and train datasets, to scale each feature to have zero mean and
 unit variance, and to evaluate each fit in the hyperparameter search using
 appropriate classification and regression metrics such as accuracy, area
-under the receiver operating curve (AUC ROC), and coefficient of determination
-($R^2$). For each set of hyperparameters, we solve the SGL using a custom
-proximal operator supplied to the C-OPT library\cite{copt}. Appropriate
-hyperparameters are found using the hyperopt library\cite{Bergstra_2015}.
+under the receiver operating curve (AUC ROC), and coefficient of
+determination ($R^2$). For each set of hyperparameters, we solve the SGL
+problem using the \texttt{groupyr} library \cite{groupyr}. Appropriate
+hyperparameters are found using the scikit-optimize library
+\cite{scikit-optimize}.
 
@@
 along the length of eighteen bundles: 
-right corticospinal (CST\_R),
-left corticospinal (CST\_L),
-right uncinate (UNC\_R),
-left uncinate (UNC\_L),
-left inferior fronto-occipital fasciculus (IFO\_L),
-right inferior fronto-occipital fasciculus (IFO\_R),
-right arcuate (ARC\_R),
-left arcuate (ARC\_L),
-right thalamic radiation (ATR\_R),
-left thalamic radiation (ATR\_L),
-right cingulum cingulate (CGC\_R),
-left cingulum cingulate (CGC\_L),
-callosum forceps major (FP),
-callosum forceps minor (FA),
-right inferior longitudinal fasciculus (ILF\_R),
-left inferior longitudinal fasciculus (ILF\_L),
-right superior longitudinal fasciculus (SLF\_R),
-and left superior longitudinal fasciculus (SLF\_L).
+right corticospinal (CSTR),
+left corticospinal (CSTL),
+right uncinate (UNCR),
+left uncinate (UNCL),
+left inferior fronto-occipital fasciculus (IFOL),
+right inferior fronto-occipital fasciculus (IFOR),
+right arcuate (ARCR),
+left arcuate (ARCL),
+right thalamic radiation (ATRR),
+left thalamic radiation (ATRL),
+right cingulum cingulate (CGCR),
+left cingulum cingulate (CGCL),
+callosum forceps major (CFP),
+callosum forceps minor (CFA),
+right inferior longitudinal fasciculus (ILFR),
+left inferior longitudinal fasciculus (ILFL),
+right superior longitudinal fasciculus (SLFR),
+and left superior longitudinal fasciculus (SLFL).
 We display results for two different diffusion metrics: fractional anisotropy
-(fa) and mean diffusivity (md). We use lower-case letters to abbreviate the
-diffusion metrics and distinguish fractional anisotropy (fa) from the
-callosum forceps minor (FA).
+(FA) and mean diffusivity (MD), which are extracted from different diffusion
+models depending on the dataset: diffusion tensor imaging (DTI) for the ALS
+and WH datasets and diffusion kurtosis imaging (DKI) for the HBN and Cam-CAN
+datasets \cite{jensen2005diffusion}. The diffusion metric is always plotted
+on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on
+the twin axis on the right-hand-side. The scale of the $\hat{\beta}$-axis is
+shared between the FA and MD metrics so that one can compare the relative
+imporance of each metric.
 
@@
         {%
-            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
             coefficients for ALS classification.
@@
 \Cref{fig:als-bp:fa,fig:als-bp:md} show the bundle profiles and regression
-coefficients for the ALS dataset fa and md metrics, respectively. The scale
-of the $\hat{\beta}$ axes is shared between the fa and md figures to
-highlight the relative importance of the fa features over the md features.
+coefficients for the ALS dataset FA and MD metrics, respectively. These
+figures reinforce the findings in the main text that ALS is localized to the
+corticospinal tract. In this study, SGL selected the right corticospinal
+tract (CSTR) as important and regularized coefficients in the CSTL. Yet,
+\cref{fig:als-bp:fa} also shows group FA differences in the CSTL. This
+highlighted a potential drawback of the SGL method, discussed in the main
+text in the context of age regression. Namely, SGL is not guaranteed to
+identify \emph{all} important features. In this case, if the diagnostic
+signal in the CSTL is redundant to that in the CSTR, SGL will regularize the
+CSTL features, thereby reducing its sparsity penalty without any
+corresponding increase in loss. This parsimony cuts both ways; it is a
+feature of the method when one seeks an efficient predictive model, but is a
+defect of the method when one wants an exhaustive explanation of feature
+importance. We will use the phrase ``parsimonious pitfall'' to refer to the
+case when SGL regularizes away redundant but obviously important features.
 
@@
         {%
-            \bf Mean diffusivity (md) Bundle profiles and $\hat{\beta}$
+            \bf Mean diffusivity (MD) Bundle profiles and $\hat{\beta}$
             coefficients for ALS classification.
@@
         {%
-            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
             coefficients for age regression in the WH dataset.
@@
 
-\hspace{1em}
+\Cref{fig:wh-bp:fa,fig:wh-bp:md} show the bundle profiles and regression
+coefficients for the WH dataset. In contrast to the ALS classification case,
+the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting
+the interpretation that aging is a large and continuous whole-brain process.
+These figures also show that SGL behaves much more like the lasso than the group
+lasso, as discussed in the main text. The parsimonious pitfall is most evident in
+the IFOL and IFOR bundles in \cref{fig:wh-bp:md}.
 
@@
         {%
-            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
+            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
             coefficients for age regression in the WH dataset.
@@
         {%
-            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
             coefficients for age regression in the HBN dataset.
@@
 
-\hspace{1em}
+\Cref{fig:hbn-bp:fa,fig:hbn-bp:md} show the bundle profiles and regression
+coefficients for the HBN dataset. Like the WH dataset, the $\hat{\beta}$
+coefficients are distributed widely through the brain and SGL behaves more
+like the lasso than the group lasso. In contrast the the WH results,
+the bundle profiles show different behaviors. For example the SLFL and SLFR
+bundle profiles in \cref{fig:wh-bp:md} and \cref{fig:hbn-bp:md} have
+different concavity. This is unsurprising, however, given the differences
+between these datasets 
+\begin{enumerate*}[%
+    label=(\roman*),%
+    before=\unskip{: },%
+    itemjoin={{, }},%
+    itemjoin*={{, and }}]
+    \item different diffusion models, with DTI for the WH dataset and DKI for
+    the HBN dataset
+    \item different age ranges and distributions (which is evident in the
+    figure legends), with HBN being a developmental dataset, while WH is a
+    lifespan maturation dataset
+    \item different anatomical extents, with the WH streamlines truncated to
+    remain with the bundle's bounding regions of interest (the default
+    behavior in the legacy \texttt{mAFQ}) and the HBN streamlines allowed
+    to retain their full extent from whole-brain tractography (the default
+    behavior in \texttt{pyAFQ}).
+\end{enumerate*}
+Thus, one should use caution when comparing bundle profiles and $\hat{\beta}$
+coefficients between the WH, HBN, and Cam-CAN models.
+The parsimonious pitfall is most evident in the UNCL, UNCR, ARCL, SLFL, and
+SLFR bundles in \cref{fig:hbn-bp:md}.
 
@@
         {%
-            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
+            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
             coefficients for age regression in the HBN dataset.
@@
         {%
-            \bf Fractional anisotropy (fa) bundle profiles and $\hat{\beta}$
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
             coefficients for age regression in the Cam-CAN dataset.
@@
 
+\Cref{fig:cc-bp:fa,fig:cc-bp:md} show the bundle profiles and regression
+coefficients for the Cam-CAN dataset. Like the WH and HBN datasets, the
+$\hat{\beta}$ coefficients are distributed widely through the brain and SGL
+behaves more like the lasso than the group lasso. As before, one must be
+cautious about comparing bundle profiles and $\hat{\beta}$ coefficients
+between models. While the HBN and Cam-CAN datasets share the same diffusion
+model and refrain from clipping streamlines, the age distributions for the
+two are roughly disjoint, with the WH age distribution straddling the two.
+The parsimonious pitfall is again evident in the UNCL, UNCR, ARCL, SLFL, and
+SLFR bundles in \cref{fig:cc-bp:md}.
+\todo[inline]{We could say more here but it's not an ``aging'' paper so I
+don't really want to. I only want to stress that you have to be careful
+comparing $\hat{\beta}$ across models.}
+
 \begin{figure*}
@@
         {%
-            \bf Mean diffusivity (md) bundle profiles and $\hat{\beta}$
+            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
             coefficients for age regression in the Cam-CAN dataset.

### 2021-01-25 reports/manuscript/sections/introduction.tex
Shortens introduction.

@@
 
-Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique
-view into the physical properties of the connections that comprise
-the brain white matter. While the measurements are usually conducted
-with voxels at the millimeter scale, water molecules within each voxel
-diffuse with characteristic lengths at the micrometer scale, providing
-aggregate information about the physical structure of the white matter,
-including the density of axons and distribution of fiber
-orientations within each voxel \cite{wandell2016clarifying}. Even though
-metrics derived from diffusion measurements are ambiguous in terms
-of their underlying biological interpretation \cite{Jones2013-xv},
-analyzing the variance in these properties has proven useful in
-characterizing individual differences in cognitive function,
-characterizing differences between populations and detecting brain
-abnormalities associated with disease \cite{Thomason2011-qn}.
-
-To relate the diffusion in each voxel to the macro-structure of
-long-range connections between different brain regions, methods for
-computational tract-tracing from diffusion MRI, or tractography, combine
-the estimates of fiber orientations in each voxel to form streamlines
-that traverse the volume of the white matter \cite{Conturo1999-je,
-Mori2002-qi}. These methods have been under increased scrutiny and
-several lines of investigation have raised critiques of their validity
-\cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
-have been efforts to shore up the inferences made with these methods
-\cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
-Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
-tracts requires extraordinary evidence, and delineating
-the exact cortical termination of the streamlines in the gray matter
-is still prone to error, there is little dispute that tractography
-can accurately define the location of several major white matter
-tracts that are known to exist within the core of the white matter
-\cite{Maier-Hein2017-vb, Catani2002-vu}.
-
-Leveraging this fact, one of the most powerful methods currently
-available to put macro- and micro-structure together is
-\emph{tractometry}: assessment of the physical properties of the white
-matter along specific tracts \cite{Bells2011-cf}. Though there are
-several different available implementations of this overall idea,
-the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
-Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
-the parts of the white matter that belong to different major ``tracts''
-(i.e. anatomical or functional groups of white matter fibers), such as
-the corticospinal tract or arcuate fasciculus, assigning tractography
-generated streamlines to ``bundles,'' which approximate the anatomical
-tracts, and sampling biophysical properties, such as fractional
-anisotropy (FA) or mean diffusivity (MD), along the length of these bundles.
-the parts of the white matter that belong to different major tracts
-(i.e. anatomical or functional groups of white matter fibers), such as
-the corticospinal tract or arcuate fasciculus, assigning tractography
-generated streamlines to ``bundles,'' which approximate the anatomical
-tracts, and sampling biophysical properties (such as fractional
-anisotropy or mean diffusivity) along the length of these bundles. In
-some previous tractometry-based studies, tissue properties along the
+Non-invasive methods for measuring human brain structure and function have revolutionized our understanding of brain function. These measurements
+have demonstrated that interactions between networks of brain regions give rise to coordinated information processing and to the complex adaptive behavior that characterizes human cognition.
+Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into the physical properties of the connections that comprise these networks, by sensitizing the measurement to the directional
+diffusion of water in each voxel \cite{wandell2016clarifying}.
+% While the measurements are usually conducted
+% with voxels at the millimeter scale, water molecules within each voxel
+% diffuse with characteristic lengths at the micrometer scale, providing
+% aggregate information about the physical structure of the white matter,
+% including the density of axons and distribution of fiber
+% orientations within each voxel \cite{wandell2016clarifying}. Even though
+% metrics derived from diffusion measurements are ambiguous in terms
+% of their underlying biological interpretation \cite{Jones2013-xv},
+% analyzing the variance in these properties has proven useful in
+% characterizing individual differences in cognitive function,
+% characterizing differences between populations and detecting brain
+% abnormalities associated with disease \cite{Thomason2011-qn}.
+Methods for computational tract-tracing from diffusion MRI, or tractography, combine the estimates of fiber orientations in each voxel to form streamlines
+that traverse the volume of the white matter~\cite{Conturo1999-je,
+Mori2002-qi}. A variety of methods can be used to delineate the
+trajectory of major neural pathways among these streamlines~\cite{yeatman2012tract}.
+% These methods have been under increased scrutiny and
+% several lines of investigation have raised critiques of their validity
+% \cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
+% have been efforts to shore up the inferences made with these methods
+% \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
+% Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
+% tracts requires extraordinary evidence, and delineating
+% the exact cortical termination of the streamlines in the gray matter
+% is still prone to error, there is little dispute that tractography
+% can accurately define the location of several major white matter
+% tracts that are known to exist within the core of the white matter
+% \cite{Maier-Hein2017-vb, Catani2002-vu}.
+\emph{Tractometry} uses the results of tractography and models
+of tissue biophysics based on the patterns of diffusion in each measurement
+voxel to assess the physical properties of the white matter along specific pathways~\cite{Bells2011-cf}.
+%Though there are several different available implementations of this overall
+%idea, the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
+%Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
+% the parts of the white matter that belong to different major ``tracts''
+% (i.e. anatomical or functional groups of white matter fibers), such as
+% the corticospinal tract or arcuate fasciculus, assigning tractography
+% generated streamlines to ``bundles,'' which approximate the anatomical
+% tracts, and sampling biophysical properties, such as fractional
+% anisotropy (FA) or mean diffusivity (MD), along the length of these bundles.
+% the parts of the white matter that belong to different major tracts
+% (i.e. anatomical or functional groups of white matter fibers), such as
+% the corticospinal tract or arcuate fasciculus, assigning tractography
+% generated streamlines to ``bundles,'' which approximate the anatomical
+% tracts, and sampling biophysical properties (such as fractional
+% anisotropy or mean diffusivity) along the length of these bundles.
+In some previous tractometry-based studies, tissue properties along the
 length of each tract were summarized by taking the mean along each
@@
 about each individual's white matter, it also presents statistical
-challenges due to the dimensionality of the data. Based on tractometry,
-researchers may choose to compare different individuals to each other.
-This is usually done according to one of the following approaches:
-
-\begin{enumerate}
-
-\item Mass univariate approaches: In this approach comparisons between
-groups or across individuals are done independently at each node
-of each bundle, for each one of the diffusion metrics available at
-that point. This approach is exhaustive, but statistical power is
-compromised by a multiple comparison problem. Different approaches
-can be taken to resolving this challenge. For example, Colby and
-colleagues \cite{colby2012} used a non-parametric resmapling approach to
-correct for family-wise error across the different possible comparisons
-\cite{Nichols2002-zu, Nichols2003-yy}.
-
-\item Region of interest(ROI)-based approaches: An alternative that
+challenges due to the dimensionality of the data. In past work,
+comparisons between groups or across individuals were done
+independently at each node of each bundle, for each one of the
+diffusion metrics available at that point. This approach is exhaustive, but
+statistical power is compromised by a multiple comparison problem
+\cite{colby2012, Nichols2002-zu, Nichols2003-yy}. An alternative that
 circumvents the multiple comparison problem is to select just a few
@@
 segments of these tracts based on \emph{a priori} hypotheses. This
-approach is very powerful when the biological basis of the process
+approach is appropriate when the biological basis of the process
 of interest is relatively well understood (for a recent example, see
-\cite{huber2018rapid}).
+\cite{huber2018rapid}). Sometimes, these approaches are combined: an
+bundle is selected based on \emph{a priori} knowledge, and all the data
+in the bundle of interest are used together to fit a model that can
+predict differences between individuals \cite{dayan2016profilometry}.
 
-\item ROI-based selection, followed by multivariate analysis: Here,
-an ROI is selected based on \emph{a priori} knowledge, and all the
-nodes or voxels in the ROI are used together to fit a model that can
-predict differences between individuals. An example of that is the
-``profilometry'' framework, in which different diffusion metrics
-from a single tract are combined together to provide input to a
-multivariate analysis of covariance, and linear discriminant analysis
-\cite{dayan2016profilometry}.
+% Different approaches can be taken to resolving this challenge. For
+% example, Colby and colleagues \cite{colby2012} used a non-parametric resmapling approach to
+% correct for family-wise error across the different possible comparisons
+% \cite{Nichols2002-zu, Nichols2003-yy}.
+% Based on tractometry, researchers may choose to compare different individuals to each other. This is usually done according to one of the following approaches:
+% \begin{enumerate}
+% \item Mass univariate approaches: In this approach
 
-\end{enumerate}
+% \item Region of interest(ROI)-based approaches:
+% An alternative that
+% circumvents the multiple comparison problem is to select just a few
+% tracts to compare in each individual, or even focusing on particular
+% segments of these tracts based on \emph{a priori} hypotheses. This
+% approach is very powerful when the biological basis of the process
+% of interest is relatively well understood (for a recent example, see
+% \cite{huber2018rapid}).
 
-Generally speaking, analysis methods should balance predictive
-accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}.
-Accordingly, tractometry analysis should simultaneously capitalize on
-all the data across all tracts to make the best possible prediction,
-while also retaining and elucidating spatial information about the
-locations that are most informative for a prediction. In the present
-work, we developed a novel framework for analysis of tractometry that
-simultaneously selects the features for analysis, and fits a model
-to these features. We use a linear modeling approach, which aims to
-predict phenotypical variance in a group of subjects, based on a linear
-combination of the features estimated with tractometry.
+% \item ROI-based selection, followed by multivariate analysis: Here,
+% an ROI is selected based on \emph{a priori} knowledge, and all the
+% nodes or voxels in the ROI are used together to fit a model that can
+% predict differences between individuals. An example of that is the
+% ``profilometry'' framework, in which different diffusion metrics
+% from a single tract are combined together to provide input to a
+% multivariate analysis of covariance, and linear discriminant analysis
+% \cite{dayan2016profilometry}.
+
+%\end{enumerate}
+
+The present work aims to balance predictive
+accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}
+by capitalizing on all of the data across all bundles, while also retaining and
+elucidating spatial information about the locations that are most informative
+for discriminative performance. To do so, we use a linear modeling approach,
+which aims to redict phenotypical variance in a group of subjects, based on a
+linear combination of the features estimated with tractometry.
+
+% Generally speaking, analysis methods should balance predictive
+% accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}.
+% Accordingly, tractometry analysis should simultaneously capitalize on
+% all the data across all tracts to make the best possible prediction,
+% while also retaining and elucidating spatial information about the
+% locations that are most informative for a prediction. In the present
+% work, we developed a novel framework for analysis of tractometry that
+% simultaneously selects the features for analysis, and fits a model
+% to these features. We use a linear modeling approach, which aims to
+% predict phenotypical variance in a group of subjects, based on a linear
+% combination of the features estimated with tractometry.
 
@@
 regime is the target of several statistical learning techniques, and
-is often solved by various forms of regularization. For example,
-Tikhonov regularization shrinks the solution such that the sum of
-squared contributions from the individual features are minimized
-\cite{Hoerl2000-ij}. Another solution to the problem is provided by
-the Lasso algorithm, which instead minimizes the sum of the absolute
-values of contributions of each feature \cite{Tibshirani1996-qs}. This
+is often solved by various forms of regularization.
+
+% For example, Tikhonov regularization shrinks the solution such that the sum of
+% squared contributions from the individual features are minimized
+% \cite{Hoerl2000-ij}. Another solution to the problem is provided by
+% the
+
+The Lasso algorithm minimizes the sum of the absolute values of
+contributions of each feature \cite{Tibshirani1996-qs}. This
 tends to shrink to zero the contributions of many of the features,
@@
 tractomery lend themselves to grouping based on the tracts from which
-each measurement is taken, GL and SGL could provide a useful tool
+each measurement is taken, GL and SGL provide a useful tool
 for linear model fitting in problems of this form. Here we, first,
@@
 tractometry data and, second, demonstrate the power and flexibility of
-this approach by applying it to both classification (disease diagnosis)
-and continuous prediction (age) problems from previously published
-studies \cite{sarica2017corticospinal, yeatman2014lifespan}.
+this approach by applying it to both classification
+and continuous prediction problems.

### 2021-01-25 reports/manuscript/sections/introduction.tex
Whitespace.

@@
 
-Non-invasive methods for measuring human brain structure and function have revolutionized our understanding of brain function. These measurements
-have demonstrated that interactions between networks of brain regions give rise to coordinated information processing and to the complex adaptive behavior that characterizes human cognition.
-Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into the physical properties of the connections that comprise these networks, by sensitizing the measurement to the directional
+Non-invasive methods for measuring human brain structure and function have
+revolutionized our understanding of brain function. These measurements
+have demonstrated that interactions between networks of brain regions give rise
+to coordinated information processing and to the complex adaptive behavior that
+characterizes human cognition. Diffusion-weighted Magnetic Resonance Imaging
+(dMRI) provides a unique view into the physical properties of the connections
+that comprise these networks, by sensitizing the measurement to the directional
 diffusion of water in each voxel \cite{wandell2016clarifying}.
@@
 % abnormalities associated with disease \cite{Thomason2011-qn}.
-Methods for computational tract-tracing from diffusion MRI, or tractography, combine the estimates of fiber orientations in each voxel to form streamlines
+Methods for computational tract-tracing from diffusion MRI, or tractography,
+combine the estimates of fiber orientations in each voxel to form streamlines
 that traverse the volume of the white matter~\cite{Conturo1999-je,
 Mori2002-qi}. A variety of methods can be used to delineate the
-trajectory of major neural pathways among these streamlines~\cite{yeatman2012tract}.
+trajectory of major neural pathways among these
+streamlines~\cite{yeatman2012tract}.
 % These methods have been under increased scrutiny and
@@
 of tissue biophysics based on the patterns of diffusion in each measurement
-voxel to assess the physical properties of the white matter along specific pathways~\cite{Bells2011-cf}.
+voxel to assess the physical properties of the white matter along specific
+pathways~\cite{Bells2011-cf}.
 %Though there are several different available implementations of this overall
@@
 % Different approaches can be taken to resolving this challenge. For
-% example, Colby and colleagues \cite{colby2012} used a non-parametric resmapling approach to
+% example, Colby and colleagues \cite{colby2012} used a non-parametric
+% resmapling approach to
 % correct for family-wise error across the different possible comparisons
 % \cite{Nichols2002-zu, Nichols2003-yy}.
-% Based on tractometry, researchers may choose to compare different individuals to each other. This is usually done according to one of the following approaches:
+% Based on tractometry, researchers may choose to compare different individuals
+% to each other. This is usually done according to one of the following
+% approaches:
 % \begin{enumerate}

### 2021-01-25 reports/manuscript/paper.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.
Mostly work in results section.

@@
                floatfix,%
-               endfloats*]{revtex4-2}
+               endfloats*]{revtex4-1}
 \usepackage[T1]{fontenc}
@@
     This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
-    National Institutes for Mental Health and by a grant from the Gordon \& Betty
+    National Institutes for Mental Health, by a grant from the Gordon \& Betty
     Moore Foundation and the Alfred P. Sloan Foundation to the University of
-    Washington eScience Institute Data Science Environment. We would like to thank
+    Washington eScience Institute Data Science Environment, and by the Google Cloud Platform Academic Research Credits Program.
+    We would like to thank
     Scott Murray for a useful discussion of the SGL method and Mareike Grotheer for

### 2021-01-25 reports/manuscript/sections/conclusion.tex
Mostly work in results section.

@@
 We present here a novel method for analysis of dMRI tractometry data that
-relies on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
+relies on the Sparse Group Lasso \cite{simon2013sparse} to make accurate
 predictions of phenotypic properties of individual subjects while,
-simultaneously, (b) identifying the features of the white matter that are
-most important for this prediction in a completely data-driven approach. The
-method is broadly applicable to a wide range of research questions: it
+simultaneously, identifying the features of the white matter that are
+most important for this prediction. The method is data-driven and it is broadly applicable to a wide range of research questions: it
 performs well in predicting both continuous variables, such as biological
@@
 cortico-spinal tract. This recapitulates the results of previous analysis of
-these same data, using a targeted ROI-based approach
+these same data, using a bundle-of-interest approach
 \cite{sarica2017corticospinal}. In contrast, for the analysis of biological
@@
 \cref{fig:class-results:false-positives,fig:class-results:false-negatives}) .
-Thus, this multivariate analysis approach both (a) achieves high
-cross-validated accuracy for precision medicine applications of dMRI data and
-(b) identifies relevant features of brain anatomy that can further our
+Thus, this multivariate analysis approach achieves high
+cross-validated accuracy for precision medicine applications of dMRI data and identifies relevant features of brain anatomy that can further our
 neuroscientific understanding of clinical disorders.
@@
 scientific questions \cite{jernigan2016ping, jernigan2018abcd,
-alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
-these data pose a substantial challenge. Dimensionality reduction with
-tractometry, followed by analysis with the approach we present here promises to
-capitalize on the wealth of data and on the co-measurement of interesting and
-important phenotypical data about brain health and about the participants'
-cognitive abilities. We also expect the group-regularized approach to improve
-with larger datasets.
+alexander2017open, Miller2016-hw, VanEssen2012}, but the volume and
+complexity of these data pose substantial challenges. Tractometry
+followed by analysis with SGL provide a promising approach to
+distill meaningful insights from the wealth of data measured in these efforts.
+%We also expect the group-regularized approach to improve
+% with larger datasets. <= ARIEL : I feel like we've demonstrated that already
+% with the age regression results
 
@@
 these recordings can form features (neurons) and groups (neurons within
-an anatomical region). More ambitiously perhaps, this approach may be
-used to understand the role of correlations in so-called resting-state
-fMRI time-series and behavior, where pairwise correlations between
-voxels in different anatomical regions are features in the matrix and
-features may be grouped by pairs of anatomical regions. Given the large
-number of voxels in the surface of the gray matter and given that
-correlations increase the number of features by a factor of $n^2$, this
-would pose a challenging problem to solve using SGL.
+an anatomical region).
+
+% More ambitiously perhaps, this approach may be
+% used to understand the role of correlations in so-called resting-state
+% fMRI time-series and behavior, where pairwise correlations between
+% voxels in different anatomical regions are features in the matrix and
+% features may be grouped by pairs of anatomical regions. Given the large
+% number of voxels in the surface of the gray matter and given that
+% correlations increase the number of features by a factor of $n^2$, this
+% would pose a challenging problem to solve using SGL.
 
@@
 The method is packaged as open-source software called AFQ-Insight
-that is openly available, and provides a clear API to allow
+that is openly available (ARIEL: ADD URL), and provides a clear API to allow
 for extensions of the method. The sofware integrates within a
 broader automated fiber quantification software ecosystem: AFQ
-\cite{yeatman2012tract}, which extracts tractometry data from raw and
-processed dMRI datasets, as well as AFQ-Browser, which visualizes
-tractometry data and facilitates sharing of the results of dMRI studies
-\cite{yeatman2018browser}. To facilitate reproducibility and ease use
-of the software, the results presented
-in this paper are also provided in
-\url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks} as a series of Jupyter notebooks
+\cite{yeatman2012tract} and pyAFQ (https://yeatmanlab.github.io), which extract tractometry data from raw and processed dMRI datasets, as well as AFQ-Browser, which visualizes tractometry data and facilitates sharing of the results of dMRI studies \cite{yeatman2018browser}.
+To facilitate reproducibility and ease use of the software, the results presented
+in this paper are also provided in \url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks} as a series of Jupyter notebooks
 \cite{kluyver2016jupyter}.

### 2021-01-25 reports/manuscript/sections/results.tex
Mostly work in results section.

@@
         controls on the left, patients on the right, predicted controls in
-        blue, and predicted patients in orange. So orange dots on the left
+        blue, and predicted patients in orange. This is, orange dots on the left
         represent false positives, while blue dots on the right represent
@@
 
-We developed a method for analyzing dMRI tractometry data with SGL. We
-demonstrate the use of this method on four previously published datasets in
+We developed a method for analyzing dMRI tractometry data that uses the Sparse
+Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
+We demonstrate the use of this method on four different datasets in
 both a classification setting and a regression setting.
@@
 
-Using data from a previous study of the corticospinal tract (CST) profile and
-ALS \cite{sarica2017corticospinal}, we tested the performance of SGL in a
+Using data from a previous study of patients with amyotrophic lateral sclerosis (ALS)~\cite{sarica2017corticospinal}, we tested the performance of SGL in a
 classification setting. The previous study predicted ALS status with a mean
-accuracy of 80\% using a random forest algorithm based on a priori selection
-of features within the CST. SGL delivers competitive
-predictive performance, with a cross-validated accuracy of {\alsAccuracy}\%
-and an area under the receiver operating characteristic curve (ROC AUC) of
-{\alsRocAuc}, all without the need for a priori feature engineering. The
-results of the classification prediction are shown in
-\cref{fig:class-results:probs} with ``ground-truth'' ALS status separated
-into columns, and predicted ALS status encoded by color. In addition to this
+accuracy of 80\% using a random forest algorithm based on \emph{a priori}
+selection of features only within the CST bundle-of-interest.
+SGL delivers improved predictive performance, with a cross-validated accuracy of {\alsAccuracy}\% and an area under the receiver operating characteristic curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature engineering (Figure \cref{fig:class-results:probs}).
+In addition to this
 classification performance, SGL also identifies the white matter tracts most
@@
 identifying the portions of the brain that were selected \emph{a priori} in
-the previous study from which we collected our data
+the previous study from which we obtained the data
 \cite{sarica2017corticospinal}.
@@
 $\alpha$, the regularization hyperparameter that controls the mixture of the
-group lasso and lasso penalties
+group lasso and lasso penalties, selected through nested cross-validation
 (see \cref{supp:eq:sgl} of the supplemental material \cite{supplement}).
@@
 insight. We found that mislabelled subjects are outliers relative to their
-group with respect to diffusion features of the CST.
-\Cref{fig:class-results:false-positives,fig:class-results:false-negatives}
-depicts the group FA values along with FA values of mislabelled subjects,
-four false negatives and three false-positives. The false positive
-classifications have reduced FA in one or more of the three sections of the
-CST where $\norm*{\hat{\beta}}$ is large
+group with respect to diffusion features of the CST (Figure
+\Cref{fig:class-results:false-positives,fig:class-results:false-negatives}).
+The false positive classifications have reduced FA in one or more of the three
+sections of the CST where $\norm*{\hat{\beta}}$ is large
 \cref{fig:class-results:tract-profiles}. The false negative subjects have FA
-profiles that oscillate between the two group means. Thus, the SGL method
-fails comprehensibly.
+profiles that oscillate between the two group means. Thus, when the SGL
+method predicts incorrectly this is done in a comprehensible manner.
 
@@
 biomarkers are subject to unique challenges and tend to be noncausative. Our
-interest in aging here relies on its utility as a methodological benthmark.
+interest in aging here relies on its utility as a methodological benchmark.
 Biological age operates on a natural scale, with meaningful and easily
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} the HBN and Cam-CAN datasets.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
 
@@
 median absolute errors are also lower than the results of a recent study that
-predicted age in a large sample, based on diffusion MRI features
-\cite{Richard2018-ux}.
+predicted age in a large sample that included the Cam-CAN data, and was based
+on diffusion MRI features \cite{Richard2018-ux}.
 

### 2021-01-25 reports/manuscript/sections/introduction.tex
Mostly work in results section.
Update reports/manuscript/sections/introduction.tex
Co-authored-by: Adam Richie-Halford <richford@users.noreply.github.com>

@@
     {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{{\bf Tractometry data lineage}
+    \caption{{\bf Tractometry data flow}
         \label{fig:methods}
@@
 tractomery lend themselves to grouping based on the tracts from which
-each measurement is taken, GL and SGL provide a useful tool
+each measurement is taken, GL and SGL provide useful tools
 for linear model fitting in problems of this form. Here we, first,

### 2021-01-25 reports/manuscript/sections/introduction.tex
Add Jason Yeatman's suggestions

@@
 comparisons between groups or across individuals were done
-independently at each node of each bundle, for each one of the
-diffusion metrics available at that point. This approach is exhaustive, but
+independently at each node of each bundle, for each
+diffusion metric. This approach is exhaustive, but
 statistical power is compromised by a multiple comparison problem
@@
 of interest is relatively well understood (for a recent example, see
-\cite{huber2018rapid}). Sometimes, these approaches are combined: an
+\cite{huber2018rapid}). Sometimes, these approaches are combined: a
 bundle is selected based on \emph{a priori} knowledge, and all the data
@@
 
-The present work aims to balance predictive
-accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}
-by capitalizing on all of the data across all bundles, while also retaining and
-elucidating spatial information about the locations that are most informative
-for discriminative performance. To do so, we use a linear modeling approach,
-which aims to redict phenotypical variance in a group of subjects, based on a
-linear combination of the features estimated with tractometry.
+The present work aims to balance predictive accuracy with descriptive power
+\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
+data across all bundles, while also retaining and elucidating spatial
+information about the locations that are most informative for discriminative
+performance. To do so, we use a linear modeling approach, which aims to
+redict phenotypical variance in a group of subjects (or classify group
+membership), based on a linear combination of the features estimated with
+tractometry.
 

### 2021-01-25 reports/manuscript/supplemental.tex
Fix internal cref to the SGL section in supplemental.tex
Add Jason Yeatman's suggestions

@@
 
-\title{Supplemental Material: Multidimensional analysis and detection of informative features in human white matter}
+\title{Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter}
 
@@
 
-Four different previously-published datasets were used here:
+Four different datasets were used here:
 
@@
 
-\Cref{sec:sgl} describes a single SGL model. To further improve model
+The previous section describes a single SGL model. To further improve model
 performance, we create ensemble models composed of $m = 20$ individual SGL

### 2021-01-26 reports/manuscript/paper.tex
Add Jason Yeatman's suggestions
Put all paper LaTeX in the same file as required by Nature methods

@@
 
-\title{Multidimensional analysis and detection of informative features in human white matter}
+\title{Multidimensional analysis and detection of informative features in human brain white matter}
 
@@
 
-% Please keep the abstract below 300 words
 \input{output}
-\input{abstract}
+
+\begin{abstract}
+    % Abstracts should be unreferenced and typically around 150 words
+    The white matter contains long-range connections between different
+    brain regions and the organization of these connections holds important
+    implications for brain function in health and disease. Tractometry
+    uses diffusion-weighted magnetic resonance imaging (dMRI)
+    to quantify tissue properties (e.g. fractional anisotropy (FA),
+    mean diffusivity (MD), etc.), along the trajectories of these
+    connections.
+    % \cite{yeatman2012tract}.
+    Statistical inference from
+    tractometry usually either averages these quantities along
+    the length of each bundle in each individual or performs analysis
+    point-by-point along each bundle, with group comparisons or regression
+    models computed separately for each point along every one of the bundles.
+    These approaches are limited in their sensitivity, in the former case, or
+    in their statistical power, in the latter.
+    In the present work, we developed a method based on the sparse group
+    lasso (SGL)
+    % \cite{simon2013sparse}
+    that takes into account tissue
+    properties measured along all of the bundles, and selects informative
+    features by enforcing sparsity, not only at the level of individual
+    bundles, but also across the entire set of bundles and all of the measured
+    tissue properties.
+    % The sparsity penalties for each of these constraints
+    % is identified using a nested cross-validation scheme that guards
+    % against over-fitting and simultaneously identifies the correct
+    % level of sparsity.
+    We demonstrate the accuracy of the method in two
+    settings: i) In a classification setting, patients with amyotrophic
+    lateral sclerosis (ALS) are accurately distinguished from matched
+    controls.
+    % \cite{sarica2017corticospinal}.
+    Furthermore, SGL automatically
+    identifies FA in the corticospinal tract as important for this
+    classification, correctly finding the parts of the white matter known
+    to be affected by the disease. ii) In a regression setting, dMRI is
+    used to accurately predict ``brain age.''
+    % \cite{yeatman2014lifespan, Brown2012-so}.
+    In this case, the weights are distributed throughout the
+    white matter indicating that many different regions of the white matter
+    change with development and contribute to the prediction of age. Thus,
+    SGL makes it possible to leverage the multivariate relationship between
+    diffusion properties measured along multiple bundles to make accurate
+    predictions of subject characteristics while simultaneously discovering
+    the most relevant features of the white matter for the characteristic of
+    interest.
+\end{abstract}
 
@@
 
-\input{sections/introduction}
-\input{sections/results}
-\input{sections/conclusion}
-\input{sections/methods}
+\subsection*{Introduction}
 
-\begin{acknowledgments}
-    {\it Acknowledgments.-}
+\begin{figure}[!h]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{0.5em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-9.75cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{{\bf Tractometry data flow}
+        \label{fig:methods}
+        {\bf (a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
+        anatomical slice.
+        {\bf (c)} Tractometry further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for CSTL.
+        {\bf (d)} the phenotypical target data and tractometric features can
+        be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the left arcuate (ARCL). The coefficients in
+        $\hat{\beta}$ follow the same natural grouping.
+        % Cross-validation:
+        % we evaluate model quality using a nested $k$-fold cross validation
+        % scheme. At level-0, the input data is decomposed into $k$
+        % shuffled groups and optimal hyperparameters are found for the level-0
+        % training set.
+        % To avoid overfitting, the optimal hyperparameters are themselves
+        % evaluated using a cross-validation scheme taking place
+        % at level-1 of the decomposition, where each
+        % level-0 training set is further decomposed into five shuffled
+        % groups. For the ALS and WH data, $k=10$, while for the HBN and
+        % Cam-CAN data, $k=5$.
+    }
+\end{figure}
+
+\todo[inline]{The introduction section should be shortened for Nature methods
+I think.}
+
+Non-invasive methods for measuring human brain structure and function have
+revolutionized our understanding of brain function. These measurements
+have demonstrated that interactions between networks of brain regions give rise
+to coordinated information processing and to the complex adaptive behavior that
+characterizes human cognition. Diffusion-weighted Magnetic Resonance Imaging
+(dMRI) provides a unique view into the physical properties of the connections
+that comprise these networks, by sensitizing the measurement to the directional
+diffusion of water in each voxel \cite{wandell2016clarifying}.
+% While the measurements are usually conducted
+% with voxels at the millimeter scale, water molecules within each voxel
+% diffuse with characteristic lengths at the micrometer scale, providing
+% aggregate information about the physical structure of the white matter,
+% including the density of axons and distribution of fiber
+% orientations within each voxel \cite{wandell2016clarifying}. Even though
+% metrics derived from diffusion measurements are ambiguous in terms
+% of their underlying biological interpretation \cite{Jones2013-xv},
+% analyzing the variance in these properties has proven useful in
+% characterizing individual differences in cognitive function,
+% characterizing differences between populations and detecting brain
+% abnormalities associated with disease \cite{Thomason2011-qn}.
+Methods for computational tract-tracing from diffusion MRI, or tractography,
+combine the estimates of fiber orientations in each voxel to form streamlines
+that traverse the volume of the white matter~\cite{Conturo1999-je,
+Mori2002-qi}. A variety of methods can be used to delineate the
+trajectory of major neural pathways among these
+streamlines~\cite{yeatman2012tract}.
+% These methods have been under increased scrutiny and
+% several lines of investigation have raised critiques of their validity
+% \cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
+% have been efforts to shore up the inferences made with these methods
+% \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
+% Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
+% tracts requires extraordinary evidence, and delineating
+% the exact cortical termination of the streamlines in the gray matter
+% is still prone to error, there is little dispute that tractography
+% can accurately define the location of several major white matter
+% tracts that are known to exist within the core of the white matter
+% \cite{Maier-Hein2017-vb, Catani2002-vu}.
+\emph{Tractometry} uses the results of tractography and models
+of tissue biophysics based on the patterns of diffusion in each measurement
+voxel to assess the physical properties of the white matter along specific
+pathways~\cite{Bells2011-cf}.
+%Though there are several different available implementations of this overall
+%idea, the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
+%Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
+% the parts of the white matter that belong to different major ``tracts''
+% (i.e. anatomical or functional groups of white matter fibers), such as
+% the corticospinal tract or arcuate fasciculus, assigning tractography
+% generated streamlines to ``bundles,'' which approximate the anatomical
+% tracts, and sampling biophysical properties, such as fractional
+% anisotropy (FA) or mean diffusivity (MD), along the length of these bundles.
+% the parts of the white matter that belong to different major tracts
+% (i.e. anatomical or functional groups of white matter fibers), such as
+% the corticospinal tract or arcuate fasciculus, assigning tractography
+% generated streamlines to ``bundles,'' which approximate the anatomical
+% tracts, and sampling biophysical properties (such as fractional
+% anisotropy or mean diffusivity) along the length of these bundles.
+In some previous tractometry-based studies, tissue properties along the
+length of each tract were summarized by taking the mean along each
+bundle, but there is a large body of evidence showing that there is
+systematic variability in the values of diffusion metrics along the
+trajectory of each bundle. This justifies retaining the individual
+samples along the length of each bundle \cite{yeatman2012tract,
+colby2012, ODonnell2009-uu}. While this retains important information
+about each individual's white matter, it also presents statistical
+challenges due to the dimensionality of the data. In past work,
+comparisons between groups or across individuals were done
+independently at each node of each bundle, for each
+diffusion metric. This approach is exhaustive, but
+statistical power is compromised by a multiple comparison problem
+\cite{colby2012, Nichols2002-zu, Nichols2003-yy}. An alternative that
+circumvents the multiple comparison problem is to select just a few
+tracts to compare in each individual, or even focusing on particular
+segments of these tracts based on \emph{a priori} hypotheses. This
+approach is appropriate when the biological basis of the process
+of interest is relatively well understood (for a recent example, see
+\cite{huber2018rapid}). Sometimes, these approaches are combined: a
+bundle is selected based on \emph{a priori} knowledge, and all the data
+in the bundle of interest are used together to fit a model that can
+predict differences between individuals \cite{dayan2016profilometry}.
+
+% Different approaches can be taken to resolving this challenge. For
+% example, Colby and colleagues \cite{colby2012} used a non-parametric
+% resmapling approach to
+% correct for family-wise error across the different possible comparisons
+% \cite{Nichols2002-zu, Nichols2003-yy}.
+% Based on tractometry, researchers may choose to compare different individuals
+% to each other. This is usually done according to one of the following
+% approaches:
+% \begin{enumerate}
+% \item Mass univariate approaches: In this approach
+
+% \item Region of interest(ROI)-based approaches:
+% An alternative that
+% circumvents the multiple comparison problem is to select just a few
+% tracts to compare in each individual, or even focusing on particular
+% segments of these tracts based on \emph{a priori} hypotheses. This
+% approach is very powerful when the biological basis of the process
+% of interest is relatively well understood (for a recent example, see
+% \cite{huber2018rapid}).
+
+% \item ROI-based selection, followed by multivariate analysis: Here,
+% an ROI is selected based on \emph{a priori} knowledge, and all the
+% nodes or voxels in the ROI are used together to fit a model that can
+% predict differences between individuals. An example of that is the
+% ``profilometry'' framework, in which different diffusion metrics
+% from a single tract are combined together to provide input to a
+% multivariate analysis of covariance, and linear discriminant analysis
+% \cite{dayan2016profilometry}.
+
+%\end{enumerate}
+
+The present work aims to balance predictive accuracy with descriptive power
+\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
+data across all bundles, while also retaining and elucidating spatial
+information about the locations that are most informative for discriminative
+performance. To do so, we use a linear modeling approach, which aims to
+redict phenotypical variance in a group of subjects (or classify group
+membership), based on a linear combination of the features estimated with
+tractometry.
+
+% Generally speaking, analysis methods should balance predictive
+% accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}.
+% Accordingly, tractometry analysis should simultaneously capitalize on
+% all the data across all tracts to make the best possible prediction,
+% while also retaining and elucidating spatial information about the
+% locations that are most informative for a prediction. In the present
+% work, we developed a novel framework for analysis of tractometry that
+% simultaneously selects the features for analysis, and fits a model
+% to these features. We use a linear modeling approach, which aims to
+% predict phenotypical variance in a group of subjects, based on a linear
+% combination of the features estimated with tractometry.
+
+Using this approach, we first need to deal with the large and
+asymmetric dimensionality of the data: tractometry data usually has
+many more features (i.e., number of measurements per individual) than
+samples (number of subjects), which makes inferences from the data
+about phenotypical differences between individuals ill-posed. This
+regime is the target of several statistical learning techniques, and
+is often solved by various forms of regularization.
+
+% For example, Tikhonov regularization shrinks the solution such that the sum of
+% squared contributions from the individual features are minimized
+% \cite{Hoerl2000-ij}. Another solution to the problem is provided by
+% the
+
+The Lasso algorithm minimizes the sum of the absolute values of
+contributions of each feature \cite{Tibshirani1996-qs}. This
+tends to shrink to zero the contributions of many of the features,
+providing results that are both accurate and interpretable. When
+additional structure is available in the organization of the data,
+regularization algorithms can take advantage of this structure. For
+example, if the features lend themselves to a natural division into
+different groups, the group lasso (GL) can be used to select groups
+of features, rather than individual features \cite{Yuan2006-ky}.
+The Sparse Group Lasso (SGL) elaborates on this idea by providing
+control both of group sparsity, as well as overall sparsity of the
+solutions \cite{simon2013sgl}. Because the features measured with
+tractomery lend themselves to grouping based on the tracts from which
+each measurement is taken, GL and SGL provide useful tools
+for linear model fitting in problems of this form. Here we, first,
+develop an implementation of SGL that is well suited to the analysis of
+tractometry data and, second, demonstrate the power and flexibility of
+this approach by applying it to both classification
+and continuous prediction problems.
+
+\subsection*{Results}
+
+\begin{figure*}
+    \vspace{3cm}
+    \rlap{
+        \includegraphics[width=0.33\textwidth]{als_coefs.pdf}
+    }
+    \vspace{-8.4cm}
+    \includegraphics[width=\textwidth]{als_results.pdf}
+    {\phantomsubcaption\label{fig:class-results:probs}}
+    {\phantomsubcaption\label{fig:class-results:coefs3d}}
+    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
+    {\phantomsubcaption\label{fig:class-results:false-positives}}
+    {\phantomsubcaption\label{fig:class-results:false-negatives}}
+    \caption{%
+        {\bf SGL accurately and interpretably predicts ALS diagnosis.}
+        \label{fig:class-results}
+        {\bf (a)} Classification probabilities for ALS diagnosis, with
+        controls on the left, patients on the right, predicted controls in
+        blue, and predicted patients in orange. That is, orange dots on the left
+        represent false positives, while blue dots on the right represent
+        false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
+        ROC AUC of {\protect\alsRocAuc}.
+        {\bf (b)} SGL coefficients are presented on the core fibers of major
+        fiber bundles. They exhibit high group sparsity and are concentrated
+        in the FA of the CST. The brain is oriented with the right hemisphere
+        in the foreground and anterior to the right of the page. The CSTL,
+        CSTR, and CFA bundles are indicated for orientation.
+        {\bf (c)} SGL identifies three portions of the CST as important,
+        where $\hat{\beta}$ (dashed line, right axis) has large values. These
+        are centered around nodes 30, 65, and 90, corresponding to locations
+        of substantial differences in FA between the ALS and control groups
+        (shaded areas indicates standard error of the mean).
+        {\bf (d)} Bundle profiles for false positive classifications. Line
+        colors correspond to the marker edge color in the top left plot.
+        These individuals have reduced FA in the CST portions which SGL
+        identified as important. Their misclassification is coherent with the
+        feature importance and the group differences in FA.
+        {\bf (e)} Individual bundle profiles for false negative
+        classifications. These individuals have bundle profiles which
+        oscillate between the group means.
+    }
+\end{figure*}
+
+We developed a method for analyzing dMRI tractometry data that uses the Sparse
+Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
+We demonstrate the use of this method on four different datasets in
+both a classification setting and a regression setting.
+
+\subsubsection*{SGL accurately detects ALS from tractometry data}
+
+Using data from a previous study of patients with amyotrophic lateral sclerosis (ALS)~\cite{sarica2017corticospinal}, we tested the performance of SGL in a
+classification setting. The previous study predicted ALS status with a mean
+accuracy of 80\% using a random forest algorithm based on \emph{a priori}
+selection of features only within the CST bundle-of-interest.
+SGL delivers improved predictive performance, with a cross-validated accuracy of {\alsAccuracy}\% and an area under the receiver operating characteristic curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature engineering (Figure \cref{fig:class-results:probs}).
+In addition to this
+classification performance, SGL also identifies the white matter tracts most
+important for ALS classification. The relative importance of white matter
+features is captured in the $\beta$ coefficients from \cref{supp:eq:sgl} of
+the supplemental material \cite{supplement}.
+\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
+right CST, plotted over the FA values for the control and ALS subject groups.
+We find that SGL selects FA metrics in the corticospinal tract and
+particularly in the right corticospinal tract as most important to ALS
+classification, confirming previous findings \cite{van2011upper,
+toosy2003diffusion, sarica2014tractography, sage2007quantitative,
+sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
+cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
+identifying the portions of the brain that were selected \emph{a priori} in
+the previous study from which we obtained the data
+\cite{sarica2017corticospinal}.
+
+The $\beta$ coefficients exhibit high bundle level sparsity; only some
+bundles are important, which can be be confirmed by observing the value of
+$\alpha$, the regularization hyperparameter that controls the mixture of the
+group lasso and lasso penalties, selected through nested cross-validation
+(see \cref{supp:eq:sgl} of the supplemental material \cite{supplement}).
+If $\alpha$ is closer to zero, it indicates that the phenotype in question
+preferentially correlates with only a few groups of covariates. For the ALS
+dataset, $\alpha = $ \alsLRatio, confirming that the white matter correlates
+of ALS reside mostly in one bundle, namely the CST.
+
+Analyzing the ways in which the model mislabels individuals also provides
+insight. We found that mislabelled subjects are outliers relative to their
+group with respect to diffusion features of the CST (Figure
+\Cref{fig:class-results:false-positives,fig:class-results:false-negatives}).
+The false positive classifications have reduced FA in one or more of the three
+sections of the CST where $\norm*{\hat{\beta}}$ is large
+\cref{fig:class-results:tract-profiles}. The false negative subjects have FA
+profiles that oscillate between the two group means. Thus, when the SGL
+method predicts incorrectly this is done in a comprehensible manner.
+
+\begin{figure*}
+    \vspace{3.65cm}
+    \rlap{
+        \hspace{1cm}
+        \includegraphics[width=0.275\textwidth]{wh_coefs.pdf}
+        \hspace{0.25em}
+        \includegraphics[width=0.275\textwidth]{hbn_coefs.pdf}
+        \hspace{0.25em}
+        \includegraphics[width=0.275\textwidth]{camcan_coefs.pdf}
+    }
+    \vspace{-7.3cm}
+    \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
+    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
+    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
+    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:wh-profile}}
+    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
+    {\phantomsubcaption\label{fig:age-results:cc-profile}}
+    \caption{%
+        {\bf Predicting age with tractometry and SGL.}
+        \label{fig:age-results}
+        {\bf (top)} The predicted age vs. true age of each individual from the test
+        splits (i.e., when each subject's data was held out in fitting the
+        model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
+        datasets; an accurate prediction falls close to the $y=x$ line
+        (dashed). The mean absolute error (MAE) and coefficient of
+        determination $R^2$ are presented in the lower right of each scatter
+        plot.
+        {\bf (middle)} Feature importance for predicting age from tractometry in
+        the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
+        The orientation of the
+        brain is that same as in \cref{fig:class-results:coefs3d}, however because
+        the coefficients exhibit high global sparsity (as opposed to group
+        sparsity), we plot the mean of the absolute value of $\hat{\beta}$
+        for each bundle on the core fiber. The global distrubution of the
+        $\hat{\beta}$ coefficients reflects the fact that aging is not
+        confined to a single white matter bundle.
+        {\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
+        {\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
+    }
+\end{figure*}
+
+\subsubsection*{SGL accurately predicts age from tractometry data}
+
+To test the performance of SGL with tractometry data in a continuous
+regression task, we focus here on the prediction of biological age in three
+datasets named WH, HBN, and Cam-CAN (see supplemental material
+\cite{supplement} for a description of each dataset). Prediction of ``brain
+age'' is a commonly undertaken task in neuroimaging machine learning, in part
+because these predictions, and deviations therefrom, may be diagnostic of
+overall brain health (for a review, see Cole et al.~\cite{Cole2019-rz}).
+However, as Nelson et al.~\cite{nelson2019biomarkers} have observed, aging
+biomarkers are subject to unique challenges and tend to be noncausative. Our
+interest in aging here relies on its utility as a methodological benchmark.
+Biological age operates on a natural scale, with meaningful and easily
+understood units, and it's popularity as a machine learning target makes it
+valuable for comparisons with other studies.
+
+The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
+\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
+data from 76, 978, and 640 subjects, respectively, ranging from 6-50, 5-21,
+and 18-88 years of age, respectively. In each case, biological age was used
+as the predicted variable $y$. SGL was fit to the tractometry-extracted
+features FA and MD in 18 major brain tracts, with diffusion metrics extracted
+from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
+
+To evaluate the fit of the model, we used a nested cross-validation
+procedure. In this procedure, batches of subjects are held out. For each
+batch (or fold), the model is fully fit without this data. Then, once the
+parameters are fixed, the model is inverted to predict the ages of held out
+subjects based on the linear coeffiecients. This scheme automatically finds
+the right level of sparsity and fits the coefficients to the ill-posed linear
+model, while guarding against overfitting. SGL accurately predicts the age of
+the subjects in this procedure, with a median absolute error of {\whMae},
+{\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
+respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq},
+and {\camcanRsq}, respectively (see \cref{fig:age-results}, top panels). The
+predictions for Cam-CAN are competitive with a recent state of the art
+prediction \cite{mcpherson2020single}, which used streamline density to
+estimate the brain's structural connectivity and achieved $R^2 = 0.63$. The
+median absolute errors are also lower than the results of a recent study that
+predicted age in a large sample that included the Cam-CAN data, and was based
+on diffusion MRI features \cite{Richard2018-ux}.
+
+In contrast to the ALS classification case, the selected $\alpha$ values
+indicate high global sparsity over group sparsity, with $\alpha = $
+{\whLRatio}, {\hbnLRatio}, and {\ccLRatio}, for the WH, HBN, and Cam-CAN
+datasets, respectively. The model weights are distributed over many different
+tracts and dMRI tissue properties (see
+\cref{fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d}
+and supplemental material
+\cref{supp:fig:wh-bp:md,supp:fig:wh-bp:fa,supp:fig:hbn-bp:md,supp:fig:hbn-bp:fa,supp:fig:cc-bp:md,supp:fig:cc-bp:fa}).
+This demonstrates that SGL is not coerced to produce overly sparse results
+when a more accurate model requires a dense selection of features.
+Furthermore, inspecting the portions of bundles with larger coefficients in
+\cref{fig:age-results:wh-profile,fig:age-results:hbn-profile,fig:age-results:cc-profile}
+reveals that SGL selects informative regions where diffusion properties are
+different between the age quintiles.
+
+\subsection*{Discussion}
+
+We present here a novel method for analysis of dMRI tractometry data that
+relies on the Sparse Group Lasso \cite{simon2013sparse} to make accurate
+predictions of phenotypic properties of individual subjects while,
+simultaneously, identifying the features of the white matter that are
+most important for this prediction. The method is data-driven and it is broadly applicable to a wide range of research questions: it
+performs well in predicting both continuous variables, such as biological
+age, as well as categorical variables, such as whether a person is a patient
+or a healthy control. In both of these cases, SGL out-performs previous
+algorithms that have been developed for these tasks
+\cite{sarica2017corticospinal, Richard2018-ux, mcpherson2020single}. The
+nested cross-validation approach used to fit the model and make both
+predictions and inferences from the model guards against overfitting and
+tunes the degree of sparseness required by the algorithm. This means that SGL
+can accurately describe phenomena that are locally confined to a particular
+anatomical location or diffusion property (e.g., FA in the CST) as well as
+phenomena that are widely distributed amongst brain regions and measured
+diffusion properties.
+
+Specifically, we demonstrated that the algorithm correctly detects the fact
+that ALS, which is a disease of lower motor neurons, is localized to the
+cortico-spinal tract. This recapitulates the results of previous analysis of
+these same data, using a bundle-of-interest approach
+\cite{sarica2017corticospinal}. In contrast, for the analysis of biological
+age, the coefficients identified by the algorithm are very widely distributed
+across many parts of the white matter, mirroring previous results that show a
+large and continuous distribution of life-span changes in white matter
+properties \cite{yeatman2014lifespan}.
+
+One drawback of our approach is also evident in the age regression results.
+There are portions of the bundle profiles in
+\cref{fig:age-results:wh-profile,fig:age-results:hbn-profile,fig:age-results:cc-profile}
+for which the $\hat{\beta}$ coefficients are zero but for which the bundle
+profiles clearly contain an age differentiating signal. While SGL correctly
+identifies certain features as important, it is not guaranteed to identify
+\emph{all} of the important features. It will identify a parsimonious set of
+important features, dense enough to predict the phenotype and sparse enough
+(at either the group or global level) to satisfy the sparsity constraints.
+
+Taken together, these results demonstrate the promise of the
+group-regularized regression approach. Even at the scale of dozens of
+subjects, the results provided by SGL are both accurate, as well as
+interpretable \cite{Murdoch2019-ax}: tractometry capitalizes on domain
+knowledge to engineer meaningful features; SGL scores these features based on
+their relative importance; enables a visualization of these feature
+importance scores in the anatomical coordinate frame of the bundles (e.g.,
+\cref{fig:class-results:coefs3d,fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d})
+and provides a means to understand model errors (e.g.,
+\cref{fig:class-results:false-positives,fig:class-results:false-negatives}) .
+Thus, this multivariate analysis approach achieves high
+cross-validated accuracy for precision medicine applications of dMRI data and identifies relevant features of brain anatomy that can further our
+neuroscientific understanding of clinical disorders.
+
+Neuroscience has entered an era in which consortium efforts are amassing
+large datasets of high-quality dMRI measurements to address a variety of
+scientific questions \cite{jernigan2016ping, jernigan2018abcd,
+alexander2017open, Miller2016-hw, VanEssen2012}, but the volume and
+complexity of these data pose substantial challenges. Tractometry
+followed by analysis with SGL provide a promising approach to
+distill meaningful insights from the wealth of data measured in these efforts.
+
+SGL has many other potential applications in neuroscience, because
+of the hierarchical and grouped nature of many data types that are
+collected in multiple sample points within anatomically-defined areas.
+For example, this method may be useful to understand the relationship
+between fMRI recordings and behavior, where activity in each voxel
+may co-vary with voxels within the same anatomical region and form
+features and groups of features. Similarly, large-scale multi-electrode
+recordings of neural activity in awake behaving animals are becoming
+increasingly feasible \cite{steinmetz2018distributed, Jun2017-gv} and
+these recordings can form features (neurons) and groups (neurons within
+an anatomical region).
+
+% More ambitiously perhaps, this approach may be
+% used to understand the role of correlations in so-called resting-state
+% fMRI time-series and behavior, where pairwise correlations between
+% voxels in different anatomical regions are features in the matrix and
+% features may be grouped by pairs of anatomical regions. Given the large
+% number of voxels in the surface of the gray matter and given that
+% correlations increase the number of features by a factor of $n^2$, this
+% would pose a challenging problem to solve using SGL.
+
+The results we present here also motivate extensions of the method using more
+sophisticated cost functions. For example, the fused sparse group lasso (FSGL)
+\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
+in the variation of diffusion metrics along the bundles. As brain measurements
+include additional structure (for example, bilateral symmetry), future work
+could also incorporate overlapping group membership for each entry in the tract
+profiles \cite{Rao2014-xm}. For example, a measurement could come from the
+corpus callosum, but also from the right hemipshere. This would also require
+extending the cost function used here to incorporate these constraints.
+Similarly, unsupervised dimensionality reduction of tractometry data (e.g.,
+\cite{Chamberland2019-mu}) could also benefit from constraints based on
+grouping.
+
+The method is packaged as open-source software called AFQ-Insight that is
+openly available \todo{Ariel: add URL}, and provides a clear API to allow for
+extensions of the method. The sofware integrates within a broader automated
+fiber quantification software ecosystem: AFQ \cite{yeatman2012tract} and
+pyAFQ (https://yeatmanlab.github.io), which extract tractometry data from raw
+and processed dMRI datasets, as well as AFQ-Browser, which visualizes
+tractometry data and facilitates sharing of the results of dMRI studies
+\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
+software, the results presented in this paper are also provided in
+\url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks}
+as a series of Jupyter notebooks \cite{kluyver2016jupyter}.
+
+\subsection*{Methods}
+
+Methods and associated references are available in the supplemental material
+\cite{supplement}.
+
+\subsection*{Acknowledgments}
+
 This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
@@
 Moore Foundation and the Alfred P. Sloan Foundation to the University of
-    Washington eScience Institute Data Science Environment, and by the Google Cloud Platform Academic Research Credits Program.
-    We would like to thank
-    Scott Murray for a useful discussion of the SGL method and Mareike Grotheer for
-    helpful comments on the manuscript.
-\end{acknowledgments}
+Washington eScience Institute Data Science Environment, and by the Google
+Cloud Platform Academic Research Credits Program. We would like to thank
+Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
+for helpful comments on the manuscript.
+
+\subsection*{Author contribution statement}
+
+All authors contributed extensively to the work presented in this paper.
 

### 2021-01-26 reports/manuscript/supplemental.tex
Put all paper LaTeX in the same file as required by Nature methods

@@
 
+For each dataset, we also perform a randomization test by training similar
+models on copies of the data for which the rows of the target variable $y$
+have been shuffled while the feature matrix $\mathbf{X}$ remains the same.
+This effectively destroys any relationship between the diffusion data and the
+outcome. Indeed, all of our models perform no better than random guessing.
+One should expect this since any better performance might indicate data
+leakage between train and test sets \cite{kaufman2012leakage} or other common
+machine learning pitfalls.
+
 \subsection{Software implementation}

### 2021-01-26 reports/manuscript/supplemental.tex
Capitalize DIPY.
Suggestions and comments on supplement.

@@
 \item {\it Diffusion data preprocessing}
+
+\todo{Ariel: This section seems incomplete. I am pretty sure there was some motion correction, eddy current correction and so forth happening in here.
+Also, we might want to drop the part that describes calculation of confounds,
+since we aren't using them.}
+
 Several confounding time-series were calculated based on the
 \emph{preprocessed DWI}: framewise displacement (FD) using the
-implementation in \emph{Nipype} \cite[following the definitions
-by]{power_fd_dvars}. The head-motion estimates calculated in the
+implementation in \emph{Nipype} following the definitions
+by \cite{power_fd_dvars}. The head-motion estimates calculated in the
 correction step were also placed within the corresponding confounds
@@
 Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
-\cite[RRID:SCR\_001362]{nilearn} and \emph{Dipy} \cite{dipy}. For more
+\cite[RRID:SCR\_001362]{nilearn} and \emph{DIPY} \cite{dipy}. For more
 details of the pipeline, see
@@
     \cite{gorgolewski2016brain}
-    \item the calculation of diffusion kertosis imaging (DKI
+    \item the calculation of diffusion kurtosis imaging (DKI
     \cite{jensen2005diffusion}) metrics
@@
 These processes create bundle profiles, in which diffusion measures
-are quantified and averaged along twenty major fiber tracts. Here,
+are quantified and averaged along eighteen major fiber tracts. Here,
 we use only the mean diffusivity (MD) and the fractional anisotropy
@@
 is an unobserved random variable that captures the error in the model.
-We denote our prediction of the targer phenotype as $\hat{y}$ and the
+We denote our prediction of the target phenotype as $\hat{y}$ and the
 coefficients that produce this prediction as $\hat{\beta}$, so that
@@
 $N$ is the number of nodes in each bundle, and $M$ is the number of
-diffusion metrics calculated at each node. Typically, $B = 20$, $N =
-100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 16,000$ features.
+diffusion metrics calculated at each node. Typically, $B = 18$, $N =
+100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 14,400$ features.
 Conversely, many dMRI studies have between a few dozen and a few
@@
 small. The sparse group lasso (SGL) is a penalized regression technique that
-satisfies exactly these criteria\cite{simon2013sparse}. It solves for a
+satisfies these criteria\cite{simon2013sparse}. It solves for a
 coefficient vector $\hat{\beta}$ that satisfies
@@
     \norm{y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2
+    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2,
     \label{eq:sgl}
 \end{multline}
-where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
+$G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
 $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
@@
 
-\subsection{Implementation, cross-validation and metaparameter optimization}
+\subsection{SGL implementation, cross-validation and metaparameter optimization}
 
@@
 
-Because the SGL is not specific to tractometry, we implement its solution as
-a separate Python package called \texttt{groupyr} \cite{groupyr}.
+Because the SGL is not specific to tractometry, we implemented its solution as
+a general-purpose Python package called \texttt{groupyr} \cite{groupyr}.
 \texttt{Groupyr} solves the cost function in \cref{eq:sgl} using proximal
@@
 
-To objectively evaluate the model performance and guard against over-fitting,
+To objectively evaluate model performance and guard against over-fitting,
 we used a nested cross-validation scheme, which is depicted for the binary
@@
 evaluating the fit on test\textsubscript{1}. We find the optimal values for
-$\alpha$ and $\lambda$ using sequential model based optimization, implemented
+$\alpha$ and $\lambda$ using sequential model-based optimization, implemented
 using the scikit-optimize \verb|BayesSearchCV| class\cite{scikit-optimize}.
@@
 The full software implementation of the SGL approach presented here is available
-in a Python software package called AFQ-Insight, which is developed publicly in
-\url{https://github.com/richford/afq-insight}. The version of the code used to
-produce the results herein is also available in
+in a Python software package called \texttt{AFQ-Insight}, which is developed
+publicly in \url{https://github.com/richford/afq-insight}.
+The version of the code used to produce the results herein is also available in
 \url{https://doi.org/10.5281/zenodo.3585942}\todo{Update version here}.
@@
 linear interpolation. For missing exterior nodes, the user may choose between
-linear extrapolation and constant forward(back)-fill. Imputation uses only
+linear extrapolation and constant forward- or back-fill. Imputation uses only
 values from adjacent nodes in the same white matter bundle in the same
@@
 under the receiver operating curve (AUC ROC), and coefficient of
-determination ($R^2$). For each set of hyperparameters, we solve the SGL
-problem using the \texttt{groupyr} library \cite{groupyr}. Appropriate
-hyperparameters are found using the scikit-optimize library
-\cite{scikit-optimize}.
+determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the \texttt{groupyr} software library \cite{groupyr} mentioned above to solve the SGL.
 
@@
 feature of the method when one seeks an efficient predictive model, but is a
-defect of the method when one wants an exhaustive explanation of feature
-importance. We will use the phrase ``parsimonious pitfall'' to refer to the
+disadvantage of the method when one wants an exhaustive explanation of feature
+importance. We will use the phrase ``parsimony pitfall'' to refer to the
 case when SGL regularizes away redundant but obviously important features.
@@
 These figures also show that SGL behaves much more like the lasso than the group
-lasso, as discussed in the main text. The parsimonious pitfall is most evident in
+lasso, as discussed in the main text. The parsimony pitfall is most evident in
 the IFOL and IFOR bundles in \cref{fig:wh-bp:md}.
@@
 coefficients between the WH, HBN, and Cam-CAN models.
-The parsimonious pitfall is most evident in the UNCL, UNCR, ARCL, SLFL, and
+The parsimony pitfall is most evident in the UNCL, UNCR, ARCL, SLFL, and
 SLFR bundles in \cref{fig:hbn-bp:md}.
@@
 two are roughly disjoint, with the WH age distribution straddling the two.
-The parsimonious pitfall is again evident in the UNCL, UNCR, ARCL, SLFL, and
+The parsimony pitfall is again evident in the UNCL, UNCR, ARCL, SLFL, and
 SLFR bundles in \cref{fig:cc-bp:md}.
@@
 don't really want to. I only want to stress that you have to be careful
-comparing $\hat{\beta}$ across models.}
+comparing $\hat{\beta}$ across models. Ariel: agreed!}
 

### 2021-01-27 reports/manuscript/paper.tex
Add some todo items, remove some todo items

@@
     % Abstracts should be unreferenced and typically around 150 words
+    \todo{Shorten abstract to roughly 150 words.}
     The white matter contains long-range connections between different
@@
 \end{figure}
-
-\todo[inline]{The introduction section should be shortened for Nature methods
-I think.}
 
@@
 
-Methods and associated references are available in the supplemental material
-\cite{supplement}.
+Methods and associated references are available in the supplemental material.
 

### 2021-01-27 reports/manuscript/supplemental.tex
Add some todo items, remove some todo items

@@
     \norm{y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2,
+    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2.
     \label{eq:sgl}
 \end{multline}
-$G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
+Here, $G$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
 $\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
@@
 SLFR bundles in \cref{fig:cc-bp:md}.
-\todo[inline]{We could say more here but it's not an ``aging'' paper so I
-don't really want to. I only want to stress that you have to be careful
-comparing $\hat{\beta}$ across models. Ariel: agreed!}
 

### 2021-01-27 reports/manuscript/supplemental.tex
Add missing preprocessing steps to supplemental.tex and corresponding bib items to paper.bib

@@
 
-\todo{Ariel: This section seems incomplete. I am pretty sure there was some motion correction, eddy current correction and so forth happening in here.
-Also, we might want to drop the part that describes calculation of confounds,
-since we aren't using them.}
+Any images with a b-value less than 100 s/mm\^{}2 were treated as a
+\emph{b}=0 image. MP-PCA denoising as implemented in MRtrix3's
+\texttt{dwidenoise}\cite{dwidenoise1} was applied with a 5-voxel
+window. After MP-PCA, B1 field inhomogeneity was corrected using
+\texttt{dwibiascorrect} from MRtrix3 with the N4 algorithm \cite{n4}.
+After B1 bias correction, the mean intensity of the DWI series was
+adjusted so all the mean intensity of the b=0 images matched across
+eachseparate DWI scanning sequence.
+\end{itemize}
+
+FSL (version 6.0.3:b862cdd5)'s eddy was used for head motion correction
+and Eddy current correction \cite{anderssoneddy}. Eddy was configured
+with a \(q\)-space smoothing factor of 10, a total of 5 iterations, and
+1000 voxels used to estimate hyperparameters. A linear first level model
+and a linear second level model were used to characterize Eddy
+current-related spatial distortion. \(q\)-space coordinates were
+forcefully assigned to shells. Field offset was attempted to be
+separated from subject movement. Shells were aligned post-eddy. Eddy's
+outlier replacement was run \cite{eddyrepol}. Data were grouped by
+slice, only including values from slices determined to contain at least
+250 intracerebral voxels. Groups deviating by more than 4 standard
+deviations from the prediction had their data replaced with imputed
+values. Data was collected with reversed phase-encode blips, resulting
+in pairs of images with distortions going in opposite directions. Here,
+b=0 reference images with reversed phase encoding directions were used
+along with an equal number of b=0 images extracted from the DWI scans.
+From these pairs the susceptibility-induced off-resonance field was
+estimated using a method similar to that described in \cite{topup}. The
+fieldmaps were ultimately incorporated into the Eddy current and head
+motion correction interpolation. Final interpolation was performed using
+the \texttt{jac} method.
 
 Several confounding time-series were calculated based on the
-\emph{preprocessed DWI}: framewise displacement (FD) using the
-implementation in \emph{Nipype} following the definitions
-by \cite{power_fd_dvars}. The head-motion estimates calculated in the
-correction step were also placed within the corresponding confounds
-file. Slicewise cross correlation was also calculated. The DWI
-time-series were resampled to ACPC, generating a \emph{preprocessed DWI
-run in ACPC space}.
-\end{itemize}
+\emph{preprocessed DWI}: framewise displacement (FD) using the implementation
+in \emph{Nipype} following the definitions by \cite{power_fd_dvars}. The DWI
+time-series were resampled to ACPC, generating a \emph{preprocessed DWI run
+in ACPC space}.
 

### 2021-01-27 reports/manuscript/paper.tex
Add more todo notes

@@
 \cite{sarica2017corticospinal}.
+\todo{Adam: Add sentence comparing to pure lasso results.}
 
@@
 on diffusion MRI features \cite{Richard2018-ux}.
+\todo{Adam: Add sentence comparing to pure lasso results.}
 
@@
 \url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks}
+\todo{Adam: Update notebooks}
 as a series of Jupyter notebooks \cite{kluyver2016jupyter}.

### 2021-01-30 reports/manuscript/paper.tex
Add suggested edits from Noah Simon

@@
 % anisotropy (FA) or mean diffusivity (MD), along the length of these bundles.
-% the parts of the white matter that belong to different major tracts
+% The parts of the white matter that belong to different major tracts
 % (i.e. anatomical or functional groups of white matter fibers), such as
@@
 circumvents the multiple comparison problem is to select just a few
-tracts to compare in each individual, or even focusing on particular
+tracts to compare in each individual, or even
 segments of these tracts based on \emph{a priori} hypotheses. This
@@
 % example, Colby and colleagues \cite{colby2012} used a non-parametric
-% resmapling approach to
+% approach to
 % correct for family-wise error across the different possible comparisons
@@
 example, if the features lend themselves to a natural division into
-different groups, the group lasso (GL) can be used to select groups
+different groups, the Group Lasso (GL) can be used to select groups
 of features, rather than individual features \cite{Yuan2006-ky}.
@@
 $\alpha$, the regularization hyperparameter that controls the mixture of the
-group lasso and lasso penalties, selected through nested cross-validation
+Group Lasso and lasso penalties, selected through nested cross-validation
 (see \cref{supp:eq:sgl} of the supplemental material \cite{supplement}).
@@
 batch (or fold), the model is fully fit without this data. Then, once the
-parameters are fixed, the model is inverted to predict the ages of held out
+parameters are fixed, the model is applied to predict the ages of held out
 subjects based on the linear coeffiecients. This scheme automatically finds

### 2021-01-30 reports/manuscript/paper.tex
Add reference to the PASTA paper.
Merge PASTA reference from arokem's addition

@@
                prl,%
-               preprint,%
+               reprint,%
                superscriptaddress,%
@@
                amsmath,%
-               floatfix,%
-               endfloats*]{revtex4-1}
+               floatfix]{revtex4-1}
 \usepackage[T1]{fontenc}
@@
 
-\begin{figure}[!h]
-    \vspace{0.25cm}
-    \rlap{
-        \hspace{0.5em}
-        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    }
-    \vspace{-9.75cm}
-    \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{{\bf Tractometry data flow}
-        \label{fig:methods}
-        {\bf (a)} Whole brain tractography generates streamlines approximating
-        the trajectories of white matter connections.
-        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
-        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
-        anatomical slice.
-        {\bf (c)} Tractometry further extracts bundle profiles,
-        quantifications of various diffusion metrics along the length of the
-        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for CSTL.
-        {\bf (d)} the phenotypical target data and tractometric features can
-        be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the CSTL, the middle (green) group
-        contains $k$ features from the left cingulum cingulate (CGCL),
-        and the right (blue) group
-        contains $k$ features from the left arcuate (ARCL). The coefficients in
-        $\hat{\beta}$ follow the same natural grouping.
-        % Cross-validation:
-        % we evaluate model quality using a nested $k$-fold cross validation
-        % scheme. At level-0, the input data is decomposed into $k$
-        % shuffled groups and optimal hyperparameters are found for the level-0
-        % training set.
-        % To avoid overfitting, the optimal hyperparameters are themselves
-        % evaluated using a cross-validation scheme taking place
-        % at level-1 of the decomposition, where each
-        % level-0 training set is further decomposed into five shuffled
-        % groups. For the ALS and WH data, $k=10$, while for the HBN and
-        % Cam-CAN data, $k=5$.
-    }
-\end{figure}
-
 Non-invasive methods for measuring human brain structure and function have
@@
 voxel to assess the physical properties of the white matter along specific
-pathways~\cite{Bells2011-cf}.
+pathways~\cite{Jones2005-yq, Bells2011-cf}.
 %Though there are several different available implementations of this overall
@@
 %\end{enumerate}
+\begin{figure}[h!]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{0.25em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-5.25cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{{\bf Tractometry data flow}
+        \label{fig:methods}
+        {\bf (a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
+        anatomical slice.
+        {\bf (c)} Tractometry further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for CSTL.
+        {\bf (d)} the phenotypical target data and tractometric features can
+        be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the left arcuate (ARCL). The coefficients in
+        $\hat{\beta}$ follow the same natural grouping.
+        % Cross-validation:
+        % we evaluate model quality using a nested $k$-fold cross validation
+        % scheme. At level-0, the input data is decomposed into $k$
+        % shuffled groups and optimal hyperparameters are found for the level-0
+        % training set.
+        % To avoid overfitting, the optimal hyperparameters are themselves
+        % evaluated using a cross-validation scheme taking place
+        % at level-1 of the decomposition, where each
+        % level-0 training set is further decomposed into five shuffled
+        % groups. For the ALS and WH data, $k=10$, while for the HBN and
+        % Cam-CAN data, $k=5$.
+    }
+\end{figure}
 
@@
 this approach by applying it to both classification
-and continuous prediction problems.
+and continuous prediction problems. Our tractometry data flow is
+represented in \cref{fig:methods} and explained in further detail in
+the supplementary material.
 
@@
 \begin{figure*}
-    \vspace{3cm}
+    \vspace{4.0cm}
     \rlap{
@@
     }
-    \vspace{-8.4cm}
+    \vspace{-9.25cm}
     \includegraphics[width=\textwidth]{als_results.pdf}
@@
 selection of features only within the CST bundle-of-interest.
-SGL delivers improved predictive performance, with a cross-validated accuracy of {\alsAccuracy}\% and an area under the receiver operating characteristic curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature engineering (Figure \cref{fig:class-results:probs}).
-In addition to this
+SGL delivers improved predictive performance, with a cross-validated accuracy
+of {\alsAccuracy}\% and an area under the receiver operating characteristic
+curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature
+engineering (Figure \cref{fig:class-results:probs}). In addition to this
 classification performance, SGL also identifies the white matter tracts most
@@
 \cite{sarica2017corticospinal}.
-\todo{Adam: Add sentence comparing to pure lasso results.}
+
+To assess the added value of incorporating anatomical knowledge into our
+model, we compared our classification results to those obtained from a lasso
+model. The pure lasso model achieved 76\% accuracy and an ROC AUC of 0.76
+using the same cross-validation strategy used to assess the SGL model. This
+difference in performance justifies the additional complexity of the SGL over
+simpler sparsity-inducing regression strategies.
 
@@
 \begin{figure*}
-    \vspace{3.65cm}
+    \vspace{4.5cm}
     \rlap{
@@
     }
-    \vspace{-7.3cm}
+    \vspace{-8.0cm}
     \includegraphics[width=\textwidth]{regression_scatter.pdf}
@@
 on diffusion MRI features \cite{Richard2018-ux}.
-\todo{Adam: Add sentence comparing to pure lasso results.}
 
@@
 different between the age quintiles.
+
+As with ALS classification, we also compared SGL performance with results
+obtained using only the lasso penalty. The pure lasso models achieved $R^2 =
+0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
+using the same cross-validation strategy used to assess the SGL. The SGL
+models' performance improvement over lasso is more modest than in the ALS
+classification case, which accords with the selected values of the $\alpha$
+hyperparameter. These SGL models were more lasso-like in their sparsity
+penalties so they are more lasso-like in their predictive performance.
 
@@
 The method is packaged as open-source software called AFQ-Insight that is
-openly available \todo{Ariel: add URL}, and provides a clear API to allow for
-extensions of the method. The sofware integrates within a broader automated
-fiber quantification software ecosystem: AFQ \cite{yeatman2012tract} and
-pyAFQ (https://yeatmanlab.github.io), which extract tractometry data from raw
-and processed dMRI datasets, as well as AFQ-Browser, which visualizes
-tractometry data and facilitates sharing of the results of dMRI studies
-\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
-software, the results presented in this paper are also provided in
-\url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks}
-\todo{Adam: Update notebooks}
-as a series of Jupyter notebooks \cite{kluyver2016jupyter}.
+openly available at \url{https://github.com/richford/AFQ-Insight}, and
+provides a clear API to allow for extensions of the method. The sofware
+integrates within a broader automated fiber quantification software
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ}, which extract
+tractometry data from raw and processed dMRI datasets, as well as
+AFQ-Browser, which visualizes tractometry data and facilitates sharing of the
+results of dMRI studies \cite{yeatman2018browser}. To facilitate
+reproducibility and ease use of the software, the results presented in this
+paper are also provided in
+\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
+notebooks \cite{kluyver2016jupyter}.
 

### 2021-02-01 notebooks/plot_utils.py
Remove revealjs presentation, update all manuscript figures, remove obsolete notebooks, update README, add external data for T2 reference volume

@@ -1,0 +1,277 @@
+import AFQ.data as afqd
+import afqinsight as afqi
+import json
+import nibabel as nib
+import numpy as np
+import pandas as pd
+import plotly.graph_objects as go
+
+from AFQ.viz.plotly_backend import visualize_volume
+from plotly.subplots import make_subplots
+
+
+def plot_coefs_on_bundle_cores(
+    results,
+    key,
+    columns,
+    metric="fa",
+    use_pyafq_bundle_names=False,
+    linewidth=15,
+    coef_func=(
+        None,
+        "abs_mean",
+    ),
+    eye=None,
+    center=None,
+    width=500,
+    height=500,
+):
+    my_results = results[key][0]
+    coefs = np.array([np.array(bag_res["coefs"]) for bag_res in my_results.values()])
+    mean_beta = np.mean(np.array(coefs), axis=(0, 1))
+    with open("../data/raw/core_streamlines.json") as fp:
+        cores = json.load(fp)
+
+    index = pd.MultiIndex.from_tuples(columns, names=["metric", "tractID", "nodeID"])
+    beta_hats = afqi.beta_hat_by_groups(mean_beta, columns=index, drop_zeros=True)
+
+    bad_keys = [k for k in beta_hats.keys() if "Cingulum Hippocampus" in k]
+    for key in bad_keys:
+        _ = beta_hats.pop(key, None)
+
+    new_cores = {}
+    if use_pyafq_bundle_names:
+        for key, val in cores.items():
+            if (
+                key in afqd.BUNDLE_MAT_2_PYTHON
+                and afqd.BUNDLE_MAT_2_PYTHON[key] in beta_hats
+            ):
+                new_cores[afqd.BUNDLE_MAT_2_PYTHON[key]] = val
+    else:
+        for key, val in cores.items():
+            if key in beta_hats:
+                new_cores[key] = val
+
+    cores = new_cores
+
+    bundle_names = beta_hats.keys()
+    bundles = {bn: np.array(cores[bn]["coreFiber"]) for bn in cores.keys()}
+
+    def color_transform(betas, func):
+        if func is None:
+            return betas
+        if func == "abs_max":
+            return np.max(np.abs(betas)) * np.ones_like(betas)
+        if func == "abs_mean":
+            return np.mean(np.abs(betas)) * np.ones_like(betas)
+        if func == "abs":
+            return np.abs(betas)
+
+    colors = {
[…]

### 2021-02-01 reports/manuscript/supplemental.tex
Add comments on comparison to lasso

@@
                amsmath,%
-               floatfix,%
-               endfloats*]{revtex4-2}
+               floatfix]{revtex4-2}
 \usepackage[T1]{fontenc}
@@
 Data from the HBN and Cam-CAN studies were processed using the updated Python
-Automated Fiber Quantification toolbox (\texttt{pyAFQ})\todo{Add pyAFQ
-citation}. In addition to demonstrating the our analysis pipeline is robust
-to changes in tractometry software, the use of the updated \texttt{pyAFQ}
-capitalized upon the following improvements over the legacy Matlab version
+Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{pyAFQ}). In
+addition to demonstrating the our analysis pipeline is robust to changes in
+tractometry software, the use of the updated \texttt{pyAFQ} capitalized upon
+the following improvements over the legacy Matlab version
 \begin{enumerate*}[%

### 2021-02-01 reports/manuscript/paper.tex
Rename notebooks and add plotting notebook
Add comments on comparison to lasso
Remove todo note in abstract

@@
     % Abstracts should be unreferenced and typically around 150 words
-    \todo{Shorten abstract to roughly 150 words.}
     The white matter contains long-range connections between different

### 2021-02-02 reports/manuscript/paper.tex
Adjust figure placement

@@
 \begin{abstract}
-    % Abstracts should be unreferenced and typically around 150 words
-    The white matter contains long-range connections between different
-    brain regions and the organization of these connections holds important
-    implications for brain function in health and disease. Tractometry
-    uses diffusion-weighted magnetic resonance imaging (dMRI)
-    to quantify tissue properties (e.g. fractional anisotropy (FA),
-    mean diffusivity (MD), etc.), along the trajectories of these
-    connections.
+    The white matter contains long-range connections between different brain
+    regions and the organization of these connections holds important
+    implications for brain function in health and disease. Tractometry uses
+    diffusion-weighted magnetic resonance imaging (dMRI) to quantify tissue
+    properties along the trajectories of these connections.
     % \cite{yeatman2012tract}.
-    Statistical inference from
-    tractometry usually either averages these quantities along
-    the length of each bundle in each individual or performs analysis
-    point-by-point along each bundle, with group comparisons or regression
-    models computed separately for each point along every one of the bundles.
-    These approaches are limited in their sensitivity, in the former case, or
-    in their statistical power, in the latter.
-    In the present work, we developed a method based on the sparse group
-    lasso (SGL)
+    Statistical inference from tractometry usually either averages these
+    quantities along the length of each fiber bundle or computes regression
+    models separately for each point along every one of the bundles. These
+    approaches are limited in their sensitivity, in the former case, or in
+    their statistical power, in the latter. We developed a method based on
+    the sparse group lasso (SGL)
     % \cite{simon2013sparse}
-    that takes into account tissue
-    properties measured along all of the bundles, and selects informative
-    features by enforcing sparsity, not only at the level of individual
-    bundles, but also across the entire set of bundles and all of the measured
-    tissue properties.
-    % The sparsity penalties for each of these constraints
-    % is identified using a nested cross-validation scheme that guards
-    % against over-fitting and simultaneously identifies the correct
-    % level of sparsity.
-    We demonstrate the accuracy of the method in two
-    settings: i) In a classification setting, patients with amyotrophic
-    lateral sclerosis (ALS) are accurately distinguished from matched
-    controls.
+    that takes into account tissue properties along all of the bundles and
+    selects informative features by enforcing both global and bundle-level
+    sparsity. We demonstrate the performance of the method in two settings:
+    i) in a classification setting, patients with amyotrophic lateral
+    sclerosis (ALS) are accurately distinguished from matched controls.
     % \cite{sarica2017corticospinal}.
-    Furthermore, SGL automatically
-    identifies FA in the corticospinal tract as important for this
-    classification, correctly finding the parts of the white matter known
-    to be affected by the disease. ii) In a regression setting, dMRI is
-    used to accurately predict ``brain age.''
+    Furthermore, SGL identifies the corticospinal tract as important for this
+    classification, correctly finding the parts of the white matter known to
+    be affected by the disease. ii) In a regression setting, SGL accurately
+    predicts ``brain age.''
     % \cite{yeatman2014lifespan, Brown2012-so}.
-    In this case, the weights are distributed throughout the
-    white matter indicating that many different regions of the white matter
-    change with development and contribute to the prediction of age. Thus,
-    SGL makes it possible to leverage the multivariate relationship between
-    diffusion properties measured along multiple bundles to make accurate
-    predictions of subject characteristics while simultaneously discovering
-    the most relevant features of the white matter for the characteristic of
-    interest.
+    In this case, the weights are distributed throughout the white matter
+    indicating that many different regions of the white matter change over
+    the lifespan. Thus, SGL leverages the multivariate relationships between
+    diffusion properties in multiple bundles to make accurate phenotypic
+    predictions while simultaneously discovering the most relevant features
+    of the white matter.
 \end{abstract}
@@
 as the predicted variable $y$. SGL was fit to the tractometry-extracted
-features FA and MD in 18 major brain tracts, with diffusion metrics extracted
+features FA and mean diffusivity (MD) in 18 major brain tracts, with diffusion metrics extracted
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
@@
 
-\printfigures
-
 \bibliographystyle{naturemag}

### 2021-02-02 reports/manuscript/supplemental.tex
Adjust figure placement

@@
 
+\begin{figure}[t]
+    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
+    \caption{{\bf Nested cross-validation}
+        \label{fig:nested-cross-val}
+        We evaluate model quality using a nested $k$-fold cross validation
+        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+        groups and optimal hyperparameters are found for the level-0 training
+        set. To avoid overfitting, the optimal hyperparameters are themselves
+        evaluated using a cross-validation scheme taking place at level-1 of
+        the decomposition, where each level-0 training set is further
+        decomposed into $k_1 = 3$ shuffled groups. In the classification
+        case, the training and test splits are stratified by diagnosis. For
+        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+        $k_0 = 5$.
+    }
+\end{figure}
+
 Before fitting a model to the data, imputation and standardization are
@@
 
-\begin{figure}[!h]
-    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
-    \caption{{\bf Nested cross-validation}
-        \label{fig:nested-cross-val}
-        We evaluate model quality using a nested $k$-fold cross validation
-        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
-        groups and optimal hyperparameters are found for the level-0 training
-        set. To avoid overfitting, the optimal hyperparameters are themselves
-        evaluated using a cross-validation scheme taking place at level-1 of
-        the decomposition, where each level-0 training set is further
-        decomposed into $k_1 = 3$ shuffled groups. In the classification
-        case, the training and test splits are stratified by diagnosis. For
-        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
-        $k_0 = 5$.
-    }
-\end{figure}
-
 Because the SGL is not specific to tractometry, we implemented its solution as
@@
 
+\begin{figure*}
+    \includegraphics[width=\textwidth]{sarica_coefs_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
+            coefficients for ALS classification.
+        }
+        \label{fig:als-bp:fa}
+    }
+\end{figure*}
+
 To objectively evaluate model performance and guard against over-fitting,
@@
 $\alpha$ and $\lambda$ using sequential model-based optimization, implemented
-using the scikit-optimize \verb|BayesSearchCV| class\cite{scikit-optimize}.
+using the scikit-optimize \verb|BayesSearchCV| class \cite{scikit_optimize}.
 For continuous numerical $y$, \verb|BayesSearchCV| searches for
@@
 
+\begin{figure*}
+    \includegraphics[width=\textwidth]{sarica_coefs_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Mean diffusivity (MD) Bundle profiles and $\hat{\beta}$
+            coefficients for ALS classification.
+        }
+        \label{fig:als-bp:md}
+    }
+\end{figure*}
+
 \subsection{Software implementation}
@@
 The version of the code used to produce the results herein is also available in
-\url{https://doi.org/10.5281/zenodo.3585942}\todo{Update version here}.
+\url{https://doi.org/10.5281/zenodo.4316000}.
 AFQ-Insight reads the target and feature data that has been processed by AFQ
@@
 determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the \texttt{groupyr} software library \cite{groupyr} mentioned above to solve the SGL.
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{wh_coefs_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the WH dataset.
+        }
+        \label{fig:wh-bp:fa}
+    }
+\end{figure*}
 
@@
 
-\subsection{ALS bundle profiles}
-
 \begin{figure*}
-    \includegraphics[width=\textwidth]{sarica_coefs_profiles_fa.pdf}
+    \includegraphics[width=\textwidth]{wh_coefs_profiles_md.pdf}
     \caption{%
         {%
-            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for ALS classification.
+            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the WH dataset.
         }
-        \label{fig:als-bp:fa}
+        \label{fig:wh-bp:md}
     }
 \end{figure*}
+
+\subsection{ALS bundle profiles}
 
@@
 \begin{figure*}
-    \includegraphics[width=\textwidth]{sarica_coefs_profiles_md.pdf}
+    \includegraphics[width=\textwidth]{hbn_coefs_profiles_fa.pdf}
     \caption{%
         {%
-            \bf Mean diffusivity (MD) Bundle profiles and $\hat{\beta}$
-            coefficients for ALS classification.
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the HBN dataset.
         }
-        \label{fig:als-bp:md}
+        \label{fig:hbn-bp:fa}
     }
@@
 \subsection{WH bundle profiles}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{wh_coefs_profiles_fa.pdf}
-    \caption{%
-        {%
-            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the WH dataset.
-        }
-        \label{fig:wh-bp:fa}
-    }
-\end{figure*}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{wh_coefs_profiles_md.pdf}
-    \caption{%
-        {%
-            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the WH dataset.
-        }
-        \label{fig:wh-bp:md}
-    }
-\end{figure*}
-
 \subsection{HBN bundle profiles}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{hbn_coefs_profiles_fa.pdf}
-    \caption{%
-        {%
-            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the HBN dataset.
-        }
-        \label{fig:hbn-bp:fa}
-    }
-\end{figure*}
 

### 2021-02-02 reports/manuscript/supplemental.tex
Update environment.yml and Dockerfile. Add line numbers to paper

@@
                preprintnumbers,%
+               linenumbers,%
                amsmath,%
@@
 
-Here, we propose that in addition to regularizing the coefficients in
+We propose that in addition to regularizing the coefficients in
 $\hat{\beta}$, we can also capitalize on our knowledge of the group structure

### 2021-02-02 reports/manuscript/cover_letter/cover_letter.tex
Use tex mplstyle in Docker image

\documentclass{letter}
\usepackage[margin=1in]{geometry}

\signature{Adam Richie-Halford, PhD \\ \vspace{4em} Ariel Rokem, PhD}
\address{The eScience Institute \\ University of Washington \\ Seattle, WA}
\begin{document}

\begin{letter}{}
\opening{Dear Editors,}

We are pleased to submit our manuscript entitled ``Multidimensional analysis
and detection of informative features in human brain white matter'' to Nature
Methods.

This work presents a novel approach to the analysis of brain connectivity in
diffusion-weighted MRI. Adopting a group-sparse linear approach, we model the
multi-dimensional data from these measurements, taking into account the
grouping of the measurement to the different anatomical connections between
brain regions. We demonstrate the accuracy of this approach in four different
datasets. Our results show that the model is highly accurate (exceeding the
accuracy of previous state-of-the-art results) in both classification of
disease states, as well as the prediction of continuous variables (i.e., the
biological age of participants). Importantly, the results show that the
method produces results that are not only accurate but also highly
interpretable, because of the linear modeling approach. We produced
high-quality open-source software implementing our approach that can easily
be used in the analysis of other datasets.

Neuroscience, like many other fields, is at the cusp of an exciting era of
Big Data. This is thanks in large part to concerted efforts to collect and
aggregate large datasets. The paradigmatic example of this kind of data
collection is the NIH-funded Human Connectome Project (HCP), which has
collected high-quality MRI data from more than 1,200 young healthy
individuals, coupled with behavioral and genetic information. Similarly, the
Healthy Brain Network study, which we analyze in the present paper, as well
as the Adolescent Brain Cognitive Development study (ABCD) will each collect
cross-sectional and longitudinal data from approximately 10,000 children
during their development, together with detailed information about their
cognitive and mental health development. Several dozen other projects are
currently collecting large datasets of diffusion-weighted MRI in specific
populations, and addressing specific brain disease states. As these datasets
are collected, the field is in dire need of analysis methods that are both
predictive and interpretable. In our manuscript, we demonstrate that our
method is applicable to very large datasets, including two different
openly-available datasets with more than 500 subjects each.

Importantly, the software and analysis methods that we provide generalize
well beyond neuroscience into other fields where group-sparse linear models
can be applied, including other fields of biology, but also other physical
and even social sciences. Therefore, we believe that this manuscript will be
of interest to a broad range of researchers.

We appreciate your consideration of our manuscript

\closing{Sincerely,}

\encl{Manuscript}
\encl{Supplemental materials}

\end{letter}
\end{document}

### 2021-02-05 reports/manuscript/cover_letter/cover_letter.tex
Change paper formatting to PLOS-CompBio

@@
 We are pleased to submit our manuscript entitled ``Multidimensional analysis
-and detection of informative features in human brain white matter'' to Nature
-Methods.
+and detection of informative features in human brain white matter'' to
+\emph{PLOS Computational Biology}.
 

### 2021-02-05 reports/manuscript/paper.tex
Update environment.yml and Dockerfile. Add line numbers to paper
Change paper formatting to PLOS-CompBio

@@
-%% ****** Start of file apstemplate.tex ****** %
-%%
-%%   This file is part of the APS files in the REVTeX 4 distribution.
-%%   Version 4.1r of REVTeX, August 2010
-%%
-%%
-%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
-%%
-%%   See the REVTeX 4 README file for restrictions and more information.
-%%
+% Template for PLoS
+% Version 3.5 March 2018
 %
-% This is a template for producing manuscripts for use with REVTEX 4.0
-% Copy this file to another name and then work on that file.
-% That way, you always have this original template file to use.
+% % % % % % % % % % % % % % % % % % % % % %
 %
-% Group addresses by affiliation; use superscriptaddress for long
-% author lists, or if there are many overlapping affiliations.
-% For Phys. Rev. appearance, change preprint to twocolumn.
-% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
-%  Add 'draft' option to mark overfull boxes with black boxes
-%  Add 'showpacs' option to make PACS codes appear
-%  Add 'showkeys' option to make keywords appear
-\documentclass[10pt,%
-               aps,%
-               prl,%
-               reprint,%
-               superscriptaddress,%
-               preprintnumbers,%
-               amsmath,%
-               floatfix]{revtex4-1}
-\usepackage[T1]{fontenc}
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
 \usepackage[utf8x]{inputenc}
-\usepackage[export]{adjustbox}  % Used to adjust figure frames
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+\usepackage[capitalize]{cleveref}
+\usepackage[inline]{enumitem}
+\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
+\usepackage{listings}
+\usepackage{todonotes}
 \usepackage{subcaption}
 \usepackage{url}
-\usepackage{color}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
 \usepackage{xcolor}
-\usepackage{listings}
-\usepackage{float}
-\usepackage{amsfonts}
-\usepackage{mathtools}
-\usepackage{dcolumn}
-\usepackage{wrapfig}
-\usepackage{physics}
-\usepackage[inline]{enumitem}
-\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
-\usepackage{todonotes}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+\usepackage{physics}  % for \norm
 \usepackage{graphicx}
@@
 
-%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
-\usepackage{xr-hyper}
-\usepackage[pdftex,%
-            colorlinks=true,%
-            linkcolor=blue,%
-            citecolor=blue,%
-            urlcolor=blue,%
-            bookmarksnumbered=true,%
-            bookmarksopen=true]{hyperref}
-\usepackage[capitalize]{cleveref}
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
 \makeatletter
-\newcommand*{\addFileDependency}[1]{
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
+\renewcommand{\@biblabel}[1]{\quad#1.}
 \makeatother
 
-\newcommand*{\myexternaldocument}[2][ext:]{
-    \externaldocument[#1]{#2}
-    \addFileDependency{#2.tex}
-    \addFileDependency{#2.aux}
-}
-%%% END HELPER CODE
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
 
-% put all the external documents here!
-\myexternaldocument[supp:]{supplemental}
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
 
 \begin{document}
+\vspace*{0.2in}
 
-\title{Multidimensional analysis and detection of informative features in human brain white matter}
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Multidimensional analysis and detection of informative features in human brain white matter} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Adam Richie-Halford\textsuperscript{1*},
+Jason Yeatman\textsuperscript{2},
+Noah Simon\textsuperscript{3},
+Ariel Rokem\textsuperscript{4},
+\\
+\bigskip
+\textbf{1} eScience Institute, University of Washington, Seattle, WA, USA
+\\
+\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, CA, USA
+\\
+\textbf{3} Department of Biostatistics, University of Washington, Seattle, WA, USA
+\\
+\textbf{4} Department of Psychology, University of Washington, Seattle, WA, USA
+\\
+\bigskip
 
-\author{Adam \surname{Richie-Halford}}%
-\email{richford@uw.edu}%
-\affiliation{%
-    eScience Institute,%
-    University of Washington, Seattle,%
-    Washington 98195--1560, USA
-}
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* richford@uw.edu
 
-\author{Jason \surname{Yeatman}}%
-\affiliation{%
-    Graduate School of Education and Division of Developmental and Behavioral Pediatrics,%
-    Stanford University,%
-    Stanford, CA, 94305, USA
-}
+\end{flushleft}
 
-\author{Noah \surname{Simon}}%
-\affiliation{%
-    Department of Biostatistics,%
-    University of Washington, Seattle,%
-    Washington 98195--1560, USA
-}
+\newcommand*{\alsLRatio}{$0.21$}
+\newcommand*{\whLRatio}{$0.84$}
+\newcommand*{\hbnLRatio}{$0.72$}
+\newcommand*{\ccLRatio}{$0.83$}
+\newcommand*{\alsAccuracy}{$83$}
+\newcommand*{\alsRocAuc}{$0.88$}
+\newcommand*{\whRsq}{$0.52$}
+\newcommand*{\whMae}{$2.84$}
+\newcommand*{\hbnRsq}{$0.56$}
+\newcommand*{\hbnMae}{$1.5$}
+\newcommand*{\camcanRsq}{$0.77$}
+\newcommand*{\camcanMae}{$6.02$}
 
-\author{Ariel \surname{Rokem}}%
-\affiliation{%
-    Department of Psychology,%
-    University of Washington, Seattle,%
-    Washington 98195--1560, USA
-}
+% Please keep the abstract below 300 words
+\section*{Abstract}
 
-\date{\today}
-
-\input{output}
-
-\begin{abstract}
 The white matter contains long-range connections between different brain
@@
 of the white matter.
-\end{abstract}
 
-\maketitle
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
+\todo[inline]{Write author summary}
 
-\subsection*{Introduction}
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
+\section*{Introduction}
 
@@
 % \item Mass univariate approaches: In this approach
-
 % \item Region of interest(ROI)-based approaches:
@@
 %\end{enumerate}
-\begin{figure}[h!]
-    \vspace{0.25cm}
-    \rlap{
-        \hspace{0.25em}
-        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    }
-    \vspace{-5.25cm}
-    \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{{\bf Tractometry data flow}
-        \label{fig:methods}
-        {\bf (a)} Whole brain tractography generates streamlines approximating
-        the trajectories of white matter connections.
-        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
-        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
-        anatomical slice.
-        {\bf (c)} Tractometry further extracts bundle profiles,
-        quantifications of various diffusion metrics along the length of the
-        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for CSTL.
-        {\bf (d)} the phenotypical target data and tractometric features can
-        be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the CSTL, the middle (green) group
-        contains $k$ features from the left cingulum cingulate (CGCL),
-        and the right (blue) group
-        contains $k$ features from the left arcuate (ARCL). The coefficients in
-        $\hat{\beta}$ follow the same natural grouping.
-        % Cross-validation:
-        % we evaluate model quality using a nested $k$-fold cross validation
-        % scheme. At level-0, the input data is decomposed into $k$
-        % shuffled groups and optimal hyperparameters are found for the level-0
-        % training set.
-        % To avoid overfitting, the optimal hyperparameters are themselves
-        % evaluated using a cross-validation scheme taking place
-        % at level-1 of the decomposition, where each
-        % level-0 training set is further decomposed into five shuffled
-        % groups. For the ALS and WH data, $k=10$, while for the HBN and
-        % Cam-CAN data, $k=5$.
-    }
-\end{figure}
-
 The present work aims to balance predictive accuracy with descriptive power
@@
 % the
-
 The Lasso algorithm minimizes the sum of the absolute values of
@@
 represented in \cref{fig:methods} and explained in further detail in
-the supplementary material.
+the methods section.
 
-\subsection*{Results}
+\begin{figure}[h!]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{0.25em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-8.25cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{{\bf Tractometry data flow}
+        \label{fig:methods}
+        {\bf (a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
+        anatomical slice.
+        {\bf (c)} Tractometry further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for CSTL.
+        {\bf (d)} the phenotypical target data and tractometric features can
+        be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the left arcuate (ARCL). The coefficients in
+        $\hat{\beta}$ follow the same natural grouping.
+    }
+\end{figure}
 
-\begin{figure*}
-    \vspace{4.0cm}
+% Results
+\section*{Results}
+
+\begin{figure}
+    \vspace{0.0cm}
     \rlap{
@@
     }
-    \vspace{-9.25cm}
+    \vspace{-7.0cm}
     \includegraphics[width=\textwidth]{als_results.pdf}
@@
     }
-\end{figure*}
+\end{figure}
 
@@
 
-\subsubsection*{SGL accurately detects ALS from tractometry data}
+\subsection*{SGL accurately detects ALS from tractometry data}
 
@@
 curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature
-engineering (Figure \cref{fig:class-results:probs}). In addition to this
+engineering (\cref{fig:class-results:probs}). In addition to this
 classification performance, SGL also identifies the white matter tracts most
 important for ALS classification. The relative importance of white matter
-features is captured in the $\beta$ coefficients from \cref{supp:eq:sgl} of
-the supplemental material \cite{supplement}.
+features is captured in the $\beta$ coefficients from \cref{eq:sgl}.
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
@@
 Group Lasso and lasso penalties, selected through nested cross-validation
-(see \cref{supp:eq:sgl} of the supplemental material \cite{supplement}).
+(see \cref{eq:sgl}).
 If $\alpha$ is closer to zero, it indicates that the phenotype in question
@@
 insight. We found that mislabelled subjects are outliers relative to their
-group with respect to diffusion features of the CST (Figure
-\Cref{fig:class-results:false-positives,fig:class-results:false-negatives}).
-The false positive classifications have reduced FA in one or more of the three
-sections of the CST where $\norm*{\hat{\beta}}$ is large
+group with respect to diffusion features of the CST
+(\cref{fig:class-results:false-positives,fig:class-results:false-negatives}).
+The false positive classifications have reduced FA in one or more of the
+three sections of the CST where $\norm*{\hat{\beta}}$ is large in
 \cref{fig:class-results:tract-profiles}. The false negative subjects have FA
@@
 
-\begin{figure*}
-    \vspace{4.5cm}
+\begin{figure}
+    \vspace{0.0cm}
     \rlap{
@@
     }
-    \vspace{-8.0cm}
+    \vspace{-6.0cm}
     \includegraphics[width=\textwidth]{regression_scatter.pdf}
@@
     }
-\end{figure*}
+\end{figure}
 
-\subsubsection*{SGL accurately predicts age from tractometry data}
+\subsection*{SGL accurately predicts age from tractometry data}
 
@@
 regression task, we focus here on the prediction of biological age in three
-datasets named WH, HBN, and Cam-CAN (see supplemental material
-\cite{supplement} for a description of each dataset). Prediction of ``brain
+datasets named WH, HBN, and Cam-CAN (see the methods section for a description of each dataset). Prediction of ``brain
 age'' is a commonly undertaken task in neuroimaging machine learning, in part
@@
 \cref{fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d}
-and supplemental material
-\cref{supp:fig:wh-bp:md,supp:fig:wh-bp:fa,supp:fig:hbn-bp:md,supp:fig:hbn-bp:fa,supp:fig:cc-bp:md,supp:fig:cc-bp:fa}).
+and supporing Figures in \nameref{S1_Appendix}).
 This demonstrates that SGL is not coerced to produce overly sparse results
@@
 
-\subsection*{Discussion}
+\section*{Discussion}
 
@@
 predictions of phenotypic properties of individual subjects while,
-simultaneously, identifying the features of the white matter that are
-most important for this prediction. The method is data-driven and it is broadly applicable to a wide range of research questions: it
-performs well in predicting both continuous variables, such as biological
-age, as well as categorical variables, such as whether a person is a patient
-or a healthy control. In both of these cases, SGL out-performs previous
-algorithms that have been developed for these tasks
-\cite{sarica2017corticospinal, Richard2018-ux, mcpherson2020single}. The
-nested cross-validation approach used to fit the model and make both
-predictions and inferences from the model guards against overfitting and
-tunes the degree of sparseness required by the algorithm. This means that SGL
-can accurately describe phenomena that are locally confined to a particular
-anatomical location or diffusion property (e.g., FA in the CST) as well as
-phenomena that are widely distributed amongst brain regions and measured
-diffusion properties.
+simultaneously, identifying the features of the white matter that are most
+important for this prediction. The method is data-driven and it is broadly
+applicable to a wide range of research questions: it performs well in
+predicting both continuous variables, such as biological age, as well as
+categorical variables, such as whether a person is a patient or a healthy
+control. In both of these cases, SGL out-performs previous algorithms that
+have been developed for these tasks \cite{sarica2017corticospinal,
+Richard2018-ux, mcpherson2020single}. The nested cross-validation approach
+used to fit the model and make both predictions and inferences from the model
+guards against overfitting and tunes the degree of sparseness required by the
+algorithm. This means that SGL can accurately describe phenomena that are
+locally confined to a particular anatomical location or diffusion property
+(e.g., FA in the CST) as well as phenomena that are widely distributed
+amongst brain regions and measured diffusion properties.
 
@@
 and provides a means to understand model errors (e.g.,
-\cref{fig:class-results:false-positives,fig:class-results:false-negatives}) .
-Thus, this multivariate analysis approach achieves high
-cross-validated accuracy for precision medicine applications of dMRI data and identifies relevant features of brain anatomy that can further our
-neuroscientific understanding of clinical disorders.
+\cref{fig:class-results:false-positives,fig:class-results:false-negatives}).
+Thus, this multivariate analysis approach achieves high cross-validated
+accuracy for precision medicine applications of dMRI data and identifies
+relevant features of brain anatomy that can further our neuroscientific
+understanding of clinical disorders.
 
@@
 alexander2017open, Miller2016-hw, VanEssen2012}, but the volume and
-complexity of these data pose substantial challenges. Tractometry
-followed by analysis with SGL provide a promising approach to
-distill meaningful insights from the wealth of data measured in these efforts.
+complexity of these data pose substantial challenges. Tractometry followed by
+analysis with SGL provide a promising approach to distill meaningful insights
+from the wealth of data measured in these efforts.
 
-SGL has many other potential applications in neuroscience, because
-of the hierarchical and grouped nature of many data types that are
-collected in multiple sample points within anatomically-defined areas.
-For example, this method may be useful to understand the relationship
-between fMRI recordings and behavior, where activity in each voxel
-may co-vary with voxels within the same anatomical region and form
-features and groups of features. Similarly, large-scale multi-electrode
-recordings of neural activity in awake behaving animals are becoming
-increasingly feasible \cite{steinmetz2018distributed, Jun2017-gv} and
-these recordings can form features (neurons) and groups (neurons within
-an anatomical region).
+SGL has many other potential applications in neuroscience, because of the
+hierarchical and grouped nature of many data types that are collected in
+multiple sample points within anatomically-defined areas. For example, this
+method may be useful to understand the relationship between fMRI recordings
+and behavior, where activity in each voxel may co-vary with voxels within the
+same anatomical region and form features and groups of features. Similarly,
+large-scale multi-electrode recordings of neural activity in awake behaving
+animals are becoming increasingly feasible \cite{steinmetz2018distributed,
+Jun2017-gv} and these recordings can form features (neurons) and groups
+(neurons within an anatomical region).
 
@@
 % would pose a challenging problem to solve using SGL.
-
 The results we present here also motivate extensions of the method using more
-sophisticated cost functions. For example, the fused sparse group lasso (FSGL)
-\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
-in the variation of diffusion metrics along the bundles. As brain measurements
-include additional structure (for example, bilateral symmetry), future work
-could also incorporate overlapping group membership for each entry in the tract
-profiles \cite{Rao2014-xm}. For example, a measurement could come from the
-corpus callosum, but also from the right hemipshere. This would also require
-extending the cost function used here to incorporate these constraints.
-Similarly, unsupervised dimensionality reduction of tractometry data (e.g.,
-\cite{Chamberland2019-mu}) could also benefit from constraints based on
-grouping.
+sophisticated cost functions. For example, the fused sparse group lasso
+(FSGL) \cite{zhou2012} extends SGL to enforce additional spatial structure:
+smoothness in the variation of diffusion metrics along the bundles. As brain
+measurements include additional structure (for example, bilateral symmetry),
+future work could also incorporate overlapping group membership for each
+entry in the tract profiles \cite{Rao2014-xm}. For example, a measurement
+could come from the corpus callosum, but also from the right hemipshere. This
+would also require extending the cost function used here to incorporate these
+constraints. Similarly, unsupervised dimensionality reduction of tractometry
+data (e.g., \cite{Chamberland2019-mu}) could also benefit from constraints
+based on grouping.
 
@@
 
-\subsection*{Methods}
+\section*{Materials and methods}
+\label{sec:methods}
 
-Methods and associated references are available in the supplemental material.
+\subsection*{Data}
+\label{sec:data}
 
-\subsection*{Acknowledgments}
+Four different datasets were used here:
+
+\begin{enumerate}
+
+\item Diffusion MRI from a previous study of the corticospinal
+tract (CST) in patients with amyotrophic lateral sclerosis
+(ALS \cite{sarica2017corticospinal}), containing data from 24 ALS
+patients and 24 demographically matched healthy controls. These data
+were measured in a GE Discovery 750 3T MRI scanner at the Institute
+of Bioimaging and Molecular Physiology in Catanzaro. Informed consent
+was provided as approved by the Ethical Committee of the University
+``Magna Graecia'' of Catanzaro. Voxel resolution was \num{2x2x2}
+$\text{mm}^3$ and 27 non-colinear directions were measured with a
+$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was preprocessed to
+correct for subject motion and for eddy currents. The diffusion tensor
+model \cite{basser1994mr} was fit in every voxel.
+We will refer to this dataset as ALS.
+
+\item Diffusion MRI data from a previous study of properties of
+the white matter across the lifespan \cite{yeatman2014lifespan},
+containing dMRI data from 76 subjects with ages 6-50. These data were
+measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
+for Cognitive and Neurobiological Imaging. The Stanford University
+IRB approved the procedures of this study. Informed consent was
+obtained from each adult participant, and assent for participation
+was provided by parents/guardians for children. Voxel resolution was
+\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
+$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
+measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. These data
+were acquired using a dual spin echo sequence, in which there is
+sufficient time for eddy currents to subside between the application of
+the gradients and the image acquisition, so no eddy current correction
+was applied, but motion correction was applied before fitting the
+diffusion tensor model \cite{basser1994mr} in every voxel using a robust
+fit \cite{chang2005restore}. We will refer to this dataset as WH.
+
+\item Diffusion MRI data from the Healthy Brain Network pediatric mental
+health study \cite{alexander2017open}, containing dMRI data from 978 subjects
+with ages 5-21. These data were measured in 3T Siemens MRI scanners at three
+sites in the New York area. Informed consent was obtained from each
+participant aged 18 or older. For participants younger than 18, written
+consent was obtained from their legal guardians and written assent was
+obtained from the participant. Voxel resolution was
+\num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions measured for
+each of $b=1000 \frac{\text{sec}}{\text{mm}^2}$ and $b=2000
+\frac{\text{sec}}{\text{mm}^2}$.
+Preprocessing was performed using \emph{QSIPrep} 0.12.1, which is based on
+\emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.
+
+\begin{itemize}
+
+\item {\it Anatomical data preprocessing}
+The T1-weighted (T1w) image was corrected for intensity non-uniformity
+(INU) using \texttt{N4BiasFieldCorrection} \cite[ANTs 2.3.1]{n4}, and
+used as T1w-reference throughout the workflow. The T1w-reference was
+then skull-stripped using \texttt{antsBrainExtraction.sh} (ANTs 2.3.1),
+using OASIS as target template. Spatial normalization to the ICBM 152
+Nonlinear Asymmetrical template version 2009c
+\cite[RRID:SCR\_008796]{mni} was performed through nonlinear
+registration with \texttt{antsRegistration} \cite[ANTs 2.3.1,
+RRID:SCR\_004757]{ants}, using brain-extracted versions of both T1w
+volume and template. Brain tissue segmentation of cerebrospinal fluid
+(CSF), white-matter (WM) and gray-matter (GM) was performed on the
+brain-extracted T1w using \texttt{FAST} \cite[FSL 6.0.3:b862cdd5,
+RRID:SCR\_002823]{fsl_fast}.
+
+\item {\it Diffusion data preprocessing}
+
+Any images with a b-value less than 100 s/mm\^{}2 were treated as a
+\emph{b}=0 image. MP-PCA denoising as implemented in MRtrix3's
+\texttt{dwidenoise}\cite{dwidenoise1} was applied with a 5-voxel
+window. After MP-PCA, B1 field inhomogeneity was corrected using
+\texttt{dwibiascorrect} from MRtrix3 with the N4 algorithm \cite{n4}.
+After B1 bias correction, the mean intensity of the DWI series was
+adjusted so all the mean intensity of the b=0 images matched across
+eachseparate DWI scanning sequence.
+\end{itemize}
+
+FSL (version 6.0.3:b862cdd5)'s eddy was used for head motion correction
+and Eddy current correction \cite{anderssoneddy}. Eddy was configured
+with a \(q\)-space smoothing factor of 10, a total of 5 iterations, and
+1000 voxels used to estimate hyperparameters. A linear first level model
+and a linear second level model were used to characterize Eddy
+current-related spatial distortion. \(q\)-space coordinates were
+forcefully assigned to shells. Field offset was attempted to be
+separated from subject movement. Shells were aligned post-eddy. Eddy's
+outlier replacement was run \cite{eddyrepol}. Data were grouped by
+slice, only including values from slices determined to contain at least
+250 intracerebral voxels. Groups deviating by more than 4 standard
+deviations from the prediction had their data replaced with imputed
+values. Data was collected with reversed phase-encode blips, resulting
+in pairs of images with distortions going in opposite directions. Here,
+b=0 reference images with reversed phase encoding directions were used
+along with an equal number of b=0 images extracted from the DWI scans.
+From these pairs the susceptibility-induced off-resonance field was
+estimated using a method similar to that described in \cite{topup}. The
+fieldmaps were ultimately incorporated into the Eddy current and head
+motion correction interpolation. Final interpolation was performed using
+the \texttt{jac} method.
+
+Several confounding time-series were calculated based on the
+\emph{preprocessed DWI}: framewise displacement (FD) using the implementation
+in \emph{Nipype} following the definitions by \cite{power_fd_dvars}. The DWI
+time-series were resampled to ACPC, generating a \emph{preprocessed DWI run
+in ACPC space}.
+
+Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
+\cite[RRID:SCR\_001362]{nilearn} and \emph{DIPY} \cite{dipy}. For more
+details of the pipeline, see
+\href{https://qsiprep.readthedocs.io/en/latest/workflows.html}{the
+section corresponding to workflows in \emph{QSIPrep}'s documentation}.
+We will refer to this dataset as HBN.
+
+\item Diffusion MRI data from the Cambridge Centre for Ageing and
+Neuroscience (Cam-CAN) ``CC700'' dataset
+\cite{shafto2014cambridge,taylor2017cambridge}, containing data from 640
+subjects with ages 18-88. These data were measured on a 3T Siemens TIM Trio
+system and written informed consent was obtained from each participant. Voxel
+resolution was \num{2x2x2}$\text{mm}^3$ with 30 non-colinear directions
+measured for each of $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$ and $b=2000$
+$\frac{\text{sec}}{\text{mm}^2}$. The diffusion weighted images were acquired
+with a twice refocused spin-echo sequence and the same preprocessing pipeline
+used for the HBN dataset was applied to this data. We will refer to this
+dataset as Cam-CAN.
+
+\end{enumerate}
+
+Data from the ALS and WH studies was processed in a similar manner,
+using the Matlab Automated Fiber Quantification toolbox (\texttt{mAFQ})
+\cite{yeatman2012tract}: streamlines representing fascicles of white
+matter tracts were generated using a determinstic tractography algorithm
+that follows the prinicpal diffusion direction of the diffusion tensor
+in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
+using multiple criteria: streamlines are selected as candidates for
+inclusion in a bundle of streamlines that represents a tract if they
+pass through known inclusion ROIs and do not pass through exclusion
+ROIs \cite{wakana2007reproducibility}. In addition, a probabilistic
+atlas is used to exclude streamlines which are unlikely to be part of
+a tract \cite{Hua2008-sh}. Each streamline is resampled to 100 nodes
+and the robust mean at each location is calculated by estimating the 3D
+covariance of the location of each node and excluding streamlines that
+are more than 5 standard deviations from the mean location in any node.
+Finally, a bundle profile of tissue properties in each bundle was created
+by interpolating the value of MRI maps of these tissue properties to the
+location of the nodes of the resampled streamlines designated to each
+bundle. In each of 100 nodes, the values are summed across streamlines,
+weighting the contribution of each streamline by the inverse of the
+mahalnobis distance of the node from the average of that node across
+streamlines. This means that streamlines that are more representative of
+the tract contribute more to the bundle profile, relative to streamlines
+that are on the edge of the tract.
+
+Data from the HBN and Cam-CAN studies were processed using the updated Python
+Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{pyAFQ}). In
+addition to demonstrating the our analysis pipeline is robust to changes in
+tractometry software, the use of the updated \texttt{pyAFQ} capitalized upon
+the following improvements over the legacy Matlab version
+\begin{enumerate*}[%
+    label=(\roman*),%
+    before=\unskip{: },%
+    itemjoin={{, }},%
+    itemjoin*={{, and }}]
+    \item the ability to ingest data provided in the BIDS format
+    \cite{gorgolewski2016brain}
+    \item the calculation of diffusion kurtosis imaging (DKI
+    \cite{jensen2005diffusion}) metrics
+\end{enumerate*}
+We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
+as \texttt{AFQ}.
+
+These processes create bundle profiles, in which diffusion measures
+are quantified and averaged along eighteen major fiber tracts. Here,
+we use only the mean diffusivity (MD) and the fractional anisotropy
+(FA) of the diffusion tensor, but additional dMRI-based maps or maps
+based on other quantitative MRI measurements can also be used. These
+bundle profiles, along with the phenotypical data we wish to explain
+or predict, form the input to the SGL algorithm. In a domain-agnostic
+machine learning context, the phenotypical data comprise the target
+variables while the bundle profiles form the feature or predictor
+variables (See \cref{fig:methods:group-structure}).
+
+\subsection*{Sparse Group Lasso}
+\label{sec:sgl}
+
+Before fitting a model to the data, imputation and standardization are
+performed. Missing node values (e.g., in cases where \texttt{AFQ} designates
+a node as not-a-number) are imputed via linear interpolation. Care is taken
+not to interpolate across the boundaries between different bundles. Some
+diffusion metrics will have naturally larger variance than others and may
+therefore dominate the objective function and make the SGL estimator unable
+to learn from the lower variance metrics. For example, fractional anisotropy
+(FA) is bounded between zero and one and could be overwhelmed by an unscaled
+higher-variance metric like the mean diffusivity (MD). To prevent this we
+remove each feature's mean and scale it to unit variance (z-score) using the
+\lstinline{StandardScaler} from scikit-learn \cite{scikit-learn}. The scaling
+parameters are learned only from the training data and then applied equally
+to the training and test data in order to prevent leakage of information
+between the testing and training sets \cite{kaufman2012leakage}.
+
+After scaling and imputation, the tractometry data and target
+phenotypical data can be organized in a linear model:
+\begin{equation}
+    y = \mathbf{X} \beta + \epsilon,
+    \label{eq:lm}
+\end{equation}
+where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
+or continuous numerical, such as the subject's age. The tractometry
+data is represented in the feature matrix $\mathbf{X}$, with rows
+corresponding to different subjects, and columns corresponding
+to diffusion measures at different nodes within each bundle. The
+relationship between tractometric features and the phenotypic target is
+characterized by the coefficients in $\beta$. The error term, $\epsilon$
+is an unobserved random variable that captures the error in the model.
+We denote our prediction of the target phenotype as $\hat{y}$ and the
+coefficients that produce this prediction as $\hat{\beta}$, so that
+\begin{equation}
+    \hat{y} = \mathbf{X} \hat{\beta},
+    \label{eq:lm-approx}
+\end{equation}
+without the error term, $\epsilon$. In general, the feature matrix
+$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
+is the number of subjects, $B$ is the number of white matter bundles,
+$N$ is the number of nodes in each bundle, and $M$ is the number of
+diffusion metrics calculated at each node. Typically, $B = 18$, $N =
+100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 14,400$ features.
+Conversely, many dMRI studies have between a few dozen and a few
+hundred subjects, yielding a feature matrix that is wide and short.
+Even in cases where more than a thousand subjects are measured (e.g.,
+in the Human Connectome Project, where 1,200 subjects were measured
+\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
+of this data requires regularization to avoid overfitting and generate
+interpretable results.
+
+We propose that in addition to regularizing the coefficients in
+$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
+of the bundle profile features in $\mathbf{X}$. The bundle-metric
+combinations form a natural grouping. For example, we expect that MD features
+within the left arcuate fasciculus will co-vary across individuals. Likewise
+for FA values within the right corticospinal tract (CST) and so on. This
+group structure is represented in \cref{fig:methods:group-structure}, which
+depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
+regularization approach that will fit a linear model with
+anatomically-grouped covariates, where we expect to observe both groupwise
+sparsity, where the number of groups (bundle/metric combinations) with at
+least one non-zero coefficients is small, as well as within-group sparsity,
+where the number of non-zero coefficients within each non-zero group is
+small. The sparse group lasso (SGL) is a penalized regression technique that
+satisfies these criteria\cite{simon2013sparse}. It solves for a
+coefficient vector $\hat{\beta}$ that satisfies
+
+\begin{multline}
+    \hat{\beta} = \min_\beta L_{\text{mse}}
+    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
+    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
+    + \alpha \lambda \norm{\beta}_1,\\%
+    \text{where} \quad
+    L_{\text{mse}} = \frac{1}{2}
+    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
+    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2.
+    \label{eq:sgl}
+\end{multline}
+Here, $G$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
+$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
+coefficient vector for group $\ell$ and $p_\ell$ is the length of
+$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
+\ell: p_\ell = 100$. The first term is the mean square error loss,
+$L_{\text{mse}}$, as in the standard linear regression framework. The second
+and third terms encourage groupwise sparsity and overall sparsity,
+respectively. If $\alpha = 1$ the SGL reduces to the traditional
+lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
+reduces to the group lasso\cite{yuan2006model}. Thus, the model
+hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
+The hyperparameter $\lambda$ controls the strength of the regularization.
+
+\subsubsection*{Bagging meta-estimators}
+
+The previous section describes a single SGL model. To further improve model
+performance, we create ensemble models composed of $m = 20$ individual SGL
+models using bootstrap aggregation (bagging) \cite{breiman1996bagging}.
+Bagging relies on the underlying assumption that some of the error in a
+single SGL model's prediction stems from a mismatch in the distributions of
+training data used to fit the model and test data used to evaluate its
+performance. To overcome this, bagging invokes the same base estimator (e.g.
+SGL) many times with different training sets, which are created by sampling
+the original training samples with replacement. The bagging meta-estimator's
+prediction is then the average of its constituent estimators' predictions.
+Likewise, when we report the hyperparameter values $\alpha$ and $\lambda$, or
+regression coefficients $\hat{\beta}$, we are refering to these values
+averaged over 20 estimators in the bagging meta-estimator.
+
+\subsubsection*{Incorporating target transformations}
+
+Often, the target variable $y$ is not in the domain in which the linear
+model can be best fit to it. \Cref{eq:lm-approx} can be slightly
+modified as:
+\begin{equation}
+    \hat{y} = f^{-1} \left( \mathbf{X} \hat{\beta} \right),
+    \label{eq:lm-transform}
+\end{equation}
+where the transformation function $f^{-1}$ characterizes the transform
+applied to the data before fitting the linear coefficients. For example,
+for the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
+\begin{equation}
+    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
+    \label{eq:log-nonlinearity}
+\end{equation}
+
+\subsubsection*{Classification of categorical targets}
+
+When the phenotypical target variable is categorical, as in the case of
+explaining or predicting the presence of a clinical diagnosis, the SGL is
+readily adapted to logistic regression, where the probability of a target
+variable belonging to an arbitrary defined ``true'' class is the logistic
+function of the result of the linear model,
+\begin{equation}
+    p(\hat{y} = 1) = \frac{1}{1 + \exp(\mathbf{X} \hat{\beta})},
+    \label{eq:logit}
+\end{equation}
+or equivalently, the mean squared error loss function in \cref{eq:sgl} is
+replaced with the cross-entropy loss, which for binary classification is the
+negative log likelihood of the SGL classifier giving the ``true'' label:
+\begin{equation}
+    L_{\text{mse}} \rightarrow L_{\log} =
+    -\left(y \log(p) + (1 - y) \log(1 - p)\right).
+    \label{eq:logloss}
+\end{equation}
+
+\subsection*{SGL implementation, cross-validation and metaparameter optimization}
+
+Because the SGL is not specific to tractometry, we implemented its solution as
+a general-purpose Python package called \texttt{groupyr} \cite{groupyr}.
+\texttt{Groupyr} solves the cost function in \cref{eq:sgl} using proximal
+gradient descent \cite{parikh2014proximal} by implementing a custom proximal
+operator and relying on the C-OPT optimization library \cite{copt}, providing
+a fitted SGL model as a scikit-learn compatible estimator \cite{sklearn_api}.
+\texttt{Groupyr} also selects the hyperparameters $\alpha$ and $\lambda$ that
+yield the best cross-validated performance using either
+\begin{enumerate*}[%
+    label=(\roman*),%
+    before=\unskip{: },%
+    itemjoin={{, }},%
+    itemjoin*={{, or }}]
+    \item an exhaustive grid search of hyperparameter combinations
+    \item sequential model based optimization using the scikit-optimize
+    library \cite{scikit_optimize}.
+\end{enumerate*}
+
+\begin{figure}[t]
+    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
+    \caption{{\bf Nested cross-validation}
+        \label{fig:nested-cross-val}
+        We evaluate model quality using a nested $k$-fold cross validation
+        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+        groups and optimal hyperparameters are found for the level-0 training
+        set. To avoid overfitting, the optimal hyperparameters are themselves
+        evaluated using a cross-validation scheme taking place at level-1 of
+        the decomposition, where each level-0 training set is further
+        decomposed into $k_1 = 3$ shuffled groups. In the classification
+        case, the training and test splits are stratified by diagnosis. For
+        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+        $k_0 = 5$.
+    }
+\end{figure}
+
+To objectively evaluate model performance and guard against over-fitting,
+we used a nested cross-validation scheme, which is depicted for the binary
+classification case in \cref{fig:nested-cross-val}. The subjects (i.e. rows
+of the feature matrix $\mathbf{X}$ in \cref{fig:methods:group-structure}
+and \cref{eq:lm}) are first shuffled and then decomposed into $k_0$ batches,
+hereafter referred to as folds. For the ALS and WH datasets, we used $k_0 =
+10$ and for the HBN and Cam-CAN datasets, $k_0 = 5$. For each unique fold, we
+hold that fold out as the test\textsubscript{0} set and let the remaining
+data comprise the train\textsubscript{0} set, with the subscript indicating
+the depth of the nested decomposition. We further decompose each
+train\textsubscript{0} set into three folds, and again for each unique fold,
+we hold out that fold as the test\textsubscript{1} set and let the remaining
+data comprise the train\textsubscript{1} set. At level-1 of the
+decomposition, we fit an SGL model using fixed regularization meta-parameters
+$\alpha$ and $\lambda$, training the model using train\textsubscript{1} and
+evaluating the fit on test\textsubscript{1}. We find the optimal values for
+$\alpha$ and $\lambda$ using sequential model-based optimization, implemented
+using the scikit-optimize \verb|BayesSearchCV| class \cite{scikit_optimize}.
+For continuous numerical $y$, \verb|BayesSearchCV| searches for
+meta-parameter values that maximize the $R^2$ averaged over test sets. For
+binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
+classification accuracy. Using hyperoptimization, we find optimal
+regularization parameters and $\hat{\beta}$ for each train\textsubscript{0}
+set and then use those to predict values for data in test\textsubscript{0}.
+Thus each subject in the dataset has a predicted phenotype derived from a
+model that never saw its particular subject's data. In the classification
+case, the shuffling into folds is stratified such that each fold has a
+population that preserves the percentage of each class found in the larger
+input data.
+
+For each dataset, we also perform a randomization test by training similar
+models on copies of the data for which the rows of the target variable $y$
+have been shuffled while the feature matrix $\mathbf{X}$ remains the same.
+This effectively destroys any relationship between the diffusion data and the
+outcome. Indeed, all of our models perform no better than random guessing.
+One should expect this since any better performance might indicate data
+leakage between train and test sets \cite{kaufman2012leakage} or other common
+machine learning pitfalls.
+
+\subsection{Software implementation}
+
+The full software implementation of the SGL approach presented here is available
+in a Python software package called \texttt{AFQ-Insight}, which is developed
+publicly in \url{https://github.com/richford/afq-insight}.
+The version of the code used to produce the results herein is also available in
+\url{https://doi.org/10.5281/zenodo.4316000}.
+AFQ-Insight reads the target and feature data that has been processed by AFQ
+from comma separated value (CSV) files conforming to the AFQ-Browser data
+format \cite{yeatman2018browser} and represents them internally as
+\lstinline{DataFrame} objects from the pandas Python library
+\cite{mckinney2010data}. The software provides different options for imputing
+missing data in the feature matrix. Missing interior nodes are imputed using
+linear interpolation. For missing exterior nodes, the user may choose between
+linear extrapolation and constant forward- or back-fill. Imputation uses only
+values from adjacent nodes in the same white matter bundle in the same
+subject so there is no danger of data leakage from other subjects. It uses
+the scikit-learn \cite{scikit-learn} library to decompose input data into
+separate test and train datasets, to scale each feature to have zero mean and
+unit variance, and to evaluate each fit in the hyperparameter search using
+appropriate classification and regression metrics such as accuracy, area
+under the receiver operating curve (AUC ROC), and coefficient of
+determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the \texttt{groupyr} software library \cite{groupyr} mentioned above to solve the SGL.
+
+\section*{Supporting information}
+
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{S1 Appendix.}
+\label{S1_Appendix}
+{\bf Bundle and regression coefficient profiles.}
+In this supporting section, we present bundle profiles and $\hat{\beta}$ coefficients
+for each anatomical bundle and in each dataset.
+
+\section*{Acknowledgments}
 
@@
 
-\subsection*{Author contribution statement}
+\nolinenumbers
 
-All authors contributed extensively to the work presented in this paper.
-
-\bibliographystyle{naturemag}
 \bibliography{paper}
-
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
 \end{document}

### 2021-02-05 reports/manuscript/supplemental.tex
Change paper formatting to PLOS-CompBio

--- 2021-02-02 reports/manuscript/supplemental.tex
@@
-%% ****** Start of file apstemplate.tex ****** %
-%%
-%%   This file is part of the APS files in the REVTeX 4 distribution.
-%%   Version 4.1r of REVTeX, August 2010
-%%
-%%
-%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
-%%
-%%   See the REVTeX 4 README file for restrictions and more information.
-%%
-%
-% This is a template for producing manuscripts for use with REVTEX 4.0
-% Copy this file to another name and then work on that file.
-% That way, you always have this original template file to use.
-%
-% Group addresses by affiliation; use superscriptaddress for long
-% author lists, or if there are many overlapping affiliations.
-% For Phys. Rev. appearance, change preprint to twocolumn.
-% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
-%  Add 'draft' option to mark overfull boxes with black boxes
-%  Add 'showpacs' option to make PACS codes appear
-%  Add 'showkeys' option to make keywords appear
-\documentclass[10pt,%
-               aps,%
-               prl,%
-               reprint,%
-               superscriptaddress,%
-               preprintnumbers,%
-               amsmath,%
-               floatfix]{revtex4-2}
-\usepackage[T1]{fontenc}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
 \usepackage[utf8x]{inputenc}
-\usepackage[export]{adjustbox}  % Used to adjust figure frames
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+\usepackage[capitalize]{cleveref}
+\usepackage[inline]{enumitem}
+\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
+\usepackage{listings}
+\usepackage{todonotes}
 \usepackage{subcaption}
 \usepackage{url}
-\usepackage{color}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
 \usepackage{xcolor}
-\usepackage{listings}
-\usepackage{float}
-\usepackage{amsfonts}
-\usepackage{wrapfig}
-\usepackage{physics}
-\usepackage{mathtools}  % For shortintertext
-\usepackage[inline]{enumitem}
-\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
-\usepackage{todonotes}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+\usepackage{physics}  % for \norm
 \usepackage{graphicx}
 \graphicspath{ {../paper_figures} }
-\usepackage{bibentry}
 
-%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
-\usepackage{xr-hyper}
-\usepackage[pdftex,%
-            colorlinks=true,%
-            linkcolor=blue,%
-            citecolor=blue,%
-            urlcolor=blue,%
-            bookmarksnumbered=true,%
-            bookmarksopen=true]{hyperref}
-\usepackage[capitalize]{cleveref}
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
 \makeatletter
-\newcommand*{\addFileDependency}[1]{
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
+\renewcommand{\@biblabel}[1]{\quad#1.}
 \makeatother
 
-\newcommand*{\myexternaldocument}[2][ext:]{
-    \externaldocument[#1]{#2}
-    \addFileDependency{#2.tex}
-    \addFileDependency{#2.aux}
-}
-%%% END HELPER CODE
-
-% put all the external documents here!
-\myexternaldocument[main:]{paper}
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
 
 \begin{document}
+\vspace*{0.2in}
 
-\title{Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter}
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Adam Richie-Halford\textsuperscript{1*},
+Jason Yeatman\textsuperscript{2},
+Noah Simon\textsuperscript{3},
+Ariel Rokem\textsuperscript{4},
+\\
+\bigskip
+\textbf{1} eScience Institute, University of Washington, Seattle, WA, USA
+\\
+\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, CA, USA
+\\
+\textbf{3} Department of Biostatistics, University of Washington, Seattle, WA, USA
+\\
+\textbf{4} Department of Psychology, University of Washington, Seattle, WA, USA
+\\
+\bigskip
 
-\author{Adam \surname{Richie-Halford}}%
-\email{richford@uw.edu}%
-\affiliation{%
-    eScience Institute,%
-    University of Washington, Seattle,%
-    Washington 98195--1560, USA
-}
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* richford@uw.edu
 
-\author{Jason \surname{Yeatman}}%
-\affiliation{%
-    Graduate School of Education and Division of Developmental and Behavioral Pediatrics,%
-    Stanford University,%
-    Stanford, CA, 94305, USA
-}
-
-\author{Noah \surname{Simon}}%
-\affiliation{%
-    Department of Biostatistics,%
-    University of Washington, Seattle,%
-    Washington 98195--1560, USA
-}
-
-\author{Ariel \surname{Rokem}}%
-\affiliation{%
-    Department of Psychology,%
-    University of Washington, Seattle,%
-    Washington 98195--1560, USA
-}
-
-\date{\today}
-
-\maketitle
-
-\makeatletter
-\def\l@subsubsection#1#2{}
-\makeatother
-\tableofcontents
-
-%\newpage
-\section{Methods}
-\label{sec:methods}
-
-\subsection{Data}
-\label{sec:data}
-
-Four different datasets were used here:
-
-\begin{enumerate}
-
-\item Diffusion MRI from a previous study of the corticospinal
-tract (CST) in patients with amyotrophic lateral sclerosis
-(ALS \cite{sarica2017corticospinal}), containing data from 24 ALS
-patients and 24 demographically matched healthy controls. These data
-were measured in a GE Discovery 750 3T MRI scanner at the Institute
-of Bioimaging and Molecular Physiology in Catanzaro. Informed consent
-was provided as approved by the Ethical Committee of the University
-``Magna Graecia'' of Catanzaro. Voxel resolution was \num{2x2x2}
-$\text{mm}^3$ and 27 non-colinear directions were measured with a
-$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was preprocessed to
-correct for subject motion and for eddy currents. The diffusion tensor
-model \cite{basser1994mr} was fit in every voxel.
-We will refer to this dataset as ALS.
-
-\item Diffusion MRI data from a previous study of properties of
-the white matter across the lifespan \cite{yeatman2014lifespan},
-containing dMRI data from 76 subjects with ages 6-50. These data were
-measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
-for Cognitive and Neurobiological Imaging. The Stanford University
-IRB approved the procedures of this study. Informed consent was
-obtained from each adult participant, and assent for participation
-was provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
-$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
-measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. These data
-were acquired using a dual spin echo sequence, in which there is
-sufficient time for eddy currents to subside between the application of
-the gradients and the image acquisition, so no eddy current correction
-was applied, but motion correction was applied before fitting the
-diffusion tensor model \cite{basser1994mr} in every voxel using a robust
-fit \cite{chang2005restore}. We will refer to this dataset as WH.
-
-\item Diffusion MRI data from the Healthy Brain Network pediatric mental
-health study \cite{alexander2017open}, containing dMRI data from 978 subjects
-with ages 5-21. These data were measured in 3T Siemens MRI scanners at three
-sites in the New York area. Informed consent was obtained from each
-participant aged 18 or older. For participants younger than 18, written
-consent was obtained from their legal guardians and written assent was
-obtained from the participant. Voxel resolution was
-\num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions measured for
-each of $b=1000 \frac{\text{sec}}{\text{mm}^2}$ and $b=2000
-\frac{\text{sec}}{\text{mm}^2}$.
-Preprocessing was performed using \emph{QSIPrep} 0.12.1, which is based on
-\emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.
-
-\begin{itemize}
-
-\item {\it Anatomical data preprocessing}
-The T1-weighted (T1w) image was corrected for intensity non-uniformity
-(INU) using \texttt{N4BiasFieldCorrection} \cite[ANTs 2.3.1]{n4}, and
-used as T1w-reference throughout the workflow. The T1w-reference was
-then skull-stripped using \texttt{antsBrainExtraction.sh} (ANTs 2.3.1),
-using OASIS as target template. Spatial normalization to the ICBM 152
-Nonlinear Asymmetrical template version 2009c
-\cite[RRID:SCR\_008796]{mni} was performed through nonlinear
-registration with \texttt{antsRegistration} \cite[ANTs 2.3.1,
-RRID:SCR\_004757]{ants}, using brain-extracted versions of both T1w
-volume and template. Brain tissue segmentation of cerebrospinal fluid
-(CSF), white-matter (WM) and gray-matter (GM) was performed on the
-brain-extracted T1w using \texttt{FAST} \cite[FSL 6.0.3:b862cdd5,
-RRID:SCR\_002823]{fsl_fast}.
-
-\item {\it Diffusion data preprocessing}
-
-Any images with a b-value less than 100 s/mm\^{}2 were treated as a
-\emph{b}=0 image. MP-PCA denoising as implemented in MRtrix3's
-\texttt{dwidenoise}\cite{dwidenoise1} was applied with a 5-voxel
-window. After MP-PCA, B1 field inhomogeneity was corrected using
-\texttt{dwibiascorrect} from MRtrix3 with the N4 algorithm \cite{n4}.
-After B1 bias correction, the mean intensity of the DWI series was
-adjusted so all the mean intensity of the b=0 images matched across
-eachseparate DWI scanning sequence.
-\end{itemize}
-
-FSL (version 6.0.3:b862cdd5)'s eddy was used for head motion correction
-and Eddy current correction \cite{anderssoneddy}. Eddy was configured
-with a \(q\)-space smoothing factor of 10, a total of 5 iterations, and
-1000 voxels used to estimate hyperparameters. A linear first level model
-and a linear second level model were used to characterize Eddy
-current-related spatial distortion. \(q\)-space coordinates were
-forcefully assigned to shells. Field offset was attempted to be
-separated from subject movement. Shells were aligned post-eddy. Eddy's
-outlier replacement was run \cite{eddyrepol}. Data were grouped by
-slice, only including values from slices determined to contain at least
-250 intracerebral voxels. Groups deviating by more than 4 standard
-deviations from the prediction had their data replaced with imputed
-values. Data was collected with reversed phase-encode blips, resulting
-in pairs of images with distortions going in opposite directions. Here,
-b=0 reference images with reversed phase encoding directions were used
-along with an equal number of b=0 images extracted from the DWI scans.
-From these pairs the susceptibility-induced off-resonance field was
-estimated using a method similar to that described in \cite{topup}. The
-fieldmaps were ultimately incorporated into the Eddy current and head
-motion correction interpolation. Final interpolation was performed using
-the \texttt{jac} method.
-
-Several confounding time-series were calculated based on the
-\emph{preprocessed DWI}: framewise displacement (FD) using the implementation
-in \emph{Nipype} following the definitions by \cite{power_fd_dvars}. The DWI
-time-series were resampled to ACPC, generating a \emph{preprocessed DWI run
-in ACPC space}.
-
-Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
-\cite[RRID:SCR\_001362]{nilearn} and \emph{DIPY} \cite{dipy}. For more
-details of the pipeline, see
-\href{https://qsiprep.readthedocs.io/en/latest/workflows.html}{the
-section corresponding to workflows in \emph{QSIPrep}'s documentation}.
-We will refer to this dataset as HBN.
-
-\item Diffusion MRI data from the Cambridge Centre for Ageing and
-Neuroscience (Cam-CAN) ``CC700'' dataset
-\cite{shafto2014cambridge,taylor2017cambridge}, containing data from 640
-subjects with ages 18-88. These data were measured on a 3T Siemens TIM Trio
-system and written informed consent was obtained from each participant. Voxel
-resolution was \num{2x2x2}$\text{mm}^3$ with 30 non-colinear directions
-measured for each of $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$ and $b=2000$
-$\frac{\text{sec}}{\text{mm}^2}$. The diffusion weighted images were acquired
-with a twice refocused spin-echo sequence and the same preprocessing pipeline
-used for the HBN dataset was applied to this data. We will refer to this
-dataset as Cam-CAN.
-
-\end{enumerate}
-
-Data from the ALS and WH studies was processed in a similar manner,
-using the Matlab Automated Fiber Quantification toolbox (\texttt{mAFQ})
-\cite{yeatman2012tract}: streamlines representing fascicles of white
-matter tracts were generated using a determinstic tractography algorithm
-that follows the prinicpal diffusion direction of the diffusion tensor
-in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
-using multiple criteria: streamlines are selected as candidates for
-inclusion in a bundle of streamlines that represents a tract if they
-pass through known inclusion ROIs and do not pass through exclusion
-ROIs \cite{wakana2007reproducibility}. In addition, a probabilistic
-atlas is used to exclude streamlines which are unlikely to be part of
-a tract \cite{Hua2008-sh}. Each streamline is resampled to 100 nodes
-and the robust mean at each location is calculated by estimating the 3D
-covariance of the location of each node and excluding streamlines that
-are more than 5 standard deviations from the mean location in any node.
-Finally, a bundle profile of tissue properties in each bundle was created
-by interpolating the value of MRI maps of these tissue properties to the
-location of the nodes of the resampled streamlines designated to each
-bundle. In each of 100 nodes, the values are summed across streamlines,
-weighting the contribution of each streamline by the inverse of the
-mahalnobis distance of the node from the average of that node across
-streamlines. This means that streamlines that are more representative of
-the tract contribute more to the bundle profile, relative to streamlines
-that are on the edge of the tract.
-
-Data from the HBN and Cam-CAN studies were processed using the updated Python
-Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{pyAFQ}). In
-addition to demonstrating the our analysis pipeline is robust to changes in
-tractometry software, the use of the updated \texttt{pyAFQ} capitalized upon
-the following improvements over the legacy Matlab version
-\begin{enumerate*}[%
-    label=(\roman*),%
-    before=\unskip{: },%
-    itemjoin={{, }},%
-    itemjoin*={{, and }}]
-    \item the ability to ingest data provided in the BIDS format
-    \cite{gorgolewski2016brain}
-    \item the calculation of diffusion kurtosis imaging (DKI
-    \cite{jensen2005diffusion}) metrics
-\end{enumerate*}
-We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
-as \texttt{AFQ}.
-
-These processes create bundle profiles, in which diffusion measures
-are quantified and averaged along eighteen major fiber tracts. Here,
-we use only the mean diffusivity (MD) and the fractional anisotropy
-(FA) of the diffusion tensor, but additional dMRI-based maps or maps
-based on other quantitative MRI measurements can also be used. These
-bundle profiles, along with the phenotypical data we wish to explain
-or predict, form the input to the SGL algorithm. In a domain-agnostic
-machine learning context, the phenotypical data comprise the target
-variables while the bundle profiles form the feature or predictor
-variables (See \cref{main:fig:methods:group-structure} in the main text).
-
-\subsection{Sparse Group Lasso}
-\label{sec:sgl}
-
-\begin{figure}[t]
-    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
-    \caption{{\bf Nested cross-validation}
-        \label{fig:nested-cross-val}
-        We evaluate model quality using a nested $k$-fold cross validation
-        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
-        groups and optimal hyperparameters are found for the level-0 training
-        set. To avoid overfitting, the optimal hyperparameters are themselves
-        evaluated using a cross-validation scheme taking place at level-1 of
-        the decomposition, where each level-0 training set is further
-        decomposed into $k_1 = 3$ shuffled groups. In the classification
-        case, the training and test splits are stratified by diagnosis. For
-        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
-        $k_0 = 5$.
-    }
-\end{figure}
-
-Before fitting a model to the data, imputation and standardization are
-performed. Missing node values (e.g., in cases where \texttt{AFQ} designates
-a node as not-a-number) are imputed via linear interpolation. Care is taken
-not to interpolate across the boundaries between different bundles. Some
-diffusion metrics will have naturally larger variance than others and may
-therefore dominate the objective function and make the SGL estimator unable
-to learn from the lower variance metrics. For example, fractional anisotropy
-(FA) is bounded between zero and one and could be overwhelmed by an unscaled
-higher-variance metric like the mean diffusivity (MD). To prevent this we
-remove each feature's mean and scale it to unit variance (z-score) using the
-\lstinline{StandardScaler} from scikit-learn \cite{scikit-learn}. The scaling
-parameters are learned only from the training data and then applied equally
-to the training and test data in order to prevent leakage of information
-between the testing and training sets \cite{kaufman2012leakage}.
-
-After scaling and imputation, the tractometry data and target
-phenotypical data can be organized in a linear model:
-\begin{equation}
-    y = \mathbf{X} \beta + \epsilon,
-    \label{eq:lm}
-\end{equation}
-where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
-or continuous numerical, such as the subject's age. The tractometry
-data is represented in the feature matrix $\mathbf{X}$, with rows
-corresponding to different subjects, and columns corresponding
-to diffusion measures at different nodes within each bundle. The
-relationship between tractometric features and the phenotypic target is
-characterized by the coefficients in $\beta$. The error term, $\epsilon$
-is an unobserved random variable that captures the error in the model.
-We denote our prediction of the target phenotype as $\hat{y}$ and the
-coefficients that produce this prediction as $\hat{\beta}$, so that
-\begin{equation}
-    \hat{y} = \mathbf{X} \hat{\beta},
-    \label{eq:lm-approx}
-\end{equation}
-without the error term, $\epsilon$. In general, the feature matrix
-$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
-is the number of subjects, $B$ is the number of white matter bundles,
-$N$ is the number of nodes in each bundle, and $M$ is the number of
-diffusion metrics calculated at each node. Typically, $B = 18$, $N =
-100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 14,400$ features.
-Conversely, many dMRI studies have between a few dozen and a few
-hundred subjects, yielding a feature matrix that is wide and short.
-Even in cases where more than a thousand subjects are measured (e.g.,
-in the Human Connectome Project, where 1,200 subjects were measured
-\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
-of this data requires regularization to avoid overfitting and generate
-interpretable results.
-
-Here, we propose that in addition to regularizing the coefficients in
-$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
-of the bundle profile features in $\mathbf{X}$. The bundle-metric
-combinations form a natural grouping. For example, we expect that MD features
-within the left arcuate fasciculus will co-vary across individuals. Likewise
-for FA values within the right corticospinal tract (CST) and so on. This
-group structure is represented in \cref{main:fig:methods:group-structure}, which
-depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
-regularization approach that will fit a linear model with
-anatomically-grouped covariates, where we expect to observe both groupwise
-sparsity, where the number of groups (bundle/metric combinations) with at
-least one non-zero coefficients is small, as well as within-group sparsity,
-where the number of non-zero coefficients within each non-zero group is
-small. The sparse group lasso (SGL) is a penalized regression technique that
-satisfies these criteria\cite{simon2013sparse}. It solves for a
-coefficient vector $\hat{\beta}$ that satisfies
-\begin{multline}
-    \hat{\beta} = \min_\beta L_{\text{mse}}
-    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
-    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
-    + \alpha \lambda \norm{\beta}_1,\\%
-    \text{where} \quad
-    L_{\text{mse}} = \frac{1}{2}
-    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
-    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2.
-    \label{eq:sgl}
-\end{multline}
-Here, $G$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
-$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
-coefficient vector for group $\ell$ and $p_\ell$ is the length of
-$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
-\ell: p_\ell = 100$. The first term is the mean square error loss,
-$L_{\text{mse}}$, as in the standard linear regression framework. The second
-and third terms encourage groupwise sparsity and overall sparsity,
-respectively. If $\alpha = 1$ the SGL reduces to the traditional
-lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
-reduces to the group lasso\cite{yuan2006model}. Thus, the model
-hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
-The hyperparameter $\lambda$ controls the strength of the regularization.
-
-\subsubsection{Bagging meta-estimators}
-
-The previous section describes a single SGL model. To further improve model
-performance, we create ensemble models composed of $m = 20$ individual SGL
-models using bootstrap aggregation (bagging) \cite{breiman1996bagging}.
-Bagging relies on the underlying assumption that some of the error in a
-single SGL model's prediction stems from a mismatch in the distributions of
-training data used to fit the model and test data used to evaluate its
-performance. To overcome this, bagging invokes the same base estimator (e.g.
-SGL) many times with different training sets, which are created by sampling
-the original training samples with replacement. The bagging meta-estimator's
-prediction is then the average of its constituent estimators' predictions.
-Likewise, when we report the hyperparameter values $\alpha$ and $\lambda$, or
-regression coefficients $\hat{\beta}$, we are refering to these values
-averaged over 20 estimators in the bagging meta-estimator.
-
-\subsubsection{Incorporating target transformations}
-
-Often, the target variable $y$ is not in the domain in which the linear
-model can be best fit to it. \Cref{eq:lm-approx} can be slightly
-modified as:
-\begin{equation}
-    \hat{y} = f^{-1} \left( \mathbf{X} \hat{\beta} \right),
-    \label{eq:lm-transform}
-\end{equation}
-where the transformation function $f^{-1}$ characterizes the transform
-applied to the data before fitting the linear coefficients. For example,
-for the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
-\begin{equation}
-    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
-    \label{eq:log-nonlinearity}
-\end{equation}
-
-\subsubsection{Classification of categorical targets}
-When the phenotypical target variable is categorical, as in the case of
-explaining or predicting the presence of a clinical diagnosis, the SGL is
-readily adapted to logistic regression, where the probability of a target
-variable belonging to an arbitrary defined ``true'' class is the logistic
-function of the result of the linear model,
-\begin{equation}
-    p(\hat{y} = 1) = \frac{1}{1 + \exp(\mathbf{X} \hat{\beta})},
-    \label{eq:logit}
-\end{equation}
-or equivalently, the mean squared error loss function in \cref{eq:sgl} is
-replaced with the cross-entropy loss, which for binary classification is the
-negative log likelihood of the SGL classifier giving the ``true'' label:
-\begin{equation}
-    L_{\text{mse}} \rightarrow L_{\log} =
-    -\left(y \log(p) + (1 - y) \log(1 - p)\right).
-    \label{eq:logloss}
-\end{equation}
-
-\subsection{SGL implementation, cross-validation and metaparameter optimization}
-
-Because the SGL is not specific to tractometry, we implemented its solution as
-a general-purpose Python package called \texttt{groupyr} \cite{groupyr}.
-\texttt{Groupyr} solves the cost function in \cref{eq:sgl} using proximal
-gradient descent \cite{parikh2014proximal} by implementing a custom proximal
-operator and relying on the C-OPT optimization library \cite{copt}, providing
-a fitted SGL model as a scikit-learn compatible estimator \cite{sklearn_api}.
-\texttt{Groupyr} also selects the hyperparameters $\alpha$ and $\lambda$ that
-yield the best cross-validated performance using either
-\begin{enumerate*}[%
-    label=(\roman*),%
-    before=\unskip{: },%
-    itemjoin={{, }},%
-    itemjoin*={{, or }}]
-    \item an exhaustive grid search of hyperparameter combinations
-    \item sequential model based optimization using the scikit-optimize
-    library \cite{scikit_optimize}.
-\end{enumerate*}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{sarica_coefs_profiles_fa.pdf}
-    \caption{%
-        {%
-            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for ALS classification.
-        }
-        \label{fig:als-bp:fa}
-    }
-\end{figure*}
-
-To objectively evaluate model performance and guard against over-fitting,
-we used a nested cross-validation scheme, which is depicted for the binary
-classification case in \cref{fig:nested-cross-val}. The subjects (i.e. rows
-of the feature matrix $\mathbf{X}$ in \cref{main:fig:methods:group-structure}
-and \cref{eq:lm}) are first shuffled and then decomposed into $k_0$ batches,
-hereafter referred to as folds. For the ALS and WH datasets, we used $k_0 =
-10$ and for the HBN and Cam-CAN datasets, $k_0 = 5$. For each unique fold, we
-hold that fold out as the test\textsubscript{0} set and let the remaining
-data comprise the train\textsubscript{0} set, with the subscript indicating
-the depth of the nested decomposition. We further decompose each
-train\textsubscript{0} set into three folds, and again for each unique fold,
-we hold out that fold as the test\textsubscript{1} set and let the remaining
-data comprise the train\textsubscript{1} set. At level-1 of the
-decomposition, we fit an SGL model using fixed regularization meta-parameters
-$\alpha$ and $\lambda$, training the model using train\textsubscript{1} and
-evaluating the fit on test\textsubscript{1}. We find the optimal values for
-$\alpha$ and $\lambda$ using sequential model-based optimization, implemented
-using the scikit-optimize \verb|BayesSearchCV| class \cite{scikit_optimize}.
-For continuous numerical $y$, \verb|BayesSearchCV| searches for
-meta-parameter values that maximize the $R^2$ averaged over test sets. For
-binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
-classification accuracy. Using hyperoptimization, we find optimal
-regularization parameters and $\hat{\beta}$ for each train\textsubscript{0}
-set and then use those to predict values for data in test\textsubscript{0}.
-Thus each subject in the dataset has a predicted phenotype derived from a
-model that never saw its particular subject's data. In the classification
-case, the shuffling into folds is stratified such that each fold has a
-population that preserves the percentage of each class found in the larger
-input data.
-
-For each dataset, we also perform a randomization test by training similar
-models on copies of the data for which the rows of the target variable $y$
-have been shuffled while the feature matrix $\mathbf{X}$ remains the same.
-This effectively destroys any relationship between the diffusion data and the
-outcome. Indeed, all of our models perform no better than random guessing.
-One should expect this since any better performance might indicate data
-leakage between train and test sets \cite{kaufman2012leakage} or other common
-machine learning pitfalls.
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{sarica_coefs_profiles_md.pdf}
-    \caption{%
-        {%
-            \bf Mean diffusivity (MD) Bundle profiles and $\hat{\beta}$
-            coefficients for ALS classification.
-        }
-        \label{fig:als-bp:md}
-    }
-\end{figure*}
-
-\subsection{Software implementation}
-
-The full software implementation of the SGL approach presented here is available
-in a Python software package called \texttt{AFQ-Insight}, which is developed
-publicly in \url{https://github.com/richford/afq-insight}.
-The version of the code used to produce the results herein is also available in
-\url{https://doi.org/10.5281/zenodo.4316000}.
-AFQ-Insight reads the target and feature data that has been processed by AFQ
-from comma separated value (CSV) files conforming to the AFQ-Browser data
-format \cite{yeatman2018browser} and represents them internally as
-\lstinline{DataFrame} objects from the pandas Python library
-\cite{mckinney2010data}. The software provides different options for imputing
-missing data in the feature matrix. Missing interior nodes are imputed using
-linear interpolation. For missing exterior nodes, the user may choose between
-linear extrapolation and constant forward- or back-fill. Imputation uses only
-values from adjacent nodes in the same white matter bundle in the same
-subject so there is no danger of data leakage from other subjects. It uses
-the scikit-learn \cite{scikit-learn} library to decompose input data into
-separate test and train datasets, to scale each feature to have zero mean and
-unit variance, and to evaluate each fit in the hyperparameter search using
-appropriate classification and regression metrics such as accuracy, area
-under the receiver operating curve (AUC ROC), and coefficient of
-determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the \texttt{groupyr} software library \cite{groupyr} mentioned above to solve the SGL.
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{wh_coefs_profiles_fa.pdf}
-    \caption{%
-        {%
-            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the WH dataset.
-        }
-        \label{fig:wh-bp:fa}
-    }
-\end{figure*}
+\end{flushleft}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{wh_coefs_profiles_md.pdf}
-    \caption{%
-        {%
-            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the WH dataset.
-        }
-        \label{fig:wh-bp:md}
-    }
-\end{figure*}
-
 \subsection{ALS bundle profiles}
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{hbn_coefs_profiles_fa.pdf}
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{sarica_coefs_profiles_fa.pdf}
     \caption{%
@@
             \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the HBN dataset.
+            coefficients for ALS classification.
         }
-        \label{fig:hbn-bp:fa}
+        \label{fig:als-bp:fa}
     }
-\end{figure*}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{sarica_coefs_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Mean diffusivity (MD) Bundle profiles and $\hat{\beta}$
+            coefficients for ALS classification.
+        }
+        \label{fig:als-bp:md}
+    }
+\end{figure}
 
@@
 the IFOL and IFOR bundles in \cref{fig:wh-bp:md}.
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{wh_coefs_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the WH dataset.
+        }
+        \label{fig:wh-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{wh_coefs_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the WH dataset.
+        }
+        \label{fig:wh-bp:md}
+    }
+\end{figure}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{hbn_coefs_profiles_md.pdf}
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_coefs_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the HBN dataset.
+        }
+        \label{fig:hbn-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_coefs_profiles_md.pdf}
     \caption{%
@@
     }
-\end{figure*}
+\end{figure}
 
 \subsection{Cam-CAN bundle profiles}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{cc_coefs_profiles_fa.pdf}
-    \caption{%
-        {%
-            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
-            coefficients for age regression in the Cam-CAN dataset.
-        }
-        \label{fig:cc-bp:fa}
-    }
-\end{figure*}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{cc_coefs_profiles_md.pdf}
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{cc_coefs_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles and $\hat{\beta}$
+            coefficients for age regression in the Cam-CAN dataset.
+        }
+        \label{fig:cc-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{cc_coefs_profiles_md.pdf}
     \caption{%
@@
     }
-\end{figure*}
+\end{figure}
 
-\bibliographystyle{naturemag}
 \bibliography{paper}

### 2021-02-05 reports/manuscript/paper.tex
Add author's summary

@@
 \section*{Author summary}
-\todo[inline]{Write author summary}
+Innovations in medical imaging are helping researchers understand the human
+brain, and in particular the neural connections that comprise the white
+matter. Mapping these connections and understanding which parts are relevant
+to disease and behavior holds great promise in understanding how the brain
+functions, diagnosing diseases, and creating more effective treatments. To
+that end, there are now many large scale neuroimaging studies with thousands
+or even tens of thousands of participants. As such, neuroimaging is on the
+cusp of a transition to big data. Yet the field's conventional statistical
+methods are better suited to the small-scale studies of the past. We need
+machine learning methods that can accurately predict disease status and
+behavior, while also providing insight into which parts of the white matter
+are important for that prediction. We have therefore developed a statistical
+method that automatically identifies important features of the white matter
+for any given disease or behavior. Our approach relies on including our
+knowledge of the anatomical grouping of the white matter fiber bundles in the
+statistical model itself. We tested our method on four different datasets and
+found that it competes with state-of-the-art methods and preserves
+interpretability, all without the need for extensive feature engineering.
 
@@
 \begin{figure}[t]
-    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
+    \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
     \caption{{\bf Nested cross-validation}

### 2021-02-06 reports/manuscript/paper.tex
Remove subsection numbering for Software implementation
Proposed changes to the author summary.

--- 2021-02-05 reports/manuscript/paper.tex
@@
 \section*{Author summary}
-\todo[inline]{Write author summary}
-
+The connections between different parts of the brain form networks that are
+important for information transmission and for brain health. These connections
+are composed of nerve fibers that travel through the white matter portion of the
+brain. Thus, mapping tissue properties in white matter pathways can help us
+understand which connections and what tissue properties are relevant to brain
+diseases, or explain differences in behavior and cognition between different
+individuals. We developed a new statistical method that helps map the white
+matter by automatically identifying the features of the white matter that
+correspond to individual differences. Our approach relies on incorporating our
+knowledge of the anatomical sub-divisions of the white matter into the
+statistical model itself. We demonstrate that the model accurately captures
+differences between individual's with amyotrophic lateral sclerosis (ALS) and
+healthy controls. It also accurately captures brain changes that correspond with
+the ages of different individuals. We tested our method on four different
+datasets and found that it is more accurate than previous methods used with
+these datasets, while also allowing us to highlight which white matter tissue
+properties and which connections account for individual differences, thus
+providing interpretable results.
 \linenumbers

### 2021-02-06 reports/manuscript/cover_letter/cover_letter.tex

@@
-\documentclass{letter}
-\usepackage[margin=1in]{geometry}
+\documentclass[11pt,letterpaper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
 
-\signature{Adam Richie-Halford, PhD \\ \vspace{4em} Ariel Rokem, PhD}
-\address{The eScience Institute \\ University of Washington \\ Seattle, WA}
+\usepackage{graphicx} % Required for including pictures
+\usepackage{microtype} % Improves typography
+%\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
+
+\usepackage[T1]{fontenc} % Required for accented characters
+\usepackage{url}
+\usepackage{fontspec}
+
+\setmainfont{Latin Modern Sans}
+
+% Create a new command for the horizontal rule in the document which allows thickness specification
+\makeatletter
+\def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
+\makeatother
+
+%----------------------------------------------------------------------------------------
+%	DOCUMENT MARGINS
+%----------------------------------------------------------------------------------------
+
+\textwidth 7in
+\textheight 10.0in
+\oddsidemargin -.25in
+\evensidemargin -.25in
+\topmargin -1.in
+\longindentation 0.50\textwidth
+\parindent 0in
+
+%----------------------------------------------------------------------------------------
+%	SENDER INFORMATION
+%----------------------------------------------------------------------------------------
+
+\def\Who{Ariel Rokem} % Your name
+\def\What{, PhD} % Your title
+\def\Where{Department of Psychology} % Your department/institution
+\def\Address{Guthrie Hall 119  A} % Your address
+\def\CityZip{Seattle, WA 98105} % Your city, zip code, country, etc
+\def\Email{E-mail: arokem@uw.edu} % Your email address
+\def\TEL{Phone: +1 (510) 387-6264} % Your phone number
+\def\URL{http://arokem.org} % Your URL
+
+%----------------------------------------------------------------------------------------
+%	HEADER AND FROM ADDRESS STRUCTURE
+%----------------------------------------------------------------------------------------
+
+\address{
+\begin{flushleft}
+\includegraphics[width=1in]{UWLogo.png} % Include the logo of your institution
+\end{flushleft}
+\hspace{5in} % Position of the institution logo, increase to move left, decrease to move right
+\vskip -1.7in~\\ % Position of the text in relation to the institution logo, increase to move down, decrease to move up
+\Large\hspace{1.5in} \hfill ~\\[0.05in] % First line of institution name, adjust hspace if your logo is wide
+\hspace{1.5in} \hfill \normalsize % Second line of institution name, adjust hspace if your logo is wide
+%\makebox[0ex][r]{\bf \Who \What }\hspace{0.08in} % Print your name and title with a little whitespace to the right
+~\\[-0.11in] % Reduce the whitespace above the horizontal rule
+\hspace{1.5in}%\vhrulefill{1pt} \\ % Horizontal rule, adjust hspace if your logo is wide and \vhrulefill for the thickness of the rule
+\hspace{\fill}\parbox[t]{2.95in}{ % Create a box for your details underneath the horizontal rule on the right
+\footnotesize % Use a smaller font size for the details
+\Who \What \\ \em % Your name, all text after this will be italicized
+\Where\\ % Your department
+\Address\\ % Your address
+\CityZip\\ % Your city and zip code
+\TEL\\ % Your phone number
+\Email\\ % Your email address
+\URL % Your URL
+}
+\hspace{-1.4in} % Horizontal position of this block, increase to move left, decrease to move right
+\vspace{-1in} % Move the letter content up for a more compact look
+}
+
+%----------------------------------------------------------------------------------------
+%	TO ADDRESS STRUCTURE
+%----------------------------------------------------------------------------------------
+
+\def\opening#1{\thispagestyle{empty}
+{\centering\fromaddress \vspace{1.2in} \\ % Print the header and from address here, add whitespace to move date down
+\hspace*{\longindentation}\today\par} % Print today's date, remove \today to not display it
+{\raggedright \toname \\ \toaddress \par} % Print the to name and address
+\vspace{0.2in} % White space after the to address
+\noindent #1 % Print the opening line
+% Uncomment the 4 lines below to print a footnote with custom text
+%\def\thefootnote{}
+%\def\footnoterule{\hrule}
+%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
+%\def\thefootnote{\arabic{footnote}}
+}
+
+%----------------------------------------------------------------------------------------
+%	SIGNATURE STRUCTURE
+%----------------------------------------------------------------------------------------
+
+\signature{\Who \What} % The signature is a combination of your name and title
+
+\long\def\closing#1{
+\vspace{0.1in} % Some whitespace after the letter content and before the signature
+\noindent % Stop paragraph indentation
+\hspace*{\longindentation} % Move the signature right
+\parbox{\indentedwidth}{\raggedright
+#1 % Print the signature text
+\vskip 0.65in % Whitespace between the signature text and your name
+\fromsig}} % Print your name and title
+
+%----------------------------------------------------------------------------------------
+
 \begin{document}
@@
 grouping of the measurement to the different anatomical connections between
-brain regions. We demonstrate the accuracy of this approach in four different
+brain regions. We demonstrate the value of this approach in four different
 datasets. Our results show that the model is highly accurate (exceeding the
@@
 high-quality open-source software implementing our approach that can easily
-be used in the analysis of other datasets.
+be used in the analysis of other datasets (available at \url{https://github.com/richford/AFQ-Insight}).
 
@@
 
-Importantly, the software and analysis methods that we provide generalize
-well beyond neuroscience into other fields where group-sparse linear models
-can be applied, including other fields of biology, but also other physical
-and even social sciences. Therefore, we believe that this manuscript will be
-of interest to a broad range of researchers.
+Importantly, while the focus of our paper is analysis of human brain white
+matter, and this will translate immediately to work by other neuroscientists,
+the software and analysis methods that we provide generalize well beyond
+neuroscience into other fields where group-sparse linear models can be applied,
+including other fields of biology, such as genetics and ecology. Therefore, we
+believe that this manuscript will be of interest to a broad range of
+researchers.
 
@@
 
-\closing{Sincerely,}
+\hspace{1cm} Sincerely,\\
 
-\encl{Manuscript}
-\encl{Supplemental materials}
+\begin{minipage}{0.8\linewidth}
+\hspace{1cm}\begin{tabular}{ll}
+Ariel Rokem, PhD & \hspace{1cm} Adam Richie-Halford, PhD\\
+Research Assistant Professor & \hspace{1cm}  Postdoctoral researcher \\
+Department of Psychology & \hspace{1cm} eScience Institute \\
+University of Washington & \hspace{1cm} University of Washington
+ \end{tabular}
+\end{minipage}
 

### 2021-02-06 reports/manuscript/cover_letter/cover_letter.tex
Change researcher to Fellow in cover letter

@@
 Ariel Rokem, PhD & \hspace{1cm} Adam Richie-Halford, PhD\\
-Research Assistant Professor & \hspace{1cm}  Postdoctoral researcher \\
+Research Assistant Professor & \hspace{1cm}  Postdoctoral Fellow \\
 Department of Psychology & \hspace{1cm} eScience Institute \\

### 2021-04-07 reports/manuscript/paper.tex
Add model comparisons to elastic net, PCR lasso, and bundle mean lasso

@@
 To assess the added value of incorporating anatomical knowledge into our
-model, we compared our classification results to those obtained from a lasso
-model. The pure lasso model achieved 76\% accuracy and an ROC AUC of 0.76
-using the same cross-validation strategy used to assess the SGL model. This
-difference in performance justifies the additional complexity of the SGL over
-simpler sparsity-inducing regression strategies.
+model, we compared our classification results to those obtained from four
+other models: a pure lasso model, an elastic net model, a bundle-mean lasso
+(i.e. a lasso model trained only on the mean metric values from each bundle),
+and a principal components regression lasso (Lasso PCR) model
+\cite{powell2018local, rasero2021integrating}. These models achieved
+accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and an ROC AUC of
+0.76, 0.75, 0.82, and 0.71, respectively using the same cross-validation
+strategy used to assess the SGL model. This difference in performance
+justifies the additional complexity of the SGL over simpler sparsity-inducing
+regression strategies.
 
@@
 As with ALS classification, we also compared SGL performance with results
-obtained using only the lasso penalty. The pure lasso models achieved $R^2 =
-0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
-using the same cross-validation strategy used to assess the SGL. The SGL
-models' performance improvement over lasso is more modest than in the ALS
-classification case, which accords with the selected values of the $\alpha$
-hyperparameter. These SGL models were more lasso-like in their sparsity
-penalties so they are more lasso-like in their predictive performance.
+obtained using the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR.
+The pure lasso models achieved $R^2 = 0.47$, $0.54$, and $0.70$ for the WH,
+HBN, and Cam-CAN datasets respectively using the same cross-validation
+strategy used to assess the SGL. The elastic net models achieved $R^2 =
+0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets,
+respectively. The bundle-mean lasso models achieved $R^2 = 0.33$, $0.22$, and
+$0.55$, respectively. And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$,
+$0.74$, respectively. The SGL models' performance improvement over lasso is
+more modest than in the ALS classification case, which accords with the
+selected values of the $\alpha$ hyperparameter. These SGL models were more
+lasso-like in their sparsity penalties so they are more lasso-like in their
+predictive performance.
 
@@
 
-\subsection{Software implementation}
+\subsection*{Software implementation}
 

### 2021-04-09 reports/manuscript/paper.tex
Use changes package to markup changes

--- 2021-02-06 reports/manuscript/paper.tex
@@
 \usepackage{url}
+
+\usepackage{changes}
+% \definechangesauthor{name={Adam Richie-Halford}, color=red}{ARH}
 
@@
 To assess the added value of incorporating anatomical knowledge into our
-model, we compared our classification results to those obtained from a lasso
-model. The pure lasso model achieved 76\% accuracy and an ROC AUC of 0.76
-using the same cross-validation strategy used to assess the SGL model. This
-difference in performance justifies the additional complexity of the SGL over
-simpler sparsity-inducing regression strategies.
+model, we compared our classification results to those obtained from
+\replaced[id={ARH}]{four other models: a pure lasso model, an elastic net model, a
+bundle-mean lasso (i.e. a lasso model trained only on the mean metric values
+from each bundle), and a principal components regression lasso (Lasso PCR)
+model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
+\replaced[id={ARH}]{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\%
+respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71,
+respectively}{The pure lasso model achieved 76\% accuracy and an ROC AUC of
+0.76} using the same cross-validation strategy used to assess the SGL model.
+This difference in performance justifies the additional complexity of the SGL
+over simpler sparsity-inducing regression strategies.
 
@@
 As with ALS classification, we also compared SGL performance with results
-obtained using only the lasso penalty. The pure lasso models achieved $R^2 =
+obtained using \replaced[id={ARH}]{the pure lasso, elastic net, bundle-mean lasso, and
+Lasso PCR}{only the lasso penalty}. The pure lasso models achieved $R^2 =
 0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
-using the same cross-validation strategy used to assess the SGL. The SGL
-models' performance improvement over lasso is more modest than in the ALS
+using the same cross-validation strategy used to assess the SGL. \added[id={ARH}]{The
+elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN,
+and Cam-CAN datasets, respectively. The bundle-mean lasso models achieved
+$R^2 = 0.33$, $0.22$, and $0.55$, respectively. And the Lasso PCR models
+achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.} The SGL models'
+performance improvement over lasso is more modest than in the ALS
 classification case, which accords with the selected values of the $\alpha$

### 2021-04-09 reports/manuscript/paper.tex
Remove author id from change markup. Add pyMergeChanges.py

@@
 \usepackage{changes}
-% \definechangesauthor{name={Adam Richie-Halford}, color=red}{ARH}
 
@@
 model, we compared our classification results to those obtained from
-\replaced[id={ARH}]{four other models: a pure lasso model, an elastic net model, a
+\replaced{four other models: a pure lasso model, an elastic net model, a
 bundle-mean lasso (i.e. a lasso model trained only on the mean metric values
@@
 model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
-\replaced[id={ARH}]{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\%
+\replaced{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\%
 respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71,
@@
 As with ALS classification, we also compared SGL performance with results
-obtained using \replaced[id={ARH}]{the pure lasso, elastic net, bundle-mean lasso, and
+obtained using \replaced{the pure lasso, elastic net, bundle-mean lasso, and
 Lasso PCR}{only the lasso penalty}. The pure lasso models achieved $R^2 =
 0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
-using the same cross-validation strategy used to assess the SGL. \added[id={ARH}]{The
+using the same cross-validation strategy used to assess the SGL. \added{The
 elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN,

### 2021-04-09 reports/manuscript/paper_changes.tex
Use pyMergeChanges.py in Makefile

--- 2021-04-09 reports/manuscript/paper.tex
@@
 model, we compared our classification results to those obtained from
-\replaced{four other models: a pure lasso model, an elastic net model, a
-bundle-mean lasso (i.e. a lasso model trained only on the mean metric values
-from each bundle), and a principal components regression lasso (Lasso PCR)
-model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
-\replaced{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\%
-respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71,
-respectively}{The pure lasso model achieved 76\% accuracy and an ROC AUC of
-0.76} using the same cross-validation strategy used to assess the SGL model.
+\replaced{four other models: a pure lasso model, an elastic net model, a bundle-mean lasso (i.e.
+a lasso model trained only on the mean metric values from each bundle), and a principal components regression lasso (Lasso PCR) model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
+\replaced{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71, respectively}{The pure lasso model achieved 76\% accuracy and an ROC AUC of 0.76}
+using the same cross-validation strategy used to assess the SGL model.
 This difference in performance justifies the additional complexity of the SGL
@@
 As with ALS classification, we also compared SGL performance with results
-obtained using \replaced{the pure lasso, elastic net, bundle-mean lasso, and
-Lasso PCR}{only the lasso penalty}. The pure lasso models achieved $R^2 =
-0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
-using the same cross-validation strategy used to assess the SGL. \added{The
-elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN,
-and Cam-CAN datasets, respectively. The bundle-mean lasso models achieved
-$R^2 = 0.33$, $0.22$, and $0.55$, respectively. And the Lasso PCR models
-achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.} The SGL models'
+obtained using
+\replaced{the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR}{only the lasso penalty}.
+The pure lasso models achieved $R^2 = 0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively using the same cross-validation strategy used to assess the SGL.
+\added{The elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets, respectively.
+The bundle-mean lasso models achieved $R^2 = 0.33$, $0.22$, and $0.55$, respectively.
+And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.}
+The SGL models'
 performance improvement over lasso is more modest than in the ALS

### 2021-04-20 reports/manuscript/paper.tex
ENH: Add responses to reviewer comments

--- 2021-04-07 reports/manuscript/paper.tex
@@
 
+\lstset{basicstyle=\ttfamily}
+
+% color can be used to apply background shading to table cells only
+\usepackage{xcolor}
+
+\usepackage[commentmarkup=footnote]{changes}
+
 % line numbers
@@
 \DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage{xcolor}
 
@@
 \newcommand*{\alsLRatio}{$0.21$}
-\newcommand*{\whLRatio}{$0.84$}
-\newcommand*{\hbnLRatio}{$0.72$}
-\newcommand*{\ccLRatio}{$0.83$}
+\newcommand*{\whLRatio}{$0.83$}
+\newcommand*{\hbnLRatio}{$0.67$}
+\newcommand*{\ccLRatio}{$0.68$}
+\newcommand*{\alsLRatioGpca}{$0.4$}
+\newcommand*{\whLRatioGpca}{$0.94$}
+\newcommand*{\hbnLRatioGpca}{$0.82$}
+\newcommand*{\ccLRatioGpca}{$0.8$}
 \newcommand*{\alsAccuracy}{$83$}
 \newcommand*{\alsRocAuc}{$0.88$}
+\newcommand*{\alsAccuracyGpca}{$88$}
+\newcommand*{\alsRocAucGpca}{$0.9$}
 \newcommand*{\whRsq}{$0.52$}
-\newcommand*{\whMae}{$2.84$}
-\newcommand*{\hbnRsq}{$0.56$}
-\newcommand*{\hbnMae}{$1.5$}
+\newcommand*{\whMae}{$2.67$}
+\newcommand*{\hbnRsq}{$0.57$}
+\newcommand*{\hbnMae}{$1.45$}
 \newcommand*{\camcanRsq}{$0.77$}
 \newcommand*{\camcanMae}{$6.02$}
+\newcommand*{\whgpcaRsq}{$0.51$}
+\newcommand*{\whgpcaMae}{$3.13$}
+\newcommand*{\hbngpcaRsq}{$0.41$}
+\newcommand*{\hbngpcaMae}{$1.61$}
+\newcommand*{\camcangpcaRsq}{$0.68$}
+\newcommand*{\camcangpcaMae}{$7.82$}
 
@@
 that comprise these networks, by sensitizing the measurement to the directional
-diffusion of water in each voxel \cite{wandell2016clarifying}.
+diffusion of water in each voxel
+\replaced{\mbox{\cite{stejskal1965spin, wandell2016clarifying}}}{\mbox{\cite{wandell2016clarifying}}}.
 % While the measurements are usually conducted
@@
 samples along the length of each bundle \cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}. While this retains important information
-about each individual's white matter, it also presents statistical
-challenges due to the dimensionality of the data. In past work,
-comparisons between groups or across individuals were done
-independently at each node of each bundle, for each
+colby2012, ODonnell2009-uu},
+hereafter referred to as tract profiling.
+While this retains important information about each individual's white
+matter, it also presents statistical challenges due to the dimensionality of
+the data. In past work, comparisons between groups or across individuals were
+done independently at each node of each bundle, for each
 diffusion metric. This approach is exhaustive, but
 statistical power is compromised by a multiple comparison problem
-\cite{colby2012, Nichols2002-zu, Nichols2003-yy}. An alternative that
+\replaced{\mbox{\cite{colby2012, Nichols2002-zu, Nichols2003-yy, chamberland2019dimensionality}}}{\mbox{\cite{colby2012, Nichols2002-zu, Nichols2003-yy}}}.
+An alternative that
 circumvents the multiple comparison problem is to select just a few
@@
 %\end{enumerate}
+
+\begin{figure}[b!]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{-0.25em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-8.4cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{\textbf{Tractometry data flow}
+        \label{fig:methods}
+        \textbf{(a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL)
+        and the left arcuate fasciculus (ARCL)
+        over a mid-saggital anatomical slice.
+        Tract profiling further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for \textbf{(c)} the CSTL and \textbf{(d)} the ARCL.
+        \textbf{(d)} the phenotypical target data and tract profile
+        features can be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the ARCL.
+        The coefficients in $\hat{\beta}$ follow the same natural grouping.
+    }
+\end{figure}
+
 The present work aims to balance predictive accuracy with descriptive power
@@
 membership), based on a linear combination of the features estimated with
-tractometry.
+tract profiling.
 
@@
 Using this approach, we first need to deal with the large and
-asymmetric dimensionality of the data: tractometry data usually has
+asymmetric dimensionality of the data: tract profile
+data usually has
 many more features (i.e., number of measurements per individual) than
@@
 develop an implementation of SGL that is well suited to the analysis of
-tractometry data and, second, demonstrate the power and flexibility of
+tract profile data and, second, demonstrate the power and flexibility of
 this approach by applying it to both classification
-and continuous prediction problems. Our tractometry data flow is
+and continuous prediction problems. Our data flow is
 represented in \cref{fig:methods} and explained in further detail in
@@
 
-\begin{figure}[h!]
-    \vspace{0.25cm}
-    \rlap{
-        \hspace{0.25em}
-        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    }
-    \vspace{-8.25cm}
-    \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{{\bf Tractometry data flow}
-        \label{fig:methods}
-        {\bf (a)} Whole brain tractography generates streamlines approximating
-        the trajectories of white matter connections.
-        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
-        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
-        anatomical slice.
-        {\bf (c)} Tractometry further extracts bundle profiles,
-        quantifications of various diffusion metrics along the length of the
-        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for CSTL.
-        {\bf (d)} the phenotypical target data and tractometric features can
-        be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the CSTL, the middle (green) group
-        contains $k$ features from the left cingulum cingulate (CGCL),
-        and the right (blue) group
-        contains $k$ features from the left arcuate (ARCL). The coefficients in
-        $\hat{\beta}$ follow the same natural grouping.
-    }
-\end{figure}
+One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.
+For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}.}
+While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}, they neglect anatomical grouping information.}
+We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using
+the most parsimonious representation of variance in the diffusion measures.
+In contrast, our SGL-based approach seeks to establish whether prior knowledge of anatomical grouping improves modeling of brain-phenotype relationships.
+Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of
+the original feature space. We demonstrate circumstances in which this approach both helps and hinders predictive performance.
 
@@
 
-\begin{figure}
-    \vspace{0.0cm}
+We developed a method for analyzing dMRI tract profile data that uses the Sparse
+Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
+We demonstrate the use of this method on four different datasets in
+both a classification setting and a regression setting.
+
+\subsection*{SGL accurately detects ALS from tractometry data}
+
+Using data from a previous study of patients with amyotrophic lateral sclerosis (ALS)~\cite{sarica2017corticospinal}, we tested the performance of SGL in a
+classification setting. The previous study predicted ALS status with a mean
+accuracy of 80\% using a random forest algorithm based on \emph{a priori}
+selection of features only within the CST bundle-of-interest.
+SGL delivers improved predictive performance, with a cross-validated accuracy
+of {\alsAccuracy}\% and an area under the receiver operating characteristic
+curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature
+engineering.
+We also predicted ALS diagnosis using the PCR-SGL, wherein each
+group of features is independently transformed to its PC basis and
+an SGL model is fit to the transformed features. This model achieves
+\protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}
+(\cref{fig:class-results:probs}). In addition to this
+classification performance, both SGL and PCR-SGL also identify
+the white matter tracts most important for ALS classification.
+\Cref{fig:class-results:coefs3d} shows that PCR-SGL identified as potential disease biomarkers the diffusion measures in the CST from the cerebral peduncle to the corona radiata, agreeing with the previous study from which these data were extracted \mbox{\cite{sarica2017corticospinal}.}
+The relative importance of white matter
+features is captured in the $\beta$ coefficients from \cref{eq:sgl}.
+\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
+right CST, plotted over the FA values for the control and ALS subject groups.
+We find that SGL and PCR-SGL select FA metrics in the corticospinal tract and
+particularly in the right corticospinal tract as most important to ALS
+classification, confirming previous findings \cite{van2011upper,
+toosy2003diffusion, sarica2014tractography, sage2007quantitative,
+sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
+cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
+identifying the portions of the brain that were selected \emph{a priori} in
+the previous study from which we obtained the data
+\cite{sarica2017corticospinal}.
+
+\begin{figure}[t!]
+    \vspace{3.0cm}
     \rlap{
-        \includegraphics[width=0.33\textwidth]{als_coefs.pdf}
+        \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
     }
     \vspace{-7.0cm}
-    \includegraphics[width=\textwidth]{als_results.pdf}
+    \includegraphics[width=\textwidth]{als_gpca_results.pdf}
     {\phantomsubcaption\label{fig:class-results:probs}}
@@
     \caption{%
-        {\bf SGL accurately and interpretably predicts ALS diagnosis.}
+        {\bf PCR-SGL accurately and interpretably predicts ALS diagnosis.}
         \label{fig:class-results}
@@
         ROC AUC of {\protect\alsRocAuc}.
-        {\bf (b)} SGL coefficients are presented on the core fibers of major
+        {\bf (b)} PCR-SGL coefficients are presented on the core fibers of major
         fiber bundles. They exhibit high group sparsity and are concentrated
-        in the FA of the CST. The brain is oriented with the right hemisphere
-        in the foreground and anterior to the right of the page. The CSTL,
-        CSTR, and CFA bundles are indicated for orientation.
-        {\bf (c)} SGL identifies three portions of the CST as important,
+        in the FA of the corticospinal tract (CST).
+        The brain is oriented with the right hemisphere
+        in the foreground and anterior to the right of the page. The CSTL, CSTR,
+        callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)
+        bundles are indicated for orientation.
+        {\bf (c)} PCR-SGL identifies three portions of the CST as important,
         where $\hat{\beta}$ (dashed line, right axis) has large values. These
@@
 
-We developed a method for analyzing dMRI tractometry data that uses the Sparse
-Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
-We demonstrate the use of this method on four different datasets in
-both a classification setting and a regression setting.
-
-\subsection*{SGL accurately detects ALS from tractometry data}
-
-Using data from a previous study of patients with amyotrophic lateral sclerosis (ALS)~\cite{sarica2017corticospinal}, we tested the performance of SGL in a
-classification setting. The previous study predicted ALS status with a mean
-accuracy of 80\% using a random forest algorithm based on \emph{a priori}
-selection of features only within the CST bundle-of-interest.
-SGL delivers improved predictive performance, with a cross-validated accuracy
-of {\alsAccuracy}\% and an area under the receiver operating characteristic
-curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature
-engineering (\cref{fig:class-results:probs}). In addition to this
-classification performance, SGL also identifies the white matter tracts most
-important for ALS classification. The relative importance of white matter
-features is captured in the $\beta$ coefficients from \cref{eq:sgl}.
-\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups.
-We find that SGL selects FA metrics in the corticospinal tract and
-particularly in the right corticospinal tract as most important to ALS
-classification, confirming previous findings \cite{van2011upper,
-toosy2003diffusion, sarica2014tractography, sage2007quantitative,
-sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
-cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
-identifying the portions of the brain that were selected \emph{a priori} in
-the previous study from which we obtained the data
-\cite{sarica2017corticospinal}.
-
 To assess the added value of incorporating anatomical knowledge into our
-model, we compared our classification results to those obtained from four
-other models: a pure lasso model, an elastic net model, a bundle-mean lasso
-(i.e. a lasso model trained only on the mean metric values from each bundle),
-and a principal components regression lasso (Lasso PCR) model
-\cite{powell2018local, rasero2021integrating}. These models achieved
-accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and an ROC AUC of
-0.76, 0.75, 0.82, and 0.71, respectively using the same cross-validation
-strategy used to assess the SGL model. This difference in performance
-justifies the additional complexity of the SGL over simpler sparsity-inducing
-regression strategies.
+model, we compared our classification results to those obtained from
+four other models: a pure lasso model, an elastic net model, a bundle-mean lasso (i.e.
+a lasso model trained only on the mean metric values from each bundle), and a principal components regression lasso (Lasso PCR) model \cite{powell2018local, rasero2021integrating}.
+These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71, respectively
+using the same cross-validation strategy used to assess the SGL model.
+This difference in performance justifies the additional complexity of the SGL
+over simpler sparsity-inducing regression strategies.
+The relatively poor performance of Lasso PCR suggests that features with small variance are nonetheless relevant for predicting ALS diagnosis.
+Or equivalently, that group differences between ALS diagnoses are not the dominant source of variance in the diffusion metrics.
 
@@
 preferentially correlates with only a few groups of covariates. For the ALS
-dataset, $\alpha = $ \alsLRatio, confirming that the white matter correlates
-of ALS reside mostly in one bundle, namely the CST.
+dataset, the SGL model has $\alpha = $ \alsLRatio 
+and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca,
+confirming that the white matter correlates of ALS reside mostly in one
+bundle, namely the CST.
 
@@
 
-\begin{figure}
-    \vspace{0.0cm}
+\subsection*{SGL accurately predicts age from tractometry data}
+
+To test the performance of SGL in a continuous
+regression task, we focus here on the prediction of biological age in three
+datasets named WH, HBN, and Cam-CAN (see the methods section for a description of each dataset). Prediction of ``brain
+age'' is a commonly undertaken task in neuroimaging machine learning, in part
+because these predictions, and deviations therefrom, may be diagnostic of
+overall brain health (for a review, see Cole et al.~\cite{Cole2019-rz}).
+However, as Nelson et al.~\cite{nelson2019biomarkers} have observed, aging
+biomarkers are subject to unique challenges and tend to be noncausative. Our
+interest in aging here relies on its utility as a methodological benchmark.
+Biological age operates on a natural scale, with meaningful and easily
+understood units, and it's popularity as a machine learning target makes it
+valuable for comparisons with other studies.
+
+The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
+\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
+data from 76, 1651, and 640 subjects, respectively, ranging from 6-50, 5-21,
+and 18-88 years of age, respectively. In each case, biological age was used
+as the predicted variable $y$. SGL was fit to the tract profile
+features FA and mean diffusivity (MD) in 18 major brain tracts, with diffusion metrics extracted
+from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
+
+\begin{figure}[t!]
+    \vspace{3.0cm}
     \rlap{
-        \hspace{1cm}
-        \includegraphics[width=0.275\textwidth]{wh_coefs.pdf}
-        \hspace{0.25em}
-        \includegraphics[width=0.275\textwidth]{hbn_coefs.pdf}
-        \hspace{0.25em}
-        \includegraphics[width=0.275\textwidth]{camcan_coefs.pdf}
+        \hspace{0.775cm}
+        \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+        \hspace{0.5em}
+        \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+        \hspace{0.5em}
+        \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
     }
-    \vspace{-6.0cm}
+    \vspace{-6.1cm}
     \includegraphics[width=\textwidth]{regression_scatter.pdf}
@@
         plot.
-        {\bf (middle)} Feature importance for predicting age from tractometry in
+        {\bf (middle)} Feature importance for predicting age from
+        tract profile in
         the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
@@
 \end{figure}
-
-\subsection*{SGL accurately predicts age from tractometry data}
-
-To test the performance of SGL with tractometry data in a continuous
-regression task, we focus here on the prediction of biological age in three
-datasets named WH, HBN, and Cam-CAN (see the methods section for a description of each dataset). Prediction of ``brain
-age'' is a commonly undertaken task in neuroimaging machine learning, in part
-because these predictions, and deviations therefrom, may be diagnostic of
-overall brain health (for a review, see Cole et al.~\cite{Cole2019-rz}).
-However, as Nelson et al.~\cite{nelson2019biomarkers} have observed, aging
-biomarkers are subject to unique challenges and tend to be noncausative. Our
-interest in aging here relies on its utility as a methodological benchmark.
-Biological age operates on a natural scale, with meaningful and easily
-understood units, and it's popularity as a machine learning target makes it
-valuable for comparisons with other studies.
-
-The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
-\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
-data from 76, 978, and 640 subjects, respectively, ranging from 6-50, 5-21,
-and 18-88 years of age, respectively. In each case, biological age was used
-as the predicted variable $y$. SGL was fit to the tractometry-extracted
-features FA and mean diffusivity (MD) in 18 major brain tracts, with diffusion metrics extracted
-from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
 
@@
 As with ALS classification, we also compared SGL performance with results
-obtained using the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR.
-The pure lasso models achieved $R^2 = 0.47$, $0.54$, and $0.70$ for the WH,
-HBN, and Cam-CAN datasets respectively using the same cross-validation
-strategy used to assess the SGL. The elastic net models achieved $R^2 =
-0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets,
-respectively. The bundle-mean lasso models achieved $R^2 = 0.33$, $0.22$, and
-$0.55$, respectively. And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$,
-$0.74$, respectively. The SGL models' performance improvement over lasso is
-more modest than in the ALS classification case, which accords with the
-selected values of the $\alpha$ hyperparameter. These SGL models were more
-lasso-like in their sparsity penalties so they are more lasso-like in their
-predictive performance.
+obtained using
+the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR.
+The pure lasso models achieved $R^2 = 0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively using the same cross-validation strategy used to assess the SGL.
+The elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets, respectively.
+The bundle-mean lasso models achieved $R^2 = 0.33$, $0.22$, and $0.55$, respectively.
+And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.
+The SGL models'
+performance improvement over lasso is more modest than in the ALS
+classification case, which accords with the selected values of the $\alpha$
+hyperparameter. These SGL models were more lasso-like in their sparsity
+penalties so they are more lasso-like in their predictive performance.
+
+\begin{figure}[t!]
+    \includegraphics[width=\textwidth]{model_performance.pdf}
+    \caption{%
+        {\bf Model performance across all datasets.}
+        \label{fig:model-performance}
+        Each panel shows model performance measured on the test set for each
+        cross-validation split, with each black dot representing a split, box
+        plots representing the quartiles, and white diamonds representing the mean
+        performance. The $y$-scale varies in each subplot.
+        \textbf{(a)} Accuracy of test set predictions for the
+        ALS dataset. Because group differences
+        in ALS diagnosis are mostly confined to a single bundle, the group
+        structure-preserving methods, SGL and PCR-SGL, outperform the other
+        models.
+        The remaining frames show coefficient of determination, \protect$R^2$ in test sets
+        for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN
+        datasets. Because aging affects the white matter globally, group structure-blind
+        methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL
+        models show competitve predictive performance, adapting to a problem where
+        group structure is not as informative. PCR-SGL performs poorly in this regime
+        because its initial group-wise PC projection destroys between bundle covariance.
+        The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.
+    }
+\end{figure}
+Model performance across all four datasets and all six model types is summarized
+in \cref{fig:model-performance}. In contrast to the ALS classification case, the PCR Lasso performs
+competitively in age regression, suggesting that aging is a significant source of global variance
+in the tract profiles. On the other hand, the PCR-SGL models destroy cross-bundle covariance information
+in their initial group-wise PC projection step (see \cref{eq:svd}), limiting performance
+for globally distributed phenomena. Conversely, the SGL models are able to adapt to this regime.
 
@@
 
-We present here a novel method for analysis of dMRI tractometry data that
+We present here a novel method for analysis of dMRI tract profile data that
 relies on the Sparse Group Lasso \cite{simon2013sparse} to make accurate
@@
 these same data, using a bundle-of-interest approach
-\cite{sarica2017corticospinal}. In contrast, for the analysis of biological
+\cite{sarica2017corticospinal}.
+As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.
+In contrast, for the analysis of biological
 age, the coefficients identified by the algorithm are very widely distributed
@@
 properties \cite{yeatman2014lifespan}.
+
+We also implemented a union of the PCR Lasso and SGL approaches by first
+projecting each group onto its PC basis. This PCR-SGL approach transformed the feature
+space into a more parsimonious representation of its variance while
+also preserving group structure. But it was unable to efficiently represent
+cross-bundle covariance, which is an advantage of PCR Lasso. As a result, PCR-SGL performed well in ALS classification,
+where the white matter interactions are highly localized, and poorly
+in age regression, where the white matter interactions are global.
 
@@
 
-Taken together, these results demonstrate the promise of the
+Another limitation of our approach is in its computational execution time,
+which, in our experience, is roughly five times slower than simpler models
+like the lasso. This slow-down is likely to be insignificant for ``production''
+cycles in which researchers report their findings, but may be prohibitive
+for ``development'' cycles in which researchers repeatedly train models while
+adjusting their analysis pipeline. In practice, we circumvent this limitation
+by developing our analysis infrastructure with fast, simple models, and substituting
+slower, more performant models afterward.
+
+Taken together, our results demonstrate the promise of the
 group-regularized regression approach. Even at the scale of dozens of
 subjects, the results provided by SGL are both accurate, as well as
-interpretable \cite{Murdoch2019-ax}: tractometry capitalizes on domain
+interpretable \cite{Murdoch2019-ax}: tract profiling capitalizes on domain
 knowledge to engineer meaningful features; SGL scores these features based on
@@
 alexander2017open, Miller2016-hw, VanEssen2012}, but the volume and
-complexity of these data pose substantial challenges. Tractometry followed by
+complexity of these data pose substantial challenges.
+Tract profiling followed by
 analysis with SGL provide a promising approach to distill meaningful insights
@@
 constraints. Similarly, unsupervised dimensionality reduction of tractometry
-data (e.g., \cite{Chamberland2019-mu}) could also benefit from constraints
-based on grouping.
+data (e.g., \cite{chamberland2019dimensionality}) could also benefit from constraints
+based on grouping, as our implementation of PCR-SGL suggests.
 
@@
 integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ}, which extract
-tractometry data from raw and processed dMRI datasets, as well as
-AFQ-Browser, which visualizes tractometry data and facilitates sharing of the
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ, kruper2021evaluating}, which extract
+tract profile data from raw and processed dMRI datasets, as well as
+AFQ-Browser, which visualizes tract profiles data and facilitates sharing of the
 results of dMRI studies \cite{yeatman2018browser}. To facilitate
@@
 $\text{mm}^3$ and 27 non-colinear directions were measured with a
-$b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was preprocessed to
+$b=1000$ $\text{s} / \text{mm}^2$. Data was preprocessed to
 correct for subject motion and for eddy currents. The diffusion tensor
@@
 was provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
-$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
-measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. These data
+\num{2x2x2}$\textrm{mm}^3$ with 96 non-colinear directions measured with a
+$b=2000$ $\textrm{s} / \textrm{mm}^2$ and 30 non-colinear directions
+measured with a $b=1000$ $\textrm{s} / \textrm{mm}^2$. These data
 were acquired using a dual spin echo sequence, in which there is
@@
 diffusion tensor model \cite{basser1994mr} in every voxel using a robust
-fit \cite{chang2005restore}. We will refer to this dataset as WH.
+fit \cite{chang2005restore}
+on the \protect$b=1000$ \protect$\textrm{s} / \textrm{mm}^2$ shell only.
+We will refer to this dataset as WH.
 
 \item Diffusion MRI data from the Healthy Brain Network pediatric mental
-health study \cite{alexander2017open}, containing dMRI data from 978 subjects
-with ages 5-21. These data were measured in 3T Siemens MRI scanners at three
-sites in the New York area. Informed consent was obtained from each
-participant aged 18 or older. For participants younger than 18, written
-consent was obtained from their legal guardians and written assent was
-obtained from the participant. Voxel resolution was
-\num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions measured for
-each of $b=1000 \frac{\text{sec}}{\text{mm}^2}$ and $b=2000
-\frac{\text{sec}}{\text{mm}^2}$.
-Preprocessing was performed using \emph{QSIPrep} 0.12.1, which is based on
-\emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.
+health study \cite{alexander2017open}, containing dMRI data from 1651 subjects
+with ages 5-21. These data were measured in 3T Siemens MRI scanners at two
+sites in the New York
+area: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center.
+Informed consent was obtained from each participant aged 18 or older. For
+participants younger than 18, written consent was obtained from their legal
+guardians and written assent was obtained from the participant. Voxel
+resolution was \num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions
+measured for each of $b=1000 \text{s} / \text{mm}^2$ and $b=2000 \text{s} /
+\text{mm}^2$. Preprocessing was performed using \emph{QSIPrep} 0.12.1, which
+is based on \emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.
 
@@
 resolution was \num{2x2x2}$\text{mm}^3$ with 30 non-colinear directions
-measured for each of $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$ and $b=2000$
-$\frac{\text{sec}}{\text{mm}^2}$. The diffusion weighted images were acquired
+measured for each of $b=1000$ $\text{s} / \text{mm}^2$ and $b=2000$
+$\text{s} / \text{mm}^2$. The diffusion weighted images were acquired
 with a twice refocused spin-echo sequence and the same preprocessing pipeline
@@
 that follows the prinicpal diffusion direction of the diffusion tensor
-in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
+in each voxel (STT) \cite{basser2000vivo}. Eighteen major
+tracts, which are enumerated in the supplemental material, were identified
 using multiple criteria: streamlines are selected as candidates for
@@
 weighting the contribution of each streamline by the inverse of the
-mahalnobis distance of the node from the average of that node across
-streamlines. This means that streamlines that are more representative of
-the tract contribute more to the bundle profile, relative to streamlines
-that are on the edge of the tract.
+mahalanobis distance of the node from the average of
+that node across streamlines. This means that streamlines that are more
+representative of the tract contribute more to the bundle profile, relative
+to streamlines that are on the edge of the tract.
 
@@
 These processes create bundle profiles, in which diffusion measures
-are quantified and averaged along eighteen major fiber tracts. Here,
+are quantified and averaged along eighteen major fiber tracts,
+which are enumerated in the supplemental material.
+See Figure S3 of \mbox{\cite{kruper2021evaluating} for}
+a depiction of these white matter bundles.
+Here,
 we use only the mean diffusivity (MD) and the fractional anisotropy
 (FA) of the diffusion tensor, but additional dMRI-based maps or maps
-based on other quantitative MRI measurements can also be used. These
-bundle profiles, along with the phenotypical data we wish to explain
+based on other quantitative MRI measurements can also be used.
+The resulting feature space was the same for all four datasets, with
+the FA and MD metrics at each of 100 nodes in eighteen bundles
+comprising 3600 features per subject.
+These bundle profiles, along with the phenotypical data we wish to explain
 or predict, form the input to the SGL algorithm. In a domain-agnostic
@@
 variables while the bundle profiles form the feature or predictor
-variables (See \cref{fig:methods:group-structure}).
+variables (see \cref{fig:methods:group-structure}).
 
@@
 remove each feature's mean and scale it to unit variance (z-score) using the
-\lstinline{StandardScaler} from scikit-learn \cite{scikit-learn}. The scaling
+\lstinline|StandardScaler| from scikit-learn \cite{scikit-learn}. The scaling
 parameters are learned only from the training data and then applied equally
@@
 
-After scaling and imputation, the tractometry data and target
+After scaling and imputation, the tract profile data and target
 phenotypical data can be organized in a linear model:
@@
 where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
-or continuous numerical, such as the subject's age. The tractometry
+or continuous numerical, such as the subject's age. The tract profile
 data is represented in the feature matrix $\mathbf{X}$, with rows
@@
 
+\subsubsection*{SGL with principal components}
+
+SGL may be combined with principal components regression (PCR-SGL) by
+performing dimensionality reduction separately for each group of covariates.
+Let
+\begin{equation}
+    \mathbf{X}^{(\ell)} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^T,
+    \label{eq:svd}
+\end{equation}
+be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$,
+the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group
+\protect$\ell$. Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where
+\protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of
+\protect$\mathbf{X}^{(\ell)}$. \protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal
+matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$. The product
+\protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the
+principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$
+in the basis provided by \protect$\mathbf{V}^T$.
+
+Since this decomposition is performed separately for each group of covariates,
+the grouping information is preserved in the transformation from \protect$\mathbf{X}$
+to \protect$\mathbf{Z}$. We may then build an SGL model relating \protect$y$
+and \protect$\mathbf{Z}$,
+
+\begin{align}
+    \hat{y} &= \mathbf{Z} \hat{\theta}, \\
+    \hat{\theta} &= \min_\theta L_{\text{mse}}
+    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
+    \sqrt{p_\ell} \norm{\theta^{(\ell)}}_2
+    + \alpha \lambda \norm{\theta}_1, \\%
+    \text{where} \quad
+    L_{\text{mse}} &= \frac{1}{2}
+    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
+    \mathbf{Z}^{(\ell)} \theta^{(\ell)}}_2^2.
+    \label{eq:pcr-sgl}
+\end{align}
+The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the
+original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.
+
 \subsubsection*{Bagging meta-estimators}
@@
 where the transformation function $f^{-1}$ characterizes the transform
-applied to the data before fitting the linear coefficients. For example,
-for the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
+applied to the data before fitting the linear coefficients.
+This is similar to the use of a link function in a generalized
+linear model, but without the adoption of an exponential probability
+distribution \mbox{\cite{nelder1972technique}.}
+For the WH, HBN, and Cam-CAN datasets, we use a
+logarithmic transform,
 \begin{equation}
-    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
+    f \left( \hat{y} \right) = \ln \left( \hat{y} \right),
     \label{eq:log-nonlinearity}
 \end{equation}
+implemented using scikit-learn's \lstinline|TransformedTargetRegressor|
+meta-estimator \mbox{\cite{scikit-learn}}
+with numpy's \lstinline|log| and \lstinline|exp| as the transform and
+inverse transform functions, respectively \mbox{\cite{harris2020array}.}
 
@@
 $\alpha$ and $\lambda$ using sequential model-based optimization, implemented
-using the scikit-optimize \verb|BayesSearchCV| class \cite{scikit_optimize}.
-For continuous numerical $y$, \verb|BayesSearchCV| searches for
+using the scikit-optimize \lstinline|BayesSearchCV| class \cite{scikit_optimize}.
+For continuous numerical $y$, \lstinline|BayesSearchCV| searches for
 meta-parameter values that maximize the $R^2$ averaged over test sets. For
-binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
+binary categorical $y$ \lstinline|BayesSearchCV| seeks to maximize the
 classification accuracy. Using hyperoptimization, we find optimal
@@
 format \cite{yeatman2018browser} and represents them internally as
-\lstinline{DataFrame} objects from the pandas Python library
+\lstinline|DataFrame| objects from the pandas Python library
 \cite{mckinney2010data}. The software provides different options for imputing
@@
 under the receiver operating curve (AUC ROC), and coefficient of
-determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the \texttt{groupyr} software library \cite{groupyr} mentioned above to solve the SGL.
+determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the
+\texttt{groupyr} software library \cite{groupyr} mentioned above to solve the
+SGL.
 
@@
 Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
+and John Kruper
 for helpful comments on the manuscript.

### 2021-04-20 reports/manuscript/paper_changes.tex
ENH: Add responses to reviewer comments

@@
 
-\usepackage{changes}
+\lstset{basicstyle=\ttfamily}
+
+% color can be used to apply background shading to table cells only
+\usepackage{xcolor}
+
+\usepackage[commentmarkup=footnote]{changes}
 
@@
 samples along the length of each bundle \cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}. While this retains important information
-about each individual's white matter, it also presents statistical
-challenges due to the dimensionality of the data. In past work,
-comparisons between groups or across individuals were done
-independently at each node of each bundle, for each
+colby2012, ODonnell2009-uu},
+\added{hereafter referred to as tract profiling}.
+While this retains important information about each individual's white
+matter, it also presents statistical challenges due to the dimensionality of
+the data. In past work, comparisons between groups or across individuals were
+done independently at each node of each bundle, for each
 diffusion metric. This approach is exhaustive, but
 statistical power is compromised by a multiple comparison problem
-\cite{colby2012, Nichols2002-zu, Nichols2003-yy}. An alternative that
+\replaced{\mbox{\cite{colby2012, Nichols2002-zu, Nichols2003-yy, chamberland2019dimensionality}}}{\mbox{\cite{colby2012, Nichols2002-zu, Nichols2003-yy}}}.
+An alternative that
 circumvents the multiple comparison problem is to select just a few
@@
 %\end{enumerate}
+
+\begin{figure}[b!]
+    \vspace{0.25cm}
+    \rlap{
+        \hspace{-0.25em}
+        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    }
+    \vspace{-8.4cm}
+    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{\textbf{Tractometry data flow}
+        \label{fig:methods}
+        \textbf{(a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL)
+        \added{and the left arcuate fasciculus (ARCL)}
+        over a mid-saggital anatomical slice.
+        \deleted{\textbf{(c)}} \replaced{Tract profiling}{Tractometry} further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for \added{\textbf{(c)}} the CSTL \added{and \textbf{(d)} the ARCL}.
+        \textbf{(d)} the phenotypical target data and \replaced{tract profile}{tractometric}
+        features can be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the \replaced{ARCL}{left arcuate (ARCL)}.
+        The coefficients in $\hat{\beta}$ follow the same natural grouping.
+    }
+\end{figure}
+
 The present work aims to balance predictive accuracy with descriptive power
@@
 membership), based on a linear combination of the features estimated with
-tractometry.
+\replaced{tract profiling}{tractometry}.
 
@@
 Using this approach, we first need to deal with the large and
-asymmetric dimensionality of the data: tractometry data usually has
+asymmetric dimensionality of the data: \replaced{tract profile}{tractometry}
+data usually has
 many more features (i.e., number of measurements per individual) than
@@
 develop an implementation of SGL that is well suited to the analysis of
-tractometry data and, second, demonstrate the power and flexibility of
+\replaced{tract profile}{tractometry} data and, second, demonstrate the power and flexibility of
 this approach by applying it to both classification
-and continuous prediction problems. Our tractometry data flow is
+and continuous prediction problems. Our \deleted{tractometry} data flow is
 represented in \cref{fig:methods} and explained in further detail in
@@
 
-\begin{figure}[h!]
-    \vspace{0.25cm}
-    \rlap{
-        \hspace{0.25em}
-        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    }
-    \vspace{-8.25cm}
-    \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{{\bf Tractometry data flow}
-        \label{fig:methods}
-        {\bf (a)} Whole brain tractography generates streamlines approximating
-        the trajectories of white matter connections.
-        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
-        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
-        anatomical slice.
-        {\bf (c)} Tractometry further extracts bundle profiles,
-        quantifications of various diffusion metrics along the length of the
-        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for CSTL.
-        {\bf (d)} the phenotypical target data and tractometric features can
-        be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the CSTL, the middle (green) group
-        contains $k$ features from the left cingulum cingulate (CGCL),
-        and the right (blue) group
-        contains $k$ features from the left arcuate (ARCL). The coefficients in
-        $\hat{\beta}$ follow the same natural grouping.
-    }
-\end{figure}
+\added{One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.}
+\added{For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}}.}
+\added{While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}}, they neglect anatomical grouping information.}
+\added{We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using}
+\added{the most parsimonious representation of variance in the diffusion measures.
+In contrast, our SGL-based approach seeks to establish whether prior knowledge of anatomical grouping improves modeling of brain-phenotype relationships.}
+\added{Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of}
+\added{the original feature space. We demonstrate circumstances in which this approach both helps and hinders predictive performance.}
 
@@
 
-\begin{figure}
-    \vspace{0.0cm}
+We developed a method for analyzing dMRI \replaced{tract profile}{tractometry} data that uses the Sparse
+Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
+We demonstrate the use of this method on four different datasets in
+both a classification setting and a regression setting.
+
+\subsection*{SGL accurately detects ALS from tractometry data}
+
+Using data from a previous study of patients with amyotrophic lateral sclerosis (ALS)~\cite{sarica2017corticospinal}, we tested the performance of SGL in a
+classification setting. The previous study predicted ALS status with a mean
+accuracy of 80\% using a random forest algorithm based on \emph{a priori}
+selection of features only within the CST bundle-of-interest.
+SGL delivers improved predictive performance, with a cross-validated accuracy
+of {\alsAccuracy}\% and an area under the receiver operating characteristic
+curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature
+engineering.
+\added{We also predicted ALS diagnosis using the PCR-SGL, wherein each}
+\added{group of features is independently transformed to its PC basis and}
+\added{an SGL model is fit to the transformed features. This model achieves}
+\added{\protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}}
+(\cref{fig:class-results:probs}). In addition to this
+classification performance, both SGL \added{and PCR-SGL} also \replaced{identify}{identifies}
+the white matter tracts most important for ALS classification.
+\added{\Cref{fig:class-results:coefs3d} shows that PCR-SGL identified as potential disease biomarkers the diffusion measures in the CST from the cerebral peduncle to the corona radiata, agreeing with the previous study from which these data were extracted \mbox{\cite{sarica2017corticospinal}}.}
+The relative importance of white matter
+features is captured in the $\beta$ coefficients from \cref{eq:sgl}.
+\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
+right CST, plotted over the FA values for the control and ALS subject groups.
+We find that SGL \replaced{and PCR-SGL select}{selects} FA metrics in the corticospinal tract and
+particularly in the right corticospinal tract as most important to ALS
+classification, confirming previous findings \cite{van2011upper,
+toosy2003diffusion, sarica2014tractography, sage2007quantitative,
+sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
+cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
+identifying the portions of the brain that were selected \emph{a priori} in
+the previous study from which we obtained the data
+\cite{sarica2017corticospinal}.
+
+\begin{figure}[t!]
+    \vspace{3.0cm}
     \rlap{
-        \includegraphics[width=0.33\textwidth]{als_coefs.pdf}
+        \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
     }
     \vspace{-7.0cm}
-    \includegraphics[width=\textwidth]{als_results.pdf}
+    \includegraphics[width=\textwidth]{als_gpca_results.pdf}
     {\phantomsubcaption\label{fig:class-results:probs}}
@@
     \caption{%
-        {\bf SGL accurately and interpretably predicts ALS diagnosis.}
+        {\bf \added{PCR-}SGL accurately and interpretably predicts ALS diagnosis.}
         \label{fig:class-results}
@@
         ROC AUC of {\protect\alsRocAuc}.
-        {\bf (b)} SGL coefficients are presented on the core fibers of major
+        {\bf (b)} \added{PCR-}SGL coefficients are presented on the core fibers of major
         fiber bundles. They exhibit high group sparsity and are concentrated
-        in the FA of the CST. The brain is oriented with the right hemisphere
-        in the foreground and anterior to the right of the page. The CSTL,
-        CSTR, and CFA bundles are indicated for orientation.
-        {\bf (c)} SGL identifies three portions of the CST as important,
+        in the FA of the \replaced{corticospinal tract (CST)}{CST}.
+        The brain is oriented with the right hemisphere
+        in the foreground and anterior to the right of the page. The CSTL, CSTR,
+        \replaced{callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)}{CFA}
+        bundles are indicated for orientation.
+        {\bf (c)} \added{PCR-}SGL identifies three portions of the CST as important,
         where $\hat{\beta}$ (dashed line, right axis) has large values. These
@@
 
-We developed a method for analyzing dMRI tractometry data that uses the Sparse
-Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
-We demonstrate the use of this method on four different datasets in
-both a classification setting and a regression setting.
-
-\subsection*{SGL accurately detects ALS from tractometry data}
-
-Using data from a previous study of patients with amyotrophic lateral sclerosis (ALS)~\cite{sarica2017corticospinal}, we tested the performance of SGL in a
-classification setting. The previous study predicted ALS status with a mean
-accuracy of 80\% using a random forest algorithm based on \emph{a priori}
-selection of features only within the CST bundle-of-interest.
-SGL delivers improved predictive performance, with a cross-validated accuracy
-of {\alsAccuracy}\% and an area under the receiver operating characteristic
-curve (ROC AUC) of {\alsRocAuc}, without the need for \emph{a priori} feature
-engineering (\cref{fig:class-results:probs}). In addition to this
-classification performance, SGL also identifies the white matter tracts most
-important for ALS classification. The relative importance of white matter
-features is captured in the $\beta$ coefficients from \cref{eq:sgl}.
-\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups.
-We find that SGL selects FA metrics in the corticospinal tract and
-particularly in the right corticospinal tract as most important to ALS
-classification, confirming previous findings \cite{van2011upper,
-toosy2003diffusion, sarica2014tractography, sage2007quantitative,
-sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
-cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
-identifying the portions of the brain that were selected \emph{a priori} in
-the previous study from which we obtained the data
-\cite{sarica2017corticospinal}.
-
 To assess the added value of incorporating anatomical knowledge into our
@@
 over simpler sparsity-inducing regression strategies.
+\added{The relatively poor performance of Lasso PCR suggests that features with small variance are nonetheless relevant for predicting ALS diagnosis.}
+\added{Or equivalently, that group differences between ALS diagnoses are not the dominant source of variance in the diffusion metrics.}
 
@@
 preferentially correlates with only a few groups of covariates. For the ALS
-dataset, $\alpha = $ \alsLRatio, confirming that the white matter correlates
-of ALS reside mostly in one bundle, namely the CST.
+dataset, \added{the SGL model has} $\alpha = $ \alsLRatio 
+\added{and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca},
+confirming that the white matter correlates of ALS reside mostly in one
+bundle, namely the CST.
 
@@
 
-\begin{figure}
-    \vspace{0.0cm}
+\subsection*{SGL accurately predicts age from tractometry data}
+
+To test the performance of SGL \deleted{with tractometry data} in a continuous
+regression task, we focus here on the prediction of biological age in three
+datasets named WH, HBN, and Cam-CAN (see the methods section for a description of each dataset). Prediction of ``brain
+age'' is a commonly undertaken task in neuroimaging machine learning, in part
+because these predictions, and deviations therefrom, may be diagnostic of
+overall brain health (for a review, see Cole et al.~\cite{Cole2019-rz}).
+However, as Nelson et al.~\cite{nelson2019biomarkers} have observed, aging
+biomarkers are subject to unique challenges and tend to be noncausative. Our
+interest in aging here relies on its utility as a methodological benchmark.
+Biological age operates on a natural scale, with meaningful and easily
+understood units, and it's popularity as a machine learning target makes it
+valuable for comparisons with other studies.
+
+The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
+\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
+data from 76, 1651, and 640 subjects, respectively, ranging from 6-50, 5-21,
+and 18-88 years of age, respectively. In each case, biological age was used
+as the predicted variable $y$. SGL was fit to the \replaced{tract profile}{tractometry-extracted}
+features FA and mean diffusivity (MD) in 18 major brain tracts, with diffusion metrics extracted
+from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
+
+\begin{figure}[t!]
+    \vspace{3.0cm}
     \rlap{
-        \hspace{1cm}
-        \includegraphics[width=0.275\textwidth]{wh_coefs.pdf}
-        \hspace{0.25em}
-        \includegraphics[width=0.275\textwidth]{hbn_coefs.pdf}
-        \hspace{0.25em}
-        \includegraphics[width=0.275\textwidth]{camcan_coefs.pdf}
+        \hspace{0.775cm}
+        \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+        \hspace{0.5em}
+        \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+        \hspace{0.5em}
+        \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
     }
-    \vspace{-6.0cm}
+    \vspace{-6.1cm}
     \includegraphics[width=\textwidth]{regression_scatter.pdf}
@@
         plot.
-        {\bf (middle)} Feature importance for predicting age from tractometry in
+        {\bf (middle)} Feature importance for predicting age from
+        \replaced{tract profile}{tractometry} in
         the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
@@
 
+\begin{figure}[t!]
+    \includegraphics[width=\textwidth]{model_performance.pdf}
+    \caption{%
+        {\bf \added{Model performance across all datasets.}}
+        \label{fig:model-performance}
+        \added{Each panel shows model performance measured on the test set for each}
+        \added{cross-validation split, with each black dot representing a split, box}
+        \added{plots representing the quartiles, and white diamonds representing the mean}
+        \added{performance. The $y$-scale varies in each subplot.}
+        \added{\textbf{(a)} Accuracy of test set predictions for the}
+        \added{ALS dataset. Because group differences}
+        \added{in ALS diagnosis are mostly confined to a single bundle, the group}
+        \added{structure-preserving methods, SGL and PCR-SGL, outperform the other}
+        \added{models.}
+        \added{The remaining frames show coefficient of determination, \protect$R^2$ in test sets}
+        \added{for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN}
+        \added{datasets. Because aging affects the white matter globally, group structure-blind}
+        \added{methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL}
+        \added{models show competitve predictive performance, adapting to a problem where}
+        \added{group structure is not as informative. PCR-SGL performs poorly in this regime}
+        \added{because its initial group-wise PC projection destroys between bundle covariance.}
+        \added{The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.}
+    }
+\end{figure}
+\added{Model performance across all four datasets and all six model types is summarized}
+\added{in \cref{fig:model-performance}. In contrast to the ALS classification case, the PCR Lasso performs}
+\added{competitively in age regression, suggesting that aging is a significant source of global variance}
+\added{in the tract profiles. On the other hand, the PCR-SGL models destroy cross-bundle covariance information}
+\added{in their initial group-wise PC projection step (see \cref{eq:svd}), limiting performance}
+\added{for globally distributed phenomena. Conversely, the SGL models are able to adapt to this regime.}
+
 \section*{Discussion}
 
-We present here a novel method for analysis of dMRI tractometry data that
+We present here a novel method for analysis of dMRI \replaced{tract profile}{tractometry} data that
 relies on the Sparse Group Lasso \cite{simon2013sparse} to make accurate
@@
 these same data, using a bundle-of-interest approach
-\cite{sarica2017corticospinal}. In contrast, for the analysis of biological
+\cite{sarica2017corticospinal}.
+\added{As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.}
+In contrast, for the analysis of biological
 age, the coefficients identified by the algorithm are very widely distributed
@@
 properties \cite{yeatman2014lifespan}.
+
+\added{We also implemented a union of the PCR Lasso and SGL approaches by first}
+\added{projecting each group onto its PC basis. This PCR-SGL approach transformed the feature}
+\added{space into a more parsimonious representation of its variance while}
+\added{also preserving group structure. But it was unable to efficiently represent}
+\added{cross-bundle covariance, which is an advantage of PCR Lasso. As a result, PCR-SGL performed well in ALS classification,}
+\added{where the white matter interactions are highly localized, and poorly}
+\added{in age regression, where the white matter interactions are global.}
 
@@
 
-Taken together, these results demonstrate the promise of the
+\added{Another limitation of our approach is in its computational execution time,}
+\added{which, in our experience, is roughly five times slower than simpler models}
+\added{like the lasso. This slow-down is likely to be insignificant for ``production''}
+\added{cycles in which researchers report their findings, but may be prohibitive}
+\added{for ``development'' cycles in which researchers repeatedly train models while}
+\added{adjusting their analysis pipeline. In practice, we circumvent this limitation}
+\added{by developing our analysis infrastructure with fast, simple models, and substituting}
+\added{slower, more performant models afterward.}
+
+Taken together, \replaced{our}{these} results demonstrate the promise of the
 group-regularized regression approach. Even at the scale of dozens of
 subjects, the results provided by SGL are both accurate, as well as
-interpretable \cite{Murdoch2019-ax}: tractometry capitalizes on domain
+interpretable \cite{Murdoch2019-ax}: \replaced{tract profiling}{tractometry} capitalizes on domain
 knowledge to engineer meaningful features; SGL scores these features based on
@@
 alexander2017open, Miller2016-hw, VanEssen2012}, but the volume and
-complexity of these data pose substantial challenges. Tractometry followed by
+complexity of these data pose substantial challenges.
+\replaced{Tract profiling}{Tractometry} followed by
 analysis with SGL provide a promising approach to distill meaningful insights
@@
 constraints. Similarly, unsupervised dimensionality reduction of tractometry
-data (e.g., \cite{Chamberland2019-mu}) could also benefit from constraints
-based on grouping.
+data (e.g., \cite{chamberland2019dimensionality}) could also benefit from constraints
+based on grouping\added{, as our implementation of PCR-SGL suggests}.
 
@@
 integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ}, which extract
-tractometry data from raw and processed dMRI datasets, as well as
-AFQ-Browser, which visualizes tractometry data and facilitates sharing of the
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ, kruper2021evaluating}, which extract
+\replaced{tract profile}{tractometry} data from raw and processed dMRI datasets, as well as
+AFQ-Browser, which visualizes \replaced{tract profiles}{tractometry} data and facilitates sharing of the
 results of dMRI studies \cite{yeatman2018browser}. To facilitate
@@
 diffusion tensor model \cite{basser1994mr} in every voxel using a robust
-fit \cite{chang2005restore}. We will refer to this dataset as WH.
+fit \cite{chang2005restore}
+\added{on the \protect$b=1000$ \protect$\textrm{s} / \textrm{mm}^2$ shell only}.
+We will refer to this dataset as WH.
 
 \item Diffusion MRI data from the Healthy Brain Network pediatric mental
-health study \cite{alexander2017open}, containing dMRI data from 978 subjects
-with ages 5-21. These data were measured in 3T Siemens MRI scanners at three
-sites in the New York area. Informed consent was obtained from each
-participant aged 18 or older. For participants younger than 18, written
-consent was obtained from their legal guardians and written assent was
-obtained from the participant. Voxel resolution was
-\num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions measured for
-each of $b=1000 \frac{\text{sec}}{\text{mm}^2}$ and $b=2000
-\frac{\text{sec}}{\text{mm}^2}$.
-Preprocessing was performed using \emph{QSIPrep} 0.12.1, which is based on
-\emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.
+health study \cite{alexander2017open}, containing dMRI data from 1651 subjects
+with ages 5-21. These data were measured in 3T Siemens MRI scanners at two
+sites in the New York
+area\added{: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center}.
+Informed consent was obtained from each participant aged 18 or older. For
+participants younger than 18, written consent was obtained from their legal
+guardians and written assent was obtained from the participant. Voxel
+resolution was \num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions
+measured for each of $b=1000 \text{s} / \text{mm}^2$ and $b=2000 \text{s} /
+\text{mm}^2$. Preprocessing was performed using \emph{QSIPrep} 0.12.1, which
+is based on \emph{Nipype} 1.5.1 \cite[RRID:SCR\_002502]{nipype1,nipype2}.
 
@@
 that follows the prinicpal diffusion direction of the diffusion tensor
-in each voxel (STT) \cite{basser2000vivo}. Major tracts were identified
+in each voxel (STT) \cite{basser2000vivo}. \replaced{Eighteen major}{Major}
+tracts\added{, which are enumerated in the supplemental material,} were identified
 using multiple criteria: streamlines are selected as candidates for
@@
 weighting the contribution of each streamline by the inverse of the
-mahalnobis distance of the node from the average of that node across
-streamlines. This means that streamlines that are more representative of
-the tract contribute more to the bundle profile, relative to streamlines
-that are on the edge of the tract.
+\replaced{mahalanobis}{mahalnobis} distance of the node from the average of
+that node across streamlines. This means that streamlines that are more
+representative of the tract contribute more to the bundle profile, relative
+to streamlines that are on the edge of the tract.
 
@@
 These processes create bundle profiles, in which diffusion measures
-are quantified and averaged along eighteen major fiber tracts. Here,
+are quantified and averaged along eighteen major fiber tracts,
+which are enumerated in the supplemental material.
+\added{See Figure S3 of \mbox{\cite{kruper2021evaluating}} for}
+\added{a depiction of these white matter bundles.}
+Here,
 we use only the mean diffusivity (MD) and the fractional anisotropy
 (FA) of the diffusion tensor, but additional dMRI-based maps or maps
-based on other quantitative MRI measurements can also be used. These
-bundle profiles, along with the phenotypical data we wish to explain
+based on other quantitative MRI measurements can also be used.
+\added{The resulting feature space was the same for all four datasets, with}
+\added{the FA and MD metrics at each of 100 nodes in eighteen bundles}
+\added{comprising 3600 features per subject.}
+These bundle profiles, along with the phenotypical data we wish to explain
 or predict, form the input to the SGL algorithm. In a domain-agnostic
@@
 variables while the bundle profiles form the feature or predictor
-variables (See \cref{fig:methods:group-structure}).
+variables (\replaced{see}{See} \cref{fig:methods:group-structure}).
 
@@
 
-After scaling and imputation, the tractometry data and target
+After scaling and imputation, the \replaced{tract profile}{tractometry} data and target
 phenotypical data can be organized in a linear model:
@@
 where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
-or continuous numerical, such as the subject's age. The tractometry
+or continuous numerical, such as the subject's age. The \replaced{tract profile}{tractometry}
 data is represented in the feature matrix $\mathbf{X}$, with rows
@@
 
+\subsubsection*{\added{SGL with principal components}}
+
+\added{SGL may be combined with principal components regression (PCR-SGL) by}
+\added{performing dimensionality reduction separately for each group of covariates.}
+\added{Let}
+\begin{equation}
+    \mathbf{X}^{(\ell)} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^T,
+    \label{eq:svd}
+\end{equation}
+\added{be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$,}
+\added{the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group}
+\added{\protect$\ell$. Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where}
+\added{\protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of}
+\added{\protect$\mathbf{X}^{(\ell)}$. \protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal}
+\added{matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$. The product}
+\added{\protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the}
+\added{principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$}
+\added{in the basis provided by \protect$\mathbf{V}^T$.}
+
+\added{Since this decomposition is performed separately for each group of covariates,}
+\added{the grouping information is preserved in the transformation from \protect$\mathbf{X}$}
+\added{to \protect$\mathbf{Z}$. We may then build an SGL model relating \protect$y$}
+\added{and \protect$\mathbf{Z}$,}
+
+\begin{align}
+    \hat{y} &= \mathbf{Z} \hat{\theta}, \\
+    \hat{\theta} &= \min_\theta L_{\text{mse}}
+    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
+    \sqrt{p_\ell} \norm{\theta^{(\ell)}}_2
+    + \alpha \lambda \norm{\theta}_1, \\%
+    \text{where} \quad
+    L_{\text{mse}} &= \frac{1}{2}
+    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
+    \mathbf{Z}^{(\ell)} \theta^{(\ell)}}_2^2.
+    \label{eq:pcr-sgl}
+\end{align}
+\added{The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the}
+\added{original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.}
+
 \subsubsection*{Bagging meta-estimators}
@@
 where the transformation function $f^{-1}$ characterizes the transform
-applied to the data before fitting the linear coefficients. For example,
-for the WH, HBN, and Cam-CAN datasets, we use a logarithmic transform,
+applied to the data before fitting the linear coefficients.
+\added{This is similar to the use of a link function in a generalized}
+\added{linear model, but without the adoption of an exponential probability}
+\added{distribution \mbox{\cite{nelder1972technique}}.}
+For \deleted{example, for} the WH, HBN, and Cam-CAN datasets, we use a
+logarithmic transform,
 \begin{equation}
-    f \left( \hat{y} \right) = \ln \left( \hat{y} \right)
+    f \left( \hat{y} \right) = \ln \left( \hat{y} \right),
     \label{eq:log-nonlinearity}
 \end{equation}
+\added{implemented using scikit-learn's \lstinline|TransformedTargetRegressor|}
+\added{meta-estimator \mbox{\cite{scikit-learn}}}
+\added{with numpy's \lstinline|log| and \lstinline|exp| as the transform and}
+\added{inverse transform functions, respectively \mbox{\cite{harris2020array}}.}
 
@@
 Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
+\added{and John Kruper}
 for helpful comments on the manuscript.

### 2021-04-20 reports/manuscript/supplemental.tex
ENH: Add responses to reviewer comments

@@
 left cingulum cingulate (CGCL),
-callosum forceps major (CFP),
-callosum forceps minor (CFA),
+callosum forceps posterior (CFP),
+callosum forceps anterior (CFA),
 right inferior longitudinal fasciculus (ILFR),

### 2021-04-20 notebooks/plot_utils.py

@@ -27,8 +27,20 @@ def plot_coefs_on_bundle_cores(
     height=500,
 ):
     my_results = results[key][0]
-    coefs = np.array([np.array(bag_res["coefs"]) for bag_res in my_results.values()])
-    mean_beta = np.mean(np.array(coefs), axis=(0, 1))
+    if all(["pca_components" in bag_res for bag_res in my_results.values()]):
+        mean_beta = np.mean([
+            np.einsum(
+                "...j,...jk",
+                np.mean(my_results[cv_idx]["coefs"], axis=0).reshape(
+                    np.array(my_results[cv_idx]["pca_components"]).shape[:2]
+                ),
+                np.array(my_results[cv_idx]["pca_components"]),
+            ).flatten() for cv_idx in my_results.keys()
+        ], axis=0)
+    else:
+        mean_beta = np.mean(np.array(
+            [np.array(bag_res["coefs"]) for bag_res in my_results.values()]
+        ), axis=(0, 1))
     with open("../data/raw/core_streamlines.json") as fp:
         cores = json.load(fp)
 
@@ -140,6 +152,58 @@ def plot_coefs_on_bundle_cores(
         fig.update_layout(
             scene=dict(
                 annotations=[
+                    dict(
+                        text="ARCR",
+                        x=bundles.get("ARC_R", bundles.get("Right Arcuate"))[
+                            10, 0
+                        ]
+                        + offset[0],
+                        y=bundles.get("ARC_R", bundles.get("Right Arcuate"))[
+                            10, 1
+                        ]
+                        + offset[1]
+                        + 20,
+                        z=bundles.get("ARC_R", bundles.get("Right Arcuate"))[
+                            10, 2
+                        ]
+                        + offset[2]
+                        - 4,
+                        showarrow=True,
+                        xanchor="center",
+                        font=dict(size=20),
+                        yanchor="middle",
+                        ax=10,
+                        ay=-50,
+                        arrowsize=2,
+                        arrowwidth=1,
+                        arrowhead=1,
+                    ),
+                    dict(
+                        text="ARCL",
+                        x=bundles.get("ARC_L", bundles.get("Left Arcuate"))[
+                            10, 0
+                        ]
+                        + offset[0],
+                        y=bundles.get("ARC_L", bundles.get("Left Arcuate"))[
+                            10, 1
+                        ]
+                        + offset[1]
+                        + 20,
+                        z=bundles.get("ARC_L", bundles.get("Left Arcuate"))[
+                            10, 2
+                        ]
[…]

### 2021-04-20 reports/manuscript/paper.tex
ENH: Add notes on generalization in discussion section

@@
 As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.
+
 In contrast, for the analysis of biological
@@
 properties \cite{yeatman2014lifespan}.
+We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the supplementary material.
+For age regression, substantial differences between the datasets preclude generalization across all three:
+\begin{enumerate*}[%
+    label=(\roman*),%
+    before=\unskip{: },%
+    itemjoin={{, }},%
+    itemjoin*={{, and }}]
+    \item different acquisition parameters, which can be challenging to harmonize \mbox{\cite{pinto2020harmonization}}
+    \item different diffusion models, with DTI for the WH dataset and DKI for the HBN and Cam-CAN datasets
+    \item different age ranges and distributions (which is evident in the figure legends for \cref{fig:age-results}), with HBN being a developmental dataset, while WH and Cam-CAN are lifespan maturation datasets
+    \item different anatomical extents, with the WH streamlines truncated to remain with the bundle's bounding regions of interest (the default behavior in the legacy \texttt{mAFQ}) and the HBN and Cam-CAN streamlines allowed to retain their full extent from whole-brain tractography (the default behavior in \texttt{pyAFQ}).
+\end{enumerate*}
+In a biological characteristic that has widespread effects in the brain, validity is difficult to assess \mbox{\cite{lermausabiaga2019replication}, so it is both unsurprising and vexing that we can do so well at predicting within each dataset, and yet do poorly in interpreting informative features across instruments.}
 

### 2021-04-20 reports/manuscript/paper_changes.tex
ENH: Add notes on generalization in discussion section

@@
 \added{As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.}
+
 In contrast, for the analysis of biological
@@
 properties \cite{yeatman2014lifespan}.
+\added{We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the supplementary material.
+For age regression, substantial differences between the datasets preclude generalization across all three:}
+\begin{enumerate*}[%
+    label=(\roman*),%
+    before=\unskip{: },%
+    itemjoin={{, }},%
+    itemjoin*={{, and }}]
+    \item \added{different acquisition parameters, which can be challenging to harmonize \mbox{\cite{pinto2020harmonization}}}
+    \item \added{different diffusion models, with DTI for the WH dataset and DKI for the HBN and Cam-CAN datasets}
+    \item \added{different age ranges and distributions (which is evident in the figure legends for \cref{fig:age-results}), with HBN being a developmental dataset, while WH and Cam-CAN are lifespan maturation datasets}
+    \item \added{different anatomical extents, with the WH streamlines truncated to remain with the bundle's bounding regions of interest (the default behavior in the legacy \texttt{mAFQ}) and the HBN and Cam-CAN streamlines allowed to retain their full extent from whole-brain tractography (the default behavior in \texttt{pyAFQ}).}
+\end{enumerate*}
+\added{In a biological characteristic that has widespread effects in the brain, validity is difficult to assess \mbox{\cite{lermausabiaga2019replication}}, so it is both unsurprising and vexing that we can do so well at predicting within each dataset, and yet do poorly in interpreting informative features across instruments.}
 

### 2021-04-20 reports/manuscript/supplemental.tex
ENH: Add notes on generalization in discussion section

@@
     \item different diffusion models, with DTI for the WH dataset and DKI for
-    the HBN dataset
+    the HBN and Cam-CAN datasets
     \item different age ranges and distributions (which is evident in the
-    figure legends), with HBN being a developmental dataset, while WH is a
-    lifespan maturation dataset
+    figure legends), with HBN being a developmental dataset, while WH and Cam-CAN are
+    lifespan maturation datasets
     \item different anatomical extents, with the WH streamlines truncated to
     remain with the bundle's bounding regions of interest (the default
-    behavior in the legacy \texttt{mAFQ}) and the HBN streamlines allowed
-    to retain their full extent from whole-brain tractography (the default
-    behavior in \texttt{pyAFQ}).
+    behavior in the legacy \texttt{mAFQ}) and the HBN and Cam-CAN streamlines
+    allowed to retain their full extent from whole-brain tractography (the
+    default behavior in \texttt{pyAFQ}).
 \end{enumerate*}

### 2021-04-20 reports/manuscript/paper_changes.tex
Replace pyAFQ citation with just citation to Kruper et al. preprint.

@@
 \added{As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.}
-
 In contrast, for the analysis of biological
@@
 integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ, kruper2021evaluating}, which extract
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{kruper2021evaluating}, which extract
 \replaced{tract profile}{tractometry} data from raw and processed dMRI datasets, as well as
@@
 Data from the HBN and Cam-CAN studies were processed using the updated Python
-Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{pyAFQ}). In
+Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{kruper2021evaluating}). In
 addition to demonstrating the our analysis pipeline is robust to changes in

### 2021-04-20 reports/manuscript/paper.tex
Adds a section on encoding and decoding.

@@
 Noah Simon\textsuperscript{3},
-Ariel Rokem\textsuperscript{4},
+Ariel Rokem\textsuperscript{1,4},
 \\
@@
 trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \cite{yeatman2012tract,
-colby2012, ODonnell2009-uu},
+samples along the length of each bundle \replaced{\mbox{{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}}}}{\mbox{\cite{yeatman2012tract,
+colby2012, ODonnell2009-uu}}},
 hereafter referred to as tract profiling.
@@
 information about the locations that are most informative for discriminative
-performance. To do so, we use a linear modeling approach, which aims to
-redict phenotypical variance in a group of subjects (or classify group
-membership), based on a linear combination of the features estimated with
-tract profiling.
+performance.
+ We approach differences between individuals through a ``decoding'' lens:
+We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling
+This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss}).
 
@@
 As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.
-
 In contrast, for the analysis of biological
@@
 integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ, kruper2021evaluating}, which extract
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{kruper2021evaluating}, which extract
 tract profile data from raw and processed dMRI datasets, as well as

### 2021-04-20 reports/manuscript/paper_changes.tex
Adds a section on encoding and decoding.

@@
 trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \cite{yeatman2012tract,
-colby2012, ODonnell2009-uu},
+samples along the length of each bundle \replaced{\mbox{{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}}}}{\mbox{\cite{yeatman2012tract,
+colby2012, ODonnell2009-uu}}},
 \added{hereafter referred to as tract profiling}.
@@
 information about the locations that are most informative for discriminative
-performance. To do so, we use a linear modeling approach, which aims to
-redict phenotypical variance in a group of subjects (or classify group
-membership), based on a linear combination of the features estimated with
-\replaced{tract profiling}{tractometry}.
+performance.
+\added{ We approach differences between individuals through a ``decoding'' lens:}
+We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}
+\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.
 

### 2021-04-20 reports/manuscript/paper_changes.tex
Line ending thingee.

@@
 We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}
-\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.
+\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.
 

### 2021-04-20 reports/manuscript/paper.tex
Adds some information about inference vs. prediction.

@@
 performance.
- We approach differences between individuals through a ``decoding'' lens:
-We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling
-This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss}).
+Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}.
+For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
+The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}.
+This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
+In the present work, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling.
 

### 2021-04-20 reports/manuscript/paper_changes.tex
Adds some information about inference vs. prediction.

--- 2021-04-20 reports/manuscript/paper_changes.tex
@@
 performance.
-\added{ We approach differences between individuals through a ``decoding'' lens:}
-We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}
-\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.
+\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}}.
+\added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
+The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}.
+This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
+In the present work}, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
 

### 2021-04-20 reports/manuscript/paper.tex
A few small things.

@@
 dataset, the SGL model has $\alpha = $ \alsLRatio
-and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca,
+~and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca,
 confirming that the white matter correlates of ALS reside mostly in one
@@
 regression task, we focus here on the prediction of biological age in three
-datasets named WH, HBN, and Cam-CAN (see the methods section for a description of each dataset). Prediction of ``brain
+datasets named WH, HBN, and Cam-CAN (see the Methods section for a description of each dataset). Prediction of ``brain
 age'' is a commonly undertaken task in neuroimaging machine learning, in part
@@
 {\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
-respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq},
-and {\camcanRsq}, respectively (see \cref{fig:age-results}, top panels). The
+respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq}, and {\camcanRsq},
+respectively (see \cref{fig:age-results}, top panels). The
 predictions for Cam-CAN are competitive with a recent state of the art
@@
 by developing our analysis infrastructure with fast, simple models, and substituting
-slower, more performant models afterward.
+slower, more performant models afterwards. The consistent \texttt{Scikit Learn}-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.
 

### 2021-04-20 reports/manuscript/paper_changes.tex
A few small things.

@@
 dataset, \added{the SGL model has} $\alpha = $ \alsLRatio
-\added{and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca},
+~\added{and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca},
 confirming that the white matter correlates of ALS reside mostly in one
@@
 the subjects in this procedure, with a median absolute error of {\whMae},
-{\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
-respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq},
-and {\camcanRsq}, respectively (see \cref{fig:age-results}, top panels). The
+\added{{\hbnMae}}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
+respectively and coefficients of determination $R^2 = $ {\whRsq} , \added{{\hbnRsq}}, and {\camcanRsq},
+respectively (see \cref{fig:age-results}, top panels). The
 predictions for Cam-CAN are competitive with a recent state of the art
@@
 \added{by developing our analysis infrastructure with fast, simple models, and substituting}
-\added{slower, more performant models afterward.}
+\added{slower, more performant models afterwards. The consistent \texttt{Scikit Learn}-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.}
 

### 2021-04-20 reports/manuscript/paper.tex
Small wording change.

@@
 performance.
-Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}.
+Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference about the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a particular phenotype.
 For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
@@
 This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
-In the present work, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling.
+In the present work, we predict the phenotypical variance in a group of subjects,or classify group membership, based on a linear combination of the features estimated with tract profiling.
 

### 2021-04-20 reports/manuscript/paper_changes.tex
Small wording change.

@@
 performance.
-\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}}.
+\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference about the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a particular phenotype}.
 \added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
@@
 This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
-In the present work}, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
+In the present work}, we predict the phenotypical variance in a group of subjects,or classify group membership, based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
 

### 2021-04-20 reports/manuscript/paper_changes.tex
More pointers to supplement.

@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups.
+right CST, plotted over the FA values for the control and ALS subject groups \added{(see supplemental Figures S1, S2 for tract profiles of all 18 tracts in these groups)}.
 We find that SGL \replaced{and PCR-SGL select}{selects} FA metrics in the corticospinal tract and
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see supplemental Figures S3-S8 for the full tract profile information in all tracts/datasets}.
 

### 2021-04-20 reports/manuscript/paper.tex
Add tractography details

--- 2021-04-20 reports/manuscript/paper.tex
@@
 Noah Simon\textsuperscript{3},
-Ariel Rokem\textsuperscript{1,4},
+Ariel Rokem\textsuperscript{4},
 \\
@@
 trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \replaced{\mbox{{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}}}}{\mbox{\cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}}},
+samples along the length of each bundle \cite{yeatman2012tract,
+colby2012, ODonnell2009-uu},
 hereafter referred to as tract profiling.
@@
 information about the locations that are most informative for discriminative
-performance.
-Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}.
-For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
-The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}.
-This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
-In the present work, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling.
+performance. To do so, we use a linear modeling approach, which aims to
+redict phenotypical variance in a group of subjects (or classify group
+membership), based on a linear combination of the features estimated with
+tract profiling.
 
@@
 integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{kruper2021evaluating}, which extract
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ, kruper2021evaluating}, which extract
 tract profile data from raw and processed dMRI datasets, as well as
@@
 eachseparate DWI scanning sequence.
-\end{itemize}
 
@@
 
+\item {\it MRtrix3 Reconstruction}
+
+Reconstruction was performed using \emph{QSIprep} 0.12.1.
+Multi-tissue fiber response functions were estimated using the dhollander algorithm.
+FODs were estimated via constrained spherical deconvolution (CSD, \mbox{\cite{originalcsd, tournier2008csd}) using an unsupervised multi-tissue method \mbox{\cite{dhollander2019response, dhollander2016unsupervised}}.
+Reconstruction was done using MRtrix3 \mbox{\cite{mrtrix3}}.
+FODs were intensity-normalized using mtnormalize \mbox{\cite{mtnormalize}}.}
+\end{itemize}
+
 Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
@@
 $\text{s} / \text{mm}^2$. The diffusion weighted images were acquired
-with a twice refocused spin-echo sequence and the same preprocessing pipeline
+with a twice refocused spin-echo sequence and the same preprocessing and reconstruction pipeline
 used for the HBN dataset was applied to this data. We will refer to this
@@
 Data from the ALS and WH studies was processed in a similar manner,
-using the Matlab Automated Fiber Quantification toolbox (\texttt{mAFQ})
+using the Matlab Automated Fiber Quantification toolbox
+(\texttt{mAFQ}, version 1.1 for WH and version 1.2 for ALS)
 \cite{yeatman2012tract}: streamlines representing fascicles of white
@@
 Data from the HBN and Cam-CAN studies were processed using the updated Python
-Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{kruper2021evaluating}). In
+Automated Fiber Quantification toolbox (\texttt{pyAFQ}; \cite{pyAFQ}). In
 addition to demonstrating the our analysis pipeline is robust to changes in

### 2021-04-20 reports/manuscript/paper_changes.tex
Add tractography details

--- 2021-04-20 reports/manuscript/paper_changes.tex
@@
 trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \replaced{\mbox{{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}}}}{\mbox{\cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}}},
+samples along the length of each bundle \cite{yeatman2012tract,
+colby2012, ODonnell2009-uu},
 \added{hereafter referred to as tract profiling}.
@@
 information about the locations that are most informative for discriminative
-performance.
-\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}}.
-\added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
-The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}.
-This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
-In the present work}, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
+performance. To do so, we use a linear modeling approach, which aims to
+redict phenotypical variance in a group of subjects (or classify group
+membership), based on a linear combination of the features estimated with
+\replaced{tract profiling}{tractometry}.
 
@@
 dataset, \added{the SGL model has} $\alpha = $ \alsLRatio 
-~\added{and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca},
+\added{and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca},
 confirming that the white matter correlates of ALS reside mostly in one
@@
 regression task, we focus here on the prediction of biological age in three
-datasets named WH, HBN, and Cam-CAN (see the Methods section for a description of each dataset). Prediction of ``brain
+datasets named WH, HBN, and Cam-CAN (see the methods section for a description of each dataset). Prediction of ``brain
 age'' is a commonly undertaken task in neuroimaging machine learning, in part
@@
 the subjects in this procedure, with a median absolute error of {\whMae},
-\added{{\hbnMae}}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
-respectively and coefficients of determination $R^2 = $ {\whRsq} , \added{{\hbnRsq}}, and {\camcanRsq},
-respectively (see \cref{fig:age-results}, top panels). The
+{\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
+respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq},
+and {\camcanRsq}, respectively (see \cref{fig:age-results}, top panels). The
 predictions for Cam-CAN are competitive with a recent state of the art
@@
 \added{by developing our analysis infrastructure with fast, simple models, and substituting}
-\added{slower, more performant models afterwards. The consistent \texttt{Scikit Learn}-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.}
+\added{slower, more performant models afterward.}
 
@@
 integrates within a broader automated fiber quantification software
-ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{kruper2021evaluating}, which extract
+ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{pyAFQ, kruper2021evaluating}, which extract
 \replaced{tract profile}{tractometry} data from raw and processed dMRI datasets, as well as
@@
 
+\item \added{{\it MRtrix3 Reconstruction}}
+
+\added{Reconstruction was performed using \emph{QSIprep} 0.12.1.
+Multi-tissue fiber response functions were estimated using the dhollander algorithm.
+FODs were estimated via constrained spherical deconvolution (CSD, \mbox{\cite{originalcsd, tournier2008csd}}) using an unsupervised multi-tissue method \mbox{\cite{dhollander2019response, dhollander2016unsupervised}}.
+Reconstruction was done using MRtrix3 \mbox{\cite{mrtrix3}}.
+FODs were intensity-normalized using mtnormalize \mbox{\cite{mtnormalize}}.}
+\end{itemize}
+
 Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
@@
 $\text{s} / \text{mm}^2$. The diffusion weighted images were acquired
-with a twice refocused spin-echo sequence and the same preprocessing pipeline
+with a twice refocused spin-echo sequence and the same preprocessing \added{and reconstruction} pipeline
 used for the HBN dataset was applied to this data. We will refer to this
@@
 Data from the ALS and WH studies was processed in a similar manner,
-using the Matlab Automated Fiber Quantification toolbox (\texttt{mAFQ})
+using the Matlab Automated Fiber Quantification toolbox
+(\texttt{mAFQ}\added{, version 1.1 for WH and version 1.2 for ALS})
 \cite{yeatman2012tract}: streamlines representing fascicles of white

### 2021-04-21 reports/manuscript/paper.tex
Add harmonization info and plots

@@
 One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.
-For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}.}
-While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}, they neglect anatomical grouping information.}
-We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using
-the most parsimonious representation of variance in the diffusion measures.
+For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}.
+While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}}, they neglect anatomical grouping information.
+We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using the most parsimonious representation of variance in the diffusion measures.
 In contrast, our SGL-based approach seeks to establish whether prior knowledge of anatomical grouping improves modeling of brain-phenotype relationships.
-Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of
-the original feature space. We demonstrate circumstances in which this approach both helps and hinders predictive performance.
+Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of the original feature space.
+We demonstrate circumstances in which this approach both helps and hinders predictive performance.}
 
@@
 engineering.
-We also predicted ALS diagnosis using the PCR-SGL, wherein each
-group of features is independently transformed to its PC basis and
-an SGL model is fit to the transformed features. This model achieves
-\protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}
-(\cref{fig:class-results:probs}). In addition to this
-classification performance, both SGL and PCR-SGL also identify
+We also predicted ALS diagnosis using the PCR-SGL, wherein each group of features is independently transformed to its PC basis and an SGL model is fit to the transformed features.
+This model achieves \protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}
+(\cref{fig:class-results:probs}). In addition to this classification
+performance, both SGL and PCR-SGL also identify
 the white matter tracts most important for ALS classification.
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups.
+right CST, plotted over the FA values for the control and ALS subject groups (see supplemental Figures S1, S2 for tract profiles of all 18 tracts in these groups).
 We find that SGL and PCR-SGL select FA metrics in the corticospinal tract and
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see supplemental Figures S3-S8 for the full tract profile information in all tracts/datasets.
 
@@
 
-Another limitation of our approach is in its computational execution time,
-which, in our experience, is roughly five times slower than simpler models
-like the lasso. This slow-down is likely to be insignificant for ``production''
-cycles in which researchers report their findings, but may be prohibitive
-for ``development'' cycles in which researchers repeatedly train models while
-adjusting their analysis pipeline. In practice, we circumvent this limitation
-by developing our analysis infrastructure with fast, simple models, and substituting
-slower, more performant models afterwards. The consistent \texttt{Scikit Learn}-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.
+Another limitation of our approach is in its computational execution time, which, in our experience, is roughly five times slower than simpler models like the lasso.
+This slow-down is likely to be insignificant for ``production'' cycles in which researchers report their findings, but may be prohibitive for ``development'' cycles in which researchers repeatedly train models while adjusting their analysis pipeline.
+In practice, we circumvent this limitation by developing our analysis infrastructure with fast, simple models, and substituting slower, more performant models afterwards.
+The consistent scikit-learn-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.
 
@@
 $\text{s} / \text{mm}^2$. The diffusion weighted images were acquired
-with a twice refocused spin-echo sequence and the same preprocessing and reconstruction pipeline
+with a twice refocused spin-echo sequence and the same preprocessing
+and reconstruction pipelines
 used for the HBN dataset was applied to this data. We will refer to this
@@
 which are enumerated in the supplemental material.
-See Figure S3 of \mbox{\cite{kruper2021evaluating} for}
-a depiction of these white matter bundles.
+See Figure S3 of \mbox{\cite{kruper2021evaluating} for a depiction of these white matter bundles.}
 Here,
@@
 based on other quantitative MRI measurements can also be used.
-The resulting feature space was the same for all four datasets, with
-the FA and MD metrics at each of 100 nodes in eighteen bundles
-comprising 3600 features per subject.
+The resulting feature space was the same for all four datasets, with the FA and MD metrics at each of 100 nodes in eighteen bundles comprising 3600 features per subject.
 These bundle profiles, along with the phenotypical data we wish to explain
@@
 variables (see \cref{fig:methods:group-structure}).
+
+\subsubsection*{Data harmonization for HBN}
+
+For the multisite HBN study, we use the ComBat harmonization method to robustly adjust for site effects in the tract profiles.
+Initially designed to correct for site effects in gene expression studies \mbox{\cite{johnson2007adjusting}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \mbox{\cite{fortin2018harmonization}}, multi-site DTI studies \mbox{\cite{fortin2017harmonization}}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \mbox{\cite{nielson2018detecting}}.
+We rely on the \texttt{neurocombat\_sklearn} library \mbox{\cite{neurocombat_sklearn}}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences in the supplemental material.}
 
@@
 
-SGL may be combined with principal components regression (PCR-SGL) by
-performing dimensionality reduction separately for each group of covariates.
-Let
+SGL may be combined with principal components regression (PCR-SGL) by performing dimensionality reduction separately for each group of covariates. Let
 \begin{equation}
@@
 \end{equation}
-be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$,
-the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group
-\protect$\ell$. Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where
-\protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of
-\protect$\mathbf{X}^{(\ell)}$. \protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal
-matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$. The product
-\protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the
-principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$
-in the basis provided by \protect$\mathbf{V}^T$.
-
-Since this decomposition is performed separately for each group of covariates,
-the grouping information is preserved in the transformation from \protect$\mathbf{X}$
-to \protect$\mathbf{Z}$. We may then build an SGL model relating \protect$y$
-and \protect$\mathbf{Z}$,
+be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$, the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group \protect$\ell$.
+Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where \protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of \protect$\mathbf{X}^{(\ell)}$.
+\protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$.
+The product \protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$ in the basis provided by \protect$\mathbf{V}^T$.
+
+Since this decomposition is performed separately for each group of covariates, the grouping information is preserved in the transformation from \protect$\mathbf{X}$ to \protect$\mathbf{Z}$.
+We may then build an SGL model relating \protect$y$ and \protect$\mathbf{Z}$,
 
@@
 \end{align}
-The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the
-original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.
+The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.
 
@@
 applied to the data before fitting the linear coefficients.
-This is similar to the use of a link function in a generalized
-linear model, but without the adoption of an exponential probability
-distribution \mbox{\cite{nelder1972technique}.}
+This is similar to the use of a link function in a generalized linear model, but without the adoption of an exponential probability distribution \mbox{\cite{nelder1972technique}.}
 For the WH, HBN, and Cam-CAN datasets, we use a
@@
 \end{equation}
-implemented using scikit-learn's \lstinline|TransformedTargetRegressor|
-meta-estimator \mbox{\cite{scikit-learn}}
-with numpy's \lstinline|log| and \lstinline|exp| as the transform and
-inverse transform functions, respectively \mbox{\cite{harris2020array}.}
+implemented using scikit-learn's \lstinline|TransformedTargetRegressor| meta-estimator \mbox{\cite{scikit-learn} with numpy's \lstinline|log| and \lstinline|exp| as the transform and inverse transform functions, respectively \mbox{\cite{harris2020array}}.}
 

### 2021-04-21 reports/manuscript/paper_changes.tex
Add harmonization info and plots

@@
 
-\added{One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.}
-\added{For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}}.}
-\added{While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}}, they neglect anatomical grouping information.}
-\added{We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using}
-\added{the most parsimonious representation of variance in the diffusion measures.
-In contrast, our SGL-based approach seeks to establish whether prior knowledge of anatomical grouping improves modeling of brain-phenotype relationships.}
-\added{Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of}
-\added{the original feature space. We demonstrate circumstances in which this approach both helps and hinders predictive performance.}
+\added{One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.
+For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}}.
+While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}}, they neglect anatomical grouping information.
+We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using the most parsimonious representation of variance in the diffusion measures.
+In contrast, our SGL-based approach seeks to establish whether prior knowledge of anatomical grouping improves modeling of brain-phenotype relationships.
+Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of the original feature space.
+We demonstrate circumstances in which this approach both helps and hinders predictive performance.}
 
@@
 engineering.
-\added{We also predicted ALS diagnosis using the PCR-SGL, wherein each}
-\added{group of features is independently transformed to its PC basis and}
-\added{an SGL model is fit to the transformed features. This model achieves}
-\added{\protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}}
-(\cref{fig:class-results:probs}). In addition to this
-classification performance, both SGL \added{and PCR-SGL} also \replaced{identify}{identifies}
+\added{We also predicted ALS diagnosis using the PCR-SGL, wherein each group of features is independently transformed to its PC basis and an SGL model is fit to the transformed features.
+This model achieves \protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}}
+(\cref{fig:class-results:probs}). In addition to this classification
+performance, both SGL \added{and PCR-SGL} also \replaced{identify}{identifies}
 the white matter tracts most important for ALS classification.
@@
 over simpler sparsity-inducing regression strategies.
-\added{The relatively poor performance of Lasso PCR suggests that features with small variance are nonetheless relevant for predicting ALS diagnosis.}
-\added{Or equivalently, that group differences between ALS diagnoses are not the dominant source of variance in the diffusion metrics.}
+\added{The relatively poor performance of Lasso PCR suggests that features with small variance are nonetheless relevant for predicting ALS diagnosis.
+Or equivalently, that group differences between ALS diagnoses are not the dominant source of variance in the diffusion metrics.}
 
@@
 
-\added{Another limitation of our approach is in its computational execution time,}
-\added{which, in our experience, is roughly five times slower than simpler models}
-\added{like the lasso. This slow-down is likely to be insignificant for ``production''}
-\added{cycles in which researchers report their findings, but may be prohibitive}
-\added{for ``development'' cycles in which researchers repeatedly train models while}
-\added{adjusting their analysis pipeline. In practice, we circumvent this limitation}
-\added{by developing our analysis infrastructure with fast, simple models, and substituting}
-\added{slower, more performant models afterwards. The consistent \texttt{Scikit Learn}-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.}
+\added{Another limitation of our approach is in its computational execution time, which, in our experience, is roughly five times slower than simpler models like the lasso.
+This slow-down is likely to be insignificant for ``production'' cycles in which researchers report their findings, but may be prohibitive for ``development'' cycles in which researchers repeatedly train models while adjusting their analysis pipeline.
+In practice, we circumvent this limitation by developing our analysis infrastructure with fast, simple models, and substituting slower, more performant models afterwards.
+The consistent scikit-learn-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.}
 
@@
 $\text{s} / \text{mm}^2$. The diffusion weighted images were acquired
-with a twice refocused spin-echo sequence and the same preprocessing \added{and reconstruction} pipeline
+with a twice refocused spin-echo sequence and the same preprocessing
+\replaced{and reconstruction pipelines}{pipeline}
 used for the HBN dataset was applied to this data. We will refer to this
@@
 which are enumerated in the supplemental material.
-\added{See Figure S3 of \mbox{\cite{kruper2021evaluating}} for}
-\added{a depiction of these white matter bundles.}
+\added{See Figure S3 of \mbox{\cite{kruper2021evaluating}} for a depiction of these white matter bundles.}
 Here,
@@
 based on other quantitative MRI measurements can also be used.
-\added{The resulting feature space was the same for all four datasets, with}
-\added{the FA and MD metrics at each of 100 nodes in eighteen bundles}
-\added{comprising 3600 features per subject.}
+\added{The resulting feature space was the same for all four datasets, with the FA and MD metrics at each of 100 nodes in eighteen bundles comprising 3600 features per subject.}
 These bundle profiles, along with the phenotypical data we wish to explain
@@
 variables (\replaced{see}{See} \cref{fig:methods:group-structure}).
+
+\subsubsection*{\added{Data harmonization for HBN}}
+
+\added{For the multisite HBN study, we use the ComBat harmonization method to robustly adjust for site effects in the tract profiles.
+Initially designed to correct for site effects in gene expression studies \mbox{\cite{johnson2007adjusting}}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \mbox{\cite{fortin2018harmonization}}, multi-site DTI studies \mbox{\cite{fortin2017harmonization}}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \mbox{\cite{nielson2018detecting}}.
+We rely on the \texttt{neurocombat\_sklearn} library \mbox{\cite{neurocombat_sklearn}}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences in the supplemental material.}
 
@@
 
-\added{SGL may be combined with principal components regression (PCR-SGL) by}
-\added{performing dimensionality reduction separately for each group of covariates.}
-\added{Let}
+\added{SGL may be combined with principal components regression (PCR-SGL) by performing dimensionality reduction separately for each group of covariates. Let}
 \begin{equation}
@@
 \end{equation}
-\added{be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$,}
-\added{the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group}
-\added{\protect$\ell$. Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where}
-\added{\protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of}
-\added{\protect$\mathbf{X}^{(\ell)}$. \protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal}
-\added{matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$. The product}
-\added{\protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the}
-\added{principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$}
-\added{in the basis provided by \protect$\mathbf{V}^T$.}
-
-\added{Since this decomposition is performed separately for each group of covariates,}
-\added{the grouping information is preserved in the transformation from \protect$\mathbf{X}$}
-\added{to \protect$\mathbf{Z}$. We may then build an SGL model relating \protect$y$}
-\added{and \protect$\mathbf{Z}$,}
+\added{be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$, the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group \protect$\ell$.
+Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where \protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of \protect$\mathbf{X}^{(\ell)}$.
+\protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$.
+The product \protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$ in the basis provided by \protect$\mathbf{V}^T$.}
+
+\added{Since this decomposition is performed separately for each group of covariates, the grouping information is preserved in the transformation from \protect$\mathbf{X}$ to \protect$\mathbf{Z}$.
+We may then build an SGL model relating \protect$y$ and \protect$\mathbf{Z}$,}
 
@@
 \end{align}
-\added{The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the}
-\added{original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.}
+\added{The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.}
 
@@
 applied to the data before fitting the linear coefficients.
-\added{This is similar to the use of a link function in a generalized}
-\added{linear model, but without the adoption of an exponential probability}
-\added{distribution \mbox{\cite{nelder1972technique}}.}
+\added{This is similar to the use of a link function in a generalized linear model, but without the adoption of an exponential probability distribution \mbox{\cite{nelder1972technique}}.}
 For \deleted{example, for} the WH, HBN, and Cam-CAN datasets, we use a
@@
 \end{equation}
-\added{implemented using scikit-learn's \lstinline|TransformedTargetRegressor|}
-\added{meta-estimator \mbox{\cite{scikit-learn}}}
-\added{with numpy's \lstinline|log| and \lstinline|exp| as the transform and}
-\added{inverse transform functions, respectively \mbox{\cite{harris2020array}}.}
+\added{implemented using scikit-learn's \lstinline|TransformedTargetRegressor| meta-estimator \mbox{\cite{scikit-learn}} with numpy's \lstinline|log| and \lstinline|exp| as the transform and inverse transform functions, respectively \mbox{\cite{harris2020array}}.}
 

### 2021-04-21 reports/manuscript/supplemental_changes.tex
Add harmonization info and plots

--- 2021-04-20 reports/manuscript/supplemental.tex
@@
 \usepackage{xcolor}
+
+\usepackage[commentmarkup=footnote]{changes}
 
@@
 
+\section{\added{Data harmonization in the HBN dataset}}
+
+\added{\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
+We see strong site differences in both FA and MD profiles.
+Conversely, \cref{fig:hbn-site-age-dist} shows that the age distributions at each site are similar.
+ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_site_age_distributions.pdf}
+    \caption{%
+        {%
+            \bf Age distributions are similar between the different
+            HBN sites.
+        }
+        \label{fig:hbn-site-age-dist}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_site_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles
+            exhibit strong site differences in the HBN dataset.
+        }
+        \label{fig:hbn-site-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_site_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Mean diffusivity (MD) bundle profiles
+            exhibit strong site differences in the HBN dataset.
+        }
+        \label{fig:hbn-site-bp:md}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_harmonized_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Site differences in fractional anisotropy (FA)
+            do not survive ComBat harmonization.
+        }
+        \label{fig:hbn-harmonized-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_harmonized_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Site differences in mean diffusivity (MD)
+            do not survive ComBat harmonization.
+        }
+        \label{fig:hbn-harmonized-bp:md}
+    }
+\end{figure}
+
+\pagebreak
+
 \bibliography{paper}

### 2021-04-23 reports/manuscript/paper.tex

@@
 \usepackage[capitalize]{cleveref}
+\crefformat{equation}{Eq~(#2#1#3)}
+\crefrangeformat{equation}{Eqs~(#3#1#4) to~(#5#2#6)}
+\crefmultiformat{equation}{Eqs~(#2#1#3)}%
+{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
+\crefformat{figure}{Fig~#2#1#3}
+\crefrangeformat{figure}{Figs~#3#1#4 to~#5#2#6}
+\crefmultiformat{figure}{Figs~#2#1#3}%
+{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
+
 \usepackage[inline]{enumitem}
@@
 diffusion of water in each voxel
-\replaced{\mbox{\cite{stejskal1965spin, wandell2016clarifying}}}{\mbox{\cite{wandell2016clarifying}}}.
+\cite{stejskal1965spin, wandell2016clarifying}.
 % While the measurements are usually conducted
@@
 trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \replaced{\mbox{{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}}}}{\mbox{\cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}}},
+samples along the length of each bundle
+\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu},
 hereafter referred to as tract profiling.
@@
 statistical power is compromised by a multiple comparison problem
-\replaced{\mbox{\cite{colby2012, Nichols2002-zu, Nichols2003-yy, chamberland2019dimensionality}}}{\mbox{\cite{colby2012, Nichols2002-zu, Nichols2003-yy}}}.
+\cite{colby2012, Nichols2002-zu, Nichols2003-yy, chamberland2019dimensionality}.
 An alternative that
@@
 One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.
-For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}.
-While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}}, they neglect anatomical grouping information.
+For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \cite{powell2018local, rasero2021integrating}.
+While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \cite{chamberland2019dimensionality}, they neglect anatomical grouping information.
 We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using the most parsimonious representation of variance in the diffusion measures.
@@
 Motivated by this distinction, we also introduce a union of the two approaches called PCR-SGL, in which each group of features is independently transformed into its PC basis, thereby retaining the anatomical grouping information of the original feature space.
-We demonstrate circumstances in which this approach both helps and hinders predictive performance.}
+We demonstrate circumstances in which this approach both helps and hinders predictive performance.
 
@@
 the white matter tracts most important for ALS classification.
-\Cref{fig:class-results:coefs3d} shows that PCR-SGL identified as potential disease biomarkers the diffusion measures in the CST from the cerebral peduncle to the corona radiata, agreeing with the previous study from which these data were extracted \mbox{\cite{sarica2017corticospinal}.}
+\Cref{fig:class-results:coefs3d} shows that PCR-SGL identified as potential disease biomarkers the diffusion measures in the CST from the cerebral peduncle to the corona radiata, agreeing with the previous study from which these data were extracted \cite{sarica2017corticospinal}.
 The relative importance of white matter
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups (see supplemental Figures S1, S2 for tract profiles of all 18 tracts in these groups).
+right CST, plotted over the FA values for the control and ALS subject groups (see supplemental Figs S1 and S2 for tract profiles of all 18 tracts in these groups).
 We find that SGL and PCR-SGL select FA metrics in the corticospinal tract and
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see supplemental Figures S3-S8 for the full tract profile information in all tracts/datasets.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see supplemental Figs S3 to S8 for the full tract profile information in all tracts/datasets.
 
@@
 \cref{fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d}
-and supporing Figures in \nameref{S1_Appendix}).
+and supporing figures in \nameref{S1_Appendix}).
 This demonstrates that SGL is not coerced to produce overly sparse results
@@
     itemjoin*={{, and }}]
-    \item different acquisition parameters, which can be challenging to harmonize \mbox{\cite{pinto2020harmonization}}
+    \item different acquisition parameters, which can be challenging to harmonize \cite{pinto2020harmonization}
     \item different diffusion models, with DTI for the WH dataset and DKI for the HBN and Cam-CAN datasets
@@
 \end{enumerate*}
-In a biological characteristic that has widespread effects in the brain, validity is difficult to assess \mbox{\cite{lermausabiaga2019replication}, so it is both unsurprising and vexing that we can do so well at predicting within each dataset, and yet do poorly in interpreting informative features across instruments.}
+In a biological characteristic that has widespread effects in the brain, validity is difficult to assess \cite{lermausabiaga2019replication}, so it is both unsurprising and vexing that we can do so well at predicting within each dataset, and yet do poorly in interpreting informative features across instruments.
 
@@
 Multi-tissue fiber response functions were estimated using the dhollander algorithm.
-FODs were estimated via constrained spherical deconvolution (CSD, \mbox{\cite{originalcsd, tournier2008csd}) using an unsupervised multi-tissue method \mbox{\cite{dhollander2019response, dhollander2016unsupervised}}.
-Reconstruction was done using MRtrix3 \mbox{\cite{mrtrix3}}.
-FODs were intensity-normalized using mtnormalize \mbox{\cite{mtnormalize}}.}
+FODs were estimated via constrained spherical deconvolution (CSD, \cite{originalcsd, tournier2008csd}) using an unsupervised multi-tissue method \cite{dhollander2019response, dhollander2016unsupervised}.
+Reconstruction was done using MRtrix3 \cite{mrtrix3}.
+FODs were intensity-normalized using mtnormalize \cite{mtnormalize}.
 \end{itemize}
@@
 which are enumerated in the supplemental material.
-See Figure S3 of \mbox{\cite{kruper2021evaluating} for a depiction of these white matter bundles.}
+See Fig S3 of \cite{kruper2021evaluating} for a depiction of these white matter bundles.
 Here,
@@
 For the multisite HBN study, we use the ComBat harmonization method to robustly adjust for site effects in the tract profiles.
-Initially designed to correct for site effects in gene expression studies \mbox{\cite{johnson2007adjusting}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \mbox{\cite{fortin2018harmonization}}, multi-site DTI studies \mbox{\cite{fortin2017harmonization}}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \mbox{\cite{nielson2018detecting}}.
-We rely on the \texttt{neurocombat\_sklearn} library \mbox{\cite{neurocombat_sklearn}}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences in the supplemental material.}
+Initially designed to correct for site effects in gene expression studies \cite{johnson2007adjusting}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \cite{fortin2018harmonization}, multi-site DTI studies \cite{fortin2017harmonization}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \cite{nielson2018detecting}.
+We rely on the \texttt{neurocombat\_sklearn} library \cite{neurocombat_sklearn}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences in the supplemental material.
 
@@
 applied to the data before fitting the linear coefficients.
-This is similar to the use of a link function in a generalized linear model, but without the adoption of an exponential probability distribution \mbox{\cite{nelder1972technique}.}
+This is similar to the use of a link function in a generalized linear model, but without the adoption of an exponential probability distribution \cite{nelder1972technique}.
 For the WH, HBN, and Cam-CAN datasets, we use a
@@
 \end{equation}
-implemented using scikit-learn's \lstinline|TransformedTargetRegressor| meta-estimator \mbox{\cite{scikit-learn} with numpy's \lstinline|log| and \lstinline|exp| as the transform and inverse transform functions, respectively \mbox{\cite{harris2020array}}.}
+implemented using scikit-learn's \lstinline|TransformedTargetRegressor| meta-estimator \cite{scikit-learn} with numpy's \lstinline|log| and \lstinline|exp| as the transform and inverse transform functions, respectively \cite{harris2020array}.
 

### 2021-04-23 reports/manuscript/paper_changes.tex

@@
 trajectory of each bundle. This justifies retaining the individual
-samples along the length of each bundle \replaced{\mbox{{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}}}}{\mbox{\cite{yeatman2012tract,
-colby2012, ODonnell2009-uu}}},
+samples along the length of each bundle
+\replaced{\mbox{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}},}{\mbox{\cite{yeatman2012tract, colby2012, ODonnell2009-uu}},}
 \added{hereafter referred to as tract profiling}.
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups \added{(see supplemental Figures S1, S2 for tract profiles of all 18 tracts in these groups)}.
+right CST, plotted over the FA values for the control and ALS subject groups \added{(see supplemental Figs S1 and S2 for tract profiles of all 18 tracts in these groups)}.
 We find that SGL \replaced{and PCR-SGL select}{selects} FA metrics in the corticospinal tract and
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see supplemental Figures S3-S8 for the full tract profile information in all tracts/datasets}.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see supplemental Figs S3 to S8 for the full tract profile information in all tracts/datasets}.
 
@@
 which are enumerated in the supplemental material.
-\added{See Figure S3 of \mbox{\cite{kruper2021evaluating}} for a depiction of these white matter bundles.}
+\added{See Fig S3 of \mbox{\cite{kruper2021evaluating}} for a depiction of these white matter bundles.}
 Here,

### 2021-04-23 reports/manuscript/supplemental.tex

@@
 
+\section{Data harmonization in the HBN dataset}
+
+\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
+We see strong site differences in both FA and MD profiles.
+Conversely, \cref{fig:hbn-site-age-dist} shows that the age distributions at each site are similar.
+ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_site_age_distributions.pdf}
+    \caption{%
+        {%
+            \bf Age distributions are similar between the different
+            HBN sites.
+        }
+        \label{fig:hbn-site-age-dist}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_site_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Fractional anisotropy (FA) bundle profiles
+            exhibit strong site differences in the HBN dataset.
+        }
+        \label{fig:hbn-site-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_site_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Mean diffusivity (MD) bundle profiles
+            exhibit strong site differences in the HBN dataset.
+        }
+        \label{fig:hbn-site-bp:md}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_harmonized_profiles_fa.pdf}
+    \caption{%
+        {%
+            \bf Site differences in fractional anisotropy (FA)
+            do not survive ComBat harmonization.
+        }
+        \label{fig:hbn-harmonized-bp:fa}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{hbn_harmonized_profiles_md.pdf}
+    \caption{%
+        {%
+            \bf Site differences in mean diffusivity (MD)
+            do not survive ComBat harmonization.
+        }
+        \label{fig:hbn-harmonized-bp:md}
+    }
+\end{figure}
+
+\pagebreak
+
 \bibliography{paper}

### 2021-04-23 reports/manuscript/paper.tex
Remove figures from main text so that we can add them as separate attachements in the submission system

@@
 \begin{figure}[b!]
-    \vspace{0.25cm}
-    \rlap{
-        \hspace{-0.25em}
-        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    }
-    \vspace{-8.4cm}
-    \includegraphics[width=\columnwidth]{method-quad.pdf}
+    % \vspace{0.25cm}
+    % \rlap{
+    %     \hspace{-0.25em}
+    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    % }
+    % \vspace{-8.4cm}
+    % \includegraphics[width=\columnwidth]{method-quad.pdf}
     {\phantomsubcaption\label{fig:methods:tractogram}}
@@
 \begin{figure}[t!]
-    \vspace{3.0cm}
-    \rlap{
-        \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
-    }
-    \vspace{-7.0cm}
-    \includegraphics[width=\textwidth]{als_gpca_results.pdf}
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
+    % }
+    % \vspace{-7.0cm}
+    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
     {\phantomsubcaption\label{fig:class-results:probs}}
@@
 \begin{figure}[t!]
-    \vspace{3.0cm}
-    \rlap{
-        \hspace{0.775cm}
-        \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
-        \hspace{0.5em}
-        \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
-        \hspace{0.5em}
-        \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
-    }
-    \vspace{-6.1cm}
-    \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \hspace{0.775cm}
+    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
+    % }
+    % \vspace{-6.1cm}
+    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
     {\phantomsubcaption\label{fig:age-results:wh-scatter}}
@@
 \begin{figure}[t!]
-    \includegraphics[width=\textwidth]{model_performance.pdf}
+    % \includegraphics[width=\textwidth]{model_performance.pdf}
     \caption{%
@@
 \begin{figure}[t]
-    \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
+    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
     \caption{{\bf Nested cross-validation}

### 2021-04-28 reports/manuscript/paper.tex
Move figure captions to the end.

@@
 
-\begin{figure}[b!]
-    % \vspace{0.25cm}
-    % \rlap{
-    %     \hspace{-0.25em}
-    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    % }
-    % \vspace{-8.4cm}
-    % \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{\textbf{Tractometry data flow}
-        \label{fig:methods}
-        \textbf{(a)} Whole brain tractography generates streamlines approximating
-        the trajectories of white matter connections.
-        \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
-        In this case, we show the left corticospinal tract (CSTL)
-        and the left arcuate fasciculus (ARCL)
-        over a mid-saggital anatomical slice.
-        Tract profiling further extracts bundle profiles,
-        quantifications of various diffusion metrics along the length of the
-        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for \textbf{(c)} the CSTL and \textbf{(d)} the ARCL.
-        \textbf{(d)} the phenotypical target data and tract profile
-        features can be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the CSTL, the middle (green) group
-        contains $k$ features from the left cingulum cingulate (CGCL),
-        and the right (blue) group
-        contains $k$ features from the ARCL.
-        The coefficients in $\hat{\beta}$ follow the same natural grouping.
-    }
-\end{figure}
-
 The present work aims to balance predictive accuracy with descriptive power
@@
 
-\begin{figure}[t!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
-    % }
-    % \vspace{-7.0cm}
-    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
-    {\phantomsubcaption\label{fig:class-results:probs}}
-    {\phantomsubcaption\label{fig:class-results:coefs3d}}
-    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
-    {\phantomsubcaption\label{fig:class-results:false-positives}}
-    {\phantomsubcaption\label{fig:class-results:false-negatives}}
-    \caption{%
-        {\bf PCR-SGL accurately and interpretably predicts ALS diagnosis.}
-        \label{fig:class-results}
-        {\bf (a)} Classification probabilities for ALS diagnosis, with
-        controls on the left, patients on the right, predicted controls in
-        blue, and predicted patients in orange. That is, orange dots on the left
-        represent false positives, while blue dots on the right represent
-        false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
-        ROC AUC of {\protect\alsRocAuc}.
-        {\bf (b)} PCR-SGL coefficients are presented on the core fibers of major
-        fiber bundles. They exhibit high group sparsity and are concentrated
-        in the FA of the corticospinal tract (CST).
-        The brain is oriented with the right hemisphere
-        in the foreground and anterior to the right of the page. The CSTL, CSTR,
-        callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)
-        bundles are indicated for orientation.
-        {\bf (c)} PCR-SGL identifies three portions of the CST as important,
-        where $\hat{\beta}$ (dashed line, right axis) has large values. These
-        are centered around nodes 30, 65, and 90, corresponding to locations
-        of substantial differences in FA between the ALS and control groups
-        (shaded areas indicates standard error of the mean).
-        {\bf (d)} Bundle profiles for false positive classifications. Line
-        colors correspond to the marker edge color in the top left plot.
-        These individuals have reduced FA in the CST portions which SGL
-        identified as important. Their misclassification is coherent with the
-        feature importance and the group differences in FA.
-        {\bf (e)} Individual bundle profiles for false negative
-        classifications. These individuals have bundle profiles which
-        oscillate between the group means.
-    }
-\end{figure}
-
 To assess the added value of incorporating anatomical knowledge into our
@@
 imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see supplemental Figs S3 to S8 for the full tract profile information in all tracts/datasets.
-
-\begin{figure}[t!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \hspace{0.775cm}
-    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
-    % }
-    % \vspace{-6.1cm}
-    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
-    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
-    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
-    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
-    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:wh-profile}}
-    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
-    {\phantomsubcaption\label{fig:age-results:cc-profile}}
-    \caption{%
-        {\bf Predicting age with tractometry and SGL.}
-        \label{fig:age-results}
-        {\bf (top)} The predicted age vs. true age of each individual from the test
-        splits (i.e., when each subject's data was held out in fitting the
-        model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
-        datasets; an accurate prediction falls close to the $y=x$ line
-        (dashed). The mean absolute error (MAE) and coefficient of
-        determination $R^2$ are presented in the lower right of each scatter
-        plot.
-        {\bf (middle)} Feature importance for predicting age from
-        tract profile in
-        the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
-        The orientation of the
-        brain is that same as in \cref{fig:class-results:coefs3d}, however because
-        the coefficients exhibit high global sparsity (as opposed to group
-        sparsity), we plot the mean of the absolute value of $\hat{\beta}$
-        for each bundle on the core fiber. The global distrubution of the
-        $\hat{\beta}$ coefficients reflects the fact that aging is not
-        confined to a single white matter bundle.
-        {\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
-        {\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
-    }
-\end{figure}
 
@@
 
-\begin{figure}[t!]
-    % \includegraphics[width=\textwidth]{model_performance.pdf}
-    \caption{%
-        {\bf Model performance across all datasets.}
-        \label{fig:model-performance}
-        Each panel shows model performance measured on the test set for each
-        cross-validation split, with each black dot representing a split, box
-        plots representing the quartiles, and white diamonds representing the mean
-        performance. The $y$-scale varies in each subplot.
-        \textbf{(a)} Accuracy of test set predictions for the
-        ALS dataset. Because group differences
-        in ALS diagnosis are mostly confined to a single bundle, the group
-        structure-preserving methods, SGL and PCR-SGL, outperform the other
-        models.
-        The remaining frames show coefficient of determination, \protect$R^2$ in test sets
-        for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN
-        datasets. Because aging affects the white matter globally, group structure-blind
-        methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL
-        models show competitve predictive performance, adapting to a problem where
-        group structure is not as informative. PCR-SGL performs poorly in this regime
-        because its initial group-wise PC projection destroys between bundle covariance.
-        The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.
-    }
-\end{figure}
 Model performance across all four datasets and all six model types is summarized
@@
 
-\begin{figure}[t]
-    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
-    \caption{{\bf Nested cross-validation}
-        \label{fig:nested-cross-val}
-        We evaluate model quality using a nested $k$-fold cross validation
-        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
-        groups and optimal hyperparameters are found for the level-0 training
-        set. To avoid overfitting, the optimal hyperparameters are themselves
-        evaluated using a cross-validation scheme taking place at level-1 of
-        the decomposition, where each level-0 training set is further
-        decomposed into $k_1 = 3$ shuffled groups. In the classification
-        case, the training and test splits are stratified by diagnosis. For
-        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
-        $k_0 = 5$.
-    }
-\end{figure}
-
 To objectively evaluate model performance and guard against over-fitting,
@@
 % step-by-step instructions.
+
+\newpage
+
+\section*{Figure legends}
+
+\begin{figure}[b!]
+    % \vspace{0.25cm}
+    % \rlap{
+    %     \hspace{-0.25em}
+    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    % }
+    % \vspace{-8.4cm}
+    % \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \phantomcaption{\label{fig:methods}}
+\end{figure}
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
+    % }
+    % \vspace{-7.0cm}
+    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
+    {\phantomsubcaption\label{fig:class-results:probs}}
+    {\phantomsubcaption\label{fig:class-results:coefs3d}}
+    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
+    {\phantomsubcaption\label{fig:class-results:false-positives}}
+    {\phantomsubcaption\label{fig:class-results:false-negatives}}
+    \phantomcaption{%
+    \label{fig:class-results}
+    }
+\end{figure}
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \hspace{0.775cm}
+    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
+    % }
+    % \vspace{-6.1cm}
+    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
+    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
+    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
+    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:wh-profile}}
+    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
+    {\phantomsubcaption\label{fig:age-results:cc-profile}}
+    \phantomcaption{%
+    \label{fig:age-results}
+    }
+\end{figure}
+
+\begin{figure}[b!]
+    % \includegraphics[width=\textwidth]{model_performance.pdf}
+    \phantomcaption{%
+    \label{fig:model-performance}
+    }
+\end{figure}
+
+\begin{figure}[h!]
+    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
+    \phantomcaption{
+    \label{fig:nested-cross-val}
+    }
+\end{figure}
+
+\paragraph{Figure 1: Tractometry data flow}
+\textbf{(a)} Whole brain tractography generates streamlines approximating
+    the trajectories of white matter connections.
+    \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
+    In this case, we show the left corticospinal tract (CSTL)
+    and the left arcuate fasciculus (ARCL)
+    over a mid-saggital anatomical slice.
+    Tract profiling further extracts bundle profiles,
+    quantifications of various diffusion metrics along the length of the
+    fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+    profile for \textbf{(c)} the CSTL and \textbf{(d)} the ARCL.
+    \textbf{(d)} the phenotypical target data and tract profile
+    features can be organized into a linear model, $\hat{y} = \mathbf{X}
+    \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+    to reveal a natural group structure: the left (orange) group
+    contains $k$ features from the CSTL, the middle (green) group
+    contains $k$ features from the left cingulum cingulate (CGCL),
+    and the right (blue) group
+    contains $k$ features from the ARCL.
+    The coefficients in $\hat{\beta}$ follow the same natural grouping.
+Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})
+
+\paragraph{Figure 2: PCR-SGL accurately and interpretably predicts ALS diagnosis.}
+{\bf (a)} Classification probabilities for ALS diagnosis, with
+controls on the left, patients on the right, predicted controls in
+blue, and predicted patients in orange. That is, orange dots on the left
+represent false positives, while blue dots on the right represent
+false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
+ROC AUC of {\protect\alsRocAuc}.
+{\bf (b)} PCR-SGL coefficients are presented on the core fibers of major
+fiber bundles. They exhibit high group sparsity and are concentrated
+in the FA of the corticospinal tract (CST).
+The brain is oriented with the right hemisphere
+in the foreground and anterior to the right of the page. The CSTL, CSTR,
+callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)
+bundles are indicated for orientation.
+{\bf (c)} PCR-SGL identifies three portions of the CST as important,
+where $\hat{\beta}$ (dashed line, right axis) has large values. These
+are centered around nodes 30, 65, and 90, corresponding to locations
+of substantial differences in FA between the ALS and control groups
+(shaded areas indicates standard error of the mean).
+{\bf (d)} Bundle profiles for false positive classifications. Line
+colors correspond to the marker edge color in the top left plot.
+These individuals have reduced FA in the CST portions which SGL
+identified as important. Their misclassification is coherent with the
+feature importance and the group differences in FA.
+{\bf (e)} Individual bundle profiles for false negative
+classifications. These individuals have bundle profiles which
+oscillate between the group means.
+
+\paragraph{Figure 3: Predicting age with tractometry and SGL.}
+{\bf (top)} The predicted age vs. true age of each individual from the test
+splits (i.e., when each subject's data was held out in fitting the
+model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
+datasets; an accurate prediction falls close to the $y=x$ line
+(dashed). The mean absolute error (MAE) and coefficient of
+determination $R^2$ are presented in the lower right of each scatter
+plot.
+{\bf (middle)} Feature importance for predicting age from
+tract profile in
+the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
+The orientation of the
+brain is that same as in \cref{fig:class-results:coefs3d}, however because
+the coefficients exhibit high global sparsity (as opposed to group
+sparsity), we plot the mean of the absolute value of $\hat{\beta}$
+for each bundle on the core fiber. The global distrubution of the
+$\hat{\beta}$ coefficients reflects the fact that aging is not
+confined to a single white matter bundle.
+{\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
+{\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
+
+\paragraph{Figure 4: Model performance across all datasets.}
+Each panel shows model performance measured on the test set for each
+cross-validation split, with each black dot representing a split, box
+plots representing the quartiles, and white diamonds representing the mean
+performance. The $y$-scale varies in each subplot.
+\textbf{(a)} Accuracy of test set predictions for the
+ALS dataset. Because group differences
+in ALS diagnosis are mostly confined to a single bundle, the group
+structure-preserving methods, SGL and PCR-SGL, outperform the other
+models.
+The remaining frames show coefficient of determination, \protect$R^2$ in test sets
+for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN
+datasets. Because aging affects the white matter globally, group structure-blind
+methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL
+models show competitve predictive performance, adapting to a problem where
+group structure is not as informative. PCR-SGL performs poorly in this regime
+because its initial group-wise PC projection destroys between bundle covariance.
+The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.
+
+\paragraph{Figure 5: Nested cross-validation.}
+We evaluate model quality using a nested $k$-fold cross validation
+scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+groups and optimal hyperparameters are found for the level-0 training
+set. To avoid overfitting, the optimal hyperparameters are themselves
+evaluated using a cross-validation scheme taking place at level-1 of
+the decomposition, where each level-0 training set is further
+decomposed into $k_1 = 3$ shuffled groups. In the classification
+case, the training and test splits are stratified by diagnosis. For
+the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+$k_0 = 5$.
+
 \end{document}

### 2021-04-28 reports/manuscript/paper_changes.tex
Move figure captions to the end.

@@
 
-\begin{figure}[b!]
-    % \vspace{0.25cm}
-    % \rlap{
-    %     \hspace{-0.25em}
-    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    % }
-    % \vspace{-8.4cm}
-    % \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \caption{\textbf{Tractometry data flow}
-        \label{fig:methods}
-        \textbf{(a)} Whole brain tractography generates streamlines approximating
-        the trajectories of white matter connections.
-        \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
-        In this case, we show the left corticospinal tract (CSTL)
-        \added{and the left arcuate fasciculus (ARCL)}
-        over a mid-saggital anatomical slice.
-        \deleted{\textbf{(c)}} \replaced{Tract profiling}{Tractometry} further extracts bundle profiles,
-        quantifications of various diffusion metrics along the length of the
-        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for \added{\textbf{(c)}} the CSTL \added{and \textbf{(d)} the ARCL}.
-        \textbf{(d)} the phenotypical target data and \replaced{tract profile}{tractometric}
-        features can be organized into a linear model, $\hat{y} = \mathbf{X}
-        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-        to reveal a natural group structure: the left (orange) group
-        contains $k$ features from the CSTL, the middle (green) group
-        contains $k$ features from the left cingulum cingulate (CGCL),
-        and the right (blue) group
-        contains $k$ features from the \replaced{ARCL}{left arcuate (ARCL)}.
-        The coefficients in $\hat{\beta}$ follow the same natural grouping.
-    }
-\end{figure}
-
 The present work aims to balance predictive accuracy with descriptive power
@@
 
-\begin{figure}[t!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
-    % }
-    % \vspace{-7.0cm}
-    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
-    {\phantomsubcaption\label{fig:class-results:probs}}
-    {\phantomsubcaption\label{fig:class-results:coefs3d}}
-    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
-    {\phantomsubcaption\label{fig:class-results:false-positives}}
-    {\phantomsubcaption\label{fig:class-results:false-negatives}}
-    \caption{%
-        {\bf \added{PCR-}SGL accurately and interpretably predicts ALS diagnosis.}
-        \label{fig:class-results}
-        {\bf (a)} Classification probabilities for ALS diagnosis, with
-        controls on the left, patients on the right, predicted controls in
-        blue, and predicted patients in orange. That is, orange dots on the left
-        represent false positives, while blue dots on the right represent
-        false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
-        ROC AUC of {\protect\alsRocAuc}.
-        {\bf (b)} \added{PCR-}SGL coefficients are presented on the core fibers of major
-        fiber bundles. They exhibit high group sparsity and are concentrated
-        in the FA of the \replaced{corticospinal tract (CST)}{CST}.
-        The brain is oriented with the right hemisphere
-        in the foreground and anterior to the right of the page. The CSTL, CSTR,
-        \replaced{callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)}{CFA}
-        bundles are indicated for orientation.
-        {\bf (c)} \added{PCR-}SGL identifies three portions of the CST as important,
-        where $\hat{\beta}$ (dashed line, right axis) has large values. These
-        are centered around nodes 30, 65, and 90, corresponding to locations
-        of substantial differences in FA between the ALS and control groups
-        (shaded areas indicates standard error of the mean).
-        {\bf (d)} Bundle profiles for false positive classifications. Line
-        colors correspond to the marker edge color in the top left plot.
-        These individuals have reduced FA in the CST portions which SGL
-        identified as important. Their misclassification is coherent with the
-        feature importance and the group differences in FA.
-        {\bf (e)} Individual bundle profiles for false negative
-        classifications. These individuals have bundle profiles which
-        oscillate between the group means.
-    }
-\end{figure}
-
 To assess the added value of incorporating anatomical knowledge into our
@@
 imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see supplemental Figs S3 to S8 for the full tract profile information in all tracts/datasets}.
-
-\begin{figure}[t!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \hspace{0.775cm}
-    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
-    % }
-    % \vspace{-6.1cm}
-    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
-    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
-    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
-    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
-    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:wh-profile}}
-    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
-    {\phantomsubcaption\label{fig:age-results:cc-profile}}
-    \caption{%
-        {\bf Predicting age with tractometry and SGL.}
-        \label{fig:age-results}
-        {\bf (top)} The predicted age vs. true age of each individual from the test
-        splits (i.e., when each subject's data was held out in fitting the
-        model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
-        datasets; an accurate prediction falls close to the $y=x$ line
-        (dashed). The mean absolute error (MAE) and coefficient of
-        determination $R^2$ are presented in the lower right of each scatter
-        plot.
-        {\bf (middle)} Feature importance for predicting age from
-        \replaced{tract profile}{tractometry} in
-        the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
-        The orientation of the
-        brain is that same as in \cref{fig:class-results:coefs3d}, however because
-        the coefficients exhibit high global sparsity (as opposed to group
-        sparsity), we plot the mean of the absolute value of $\hat{\beta}$
-        for each bundle on the core fiber. The global distrubution of the
-        $\hat{\beta}$ coefficients reflects the fact that aging is not
-        confined to a single white matter bundle.
-        {\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
-        {\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
-    }
-\end{figure}
 
@@
 
-\begin{figure}[t!]
-    % \includegraphics[width=\textwidth]{model_performance.pdf}
-    \caption{%
-        {\bf \added{Model performance across all datasets.}}
-        \label{fig:model-performance}
-        \added{Each panel shows model performance measured on the test set for each}
-        \added{cross-validation split, with each black dot representing a split, box}
-        \added{plots representing the quartiles, and white diamonds representing the mean}
-        \added{performance. The $y$-scale varies in each subplot.}
-        \added{\textbf{(a)} Accuracy of test set predictions for the}
-        \added{ALS dataset. Because group differences}
-        \added{in ALS diagnosis are mostly confined to a single bundle, the group}
-        \added{structure-preserving methods, SGL and PCR-SGL, outperform the other}
-        \added{models.}
-        \added{The remaining frames show coefficient of determination, \protect$R^2$ in test sets}
-        \added{for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN}
-        \added{datasets. Because aging affects the white matter globally, group structure-blind}
-        \added{methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL}
-        \added{models show competitve predictive performance, adapting to a problem where}
-        \added{group structure is not as informative. PCR-SGL performs poorly in this regime}
-        \added{because its initial group-wise PC projection destroys between bundle covariance.}
-        \added{The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.}
-    }
-\end{figure}
 \added{Model performance across all four datasets and all six model types is summarized}
@@
 % step-by-step instructions.
+
+\newpage
+
+\section*{Figure legends}
+
+\begin{figure}[b!]
+    % \vspace{0.25cm}
+    % \rlap{
+    %     \hspace{-0.25em}
+    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    % }
+    % \vspace{-8.4cm}
+    % \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \phantomcaption{\label{fig:methods}}
+\end{figure}
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
+    % }
+    % \vspace{-7.0cm}
+    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
+    {\phantomsubcaption\label{fig:class-results:probs}}
+    {\phantomsubcaption\label{fig:class-results:coefs3d}}
+    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
+    {\phantomsubcaption\label{fig:class-results:false-positives}}
+    {\phantomsubcaption\label{fig:class-results:false-negatives}}
+    \phantomcaption{%
+    \label{fig:class-results}
+    }
+\end{figure}
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \hspace{0.775cm}
+    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
+    % }
+    % \vspace{-6.1cm}
+    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
+    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
+    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
+    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:wh-profile}}
+    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
+    {\phantomsubcaption\label{fig:age-results:cc-profile}}
+    \phantomcaption{%
+    \label{fig:age-results}
+    }
+\end{figure}
+
+\begin{figure}[b!]
+    % \includegraphics[width=\textwidth]{model_performance.pdf}
+    \phantomcaption{%
+    \label{fig:model-performance}
+    }
+\end{figure}
+
+\begin{figure}[h!]
+    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
+    \phantomcaption{
+    \label{fig:nested-cross-val}
+    }
+\end{figure}
+
+\paragraph{Figure 1: Tractometry data flow}
+\textbf{(a)} Whole brain tractography generates streamlines approximating
+    the trajectories of white matter connections.
+    \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
+    In this case, we show the left corticospinal tract (CSTL)
+    \added{and the left arcuate fasciculus (ARCL)}
+    over a mid-saggital anatomical slice.
+    \deleted{\textbf{(c)}} \replaced{Tract profiling}{Tractometry} further extracts bundle profiles,
+    quantifications of various diffusion metrics along the length of the
+    fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+    profile for \added{\textbf{(c)}} the CSTL \added{and \textbf{(d)} the ARCL}.
+    \textbf{(d)} the phenotypical target data and \replaced{tract profile}{tractometric}
+    features can be organized into a linear model, $\hat{y} = \mathbf{X}
+    \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+    to reveal a natural group structure: the left (orange) group
+    contains $k$ features from the CSTL, the middle (green) group
+    contains $k$ features from the left cingulum cingulate (CGCL),
+    and the right (blue) group
+    contains $k$ features from the \replaced{ARCL}{left arcuate (ARCL)}.
+    The coefficients in $\hat{\beta}$ follow the same natural grouping.
+\added{Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})}
+
+\paragraph{Figure 2: \added{PCR-}SGL accurately and interpretably predicts ALS diagnosis.}
+{\bf (a)} Classification probabilities for ALS diagnosis, with
+controls on the left, patients on the right, predicted controls in
+blue, and predicted patients in orange. That is, orange dots on the left
+represent false positives, while blue dots on the right represent
+false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
+ROC AUC of {\protect\alsRocAuc}.
+{\bf (b)} \added{PCR-}SGL coefficients are presented on the core fibers of major
+fiber bundles. They exhibit high group sparsity and are concentrated
+in the FA of the \replaced{corticospinal tract (CST)}{CST}.
+The brain is oriented with the right hemisphere
+in the foreground and anterior to the right of the page. The CSTL, CSTR,
+\replaced{callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)}{CFA}
+bundles are indicated for orientation.
+{\bf (c)} \added{PCR-}SGL identifies three portions of the CST as important,
+where $\hat{\beta}$ (dashed line, right axis) has large values. These
+are centered around nodes 30, 65, and 90, corresponding to locations
+of substantial differences in FA between the ALS and control groups
+(shaded areas indicates standard error of the mean).
+{\bf (d)} Bundle profiles for false positive classifications. Line
+colors correspond to the marker edge color in the top left plot.
+These individuals have reduced FA in the CST portions which SGL
+identified as important. Their misclassification is coherent with the
+feature importance and the group differences in FA.
+{\bf (e)} Individual bundle profiles for false negative
+classifications. These individuals have bundle profiles which
+oscillate between the group means.
+
+\paragraph{Figure 3: Predicting age with tractometry and SGL.}
+{\bf (top)} The predicted age vs. true age of each individual from the test
+splits (i.e., when each subject's data was held out in fitting the
+model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
+datasets; an accurate prediction falls close to the $y=x$ line
+(dashed). The mean absolute error (MAE) and coefficient of
+determination $R^2$ are presented in the lower right of each scatter
+plot.
+{\bf (middle)} Feature importance for predicting age from
+\replaced{tract profile}{tractometry} in
+the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
+The orientation of the
+brain is that same as in \cref{fig:class-results:coefs3d}, however because
+the coefficients exhibit high global sparsity (as opposed to group
+sparsity), we plot the mean of the absolute value of $\hat{\beta}$
+for each bundle on the core fiber. The global distrubution of the
+$\hat{\beta}$ coefficients reflects the fact that aging is not
+confined to a single white matter bundle.
+{\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
+{\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
+
+\paragraph{\added{Figure 4: Model performance across all datasets.}}
+\added{Each panel shows model performance measured on the test set for each}
+\added{cross-validation split, with each black dot representing a split, box}
+\added{plots representing the quartiles, and white diamonds representing the mean}
+\added{performance. The $y$-scale varies in each subplot.}
+\added{\textbf{(a)} Accuracy of test set predictions for the}
+\added{ALS dataset. Because group differences}
+\added{in ALS diagnosis are mostly confined to a single bundle, the group}
+\added{structure-preserving methods, SGL and PCR-SGL, outperform the other}
+\added{models.}
+\added{The remaining frames show coefficient of determination, \protect$R^2$ in test sets}
+\added{for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN}
+\added{datasets. Because aging affects the white matter globally, group structure-blind}
+\added{methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL}
+\added{models show competitve predictive performance, adapting to a problem where}
+\added{group structure is not as informative. PCR-SGL performs poorly in this regime}
+\added{because its initial group-wise PC projection destroys between bundle covariance.}
+\added{The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.}
+
+\paragraph{Figure 5: Nested cross-validation.}
+We evaluate model quality using a nested $k$-fold cross validation
+scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+groups and optimal hyperparameters are found for the level-0 training
+set. To avoid overfitting, the optimal hyperparameters are themselves
+evaluated using a cross-validation scheme taking place at level-1 of
+the decomposition, where each level-0 training set is further
+decomposed into $k_1 = 3$ shuffled groups. In the classification
+case, the training and test splits are stratified by diagnosis. For
+the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+$k_0 = 5$.
+
 \end{document}

### 2021-04-29 reports/manuscript/paper.tex
Add required acknowledgements to data providers.

@@
 for helpful comments on the manuscript.
+Data collection and sharing for this project was provided by the Cambridge Centre for Ageing and Neuroscience (CamCAN).
+CamCAN funding was provided by the UK Biotechnology and Biological Sciences Research Council (grant number BB/H008217/1), together with support from the UK Medical Research Council and University of Cambridge, UK.
+This manuscript was prepared using a limited access dataset obtained from the Child Mind Institute Biobank, The Healthy Brain Network dataset.
+This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute
 

### 2021-04-29 reports/manuscript/paper_changes.tex
Add required acknowledgements to data providers.

@@
 for helpful comments on the manuscript.
+\added{Data collection and sharing for this project was provided by the Cambridge Centre for Ageing and Neuroscience (CamCAN).
+CamCAN funding was provided by the UK Biotechnology and Biological Sciences Research Council (grant number BB/H008217/1), together with support from the UK Medical Research Council and University of Cambridge, UK.
+This manuscript was prepared using a limited access dataset obtained from the Child Mind Institute Biobank, The Healthy Brain Network dataset.
+This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute}
 

### 2021-04-29 reports/manuscript/paper_changes.tex
Correct wording.

@@
 measured with a $b=1000$ $\textrm{s} / \textrm{mm}^2$. These data
-were acquired using a dual spin echo sequence, in which there is
+were acquired using a twice refocused spin echo sequence, in which there is
 sufficient time for eddy currents to subside between the application of

### 2021-06-07 reports/manuscript/paper_changes.tex

@@
 
+\begin{figure}[b!]
+    % \vspace{0.25cm}
+    % \rlap{
+    %     \hspace{-0.25em}
+    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    % }
+    % \vspace{-8.4cm}
+    % \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{\label{fig:methods}
+    {\bf Figure 1: Tractometry data flow}
+    \textbf{(a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL)
+        \added{and the left arcuate fasciculus (ARCL)}
+        over a mid-saggital anatomical slice.
+        \deleted{\textbf{(c)}} \replaced{Tract profiling}{Tractometry} further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for \added{\textbf{(c)}} the CSTL \added{and \textbf{(d)} the ARCL}.
+        \textbf{(d)} the phenotypical target data and \replaced{tract profile}{tractometric}
+        features can be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the \replaced{ARCL}{left arcuate (ARCL)}.
+        The coefficients in $\hat{\beta}$ follow the same natural grouping.
+\added{Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})}
+    }
+\end{figure}
+
 % Results
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups \added{(see supplemental Figs S1 and S2 for tract profiles of all 18 tracts in these groups)}.
+right CST, plotted over the FA values for the control and ALS subject groups \added{(see Supporting Figures S1 and S2 for tract profiles of all 18 tracts in these groups)}.
 We find that SGL \replaced{and PCR-SGL select}{selects} FA metrics in the corticospinal tract and
@@
 method predicts incorrectly this is done in a comprehensible manner.
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
+    % }
+    % \vspace{-7.0cm}
+    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
+    {\phantomsubcaption\label{fig:class-results:probs}}
+    {\phantomsubcaption\label{fig:class-results:coefs3d}}
+    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
+    {\phantomsubcaption\label{fig:class-results:false-positives}}
+    {\phantomsubcaption\label{fig:class-results:false-negatives}}
+    \caption{
+    {\bf Figure 2: \added{PCR-}SGL accurately and interpretably predicts ALS diagnosis.}
+    {\bf (a)} Classification probabilities for ALS diagnosis, with
+    controls on the left, patients on the right, predicted controls in
+    blue, and predicted patients in orange. That is, orange dots on the left
+    represent false positives, while blue dots on the right represent
+    false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
+    ROC AUC of {\protect\alsRocAuc}.
+    {\bf (b)} \added{PCR-}SGL coefficients are presented on the core fibers of major
+    fiber bundles. They exhibit high group sparsity and are concentrated
+    in the FA of the \replaced{corticospinal tract (CST)}{CST}.
+    The brain is oriented with the right hemisphere
+    in the foreground and anterior to the right of the page. The CSTL, CSTR,
+    \replaced{callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)}{CFA}
+    bundles are indicated for orientation.
+    {\bf (c)} \added{PCR-}SGL identifies three portions of the CST as important,
+    where $\hat{\beta}$ (dashed line, right axis) has large values. These
+    are centered around nodes 30, 65, and 90, corresponding to locations
+    of substantial differences in FA between the ALS and control groups
+    (shaded areas indicates standard error of the mean).
+    {\bf (d)} Bundle profiles for false positive classifications. Line
+    colors correspond to the marker edge color in the top left plot.
+    These individuals have reduced FA in the CST portions which SGL
+    identified as important. Their misclassification is coherent with the
+    feature importance and the group differences in FA.
+    {\bf (e)} Individual bundle profiles for false negative
+    classifications. These individuals have bundle profiles which
+    oscillate between the group means.
+    \label{fig:class-results}
+    }
+\end{figure}
 
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see supplemental Figs S3 to S8 for the full tract profile information in all tracts/datasets}.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see Supporting Figures S3 to S8 for the full tract profile information in all tracts/datasets}.
 
@@
 
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \hspace{0.775cm}
+    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
+    % }
+    % \vspace{-6.1cm}
+    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
+    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
+    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
+    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:wh-profile}}
+    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
+    {\phantomsubcaption\label{fig:age-results:cc-profile}}
+    \phantomcaption{%
+    {\bf Figure 3: Predicting age with tractometry and SGL.}
+    {\bf (top)} The predicted age vs. true age of each individual from the test
+splits (i.e., when each subject's data was held out in fitting the model) for
+the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN datasets; an accurate
+prediction falls close to the $y=x$ line (dashed). The mean absolute error (MAE)
+and coefficient of determination $R^2$ are presented in the lower right of each
+scatter plot. {\bf (middle)} Feature importance for predicting age from
+\replaced{tract profile}{tractometry} in the {\bf (d)} WH, {\bf (e)} HBN, and
+{\bf (f)} Cam-CAN datasets. The orientation of the brain is that same as in
+\cref{fig:class-results:coefs3d}, however because the coefficients exhibit high
+global sparsity (as opposed to group sparsity), we plot the mean of the absolute
+value of $\hat{\beta}$ for each bundle on the core fiber. The global
+distrubution of the $\hat{\beta}$ coefficients reflects the fact that aging is
+not confined to a single white matter bundle. {\bf (bottom)} Age quintile bundle
+profiles for the {\bf (g)} WH, {\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
+    \label{fig:age-results}
+    }
+\end{figure}
+
+\begin{figure}[b!]
+    % \includegraphics[width=\textwidth]{model_performance.pdf}
+    \caption{%
+    {\bf \added{Figure 4: Model performance across all datasets.}}
+\added{Each panel shows model performance measured on the test set for each}
+\added{cross-validation split, with each black dot representing a split, box}
+\added{plots representing the quartiles, and white diamonds representing the mean}
+\added{performance. The $y$-scale varies in each subplot.}
+\added{\textbf{(a)} Accuracy of test set predictions for the}
+\added{ALS dataset. Because group differences}
+\added{in ALS diagnosis are mostly confined to a single bundle, the group}
+\added{structure-preserving methods, SGL and PCR-SGL, outperform the other}
+\added{models.}
+\added{The remaining frames show coefficient of determination, \protect$R^2$ in test sets}
+\added{for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN}
+\added{datasets. Because aging affects the white matter globally, group structure-blind}
+\added{methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL}
+\added{models show competitve predictive performance, adapting to a problem where}
+\added{group structure is not as informative. PCR-SGL performs poorly in this regime}
+\added{because its initial group-wise PC projection destroys between bundle covariance.}
+\added{The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.}
+    \label{fig:model-performance}
+    }
+\end{figure}
+
 \section*{Discussion}
@@
 properties \cite{yeatman2014lifespan}.
-\added{We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the supplementary material.
+\added{We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the Supporting Information.
 For age regression, substantial differences between the datasets preclude generalization across all three:}
@@
 sites in the New York
-area\added{: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center}.
+area\added{: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center. Age distributions of participants in the different sites are in Supporting Figure S9}.
 Informed consent was obtained from each participant aged 18 or older. For
@@
 in each voxel (STT) \cite{basser2000vivo}. \replaced{Eighteen major}{Major}
-tracts\added{, which are enumerated in the supplemental material,} were identified
+tracts\added{, which are enumerated in Figure S1,} were identified
 using multiple criteria: streamlines are selected as candidates for
@@
 are quantified and averaged along eighteen major fiber tracts,
-which are enumerated in the supplemental material.
+which are enumerated in the Supporting Information.
 \added{See Fig S3 of \mbox{\cite{kruper2021evaluating}} for a depiction of these white matter bundles.}
@@
 Initially designed to correct for site effects in gene expression studies \mbox{\cite{johnson2007adjusting}}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \mbox{\cite{fortin2018harmonization}}, multi-site DTI studies \mbox{\cite{fortin2017harmonization}}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \mbox{\cite{nielson2018detecting}}.
-We rely on the \texttt{neurocombat\_sklearn} library \mbox{\cite{neurocombat_sklearn}}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences in the supplemental material.}
+We rely on the \texttt{neurocombat\_sklearn} library \mbox{\cite{neurocombat_sklearn}}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences and ComBat correction in Supporting Figures S10-S13.}
 
@@
 
+\begin{figure}[h!]
+    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
+    \phantomcaption{
+    {\bf Figure 5: Nested cross-validation.}
+We evaluate model quality using a nested $k$-fold cross validation
+scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+groups and optimal hyperparameters are found for the level-0 training
+set. To avoid overfitting, the optimal hyperparameters are themselves
+evaluated using a cross-validation scheme taking place at level-1 of
+the decomposition, where each level-0 training set is further
+decomposed into $k_1 = 3$ shuffled groups. In the classification
+case, the training and test splits are stratified by diagnosis. For
+the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+$k_0 = 5$.
+    \label{fig:nested-cross-val}
+    }
+\end{figure}
+
 \subsection*{Software implementation}
@@
 
-\section*{Supporting information}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Bundle and regression coefficient profiles.}
-In this supporting section, we present bundle profiles and $\hat{\beta}$ coefficients
-for each anatomical bundle and in each dataset.
-
 \section*{Acknowledgments}
@@
 
-\newpage
-
-\section*{Figure legends}
-
-\begin{figure}[b!]
-    % \vspace{0.25cm}
-    % \rlap{
-    %     \hspace{-0.25em}
-    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    % }
-    % \vspace{-8.4cm}
-    % \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \phantomcaption{\label{fig:methods}}
-\end{figure}
-
-\begin{figure}[b!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
-    % }
-    % \vspace{-7.0cm}
-    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
-    {\phantomsubcaption\label{fig:class-results:probs}}
-    {\phantomsubcaption\label{fig:class-results:coefs3d}}
-    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
-    {\phantomsubcaption\label{fig:class-results:false-positives}}
-    {\phantomsubcaption\label{fig:class-results:false-negatives}}
-    \phantomcaption{%
-    \label{fig:class-results}
-    }
-\end{figure}
-
-\begin{figure}[b!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \hspace{0.775cm}
-    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
-    % }
-    % \vspace{-6.1cm}
-    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
-    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
-    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
-    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
-    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:wh-profile}}
-    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
-    {\phantomsubcaption\label{fig:age-results:cc-profile}}
-    \phantomcaption{%
-    \label{fig:age-results}
-    }
-\end{figure}
-
-\begin{figure}[b!]
-    % \includegraphics[width=\textwidth]{model_performance.pdf}
-    \phantomcaption{%
-    \label{fig:model-performance}
-    }
-\end{figure}
-
-\begin{figure}[h!]
-    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
-    \phantomcaption{
-    \label{fig:nested-cross-val}
-    }
-\end{figure}
-
-\paragraph{Figure 1: Tractometry data flow}
-\textbf{(a)} Whole brain tractography generates streamlines approximating
-    the trajectories of white matter connections.
-    \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
-    In this case, we show the left corticospinal tract (CSTL)
-    \added{and the left arcuate fasciculus (ARCL)}
-    over a mid-saggital anatomical slice.
-    \deleted{\textbf{(c)}} \replaced{Tract profiling}{Tractometry} further extracts bundle profiles,
-    quantifications of various diffusion metrics along the length of the
-    fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-    profile for \added{\textbf{(c)}} the CSTL \added{and \textbf{(d)} the ARCL}.
-    \textbf{(d)} the phenotypical target data and \replaced{tract profile}{tractometric}
-    features can be organized into a linear model, $\hat{y} = \mathbf{X}
-    \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-    to reveal a natural group structure: the left (orange) group
-    contains $k$ features from the CSTL, the middle (green) group
-    contains $k$ features from the left cingulum cingulate (CGCL),
-    and the right (blue) group
-    contains $k$ features from the \replaced{ARCL}{left arcuate (ARCL)}.
-    The coefficients in $\hat{\beta}$ follow the same natural grouping.
-\added{Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})}
-
-\paragraph{Figure 2: \added{PCR-}SGL accurately and interpretably predicts ALS diagnosis.}
-{\bf (a)} Classification probabilities for ALS diagnosis, with
-controls on the left, patients on the right, predicted controls in
-blue, and predicted patients in orange. That is, orange dots on the left
-represent false positives, while blue dots on the right represent
-false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
-ROC AUC of {\protect\alsRocAuc}.
-{\bf (b)} \added{PCR-}SGL coefficients are presented on the core fibers of major
-fiber bundles. They exhibit high group sparsity and are concentrated
-in the FA of the \replaced{corticospinal tract (CST)}{CST}.
-The brain is oriented with the right hemisphere
-in the foreground and anterior to the right of the page. The CSTL, CSTR,
-\replaced{callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)}{CFA}
-bundles are indicated for orientation.
-{\bf (c)} \added{PCR-}SGL identifies three portions of the CST as important,
-where $\hat{\beta}$ (dashed line, right axis) has large values. These
-are centered around nodes 30, 65, and 90, corresponding to locations
-of substantial differences in FA between the ALS and control groups
-(shaded areas indicates standard error of the mean).
-{\bf (d)} Bundle profiles for false positive classifications. Line
-colors correspond to the marker edge color in the top left plot.
-These individuals have reduced FA in the CST portions which SGL
-identified as important. Their misclassification is coherent with the
-feature importance and the group differences in FA.
-{\bf (e)} Individual bundle profiles for false negative
-classifications. These individuals have bundle profiles which
-oscillate between the group means.
-
-\paragraph{Figure 3: Predicting age with tractometry and SGL.}
-{\bf (top)} The predicted age vs. true age of each individual from the test
-splits (i.e., when each subject's data was held out in fitting the
-model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
-datasets; an accurate prediction falls close to the $y=x$ line
-(dashed). The mean absolute error (MAE) and coefficient of
-determination $R^2$ are presented in the lower right of each scatter
-plot.
-{\bf (middle)} Feature importance for predicting age from
-\replaced{tract profile}{tractometry} in
-the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
-The orientation of the
-brain is that same as in \cref{fig:class-results:coefs3d}, however because
-the coefficients exhibit high global sparsity (as opposed to group
-sparsity), we plot the mean of the absolute value of $\hat{\beta}$
-for each bundle on the core fiber. The global distrubution of the
-$\hat{\beta}$ coefficients reflects the fact that aging is not
-confined to a single white matter bundle.
-{\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
-{\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
-
-\paragraph{\added{Figure 4: Model performance across all datasets.}}
-\added{Each panel shows model performance measured on the test set for each}
-\added{cross-validation split, with each black dot representing a split, box}
-\added{plots representing the quartiles, and white diamonds representing the mean}
-\added{performance. The $y$-scale varies in each subplot.}
-\added{\textbf{(a)} Accuracy of test set predictions for the}
-\added{ALS dataset. Because group differences}
-\added{in ALS diagnosis are mostly confined to a single bundle, the group}
-\added{structure-preserving methods, SGL and PCR-SGL, outperform the other}
-\added{models.}
-\added{The remaining frames show coefficient of determination, \protect$R^2$ in test sets}
-\added{for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN}
-\added{datasets. Because aging affects the white matter globally, group structure-blind}
-\added{methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL}
-\added{models show competitve predictive performance, adapting to a problem where}
-\added{group structure is not as informative. PCR-SGL performs poorly in this regime}
-\added{because its initial group-wise PC projection destroys between bundle covariance.}
-\added{The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.}
-
-\paragraph{Figure 5: Nested cross-validation.}
-We evaluate model quality using a nested $k$-fold cross validation
-scheme. At level-0, the input data is decomposed into $k_0$ shuffled
-groups and optimal hyperparameters are found for the level-0 training
-set. To avoid overfitting, the optimal hyperparameters are themselves
-evaluated using a cross-validation scheme taking place at level-1 of
-the decomposition, where each level-0 training set is further
-decomposed into $k_1 = 3$ shuffled groups. In the classification
-case, the training and test splits are stratified by diagnosis. For
-the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
-$k_0 = 5$.
+\section*{Supporting information}
+
+\paragraph{Figure S1: Bundle profiles and regression coefficients for the ALS dataset FA.}
+Diffusion metrics are plotted
+along the length of eighteen bundles:
+right corticospinal (CSTR),
+left corticospinal (CSTL),
+right uncinate (UNCR),
+left uncinate (UNCL),
+left inferior fronto-occipital fasciculus (IFOL),
+right inferior fronto-occipital fasciculus (IFOR),
+right arcuate (ARCR),
+left arcuate (ARCL),
+right thalamic radiation (ATRR),
+left thalamic radiation (ATRL),
+right cingulum cingulate (CGCR),
+left cingulum cingulate (CGCL),
+callosum forceps posterior (CFP),
+callosum forceps anterior (CFA),
+right inferior longitudinal fasciculus (ILFR),
+left inferior longitudinal fasciculus (ILFL),
+right superior longitudinal fasciculus (SLFR),
+and left superior longitudinal fasciculus (SLFL). We use these acronyms throughout the Supporting Information.
+FA is plotted on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on the twin axis on the right-hand-side. SGL selected
+the right corticospinal tract (CSTR) as important and regularized coefficients
+in the CSTL. Yet, there are also group FA differences in the
+CSTL. This highlighted a potential drawback of the SGL method, discussed in the
+main text in the context of age regression. Namely, SGL is not guaranteed to
+identify \emph{all} important features. In this case, if the diagnostic signal
+in the CSTL is redundant to that in the CSTR, SGL will regularize the CSTL
+features, thereby reducing its sparsity penalty without any corresponding
+increase in loss. This parsimony cuts both ways; it is a feature of the method
+when one seeks an efficient predictive model, but is a disadvantage of the
+method when one wants an exhaustive explanation of feature importance. We use the phrase ``parsimony pitfall'' to refer to the case when SGL regularizes
+away redundant but obviously important features.
+
+\paragraph*{Figure S2: Bundle profiles and regression coefficients for the ALS dataset MD.} The scale of the $\hat{\beta}$-axis is identical to that used in Figure S1, to facilitate the comparison of the relative importance of each metric.
+
+\paragraph*{Figure S3: Bundle profiles and regression
+coefficients for the WH dataset FA.} In contrast to the ALS classification case,
+the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting the interpretation that aging is a large and continuous whole-brain process.
+
+\paragraph*{Figure S4: Bundle profiles and regression coefficients for the WH
+dataset MD.} This and Figure S3 demonstrate that SGL behaves much more like the
+lasso than the group lasso, as discussed in the main text. The parsimony pitfall
+is most evident in the IFOL and IFOR bundles.
+
+\paragraph*{Figure S5: FA bundle profiles and $\hat{\beta}$ coefficients for age
+regression in the HBN dataset.} Like the WH dataset, the $\hat{\beta}$
+coefficients are distributed widely through the brain and SGL behaves more like
+the lasso than the group lasso.
+
+\paragraph*{Figure S6: MD bundle profiles and $\hat{\beta}$ coefficients for age
+regression in the HBN dataset.} In contrast to the WH results, the bundle
+profiles show different behaviors. For example the SLFL and SLFR bundle profiles
+in have different concavity. This is unsurprising, however, given the
+differences between these datasets (see also Discussion). The parsimony pitfall
+is most evident in the UNCL, UNCR, ARCL, SLFL, and SLFR bundles
+
+\paragraph*{Figure S7: FA bundle profiles and $\hat{\beta}$ coefficients for age
+regression in the Cam-CAN dataset.} The $\hat{\beta}$ coefficients are
+distributed widely through the brain and SGL behaves more like the lasso than
+the group lasso. As before, one must be cautious about comparing bundle profiles
+and $\hat{\beta}$ coefficients between models. While the HBN and Cam-CAN
+datasets share the same diffusion model and refrain from clipping streamlines,
+the age distributions for the two are roughly disjoint, with the WH age
+distribution straddling the two.
+
+\paragraph*{Figure S8: Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
+coefficients for age regression in the Cam-CAN dataset.}
+
+\paragraph*{Figure S9: Age distributions are similar between the different
+HBN sites.} Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
+
+\paragraph*{Figure S10: FA bundle profiles exhibit strong site differences in the HBN dataset.}
+
+\paragraph*{Figure S11: MD bundle profiles exhibit strong site differences in the HBN dataset.}
+
+\paragraph*{Figure S12: Site differences in FA are eliminated by ComBat harmonization.}
+
+\paragraph*{Figure S13: Site differences in MD are eliminated by ComBat harmonization.}
 

### 2021-06-09 reports/manuscript/paper_changes.tex
Accept all changes

@@
 samples along the length of each bundle
-\replaced{\mbox{\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu}},}{\mbox{\cite{yeatman2012tract, colby2012, ODonnell2009-uu}},}
-\added{hereafter referred to as tract profiling}.
+\cite{Jones2005-yq, yeatman2012tract, colby2012, ODonnell2009-uu},
+hereafter referred to as tract profiling.
 While this retains important information about each individual's white
@@
 performance.
-\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference about the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a particular phenotype}.
-\added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
+Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference about the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a particular phenotype.
+For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error.
 The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}.
 This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}.
-In the present work}, we predict the phenotypical variance in a group of subjects,or classify group membership, based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
+In the present work, we predict the phenotypical variance in a group of subjects,or classify group membership, based on a linear combination of the features estimated with tract profiling.
 
@@
 Using this approach, we first need to deal with the large and
-asymmetric dimensionality of the data: \replaced{tract profile}{tractometry}
+asymmetric dimensionality of the data: tract profile
 data usually has
@@
 develop an implementation of SGL that is well suited to the analysis of
-\replaced{tract profile}{tractometry} data and, second, demonstrate the power and flexibility of
+tract profile data and, second, demonstrate the power and flexibility of
 this approach by applying it to both classification
-and continuous prediction problems. Our \deleted{tractometry} data flow is
+and continuous prediction problems. Our data flow is
 represented in \cref{fig:methods} and explained in further detail in
@@
 
-\added{One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.
-For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \mbox{\cite{powell2018local, rasero2021integrating}}.
-While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \mbox{\cite{chamberland2019dimensionality}}, they neglect anatomical grouping information.
+One more approach to multivariate analysis of neuroimaging data is to perform inference or prediction in a transformed feature space rather then the original diffusion metric feature space.
+For example, in Lasso PCR, diffusion features can be projected onto a principal components (PC) basis for use in a sparsity constrained model \cite{powell2018local, rasero2021integrating}.
+While these approaches achieve high predictive performance and may even yield biologically interpretable principal components \cite{chamberland2019dimensionality}, they neglect anatomical grouping information.
 We view these approaches as complementary to the SGL-based approach: PCR based approaches seeks to model brain-phenotype relationships using the most parsimonious representation of variance in the diffusion measures.
@@
         In this case, we show the left corticospinal tract (CSTL)
-        \added{and the left arcuate fasciculus (ARCL)}
+        and the left arcuate fasciculus (ARCL)
         over a mid-saggital anatomical slice.
-        \deleted{\textbf{(c)}} \replaced{Tract profiling}{Tractometry} further extracts bundle profiles,
+        Tract profiling further extracts bundle profiles,
         quantifications of various diffusion metrics along the length of the
         fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-        profile for \added{\textbf{(c)}} the CSTL \added{and \textbf{(d)} the ARCL}.
-        \textbf{(d)} the phenotypical target data and \replaced{tract profile}{tractometric}
+        profile for \textbf{(c)} the CSTL and \textbf{(d)} the ARCL.
+        \textbf{(d)} the phenotypical target data and tract profile
         features can be organized into a linear model, $\hat{y} = \mathbf{X}
@@
         and the right (blue) group
-        contains $k$ features from the \replaced{ARCL}{left arcuate (ARCL)}.
+        contains $k$ features from the ARCL.
         The coefficients in $\hat{\beta}$ follow the same natural grouping.
-\added{Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})}
+Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})
     }
@@
 
-We developed a method for analyzing dMRI \replaced{tract profile}{tractometry} data that uses the Sparse
+We developed a method for analyzing dMRI tract profile data that uses the Sparse
 Group Lasso (SGL) to select features that are sparse both at the group (bundle) level, as well as overall.
@@
 engineering.
-\added{We also predicted ALS diagnosis using the PCR-SGL, wherein each group of features is independently transformed to its PC basis and an SGL model is fit to the transformed features.
-This model achieves \protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}}
+We also predicted ALS diagnosis using the PCR-SGL, wherein each group of features is independently transformed to its PC basis and an SGL model is fit to the transformed features.
+This model achieves \protect{\alsAccuracyGpca}\% accuracy and an ROC AUC of \protect{\alsRocAucGpca}
 (\cref{fig:class-results:probs}). In addition to this classification
-performance, both SGL \added{and PCR-SGL} also \replaced{identify}{identifies}
+performance, both SGL and PCR-SGL also identify
 the white matter tracts most important for ALS classification.
-\added{\Cref{fig:class-results:coefs3d} shows that PCR-SGL identified as potential disease biomarkers the diffusion measures in the CST from the cerebral peduncle to the corona radiata, agreeing with the previous study from which these data were extracted \mbox{\cite{sarica2017corticospinal}}.}
+\Cref{fig:class-results:coefs3d} shows that PCR-SGL identified as potential disease biomarkers the diffusion measures in the CST from the cerebral peduncle to the corona radiata, agreeing with the previous study from which these data were extracted \cite{sarica2017corticospinal}.
 The relative importance of white matter
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups \added{(see Supporting Figures S1 and S2 for tract profiles of all 18 tracts in these groups)}.
-We find that SGL \replaced{and PCR-SGL select}{selects} FA metrics in the corticospinal tract and
+right CST, plotted over the FA values for the control and ALS subject groups (see Supporting Figures S1 and S2 for tract profiles of all 18 tracts in these groups).
+We find that SGL and PCR-SGL select FA metrics in the corticospinal tract and
 particularly in the right corticospinal tract as most important to ALS
@@
 model, we compared our classification results to those obtained from
-\replaced{four other models: a pure lasso model, an elastic net model, a bundle-mean lasso (i.e.
-a lasso model trained only on the mean metric values from each bundle), and a principal components regression lasso (Lasso PCR) model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
-\replaced{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71, respectively}{The pure lasso model achieved 76\% accuracy and an ROC AUC of 0.76}
+four other models: a pure lasso model, an elastic net model, a bundle-mean lasso (i.e.
+a lasso model trained only on the mean metric values from each bundle), and a principal components regression lasso (Lasso PCR) model \cite{powell2018local, rasero2021integrating}.
+These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71, respectively
 using the same cross-validation strategy used to assess the SGL model.
@@
 over simpler sparsity-inducing regression strategies.
-\added{The relatively poor performance of Lasso PCR suggests that features with small variance are nonetheless relevant for predicting ALS diagnosis.
-Or equivalently, that group differences between ALS diagnoses are not the dominant source of variance in the diffusion metrics.}
+The relatively poor performance of Lasso PCR suggests that features with small variance are nonetheless relevant for predicting ALS diagnosis.
+Or equivalently, that group differences between ALS diagnoses are not the dominant source of variance in the diffusion metrics.
 
@@
 preferentially correlates with only a few groups of covariates. For the ALS
-dataset, \added{the SGL model has} $\alpha = $ \alsLRatio
-~\added{and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca},
+dataset, the SGL model has $\alpha = $ \alsLRatio
+~and the PCR-SGL model has \protect$\alpha = $ \protect\alsLRatioGpca,
 confirming that the white matter correlates of ALS reside mostly in one
@@
     \caption{
-    {\bf Figure 2: \added{PCR-}SGL accurately and interpretably predicts ALS diagnosis.}
+    {\bf Figure 2: PCR-SGL accurately and interpretably predicts ALS diagnosis.}
     {\bf (a)} Classification probabilities for ALS diagnosis, with
@@
     ROC AUC of {\protect\alsRocAuc}.
-    {\bf (b)} \added{PCR-}SGL coefficients are presented on the core fibers of major
+    {\bf (b)} PCR-SGL coefficients are presented on the core fibers of major
     fiber bundles. They exhibit high group sparsity and are concentrated
-    in the FA of the \replaced{corticospinal tract (CST)}{CST}.
+    in the FA of the corticospinal tract (CST).
     The brain is oriented with the right hemisphere
     in the foreground and anterior to the right of the page. The CSTL, CSTR,
-    \replaced{callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)}{CFA}
+    callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)
     bundles are indicated for orientation.
-    {\bf (c)} \added{PCR-}SGL identifies three portions of the CST as important,
+    {\bf (c)} PCR-SGL identifies three portions of the CST as important,
     where $\hat{\beta}$ (dashed line, right axis) has large values. These
@@
 
-To test the performance of SGL \deleted{with tractometry data} in a continuous
+To test the performance of SGL in a continuous
 regression task, we focus here on the prediction of biological age in three
@@
 and 18-88 years of age, respectively. In each case, biological age was used
-as the predicted variable $y$. SGL was fit to the \replaced{tract profile}{tractometry-extracted}
+as the predicted variable $y$. SGL was fit to the tract profile
 features FA and mean diffusivity (MD) in 18 major brain tracts, with diffusion metrics extracted
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets \added{see Supporting Figures S3 to S8 for the full tract profile information in all tracts/datasets}.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see Supporting Figures S3 to S8 for the full tract profile information in all tracts/datasets.
 
@@
 the subjects in this procedure, with a median absolute error of {\whMae},
-\added{{\hbnMae}}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
-respectively and coefficients of determination $R^2 = $ {\whRsq} , \added{{\hbnRsq}}, and {\camcanRsq},
+{\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
+respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq}, and {\camcanRsq},
 respectively (see \cref{fig:age-results}, top panels). The
@@
 obtained using
-\replaced{the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR}{only the lasso penalty}.
+the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR.
 The pure lasso models achieved $R^2 = 0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively using the same cross-validation strategy used to assess the SGL.
-\added{The elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets, respectively.
+The elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets, respectively.
 The bundle-mean lasso models achieved $R^2 = 0.33$, $0.22$, and $0.55$, respectively.
-And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.}
+And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.
 The SGL models'
@@
 
-\added{Model performance across all four datasets and all six model types is summarized}
-\added{in \cref{fig:model-performance}. In contrast to the ALS classification case, the PCR Lasso performs}
-\added{competitively in age regression, suggesting that aging is a significant source of global variance}
-\added{in the tract profiles. On the other hand, the PCR-SGL models destroy cross-bundle covariance information}
-\added{in their initial group-wise PC projection step (see \cref{eq:svd}), limiting performance}
-\added{for globally distributed phenomena. Conversely, the SGL models are able to adapt to this regime.}
+Model performance across all four datasets and all six model types is summarized
+in \cref{fig:model-performance}. In contrast to the ALS classification case, the PCR Lasso performs
+competitively in age regression, suggesting that aging is a significant source of global variance
+in the tract profiles. On the other hand, the PCR-SGL models destroy cross-bundle covariance information
+in their initial group-wise PC projection step (see \cref{eq:svd}), limiting performance
+for globally distributed phenomena. Conversely, the SGL models are able to adapt to this regime.
 
@@
 scatter plot. {\bf (middle)} Feature importance for predicting age from
-\replaced{tract profile}{tractometry} in the {\bf (d)} WH, {\bf (e)} HBN, and
+tract profile in the {\bf (d)} WH, {\bf (e)} HBN, and
 {\bf (f)} Cam-CAN datasets. The orientation of the brain is that same as in
@@
     \caption{%
-    {\bf \added{Figure 4: Model performance across all datasets.}}
-\added{Each panel shows model performance measured on the test set for each}
-\added{cross-validation split, with each black dot representing a split, box}
-\added{plots representing the quartiles, and white diamonds representing the mean}
-\added{performance. The $y$-scale varies in each subplot.}
-\added{\textbf{(a)} Accuracy of test set predictions for the}
-\added{ALS dataset. Because group differences}
-\added{in ALS diagnosis are mostly confined to a single bundle, the group}
-\added{structure-preserving methods, SGL and PCR-SGL, outperform the other}
-\added{models.}
-\added{The remaining frames show coefficient of determination, \protect$R^2$ in test sets}
-\added{for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN}
-\added{datasets. Because aging affects the white matter globally, group structure-blind}
-\added{methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL}
-\added{models show competitve predictive performance, adapting to a problem where}
-\added{group structure is not as informative. PCR-SGL performs poorly in this regime}
-\added{because its initial group-wise PC projection destroys between bundle covariance.}
-\added{The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.}
+    {\bf Figure 4: Model performance across all datasets.}
+Each panel shows model performance measured on the test set for each
+cross-validation split, with each black dot representing a split, box
+plots representing the quartiles, and white diamonds representing the mean
+performance. The $y$-scale varies in each subplot.
+\textbf{(a)} Accuracy of test set predictions for the
+ALS dataset. Because group differences
+in ALS diagnosis are mostly confined to a single bundle, the group
+structure-preserving methods, SGL and PCR-SGL, outperform the other
+models.
+The remaining frames show coefficient of determination, \protect$R^2$ in test sets
+for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN
+datasets. Because aging affects the white matter globally, group structure-blind
+methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL
+models show competitve predictive performance, adapting to a problem where
+group structure is not as informative. PCR-SGL performs poorly in this regime
+because its initial group-wise PC projection destroys between bundle covariance.
+The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.
     \label{fig:model-performance}
@@
 
-We present here a novel method for analysis of dMRI \replaced{tract profile}{tractometry} data that
+We present here a novel method for analysis of dMRI tract profile data that
 relies on the Sparse Group Lasso \cite{simon2013sparse} to make accurate
@@
 \cite{sarica2017corticospinal}.
-\added{As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.}
+As with the original study, it is unclear whether our strong predictive performance based on image properties that would be visible in patient scans or whether it is identifying a new subclinical disease biomarker.
 In contrast, for the analysis of biological
@@
 properties \cite{yeatman2014lifespan}.
-\added{We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the Supporting Information.
-For age regression, substantial differences between the datasets preclude generalization across all three:}
+We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the Supporting Information.
+For age regression, substantial differences between the datasets preclude generalization across all three:
 \begin{enumerate*}[%
@@
     itemjoin*={{, and }}]
-    \item \added{different acquisition parameters, which can be challenging to harmonize \mbox{\cite{pinto2020harmonization}}}
-    \item \added{different diffusion models, with DTI for the WH dataset and DKI for the HBN and Cam-CAN datasets}
-    \item \added{different age ranges and distributions (which is evident in the figure legends for \cref{fig:age-results}), with HBN being a developmental dataset, while WH and Cam-CAN are lifespan maturation datasets}
-    \item \added{different anatomical extents, with the WH streamlines truncated to remain with the bundle's bounding regions of interest (the default behavior in the legacy \texttt{mAFQ}) and the HBN and Cam-CAN streamlines allowed to retain their full extent from whole-brain tractography (the default behavior in \texttt{pyAFQ}).}
+    \item different acquisition parameters, which can be challenging to harmonize \cite{pinto2020harmonization}
+    \item different diffusion models, with DTI for the WH dataset and DKI for the HBN and Cam-CAN datasets
+    \item different age ranges and distributions (which is evident in the figure legends for \cref{fig:age-results}), with HBN being a developmental dataset, while WH and Cam-CAN are lifespan maturation datasets
+    \item different anatomical extents, with the WH streamlines truncated to remain with the bundle's bounding regions of interest (the default behavior in the legacy \texttt{mAFQ}) and the HBN and Cam-CAN streamlines allowed to retain their full extent from whole-brain tractography (the default behavior in \texttt{pyAFQ}).
 \end{enumerate*}
-\added{In a biological characteristic that has widespread effects in the brain, validity is difficult to assess \mbox{\cite{lermausabiaga2019replication}}, so it is both unsurprising and vexing that we can do so well at predicting within each dataset, and yet do poorly in interpreting informative features across instruments.}
-
-\added{We also implemented a union of the PCR Lasso and SGL approaches by first}
-\added{projecting each group onto its PC basis. This PCR-SGL approach transformed the feature}
-\added{space into a more parsimonious representation of its variance while}
-\added{also preserving group structure. But it was unable to efficiently represent}
-\added{cross-bundle covariance, which is an advantage of PCR Lasso. As a result, PCR-SGL performed well in ALS classification,}
-\added{where the white matter interactions are highly localized, and poorly}
-\added{in age regression, where the white matter interactions are global.}
+In a biological characteristic that has widespread effects in the brain, validity is difficult to assess \cite{lermausabiaga2019replication}, so it is both unsurprising and vexing that we can do so well at predicting within each dataset, and yet do poorly in interpreting informative features across instruments.
+
+We also implemented a union of the PCR Lasso and SGL approaches by first
+projecting each group onto its PC basis. This PCR-SGL approach transformed the feature
+space into a more parsimonious representation of its variance while
+also preserving group structure. But it was unable to efficiently represent
+cross-bundle covariance, which is an advantage of PCR Lasso. As a result, PCR-SGL performed well in ALS classification,
+where the white matter interactions are highly localized, and poorly
+in age regression, where the white matter interactions are global.
 
@@
 
-\added{Another limitation of our approach is in its computational execution time, which, in our experience, is roughly five times slower than simpler models like the lasso.
+Another limitation of our approach is in its computational execution time, which, in our experience, is roughly five times slower than simpler models like the lasso.
 This slow-down is likely to be insignificant for ``production'' cycles in which researchers report their findings, but may be prohibitive for ``development'' cycles in which researchers repeatedly train models while adjusting their analysis pipeline.
 In practice, we circumvent this limitation by developing our analysis infrastructure with fast, simple models, and substituting slower, more performant models afterwards.
-The consistent scikit-learn-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.}
-
-Taken together, \replaced{our}{these} results demonstrate the promise of the
+The consistent scikit-learn-based application programming interface of \texttt{AFQ-Insight} provides a good basis for this pattern.
+
+Taken together, our results demonstrate the promise of the
 group-regularized regression approach. Even at the scale of dozens of
 subjects, the results provided by SGL are both accurate, as well as
-interpretable \cite{Murdoch2019-ax}: \replaced{tract profiling}{tractometry} capitalizes on domain
+interpretable \cite{Murdoch2019-ax}: tract profiling capitalizes on domain
 knowledge to engineer meaningful features; SGL scores these features based on
@@
 complexity of these data pose substantial challenges.
-\replaced{Tract profiling}{Tractometry} followed by
+Tract profiling followed by
 analysis with SGL provide a promising approach to distill meaningful insights
@@
 data (e.g., \cite{chamberland2019dimensionality}) could also benefit from constraints
-based on grouping\added{, as our implementation of PCR-SGL suggests}.
+based on grouping, as our implementation of PCR-SGL suggests.
 
@@
 ecosystem: AFQ \cite{yeatman2012tract} and pyAFQ \cite{kruper2021evaluating}, which extract
-\replaced{tract profile}{tractometry} data from raw and processed dMRI datasets, as well as
-AFQ-Browser, which visualizes \replaced{tract profiles}{tractometry} data and facilitates sharing of the
+tract profile data from raw and processed dMRI datasets, as well as
+AFQ-Browser, which visualizes tract profiles data and facilitates sharing of the
 results of dMRI studies \cite{yeatman2018browser}. To facilitate
@@
 fit \cite{chang2005restore}
-\added{on the \protect$b=1000$ \protect$\textrm{s} / \textrm{mm}^2$ shell only}.
+on the \protect$b=1000$ \protect$\textrm{s} / \textrm{mm}^2$ shell only.
 We will refer to this dataset as WH.
@@
 sites in the New York
-area\added{: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center. Age distributions of participants in the different sites are in Supporting Figure S9}.
+area: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center. Age distributions of participants in the different sites are in Supporting Figure S9.
 Informed consent was obtained from each participant aged 18 or older. For
@@
 
-\item \added{{\it MRtrix3 Reconstruction}}
-
-\added{Reconstruction was performed using \emph{QSIprep} 0.12.1.
+\item {\it MRtrix3 Reconstruction}
+
+Reconstruction was performed using \emph{QSIprep} 0.12.1.
 Multi-tissue fiber response functions were estimated using the dhollander algorithm.
-FODs were estimated via constrained spherical deconvolution (CSD, \mbox{\cite{originalcsd, tournier2008csd}}) using an unsupervised multi-tissue method \mbox{\cite{dhollander2019response, dhollander2016unsupervised}}.
-Reconstruction was done using MRtrix3 \mbox{\cite{mrtrix3}}.
-FODs were intensity-normalized using mtnormalize \mbox{\cite{mtnormalize}}.}
+FODs were estimated via constrained spherical deconvolution (CSD, \cite{originalcsd, tournier2008csd}) using an unsupervised multi-tissue method \cite{dhollander2019response, dhollander2016unsupervised}.
+Reconstruction was done using MRtrix3 \cite{mrtrix3}.
+FODs were intensity-normalized using mtnormalize \cite{mtnormalize}.
 \end{itemize}
@@
 with a twice refocused spin-echo sequence and the same preprocessing
-\replaced{and reconstruction pipelines}{pipeline}
+and reconstruction pipelines
 used for the HBN dataset was applied to this data. We will refer to this
@@
 using the Matlab Automated Fiber Quantification toolbox
-(\texttt{mAFQ}\added{, version 1.1 for WH and version 1.2 for ALS})
+(\texttt{mAFQ}, version 1.1 for WH and version 1.2 for ALS)
 \cite{yeatman2012tract}: streamlines representing fascicles of white
@@
 that follows the prinicpal diffusion direction of the diffusion tensor
-in each voxel (STT) \cite{basser2000vivo}. \replaced{Eighteen major}{Major}
-tracts\added{, which are enumerated in Figure S1,} were identified
+in each voxel (STT) \cite{basser2000vivo}. Eighteen major
+tracts, which are enumerated in Figure S1, were identified
 using multiple criteria: streamlines are selected as candidates for
@@
 weighting the contribution of each streamline by the inverse of the
-\replaced{mahalanobis}{mahalnobis} distance of the node from the average of
+mahalanobis distance of the node from the average of
 that node across streamlines. This means that streamlines that are more
@@
 which are enumerated in the Supporting Information.
-\added{See Fig S3 of \mbox{\cite{kruper2021evaluating}} for a depiction of these white matter bundles.}
+See Fig S3 of \cite{kruper2021evaluating} for a depiction of these white matter bundles.
 Here,
@@
 based on other quantitative MRI measurements can also be used.
-\added{The resulting feature space was the same for all four datasets, with the FA and MD metrics at each of 100 nodes in eighteen bundles comprising 3600 features per subject.}
+The resulting feature space was the same for all four datasets, with the FA and MD metrics at each of 100 nodes in eighteen bundles comprising 3600 features per subject.
 These bundle profiles, along with the phenotypical data we wish to explain
@@
 variables while the bundle profiles form the feature or predictor
-variables (\replaced{see}{See} \cref{fig:methods:group-structure}).
-
-\subsubsection*{\added{Data harmonization for HBN}}
-
-\added{For the multisite HBN study, we use the ComBat harmonization method to robustly adjust for site effects in the tract profiles.
-Initially designed to correct for site effects in gene expression studies \mbox{\cite{johnson2007adjusting}}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \mbox{\cite{fortin2018harmonization}}, multi-site DTI studies \mbox{\cite{fortin2017harmonization}}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \mbox{\cite{nielson2018detecting}}.
-We rely on the \texttt{neurocombat\_sklearn} library \mbox{\cite{neurocombat_sklearn}}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences and ComBat correction in Supporting Figures S10-S13.}
+variables (see \cref{fig:methods:group-structure}).
+
+\subsubsection*{Data harmonization for HBN}
+
+For the multisite HBN study, we use the ComBat harmonization method to robustly adjust for site effects in the tract profiles.
+Initially designed to correct for site effects in gene expression studies \cite{johnson2007adjusting}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \cite{fortin2018harmonization}, multi-site DTI studies \cite{fortin2017harmonization}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \cite{nielson2018detecting}.
+We rely on the \texttt{neurocombat\_sklearn} library \cite{neurocombat_sklearn}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences and ComBat correction in Supporting Figures S10-S13.
 
@@
 
-After scaling and imputation, the \replaced{tract profile}{tractometry} data and target
+After scaling and imputation, the tract profile data and target
 phenotypical data can be organized in a linear model:
@@
 where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
-or continuous numerical, such as the subject's age. The \replaced{tract profile}{tractometry}
+or continuous numerical, such as the subject's age. The tract profile
 data is represented in the feature matrix $\mathbf{X}$, with rows
@@
 
-\subsubsection*{\added{SGL with principal components}}
-
-\added{SGL may be combined with principal components regression (PCR-SGL) by performing dimensionality reduction separately for each group of covariates. Let}
+\subsubsection*{SGL with principal components}
+
+SGL may be combined with principal components regression (PCR-SGL) by performing dimensionality reduction separately for each group of covariates. Let
 \begin{equation}
@@
 \end{equation}
-\added{be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$, the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group \protect$\ell$.
+be the compact singular value decomposition (SVD) of \protect$\mathbf{X}^{(\ell)}$, the \protect$n \times p_\ell$ submatrix of \protect$\mathbf{X}$ corresponding to group \protect$\ell$.
 Here, \protect$\mathbf{\Sigma}$ is an \protect$r \times r$ matrix, where \protect$r = \min(n, p_\ell)$, that contains the non-zero singular values of \protect$\mathbf{X}^{(\ell)}$.
 \protect$\mathbf{V}^T$ is an \protect$r \times p$ semi-orthogonal matrix containing the principal axes of \protect$\mathbf{X}^{(\ell)}$.
-The product \protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$ in the basis provided by \protect$\mathbf{V}^T$.}
-
-\added{Since this decomposition is performed separately for each group of covariates, the grouping information is preserved in the transformation from \protect$\mathbf{X}$ to \protect$\mathbf{Z}$.
-We may then build an SGL model relating \protect$y$ and \protect$\mathbf{Z}$,}
+The product \protect$\mathbf{Z} = \mathbf{U \Sigma}$ is an \protect$n \times r$ matrix containing the principal component row vectors needed to reproduce \protect$\mathbf{X}^{(\ell)}$ in the basis provided by \protect$\mathbf{V}^T$.
+
+Since this decomposition is performed separately for each group of covariates, the grouping information is preserved in the transformation from \protect$\mathbf{X}$ to \protect$\mathbf{Z}$.
+We may then build an SGL model relating \protect$y$ and \protect$\mathbf{Z}$,
 
@@
 \end{align}
-\added{The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.}
+The PCR-SGL coefficients \protect$\hat{\theta}$ may be projected back onto the original feature space using \protect$\hat{\beta} = \mathbf{V} \hat{\theta}$.
 
@@
 applied to the data before fitting the linear coefficients.
-\added{This is similar to the use of a link function in a generalized linear model, but without the adoption of an exponential probability distribution \mbox{\cite{nelder1972technique}}.}
-For \deleted{example, for} the WH, HBN, and Cam-CAN datasets, we use a
+This is similar to the use of a link function in a generalized linear model, but without the adoption of an exponential probability distribution \cite{nelder1972technique}.
+For the WH, HBN, and Cam-CAN datasets, we use a
 logarithmic transform,
@@
 \end{equation}
-\added{implemented using scikit-learn's \lstinline|TransformedTargetRegressor| meta-estimator \mbox{\cite{scikit-learn}} with numpy's \lstinline|log| and \lstinline|exp| as the transform and inverse transform functions, respectively \mbox{\cite{harris2020array}}.}
+implemented using scikit-learn's \lstinline|TransformedTargetRegressor| meta-estimator \cite{scikit-learn} with numpy's \lstinline|log| and \lstinline|exp| as the transform and inverse transform functions, respectively \cite{harris2020array}.
 
@@
 Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
-\added{and John Kruper}
+and John Kruper
 for helpful comments on the manuscript.
-\added{Data collection and sharing for this project was provided by the Cambridge Centre for Ageing and Neuroscience (CamCAN).
+Data collection and sharing for this project was provided by the Cambridge Centre for Ageing and Neuroscience (CamCAN).
 CamCAN funding was provided by the UK Biotechnology and Biological Sciences Research Council (grant number BB/H008217/1), together with support from the UK Medical Research Council and University of Cambridge, UK.
 This manuscript was prepared using a limited access dataset obtained from the Child Mind Institute Biobank, The Healthy Brain Network dataset.
-This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute}
+This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute
 

### 2021-06-09 reports/manuscript/paper.tex
Fix PLOS formatting requests

@@
 \bigskip
-\textbf{1} eScience Institute, University of Washington, Seattle, WA, USA
+\textbf{1} eScience Institute, University of Washington, Seattle, Washington, United States of America
 \\
-\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, CA, USA
+\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, California, United States of America
 \\
-\textbf{3} Department of Biostatistics, University of Washington, Seattle, WA, USA
+\textbf{3} Department of Biostatistics, University of Washington, Seattle, Washington, United States of America
 \\
-\textbf{4} Department of Psychology, University of Washington, Seattle, WA, USA
+\textbf{4} Department of Psychology, University of Washington, Seattle, Washington, United States of America
 \\
@@
 
+\begin{figure}[b!]
+    % \vspace{0.25cm}
+    % \rlap{
+    %     \hspace{-0.25em}
+    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
+    % }
+    % \vspace{-8.4cm}
+    % \includegraphics[width=\columnwidth]{method-quad.pdf}
+    {\phantomsubcaption\label{fig:methods:tractogram}}
+    {\phantomsubcaption\label{fig:methods:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
+    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
+    {\phantomsubcaption\label{fig:methods:group-structure}}
+    \caption{\label{fig:methods}
+    {\bf Tractometry data flow}
+    \textbf{(a)} Whole brain tractography generates streamlines approximating
+        the trajectories of white matter connections.
+        \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
+        In this case, we show the left corticospinal tract (CSTL)
+        and the left arcuate fasciculus (ARCL)
+        over a mid-saggital anatomical slice.
+        Tract profiling further extracts bundle profiles,
+        quantifications of various diffusion metrics along the length of the
+        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
+        profile for \textbf{(c)} the CSTL and \textbf{(d)} the ARCL.
+        \textbf{(d)} the phenotypical target data and tract profile
+        features can be organized into a linear model, $\hat{y} = \mathbf{X}
+        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
+        to reveal a natural group structure: the left (orange) group
+        contains $k$ features from the CSTL, the middle (green) group
+        contains $k$ features from the left cingulum cingulate (CGCL),
+        and the right (blue) group
+        contains $k$ features from the ARCL.
+        The coefficients in $\hat{\beta}$ follow the same natural grouping.
+Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})
+    }
+\end{figure}
+
 % Results
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups (see supplemental Figs S1 and S2 for tract profiles of all 18 tracts in these groups).
+right CST, plotted over the FA values for the control and ALS subject groups
+(see \nameref{S1_Fig} and \nameref{S2_Fig} for tract profiles of all 18 tracts in these groups).
 We find that SGL and PCR-SGL select FA metrics in the corticospinal tract and
@@
 method predicts incorrectly this is done in a comprehensible manner.
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
+    % }
+    % \vspace{-7.0cm}
+    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
+    {\phantomsubcaption\label{fig:class-results:probs}}
+    {\phantomsubcaption\label{fig:class-results:coefs3d}}
+    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
+    {\phantomsubcaption\label{fig:class-results:false-positives}}
+    {\phantomsubcaption\label{fig:class-results:false-negatives}}
+    \caption{
+    {\bf PCR-SGL accurately and interpretably predicts ALS diagnosis.}
+    {\bf (a)} Classification probabilities for ALS diagnosis, with
+    controls on the left, patients on the right, predicted controls in
+    blue, and predicted patients in orange. That is, orange dots on the left
+    represent false positives, while blue dots on the right represent
+    false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
+    ROC AUC of {\protect\alsRocAuc}.
+    {\bf (b)} PCR-SGL coefficients are presented on the core fibers of major
+    fiber bundles. They exhibit high group sparsity and are concentrated
+    in the FA of the corticospinal tract (CST).
+    The brain is oriented with the right hemisphere
+    in the foreground and anterior to the right of the page. The CSTL, CSTR,
+    callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)
+    bundles are indicated for orientation.
+    {\bf (c)} PCR-SGL identifies three portions of the CST as important,
+    where $\hat{\beta}$ (dashed line, right axis) has large values. These
+    are centered around nodes 30, 65, and 90, corresponding to locations
+    of substantial differences in FA between the ALS and control groups
+    (shaded areas indicates standard error of the mean).
+    {\bf (d)} Bundle profiles for false positive classifications. Line
+    colors correspond to the marker edge color in the top left plot.
+    These individuals have reduced FA in the CST portions which SGL
+    identified as important. Their misclassification is coherent with the
+    feature importance and the group differences in FA.
+    {\bf (e)} Individual bundle profiles for false negative
+    classifications. These individuals have bundle profiles which
+    oscillate between the group means.
+    \label{fig:class-results}
+    }
+\end{figure}
 
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see supplemental Figs S3 to S8 for the full tract profile information in all tracts/datasets.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets
+see \nameref{S3_Fig} to \nameref{S8_Fig} for the full tract profile information in all tracts/datasets.
 
@@
 \cref{fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d}
-and supporing figures in \nameref{S1_Appendix}).
+and supporing figures in \nameref{S3_Fig} to \nameref{S8_Fig}).
 This demonstrates that SGL is not coerced to produce overly sparse results
@@
 for globally distributed phenomena. Conversely, the SGL models are able to adapt to this regime.
+
+\begin{figure}[b!]
+    % \vspace{3.0cm}
+    % \rlap{
+    %     \hspace{0.775cm}
+    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
+    %     \hspace{0.5em}
+    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
+    % }
+    % \vspace{-6.1cm}
+    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
+    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
+    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
+    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
+    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
+    {\phantomsubcaption\label{fig:age-results:wh-profile}}
+    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
+    {\phantomsubcaption\label{fig:age-results:cc-profile}}
+    \phantomcaption{%
+    {\bf Predicting age with tractometry and SGL.}
+    {\bf (top)} The predicted age vs. true age of each individual from the test
+splits (i.e., when each subject's data was held out in fitting the model) for
+the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN datasets; an accurate
+prediction falls close to the $y=x$ line (dashed). The mean absolute error (MAE)
+and coefficient of determination $R^2$ are presented in the lower right of each
+scatter plot. {\bf (middle)} Feature importance for predicting age from
+tract profile in the {\bf (d)} WH, {\bf (e)} HBN, and
+{\bf (f)} Cam-CAN datasets. The orientation of the brain is that same as in
+\cref{fig:class-results:coefs3d}, however because the coefficients exhibit high
+global sparsity (as opposed to group sparsity), we plot the mean of the absolute
+value of $\hat{\beta}$ for each bundle on the core fiber. The global
+distrubution of the $\hat{\beta}$ coefficients reflects the fact that aging is
+not confined to a single white matter bundle. {\bf (bottom)} Age quintile bundle
+profiles for the {\bf (g)} WH, {\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
+    \label{fig:age-results}
+    }
+\end{figure}
+
+\begin{figure}[b!]
+    % \includegraphics[width=\textwidth]{model_performance.pdf}
+    \caption{%
+    {\bf Model performance across all datasets.}
+Each panel shows model performance measured on the test set for each
+cross-validation split, with each black dot representing a split, box
+plots representing the quartiles, and white diamonds representing the mean
+performance. The $y$-scale varies in each subplot.
+\textbf{(a)} Accuracy of test set predictions for the
+ALS dataset. Because group differences
+in ALS diagnosis are mostly confined to a single bundle, the group
+structure-preserving methods, SGL and PCR-SGL, outperform the other
+models.
+The remaining frames show coefficient of determination, \protect$R^2$ in test sets
+for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN
+datasets. Because aging affects the white matter globally, group structure-blind
+methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL
+models show competitve predictive performance, adapting to a problem where
+group structure is not as informative. PCR-SGL performs poorly in this regime
+because its initial group-wise PC projection destroys between bundle covariance.
+The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.
+    \label{fig:model-performance}
+    }
+\end{figure}
 
@@
 properties \cite{yeatman2014lifespan}.
-We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the supplementary material.
+We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in \nameref{S3_Fig} to \nameref{S8_Fig}.
 For age regression, substantial differences between the datasets preclude generalization across all three:
@@
 was provided as approved by the Ethical Committee of the University
-``Magna Graecia'' of Catanzaro. Voxel resolution was \num{2x2x2}
-$\text{mm}^3$ and 27 non-colinear directions were measured with a
+``Magna Graecia'' of Catanzaro. Voxel resolution was
+$2 \times 2 \times 2 \text{mm}^3$ and 27 non-colinear directions were measured with a
 $b=1000$ $\text{s} / \text{mm}^2$. Data was preprocessed to
@@
 was provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$\textrm{mm}^3$ with 96 non-colinear directions measured with a
+$2 \times 2 \times 2 \textrm{mm}^3$ with 96 non-colinear directions measured with a
 $b=2000$ $\textrm{s} / \textrm{mm}^2$ and 30 non-colinear directions
 measured with a $b=1000$ $\textrm{s} / \textrm{mm}^2$. These data
-were acquired using a dual spin echo sequence, in which there is
+were acquired using a twice refocused spin echo sequence, in which there is
 sufficient time for eddy currents to subside between the application of
@@
 sites in the New York
-area: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center.
+area: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center. Age distributions of participants in the different sites are in \nameref{S9_Fig}.
 Informed consent was obtained from each participant aged 18 or older. For
@@
 guardians and written assent was obtained from the participant. Voxel
-resolution was \num{1.8x1.8x1.8}$\text{mm}^3$ with 64 non-colinear directions
+resolution was $1.8 \times 1.8 \times 1.8 \text{mm}^3$ with 64 non-colinear directions
 measured for each of $b=1000 \text{s} / \text{mm}^2$ and $b=2000 \text{s} /
@@
 system and written informed consent was obtained from each participant. Voxel
-resolution was \num{2x2x2}$\text{mm}^3$ with 30 non-colinear directions
+resolution was $2 \times 2 \times 2 \text{mm}^3$ with 30 non-colinear directions
 measured for each of $b=1000$ $\text{s} / \text{mm}^2$ and $b=2000$
@@
 in each voxel (STT) \cite{basser2000vivo}. Eighteen major
-tracts, which are enumerated in the supplemental material, were identified
+tracts, which are enumerated in \nameref{S1_Fig}, were identified
 using multiple criteria: streamlines are selected as candidates for
@@
 are quantified and averaged along eighteen major fiber tracts,
-which are enumerated in the supplemental material.
+which are enumerated in \nameref{S1_Fig}.
 See Fig S3 of \cite{kruper2021evaluating} for a depiction of these white matter bundles.
@@
 Initially designed to correct for site effects in gene expression studies \cite{johnson2007adjusting}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \cite{fortin2018harmonization}, multi-site DTI studies \cite{fortin2017harmonization}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \cite{nielson2018detecting}.
-We rely on the \texttt{neurocombat\_sklearn} library \cite{neurocombat_sklearn}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences in the supplemental material.
+We rely on the \texttt{neurocombat\_sklearn} library \cite{neurocombat_sklearn}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences and ComBat correction in \nameref{S10_Fig} to \nameref{S13_Fig}.
 
@@
 
+\begin{figure}[h!]
+    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
+    \phantomcaption{
+    {\bf Nested cross-validation.}
+We evaluate model quality using a nested $k$-fold cross validation
+scheme. At level-0, the input data is decomposed into $k_0$ shuffled
+groups and optimal hyperparameters are found for the level-0 training
+set. To avoid overfitting, the optimal hyperparameters are themselves
+evaluated using a cross-validation scheme taking place at level-1 of
+the decomposition, where each level-0 training set is further
+decomposed into $k_1 = 3$ shuffled groups. In the classification
+case, the training and test splits are stratified by diagnosis. For
+the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
+$k_0 = 5$.
+    \label{fig:nested-cross-val}
+    }
+\end{figure}
+
 \subsection*{Software implementation}
@@
 
-\section*{Supporting information}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Bundle and regression coefficient profiles.}
-In this supporting section, we present bundle profiles and $\hat{\beta}$ coefficients
-for each anatomical bundle and in each dataset.
-
 \section*{Acknowledgments}
 
-This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
-National Institutes for Mental Health, by a grant from the Gordon \& Betty
-Moore Foundation and the Alfred P. Sloan Foundation to the University of
-Washington eScience Institute Data Science Environment, and by the Google
-Cloud Platform Academic Research Credits Program. We would like to thank
-Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
-and John Kruper
+We would like to thank Scott Murray for a useful discussion of the SGL method
+and Mareike Grotheer and John Kruper
 for helpful comments on the manuscript.
@@
 This manuscript was prepared using a limited access dataset obtained from the Child Mind Institute Biobank, The Healthy Brain Network dataset.
-This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute
+This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute.
 
@@
 
-\bibliography{paper}
+% \bibliography{paper}
 % Compile your BiBTeX database using our plos2015.bst
@@
 
-\newpage
-
-\section*{Figure legends}
-
-\begin{figure}[b!]
-    % \vspace{0.25cm}
-    % \rlap{
-    %     \hspace{-0.25em}
-    %     \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
-    % }
-    % \vspace{-8.4cm}
-    % \includegraphics[width=\columnwidth]{method-quad.pdf}
-    {\phantomsubcaption\label{fig:methods:tractogram}}
-    {\phantomsubcaption\label{fig:methods:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:cst}}
-    {\phantomsubcaption\label{fig:methods:tract-profile:fa}}
-    {\phantomsubcaption\label{fig:methods:group-structure}}
-    \phantomcaption{\label{fig:methods}}
-\end{figure}
-
-\begin{figure}[b!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \includegraphics[width=0.33\textwidth]{als_gpca_coefs.pdf}
-    % }
-    % \vspace{-7.0cm}
-    % \includegraphics[width=\textwidth]{als_gpca_results.pdf}
-    {\phantomsubcaption\label{fig:class-results:probs}}
-    {\phantomsubcaption\label{fig:class-results:coefs3d}}
-    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
-    {\phantomsubcaption\label{fig:class-results:false-positives}}
-    {\phantomsubcaption\label{fig:class-results:false-negatives}}
-    \phantomcaption{%
-    \label{fig:class-results}
-    }
-\end{figure}
-
-\begin{figure}[b!]
-    % \vspace{3.0cm}
-    % \rlap{
-    %     \hspace{0.775cm}
-    %     \includegraphics[width=0.26\textwidth]{wh_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{hbn_coefs.pdf}
-    %     \hspace{0.5em}
-    %     \includegraphics[width=0.26\textwidth]{camcan_coefs.pdf}
-    % }
-    % \vspace{-6.1cm}
-    % \includegraphics[width=\textwidth]{regression_scatter.pdf}
-    {\phantomsubcaption\label{fig:age-results:wh-scatter}}
-    {\phantomsubcaption\label{fig:age-results:hbn-scatter}}
-    {\phantomsubcaption\label{fig:age-results:cc-scatter}}
-    {\phantomsubcaption\label{fig:age-results:wh-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:hbn-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:cc-coefs3d}}
-    {\phantomsubcaption\label{fig:age-results:wh-profile}}
-    {\phantomsubcaption\label{fig:age-results:hbn-profile}}
-    {\phantomsubcaption\label{fig:age-results:cc-profile}}
-    \phantomcaption{%
-    \label{fig:age-results}
-    }
-\end{figure}
-
-\begin{figure}[b!]
-    % \includegraphics[width=\textwidth]{model_performance.pdf}
-    \phantomcaption{%
-    \label{fig:model-performance}
-    }
-\end{figure}
-
-\begin{figure}[h!]
-    % \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
-    \phantomcaption{
-    \label{fig:nested-cross-val}
-    }
-\end{figure}
-
-\paragraph{Figure 1: Tractometry data flow}
-\textbf{(a)} Whole brain tractography generates streamlines approximating
-    the trajectories of white matter connections.
-    \textbf{(b)} Tractometry classifies these streamlines into anatomical bundles.
-    In this case, we show the left corticospinal tract (CSTL)
-    and the left arcuate fasciculus (ARCL)
-    over a mid-saggital anatomical slice.
-    Tract profiling further extracts bundle profiles,
-    quantifications of various diffusion metrics along the length of the
-    fiber bundle. Here, we show one subject's fractional anisotropy (FA)
-    profile for \textbf{(c)} the CSTL and \textbf{(d)} the ARCL.
-    \textbf{(d)} the phenotypical target data and tract profile
-    features can be organized into a linear model, $\hat{y} = \mathbf{X}
-    \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
-    to reveal a natural group structure: the left (orange) group
-    contains $k$ features from the CSTL, the middle (green) group
-    contains $k$ features from the left cingulum cingulate (CGCL),
-    and the right (blue) group
-    contains $k$ features from the ARCL.
-    The coefficients in $\hat{\beta}$ follow the same natural grouping.
-Panels (a) and (b) are adapted from \url{https://figshare.com/articles/figure/example_tractography-segmentation/14485350}, and reproduced under the CC-BY license (\url{https://creativecommons.org/licenses/by/4.0/})
-
-\paragraph{Figure 2: PCR-SGL accurately and interpretably predicts ALS diagnosis.}
-{\bf (a)} Classification probabilities for ALS diagnosis, with
-controls on the left, patients on the right, predicted controls in
-blue, and predicted patients in orange. That is, orange dots on the left
-represent false positives, while blue dots on the right represent
-false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
-ROC AUC of {\protect\alsRocAuc}.
-{\bf (b)} PCR-SGL coefficients are presented on the core fibers of major
-fiber bundles. They exhibit high group sparsity and are concentrated
-in the FA of the corticospinal tract (CST).
-The brain is oriented with the right hemisphere
-in the foreground and anterior to the right of the page. The CSTL, CSTR,
-callosum forceps anterior (CFA), left arcuate (ARCL), and right arcuate (ARCR)
-bundles are indicated for orientation.
-{\bf (c)} PCR-SGL identifies three portions of the CST as important,
-where $\hat{\beta}$ (dashed line, right axis) has large values. These
-are centered around nodes 30, 65, and 90, corresponding to locations
-of substantial differences in FA between the ALS and control groups
-(shaded areas indicates standard error of the mean).
-{\bf (d)} Bundle profiles for false positive classifications. Line
-colors correspond to the marker edge color in the top left plot.
-These individuals have reduced FA in the CST portions which SGL
-identified as important. Their misclassification is coherent with the
-feature importance and the group differences in FA.
-{\bf (e)} Individual bundle profiles for false negative
-classifications. These individuals have bundle profiles which
-oscillate between the group means.
-
-\paragraph{Figure 3: Predicting age with tractometry and SGL.}
-{\bf (top)} The predicted age vs. true age of each individual from the test
-splits (i.e., when each subject's data was held out in fitting the
-model) for the {\bf (a)} WH, {\bf (b)} HBN, and {\bf (c)} Cam-CAN
-datasets; an accurate prediction falls close to the $y=x$ line
-(dashed). The mean absolute error (MAE) and coefficient of
-determination $R^2$ are presented in the lower right of each scatter
-plot.
-{\bf (middle)} Feature importance for predicting age from
-tract profile in
-the {\bf (d)} WH, {\bf (e)} HBN, and {\bf (f)} Cam-CAN datasets.
-The orientation of the
-brain is that same as in \cref{fig:class-results:coefs3d}, however because
-the coefficients exhibit high global sparsity (as opposed to group
-sparsity), we plot the mean of the absolute value of $\hat{\beta}$
-for each bundle on the core fiber. The global distrubution of the
-$\hat{\beta}$ coefficients reflects the fact that aging is not
-confined to a single white matter bundle.
-{\bf (bottom)} Age quintile bundle profiles for the {\bf (g)} WH,
-{\bf (h)} HBN, and {\bf (i)} Cam-CAN datasets.
-
-\paragraph{Figure 4: Model performance across all datasets.}
-Each panel shows model performance measured on the test set for each
-cross-validation split, with each black dot representing a split, box
-plots representing the quartiles, and white diamonds representing the mean
-performance. The $y$-scale varies in each subplot.
-\textbf{(a)} Accuracy of test set predictions for the
-ALS dataset. Because group differences
-in ALS diagnosis are mostly confined to a single bundle, the group
-structure-preserving methods, SGL and PCR-SGL, outperform the other
-models.
-The remaining frames show coefficient of determination, \protect$R^2$ in test sets
-for the \textbf{(b)} WH, \textbf{(c)} HBN, and \textbf{(c)} Cam-CAN
-datasets. Because aging affects the white matter globally, group structure-blind
-methods like elastic net and PCR Lasso perform well. Nonetheless, the SGL
-models show competitve predictive performance, adapting to a problem where
-group structure is not as informative. PCR-SGL performs poorly in this regime
-because its initial group-wise PC projection destroys between bundle covariance.
-The bundle-mean lasso performs poorly, demonstrating the value of along-tract profiling.
-
-\paragraph{Figure 5: Nested cross-validation.}
-We evaluate model quality using a nested $k$-fold cross validation
-scheme. At level-0, the input data is decomposed into $k_0$ shuffled
-groups and optimal hyperparameters are found for the level-0 training
-set. To avoid overfitting, the optimal hyperparameters are themselves
-evaluated using a cross-validation scheme taking place at level-1 of
-the decomposition, where each level-0 training set is further
-decomposed into $k_1 = 3$ shuffled groups. In the classification
-case, the training and test splits are stratified by diagnosis. For
-the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
-$k_0 = 5$.
+\begin{thebibliography}{100}
+
+\bibitem{stejskal1965spin}
+Stejskal EO, Tanner JE.
+\newblock {Spin Diffusion Measurements: Spin Echoes in the Presence of a
+  Time-Dependent Field Gradient}.
+\newblock The Journal of Chemical Physics. 1965;42(1):288--292.
+\newblock doi:{10.1063/1.1695690}.
+
+\bibitem{wandell2016clarifying}
+Wandell BA.
+\newblock Clarifying human white matter.
+\newblock Annual review of neuroscience. 2016;39:103--128.
+
+\bibitem{Conturo1999-je}
+Conturo TE, Lori NF, Cull TS, Akbudak E, Snyder AZ, Shimony JS, et~al.
+\newblock Tracking neuronal fiber pathways in the living human brain.
+\newblock Proc Natl Acad Sci U S A. 1999;96(18):10422--10427.
+
+\bibitem{Mori2002-qi}
+Mori S, Van~Zijl PCM.
+\newblock Fiber tracking: principles and strategies--a technical review.
+\newblock NMR in Biomedicine: An International Journal Devoted to the
+  Development and Application of Magnetic Resonance In Vivo.
+  2002;15(7-8):468--480.
+
+\bibitem{yeatman2012tract}
+Yeatman JD, Dougherty RF, Myall NJ, Wandell BA, Feldman HM.
+\newblock Tract profiles of white matter properties: automating fiber-tract
+  quantification.
+\newblock PloS one. 2012;7(11):e49790.
+
+\bibitem{Jones2005-yq}
+Jones DK, Travis AR, Eden G, Pierpaoli C, Basser PJ.
+\newblock {PASTA}: pointwise assessment of streamline tractography attributes.
+\newblock Magn Reson Med. 2005;53(6):1462--1467.
+
+\bibitem{Bells2011-cf}
+Bells S, Cercignani M, Deoni S, Assaf Y, Pasternak O, Evans C, et~al.
+\newblock Tractometry--comprehensive multi-modal quantitative assessment of
+  white matter along specific tracts.
+\newblock In: Proc. ISMRM. vol. 678; 2011. p.~1.
+
+\bibitem{colby2012}
+Colby JB, Soderberg L, Lebel C, Dinov ID, Thompson PM, Sowell ER.
+\newblock Along-tract statistics allow for enhanced tractography analysis.
+\newblock Neuroimage. 2012;59(4):3227--3242.
+
+\bibitem{ODonnell2009-uu}
+O'Donnell LJ, Westin CF, Golby AJ.
+\newblock Tract-based morphometry for white matter group analysis.
+\newblock Neuroimage. 2009;45(3):832--844.
+
+\bibitem{Nichols2002-zu}
+Nichols TE, Holmes AP.
+\newblock Nonparametric permutation tests for functional neuroimaging: a primer
+  with examples.
+\newblock Hum Brain Mapp. 2002;15(1):1--25.
+
+\bibitem{Nichols2003-yy}
+Nichols T, Hayasaka S.
+\newblock {Controlling the familywise error rate in functional neuroimaging: a
+  comparative review}.
+\newblock Stat Methods Med Res. 2003;12(5):419--446.
+
+\bibitem{chamberland2019dimensionality}
+Chamberland M, Raven EP, Genc S, Duffy K, Descoteaux M, Parker GD, et~al.
+\newblock Dimensionality reduction of diffusion {MRI} measures for improved
+  tractometry of the human brain.
+\newblock NeuroImage. 2019;200:89--100.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2019.06.020}.
+
+\bibitem{huber2018rapid}
+Huber E, Donnelly PM, Rokem A, Yeatman JD.
+\newblock Rapid and widespread white matter plasticity during an intensive
+  reading intervention.
+\newblock Nature communications. 2018;9(1):2260.
+
+\bibitem{dayan2016profilometry}
+Dayan M, Monohan E, Pandya S, Kuceyeski A, Nguyen TD, Raj A, et~al.
+\newblock Profilometry: a new statistical framework for the characterization of
+  white matter pathways, with application to multiple sclerosis.
+\newblock Human brain mapping. 2016;37(3):989--1004.
+
+\bibitem{Murdoch2019-ax}
+Murdoch WJ, Singh C, Kumbier K, Abbasi-Asl R, Yu B.
+\newblock Definitions, methods, and applications in interpretable machine
+  learning.
+\newblock Proc Natl Acad Sci U S A. 2019;116(44):22071--22080.
+
+\bibitem{Breiman2001-uz}
+Breiman L.
+\newblock {Statistical Modeling: The Two Cultures (with comments and a
+  rejoinder by the author)}.
+\newblock Stat Sci. 2001;16(3):199--231.
+
+\bibitem{smith2006tract}
+Smith SM, Jenkinson M, Johansen-Berg H, Rueckert D, Nichols TE, Mackay CE,
+  et~al.
+\newblock Tract-based spatial statistics: voxelwise analysis of multi-subject
+  diffusion data.
+\newblock Neuroimage. 2006;31(4):1487--1505.
+
+\bibitem{yeh2016connectometry}
+Yeh FC, Badre D, Verstynen T.
+\newblock Connectometry: a statistical approach harnessing the analytical
+  potential of the local connectome.
+\newblock Neuroimage. 2016;125:162--171.
+
+\bibitem{Bzdok2020-sd}
+Bzdok D, Engemann D, Thirion B.
+\newblock Inference and Prediction Diverge in Biomedicine.
+\newblock Patterns (N Y). 2020;1(8):100119.
+
+\bibitem{Naselaris2011-ss}
+Naselaris T, Kay KN, Nishimoto S, Gallant JL.
+\newblock Encoding and decoding in {fMRI}.
+\newblock Neuroimage. 2011;56(2):400--410.
+
+\bibitem{Tibshirani1996-qs}
+Tibshirani R.
+\newblock {Regression Shrinkage and Selection via the Lasso}.
+\newblock J R Stat Soc Series B Stat Methodol. 1996;58(1):267--288.
+
+\bibitem{Yuan2006-ky}
+Yuan M, Lin Y.
+\newblock Model selection and estimation in regression with grouped variables.
+\newblock J R Stat Soc Series B Stat Methodol. 2006;68(1):49--67.
+
+\bibitem{simon2013sgl}
+Simon N, Friedman J, Hastie T, Tibshirani R.
+\newblock A sparse-group lasso.
+\newblock Journal of Computational and Graphical Statistics.
+  2013;22(2):231--245.
+
+\bibitem{powell2018local}
+Powell MA, Garcia JO, Yeh FC, Vettel JM, Verstynen T.
+\newblock {Local connectome phenotypes predict social, health, and cognitive
+  factors}.
+\newblock Network Neuroscience. 2018;2(1):86--105.
+\newblock doi:{10.1162/NETN\_a\_00031}.
+
+\bibitem{rasero2021integrating}
+Rasero J, Sentis AI, Yeh FC, Verstynen T.
+\newblock Integrating across neuroimaging modalities boosts prediction accuracy
+  of cognitive ability.
+\newblock PLOS Computational Biology. 2021;17(3):1--25.
+\newblock doi:{10.1371/journal.pcbi.1008347}.
+
+\bibitem{sarica2017corticospinal}
+Sarica A, Cerasa A, Valentino P, Yeatman J, Trotta M, Barone S, et~al.
+\newblock The corticospinal tract profile in amyotrophic lateral sclerosis.
+\newblock Human brain mapping. 2017;38(2):727--739.
+
+\bibitem{van2011upper}
+van~der Graaff MM, Sage CA, Caan MW, Akkerman EM, Lavini C, Majoie CB, et~al.
+\newblock Upper and extra-motoneuron involvement in early motoneuron disease: a
+  diffusion tensor imaging study.
+\newblock Brain. 2011;134(4):1211--1228.
+
+\bibitem{toosy2003diffusion}
+Toosy A, Werring D, Orrell R, Howard R, King M, Barker G, et~al.
+\newblock Diffusion tensor imaging detects corticospinal tract involvement at
+  multiple levels in amyotrophic lateral sclerosis.
+\newblock Journal of Neurology, Neurosurgery \& Psychiatry.
+  2003;74(9):1250--1257.
+
+\bibitem{sarica2014tractography}
+Sarica A, Cerasa A, Vasta R, Perrotta P, Valentino P, Mangone G, et~al.
+\newblock Tractography in amyotrophic lateral sclerosis using a novel
+  probabilistic tool: a study with tract-based reconstruction compared to
+  voxel-based approach.
+\newblock Journal of neuroscience methods. 2014;224:79--87.
+
+\bibitem{sage2007quantitative}
+Sage CA, Peeters RR, G{\"o}rner A, Robberecht W, Sunaert S.
+\newblock Quantitative diffusion tensor imaging in amyotrophic lateral
+  sclerosis.
+\newblock Neuroimage. 2007;34(2):486--499.
+
+\bibitem{sage2009quantitative}
+Sage CA, Van~Hecke W, Peeters R, Sijbers J, Robberecht W, Parizel P, et~al.
+\newblock Quantitative diffusion tensor imaging in amyotrophic lateral
+  sclerosis: revisited.
+\newblock Human brain mapping. 2009;30(11):3657--3675.
+
+\bibitem{karlsborg2004corticospinal}
+Karlsborg M, Rosenbaum S, Wiegell MR, Simonsen H, Larsson HB, Werdelin LM,
+  et~al.
+\newblock {Corticospinal tract degeneration and possible pathogenesis in ALS
+  evaluated by MR diffusion tensor imaging}.
+\newblock Amyotrophic Lateral Sclerosis and Other Motor Neuron Disorders.
+  2004;5(3):136--140.
+
+\bibitem{ellis1999diffusion}
+Ellis C, Simmons A, Jones D, Bland J, Dawson J, Horsfield M, et~al.
+\newblock {Diffusion tensor MRI assesses corticospinal tract damage in ALS}.
+\newblock Neurology. 1999;53(5):1051--1051.
+
+\bibitem{cosottini2005diffusion}
+Cosottini M, Giannelli M, Siciliano G, Lazzarotti G, Michelassi MC, Del~Corona
+  A, et~al.
+\newblock {Diffusion-tensor MR imaging of corticospinal tract in amyotrophic
+  lateral sclerosis and progressive muscular atrophy}.
+\newblock Radiology. 2005;237(1):258--264.
+
+\bibitem{ciccarelli2009investigation}
+Ciccarelli O, Behrens TE, Johansen-Berg H, Talbot K, Orrell RW, Howard RS,
+  et~al.
+\newblock {Investigation of white matter pathology in ALS and PLS using
+  tract-based spatial statistics}.
+\newblock Human brain mapping. 2009;30(2):615--624.
+
+\bibitem{abe2010voxel}
+Abe O, Takao H, Gonoi W, Sasaki H, Murakami M, Kabasawa H, et~al.
+\newblock Voxel-based analysis of the diffusion tensor.
+\newblock Neuroradiology. 2010;52(8):699--710.
+
+\bibitem{Cole2019-rz}
+Cole JH, Marioni RE, Harris SE, Deary IJ.
+\newblock Brain age and other bodily 'ages': implications for neuropsychiatry.
+\newblock Mol Psychiatry. 2019;24(2):266--281.
+
+\bibitem{nelson2019biomarkers}
+Nelson PG, Promislow DEL, Masel J.
+\newblock {Biomarkers for Aging Identified in Cross-sectional Studies Tend to
+  Be Non-causative}.
+\newblock The Journals of Gerontology: Series A. 2019;75(3):466--472.
+\newblock doi:{10.1093/gerona/glz174}.
+
+\bibitem{yeatman2014lifespan}
+Yeatman JD, Wandell BA, Mezer AA.
+\newblock Lifespan maturation and degeneration of human brain white matter.
+\newblock Nature communications. 2014;5:4932.
+
+\bibitem{alexander2017open}
+Alexander LM, Escalera J, Ai L, Andreotti C, Febre K, Mangone A, et~al.
+\newblock An open resource for transdiagnostic research in pediatric mental
+  health and learning disorders.
+\newblock Scientific Data. 2017;4:170181.
+
+\bibitem{shafto2014cambridge}
+Shafto MA, Tyler LK, Dixon M, Taylor JR, Rowe JB, Cusack R, et~al.
+\newblock {The Cambridge Centre for Ageing and Neuroscience (Cam-CAN) study
+  protocol: a cross-sectional, lifespan, multidisciplinary examination of
+  healthy cognitive ageing}.
+\newblock BMC Neurology. 2014;14:204.
+\newblock doi:{https://doi.org/10.1186/s12883-014-0204-1}.
+
+\bibitem{taylor2017cambridge}
+Taylor JR, Williams N, Cusack R, Auer T, Shafto MA, Dixon M, et~al.
+\newblock {The Cambridge Centre for Ageing and Neuroscience (Cam-CAN) data
+  repository: Structural and functional MRI, MEG, and cognitive data from a
+  cross-sectional adult lifespan sample}.
+\newblock NeuroImage. 2017;144:262 -- 269.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2015.09.018}.
+
+\bibitem{jensen2005diffusion}
+Jensen JH, Helpern JA, Ramani A, Lu H, Kaczynski K.
+\newblock Diffusional kurtosis imaging: The quantification of non-gaussian
+  water diffusion by means of magnetic resonance imaging.
+\newblock Magnetic Resonance in Medicine. 2005;53(6):1432--1440.
+\newblock doi:{https://doi.org/10.1002/mrm.20508}.
+
+\bibitem{mcpherson2020single}
+{McPherson} B, Pestilli F.
+\newblock A single-mode associates global patterns of brain network structure
+  and behavior across the human lifespan.
+\newblock bioRxiv. 2020;doi:{10.1101/2020.09.24.312090}.
+
+\bibitem{Richard2018-ux}
+Richard G, Kolsk{\aa}r K, Sanders AM, Kaufmann T, Petersen A, Doan NT, et~al.
+\newblock Assessing distinct patterns of cognitive aging using tissue-specific
+  brain age prediction based on diffusion tensor imaging and brain morphometry.
+\newblock PeerJ. 2018;6:e5908.
+
+\bibitem{simon2013sparse}
+Simon N, Friedman J, Hastie T, Tibshirani R.
+\newblock A sparse-group lasso.
+\newblock Journal of Computational and Graphical Statistics.
+  2013;22(2):231--245.
+
+\bibitem{pinto2020harmonization}
+Pinto MS, Paolella R, Billiet T, Van~Dyck P, Guns PJ, Jeurissen B, et~al.
+\newblock Harmonization of Brain Diffusion MRI: Concepts and Methods.
+\newblock Frontiers in Neuroscience. 2020;14:396.
+\newblock doi:{10.3389/fnins.2020.00396}.
+
+\bibitem{lermausabiaga2019replication}
+Lerma-Usabiaga G, Mukherjee P, Ren Z, Perry ML, Wandell BA.
+\newblock Replication and generalization in applied neuroimaging.
+\newblock NeuroImage. 2019;202:116048.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2019.116048}.
+
+\bibitem{jernigan2016ping}
+Jernigan TL, Brown TT, Hagler DJ Jr, Akshoomoff N, Bartsch H, Newman E, et~al.
+\newblock {The Pediatric Imaging, Neurocognition, and Genetics (PING) Data
+  Repository}.
+\newblock Neuroimage. 2016;124(Pt B):1149--1154.
+
+\bibitem{jernigan2018abcd}
+Jernigan TL, Brown SA, Dowling GJ.
+\newblock {The Adolescent Brain Cognitive Development Study}.
+\newblock J Res Adolesc. 2018;28(1):154--156.
+
+\bibitem{Miller2016-hw}
+Miller KL, Alfaro-Almagro F, Bangerter NK, Thomas DL, Yacoub E, Xu J, et~al.
+\newblock Multimodal population brain imaging in the {UK} {B}iobank prospective
+  epidemiological study.
+\newblock Nat Neurosci. 2016;.
+
+\bibitem{VanEssen2012}
+{Van Essen} DC, Ugurbil K, Auerbach E, Barch D, Behrens TEJ, Bucholz R, et~al.
+\newblock {The Human Connectome Project: A data acquisition perspective}.
+\newblock NeuroImage. 2012;62(4):2222 -- 2231.
+\newblock doi:{http://dx.doi.org/10.1016/j.neuroimage.2012.02.018}.
+
+\bibitem{steinmetz2018distributed}
+Steinmetz N, Zatka-Haas P, Carandini M, Harris K.
+\newblock Distributed correlates of visually-guided behavior across the mouse
+  brain.
+\newblock Nature. 2018; p. in press.
+
+\bibitem{Jun2017-gv}
+Jun JJ, Steinmetz NA, Siegle JH, Denman DJ, Bauza M, Barbarits B, et~al.
+\newblock Fully integrated silicon probes for high-density recording of neural
+  activity.
+\newblock Nature. 2017;551(7679):232--236.
+
+\bibitem{zhou2012}
+Zhou J, Liu J, Narayan VA, Ye J.
+\newblock {Modeling Disease Progression via Fused Sparse Group Lasso}.
+\newblock In: Proceedings of the 18th {ACM} {SIGKDD} International Conference
+  on Knowledge Discovery and Data Mining. KDD '12. New York, NY, USA: ACM;
+  2012. p. 1095--1103.
+
+\bibitem{Rao2014-xm}
+Rao N, Nowak R, Cox C, Rogers T. Classification with Sparse Overlapping Groups;
+  2014.
+
+\bibitem{kruper2021evaluating}
+Kruper J, Yeatman JD, Richie-Halford A, Bloom D, Grotheer M, Caffarra S, et~al.
+\newblock Evaluating the reliability of human brain white matter tractometry.
+\newblock bioRxiv. 2021;doi:{10.1101/2021.02.24.432740}.
+
+\bibitem{yeatman2018browser}
+Yeatman JD, Richie-Halford A, Smith JK, Keshavan A, Rokem A.
+\newblock {A browser-based tool for visualization and analysis of diffusion MRI
+  data}.
+\newblock Nature communications. 2018;9(1):940.
+
+\bibitem{kluyver2016jupyter}
+Kluyver T, Ragan-Kelley B, P{\'e}rez F, Granger BE, Bussonnier M, Frederic J,
+  et~al.
+\newblock {Jupyter Notebooks-a publishing format for reproducible computational
+  workflows.}
+\newblock In: ELPUB; 2016. p. 87--90.
+
+\bibitem{basser1994mr}
+Basser PJ, Mattiello J, LeBihan D.
+\newblock {MR diffusion tensor spectroscopy and imaging}.
+\newblock Biophysical journal. 1994;66(1):259--267.
+
+\bibitem{chang2005restore}
+Chang LC, Jones DK, Pierpaoli C.
+\newblock {RESTORE: robust estimation of tensors by outlier rejection}.
+\newblock Magnetic Resonance in Medicine: An Official Journal of the
+  International Society for Magnetic Resonance in Medicine.
+  2005;53(5):1088--1095.
+
+\bibitem{nipype1}
+Gorgolewski K, Burns CD, Madison C, Clark D, Halchenko YO, Waskom ML, et~al.
+\newblock {Nipype: a flexible, lightweight and extensible neuroimaging data
+  processing framework in Python}.
+\newblock Frontiers in Neuroinformatics. 2011;5:13.
+\newblock doi:{10.3389/fninf.2011.00013}.
+
+\bibitem{nipype2}
+Gorgolewski KJ, Esteban O, Markiewicz CJ, Ziegler E, Ellis DG, Notter MP,
+  et~al.
+\newblock {Nipype}.
+\newblock Software. 2018;doi:{10.5281/zenodo.596855}.
+
+\bibitem{n4}
+Tustison NJ, Avants BB, Cook PA, Zheng Y, Egan A, Yushkevich PA, et~al.
+\newblock {N4ITK: Improved N3 Bias Correction}.
+\newblock IEEE Transactions on Medical Imaging. 2010;29(6):1310--1320.
+\newblock doi:{10.1109/TMI.2010.2046908}.
+
+\bibitem{mni}
+Fonov V, Evans A, McKinstry R, Almli C, Collins D.
+\newblock Unbiased nonlinear average age-appropriate brain templates from birth
+  to adulthood.
+\newblock NeuroImage. 2009;47, Supplement 1:S102.
+\newblock doi:{10.1016/S1053-8119(09)70884-5}.
+
+\bibitem{ants}
+Avants BB, Epstein CL, Grossman M, Gee JC.
+\newblock {Symmetric diffeomorphic image registration with cross-correlation:
+  Evaluating automated labeling of elderly and neurodegenerative brain}.
+\newblock Medical Image Analysis. 2008;12(1):26--41.
+\newblock doi:{10.1016/j.media.2007.06.004}.
+
+\bibitem{fsl_fast}
+Zhang Y, Brady M, Smith S.
+\newblock Segmentation of brain {MR} images through a hidden {M}arkov random
+  field model and the expectation-maximization algorithm.
+\newblock IEEE Transactions on Medical Imaging. 2001;20(1):45--57.
+\newblock doi:{10.1109/42.906424}.
+
+\bibitem{dwidenoise1}
+Veraart J, Novikov DS, Christiaens D, Ades-Aron B, Sijbers J, Fieremans E.
+\newblock Denoising of diffusion {MRI} using random matrix theory.
+\newblock NeuroImage. 2016;142:394--406.
+
+\bibitem{anderssoneddy}
+Andersson JL, Sotiropoulos SN.
+\newblock {An integrated approach to correction for off-resonance effects and
+  subject movement in diffusion MR imaging}.
+\newblock Neuroimage. 2016;125:1063--1078.
+
+\bibitem{eddyrepol}
+Andersson JL, Graham MS, Zsoldos E, Sotiropoulos SN.
+\newblock {Incorporating outlier detection and replacement into a
+  non-parametric framework for movement and distortion correction of diffusion
+  MR images}.
+\newblock Neuroimage. 2016;141:556--572.
+
+\bibitem{topup}
+Andersson JL, Skare S, Ashburner J.
+\newblock How to correct susceptibility distortions in spin-echo echo-planar
+  images: application to diffusion tensor imaging.
+\newblock Neuroimage. 2003;20(2):870--888.
+
+\bibitem{power_fd_dvars}
+Power JD, Mitra A, Laumann TO, Snyder AZ, Schlaggar BL, Petersen SE.
+\newblock {Methods to detect, characterize, and remove motion artifact in
+  resting state fMRI}.
+\newblock NeuroImage. 2014;84(Supplement C):320--341.
+\newblock doi:{10.1016/j.neuroimage.2013.08.048}.
+
+\bibitem{originalcsd}
+Tournier JD, Calamante F, Gadian DG, Connelly A.
+\newblock Direct estimation of the fiber orientation density function from
+  diffusion-weighted {MRI} data using spherical deconvolution.
+\newblock NeuroImage. 2004;23(3):1176--1185.
+
+\bibitem{tournier2008csd}
+Tournier JD, Yeh CH, Calamante F, Cho KH, Connelly A, Lin CP.
+\newblock Resolving crossing fibres using constrained spherical deconvolution:
+  validation using diffusion-weighted imaging phantom data.
+\newblock Neuroimage. 2008;42(2):617--625.
+
+\bibitem{dhollander2019response}
+Dhollander T, Mito R, Raffelt D, Connelly A.
+\newblock Improved white matter response function estimation for 3-tissue
+  constrained spherical deconvolution.
+\newblock In: Proc. Intl. Soc. Mag. Reson. Med; 2019. p. 555.
+
+\bibitem{dhollander2016unsupervised}
+Dhollander T, Raffelt D, Connelly A.
+\newblock Unsupervised 3-tissue response function estimation from single-shell
+  or multi-shell diffusion {MR} data without a co-registered {T1} image.
+\newblock In: ISMRM Workshop on Breaking the Barriers of Diffusion MRI. vol.~5;
+  2016. p.~5.
+
+\bibitem{mrtrix3}
+J-Donald, Smith R, Raffelt D, Tabbara R, Dhollander T, Pietsch M, et~al.
+\newblock {MRtrix3: A fast, flexible and open software framework for medical
+  image processing and visualisation}.
+\newblock NeuroImage. 2019;202:116137.
+
+\bibitem{mtnormalize}
+Raffelt D, Dhollander T, Tournier JD, Tabbara R, Smith RE, Pierre E, et~al.
+\newblock Bias field correction and intensity normalisation for quantitative
+  analysis of apparent fibre density.
+\newblock In: Proc. Intl. Soc. Mag. Reson. Med. vol.~25; 2017. p. 3541.
+
+\bibitem{nilearn}
+Abraham A, Pedregosa F, Eickenberg M, Gervais P, Mueller A, Kossaifi J, et~al.
+\newblock {Machine learning for neuroimaging with scikit-learn}.
+\newblock Frontiers in Neuroinformatics. 2014;8.
+\newblock doi:{10.3389/fninf.2014.00014}.
+
+\bibitem{dipy}
+Garyfallidis E, Brett M, Amirbekian B, Rokem A, Van Der~Walt S, Descoteaux M,
+  et~al.
+\newblock {DIPY, a library for the analysis of diffusion MRI data}.
+\newblock Frontiers in neuroinformatics. 2014;8:8.
+
+\bibitem{basser2000vivo}
+Basser PJ, Pajevic S, Pierpaoli C, Duda J, Aldroubi A.
+\newblock {In vivo fiber tractography using DT-MRI data}.
+\newblock Magnetic resonance in medicine. 2000;44(4):625--632.
+
+\bibitem{wakana2007reproducibility}
+Wakana S, Caprihan A, Panzenboeck MM, Fallon JH, Perry M, Gollub RL, et~al.
+\newblock Reproducibility of quantitative tractography methods applied to
+  cerebral white matter.
+\newblock Neuroimage. 2007;36(3):630--644.
+
+\bibitem{Hua2008-sh}
+Hua K, Zhang J, Wakana S, Jiang H, Li X, Reich DS, et~al.
+\newblock Tract probability maps in stereotaxic spaces: analyses of white
+  matter anatomy and tract-specific quantification.
+\newblock Neuroimage. 2008;39(1):336--347.
+
+\bibitem{gorgolewski2016brain}
+Gorgolewski KJ, Auer T, Calhoun VD, Craddock RC, Das S, Duff EP, et~al.
+\newblock The brain imaging data structure, a format for organizing and
+  describing outputs of neuroimaging experiments.
+\newblock Scientific data. 2016;3(1):1--9.
+
+\bibitem{johnson2007adjusting}
+Johnson WE, Li C, Rabinovic A.
+\newblock Adjusting batch effects in microarray expression data using empirical
+  Bayes methods.
+\newblock Biostatistics. 2007;8(1):118--127.
+
+\bibitem{fortin2018harmonization}
+Fortin JP, Cullen N, Sheline YI, Taylor WD, Aselcioglu I, Cook PA, et~al.
+\newblock Harmonization of cortical thickness measurements across scanners and
+  sites.
+\newblock Neuroimage. 2018;167:104--120.
+
+\bibitem{fortin2017harmonization}
+Fortin JP, Parker D, Tunç B, Watanabe T, Elliott MA, Ruparel K, et~al.
+\newblock Harmonization of multi-site diffusion tensor imaging data.
+\newblock NeuroImage. 2017;161:149--170.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2017.08.047}.
+
+\bibitem{nielson2018detecting}
+Nielson DM, Pereira F, Zheng CY, Migineishvili N, Lee JA, Thomas AG, et~al.
+\newblock Detecting and harmonizing scanner differences in the ABCD study -
+  annual release 1.0.
+\newblock bioRxiv. 2018;doi:{10.1101/309260}.
+
+\bibitem{neurocombat_sklearn}
+Pinaya WHL. NeuroCombat-sklearn; 2020.
+\newblock Available from: \url{https://github.com/Warvito/neurocombat_sklearn}.
+
+\bibitem{scikit-learn}
+Pedregosa F, Varoquaux G, Gramfort A, Michel V, Thirion B, Grisel O, et~al.
+\newblock {Scikit-learn: Machine Learning in Python}.
+\newblock Journal of Machine Learning Research. 2011;12:2825--2830.
+
+\bibitem{kaufman2012leakage}
+Kaufman S, Rosset S, Perlich C, Stitelman O.
+\newblock Leakage in data mining: Formulation, detection, and avoidance.
+\newblock ACM Transactions on Knowledge Discovery from Data (TKDD).
+  2012;6(4):15.
+
+\bibitem{tibshirani1996regression}
+Tibshirani R.
+\newblock Regression shrinkage and selection via the lasso.
+\newblock Journal of the Royal Statistical Society Series B (Methodological).
+  1996; p. 267--288.
+
+\bibitem{yuan2006model}
+Yuan M, Lin Y.
+\newblock Model selection and estimation in regression with grouped variables.
+\newblock Journal of the Royal Statistical Society: Series B (Statistical
+  Methodology). 2006;68(1):49--67.
+
+\bibitem{breiman1996bagging}
+Breiman L.
+\newblock Bagging predictors.
+\newblock Machine learning. 1996;24(2):123--140.
+
+\bibitem{nelder1972technique}
+Nelder JA, Wedderburn RWM.
+\newblock Generalized Linear Models.
+\newblock Journal of the Royal Statistical Society Series A (General).
+  1972;135(3):370--384.
+
+\bibitem{harris2020array}
+Harris CR, Millman KJ, van~der Walt SJ, Gommers R, Virtanen P, Cournapeau D,
+  et~al.
+\newblock Array programming with {NumPy}.
+\newblock Nature. 2020;585(7825):357--362.
+\newblock doi:{10.1038/s41586-020-2649-2}.
+
+\bibitem{groupyr}
+{R}ichie {H}alford A, Narayan M, Simon N, Yeatman J, Rokem A.
+\newblock {G}roupyr: {S}parse {G}roup {L}asso in {P}ython.
+\newblock Journal of Open Source Software. 2021;6(58):3024.
+\newblock doi:{10.21105/joss.03024}.
+
+\bibitem{parikh2014proximal}
+Parikh N, Boyd S, et~al.
+\newblock Proximal algorithms.
+\newblock Foundations and Trends in Optimization. 2014;1(3):127--239.
+
+\bibitem{copt}
+Pedregosa F.
+\newblock {C-OPT: composite optimization in Python}; 2018.
+\newblock Available from: \url{http://openopt.github.io/copt/}.
+
+\bibitem{sklearn_api}
+Buitinck L, Louppe G, Blondel M, Pedregosa F, Mueller A, Grisel O, et~al.
+\newblock {API} design for machine learning software: experiences from the
+  scikit-learn project.
+\newblock In: ECML PKDD Workshop: Languages for Data Mining and Machine
+  Learning; 2013. p. 108--122.
+
+\bibitem{scikit_optimize}
+Head T, Kumar M, Nahrstaedt H, Louppe G, Shcherbatyi I.
+  scikit-optimize/scikit-optimize; 2020.
+\newblock Available from: \url{https://doi.org/10.5281/zenodo.4014775}.
+
+\bibitem{mckinney2010data}
+McKinney W, et~al.
+\newblock Data structures for statistical computing in python.
+\newblock In: Proceedings of the 9th Python in Science Conference. vol. 445.
+  Austin, TX; 2010. p. 51--56.
+
+\end{thebibliography}
+
+\section*{Supporting information}
+
+\paragraph{S1 Fig}
+\label{S1_Fig}
+{\bf Bundle profiles and regression coefficients for the ALS dataset FA.}
+Diffusion metrics are plotted
+along the length of eighteen bundles:
+right corticospinal (CSTR),
+left corticospinal (CSTL),
+right uncinate (UNCR),
+left uncinate (UNCL),
+left inferior fronto-occipital fasciculus (IFOL),
+right inferior fronto-occipital fasciculus (IFOR),
+right arcuate (ARCR),
+left arcuate (ARCL),
+right thalamic radiation (ATRR),
+left thalamic radiation (ATRL),
+right cingulum cingulate (CGCR),
+left cingulum cingulate (CGCL),
+callosum forceps posterior (CFP),
+callosum forceps anterior (CFA),
+right inferior longitudinal fasciculus (ILFR),
+left inferior longitudinal fasciculus (ILFL),
+right superior longitudinal fasciculus (SLFR),
+and left superior longitudinal fasciculus (SLFL).
+FA is plotted on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on the twin axis on the right-hand-side. SGL selected
+the right corticospinal tract (CSTR) as important and regularized coefficients
+in the CSTL. Yet, there are also group FA differences in the
+CSTL. This highlighted a potential drawback of the SGL method, discussed in the
+main text in the context of age regression. Namely, SGL is not guaranteed to
+identify \emph{all} important features. In this case, if the diagnostic signal
+in the CSTL is redundant to that in the CSTR, SGL will regularize the CSTL
+features, thereby reducing its sparsity penalty without any corresponding
+increase in loss. This parsimony cuts both ways; it is a feature of the method
+when one seeks an efficient predictive model, but is a disadvantage of the
+method when one wants an exhaustive explanation of feature importance. We use the phrase ``parsimony pitfall'' to refer to the case when SGL regularizes
+away redundant but obviously important features.
+
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+{\bf Bundle profiles and regression coefficients for the ALS dataset MD.}
+The scale of the $\hat{\beta}$-axis is identical to that used in \mbox{\nameref{S1_Fig}, to facilitate the comparison of the relative importance of each metric.}
+
+\paragraph*{S3 Fig.}
+\label{S3_Fig}
+{\bf Bundle profiles and regression coefficients for the WH dataset FA.}
+In contrast to the ALS classification case,
+the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting the interpretation that aging is a large and continuous whole-brain process.
+
+\paragraph*{S4 Fig.}
+\label{S4_Fig}
+{\bf Bundle profiles and regression coefficients for the WH dataset MD.}
+This and \nameref{S3_Fig} demonstrate that SGL behaves much more like the
+lasso than the group lasso, as discussed in the main text. The parsimony pitfall
+is most evident in the IFOL and IFOR bundles.
+
+\paragraph*{S5 Fig.}
+\label{S5_Fig}
+{\bf FA bundle profiles and $\hat{\beta}$ coefficients for age regression in the HBN dataset.}
+Like the WH dataset, the $\hat{\beta}$
+coefficients are distributed widely through the brain and SGL behaves more like
+the lasso than the group lasso.
+
+\paragraph*{S6 Fig.}
+\label{S6_Fig}
+{\bf MD bundle profiles and $\hat{\beta}$ coefficients for age regression in the HBN dataset.}
+In contrast to the WH results, the bundle
+profiles show different behaviors. For example the SLFL and SLFR bundle profiles
+in have different concavity. This is unsurprising, however, given the
+differences between these datasets (see also Discussion). The parsimony pitfall
+is most evident in the UNCL, UNCR, ARCL, SLFL, and SLFR bundles
+
+\paragraph*{S7 Fig.}
+\label{S7_Fig}
+{\bf FA bundle profiles and $\hat{\beta}$ coefficients for age regression in the Cam-CAN dataset.}
+The $\hat{\beta}$ coefficients are
+distributed widely through the brain and SGL behaves more like the lasso than
+the group lasso. As before, one must be cautious about comparing bundle profiles
+and $\hat{\beta}$ coefficients between models. While the HBN and Cam-CAN
+datasets share the same diffusion model and refrain from clipping streamlines,
+the age distributions for the two are roughly disjoint, with the WH age
+distribution straddling the two.
+
+\paragraph*{S8 Fig.}
+\label{S8_Fig}
+{\bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$ coefficients for age regression in the Cam-CAN dataset.}
+
+\paragraph*{S9 Fig.}
+\label{S9_Fig}
+{\bf Age distributions are similar between the different HBN sites.}
+Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
+
+\paragraph*{S10 Fig.}
+\label{S10_Fig}
+{\bf FA bundle profiles exhibit strong site differences in the HBN dataset.}
+
+\paragraph*{S11 Fig.}
+\label{S11_Fig}
+{\bf MD bundle profiles exhibit strong site differences in the HBN dataset.}
+
+\paragraph*{S12 Fig.}
+\label{S12_Fig}
+{\bf Site differences in FA are eliminated by ComBat harmonization.}
+
+\paragraph*{S13 Fig.}
+\label{S13_Fig}
+{\bf Site differences in MD are eliminated by ComBat harmonization.}
 

### 2021-06-09 reports/manuscript/paper_changes.tex

@@
 \bigskip
-\textbf{1} eScience Institute, University of Washington, Seattle, WA, USA
+\textbf{1} eScience Institute, University of Washington, Seattle, \replaced{Washington, United States of America}{WA, USA}
 \\
-\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, CA, USA
+\textbf{2} Graduate School of Education and Division of Developmental and Behavioral Pediatrics, Stanford University, Stanford, \replaced{California, United States of America}{CA, USA}
 \\
-\textbf{3} Department of Biostatistics, University of Washington, Seattle, WA, USA
+\textbf{3} Department of Biostatistics, University of Washington, Seattle, \replaced{Washington, United States of America}{WA, USA}
 \\
-\textbf{4} Department of Psychology, University of Washington, Seattle, WA, USA
+\textbf{4} Department of Psychology, University of Washington, Seattle, \replaced{Washington, United States of America}{WA, USA}
 \\
@@
     \caption{\label{fig:methods}
-    {\bf Figure 1: Tractometry data flow}
+    {\bf \deleted{Figure 1}: Tractometry data flow}
     \textbf{(a)} Whole brain tractography generates streamlines approximating
@@
 \Cref{fig:class-results:tract-profiles} depicts these coefficients along the
-right CST, plotted over the FA values for the control and ALS subject groups (see Supporting Figures S1 and S2 for tract profiles of all 18 tracts in these groups).
+right CST, plotted over the FA values for the control and ALS subject groups
+(see \replaced{S1 Fig and S2 Fig}{Supporting Figures S1 and S2} for tract profiles of all 18 tracts in these groups).
 We find that SGL and PCR-SGL select FA metrics in the corticospinal tract and
@@
     \caption{
-    {\bf Figure 2: PCR-SGL accurately and interpretably predicts ALS diagnosis.}
+    {\bf \deleted{Figure 2}: PCR-SGL accurately and interpretably predicts ALS diagnosis.}
     {\bf (a)} Classification probabilities for ALS diagnosis, with
@@
 from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
-imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets see Supporting Figures S3 to S8 for the full tract profile information in all tracts/datasets.
+imaging (DKI) \cite{jensen2005diffusion} for the HBN and Cam-CAN datasets
+see \replaced{S3 Fig to S8 Fig}{Supporting Figures S3 to S8} for the full tract profile information in all tracts/datasets.
 
@@
 \cref{fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d}
-and supporing figures in \nameref{S1_Appendix}).
+and supporing figures in \replaced{S3 Fig to S8 Fig}{S1 Appendix}).
 This demonstrates that SGL is not coerced to produce overly sparse results
@@
     \phantomcaption{%
-    {\bf Figure 3: Predicting age with tractometry and SGL.}
+    {\bf \deleted{Figure 3}: Predicting age with tractometry and SGL.}
     {\bf (top)} The predicted age vs. true age of each individual from the test
@@
     \caption{%
-    {\bf Figure 4: Model performance across all datasets.}
+    {\bf \deleted{Figure 4}: Model performance across all datasets.}
 Each panel shows model performance measured on the test set for each
@@
 properties \cite{yeatman2014lifespan}.
-We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in the Supporting Information.
+We present age quintile bundle profiles and SGL \protect$\beta$ coefficients for all four datasets in \replaced{S3 Fig to S8 Fig}{the Supporting Information}.
 For age regression, substantial differences between the datasets preclude generalization across all three:
@@
 was provided by parents/guardians for children. Voxel resolution was
-\num{2x2x2}$\textrm{mm}^3$ with 96 non-colinear directions measured with a
+$2 \times 2 \times 2 \textrm{mm}^3$ with 96 non-colinear directions measured with a
 $b=2000$ $\textrm{s} / \textrm{mm}^2$ and 30 non-colinear directions
@@
 sites in the New York
-area: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center. Age distributions of participants in the different sites are in Supporting Figure S9.
+area: Rutgers University Brain Imaging Center and the CitiGroup Cornell Brain Imaging Center. Age distributions of participants in the different sites are in \replaced{S9 Fig}{Supporting Figure S9}.
 Informed consent was obtained from each participant aged 18 or older. For
@@
 in each voxel (STT) \cite{basser2000vivo}. Eighteen major
-tracts, which are enumerated in Figure S1, were identified
+tracts, which are enumerated in \replaced{S1 Fig}{Figure S1}, were identified
 using multiple criteria: streamlines are selected as candidates for
@@
 are quantified and averaged along eighteen major fiber tracts,
-which are enumerated in the Supporting Information.
+which are enumerated in \replaced{S1 Fig}{the Supporting Information}.
 See Fig S3 of \cite{kruper2021evaluating} for a depiction of these white matter bundles.
@@
 Initially designed to correct for site effects in gene expression studies \cite{johnson2007adjusting}, ComBat employs a parametric empirical Bayes approach to adjust for batch effects and has since been applied to multi-site cortical thickness measurements \cite{fortin2018harmonization}, multi-site DTI studies \cite{fortin2017harmonization}, and functional MRI data in the Adolescent Brain Cognitive Development Study (ABCD) \cite{nielson2018detecting}.
-We rely on the \texttt{neurocombat\_sklearn} library \cite{neurocombat_sklearn}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences and ComBat correction in Supporting Figures S10-S13.
+We rely on the \texttt{neurocombat\_sklearn} library \cite{neurocombat_sklearn}, to apply ComBat in our scikit-learn analysis pipeline and present bundle profile site differences and ComBat correction in \replaced{S10 Fig to S13 Fig}{Supporting Figures S10-S13}.
 
@@
     \phantomcaption{
-    {\bf Figure 5: Nested cross-validation.}
+    {\bf \deleted{Figure 5}: Nested cross-validation.}
 We evaluate model quality using a nested $k$-fold cross validation
@@
 
-This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
-National Institutes for Mental Health, by a grant from the Gordon \& Betty
-Moore Foundation and the Alfred P. Sloan Foundation to the University of
-Washington eScience Institute Data Science Environment, and by the Google
-Cloud Platform Academic Research Credits Program. We would like to thank
-Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
-and John Kruper
+\deleted{This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the National Institutes for Mental Health, by a grant from the Gordon \& Betty Moore Foundation and the Alfred P.
+Sloan Foundation to the University of Washington eScience Institute Data Science Environment, and by the Google Cloud Platform Academic Research Credits Program.}
+We would like to thank Scott Murray for a useful discussion of the SGL method
+and Mareike Grotheer and John Kruper
 for helpful comments on the manuscript.
@@
 
+\begin{thebibliography}{100}
+
+\bibitem{stejskal1965spin}
+Stejskal EO, Tanner JE.
+\newblock {Spin Diffusion Measurements: Spin Echoes in the Presence of a
+  Time-Dependent Field Gradient}.
+\newblock The Journal of Chemical Physics. 1965;42(1):288--292.
+\newblock doi:{10.1063/1.1695690}.
+
+\bibitem{wandell2016clarifying}
+Wandell BA.
+\newblock Clarifying human white matter.
+\newblock Annual review of neuroscience. 2016;39:103--128.
+
+\bibitem{Conturo1999-je}
+Conturo TE, Lori NF, Cull TS, Akbudak E, Snyder AZ, Shimony JS, et~al.
+\newblock Tracking neuronal fiber pathways in the living human brain.
+\newblock Proc Natl Acad Sci U S A. 1999;96(18):10422--10427.
+
+\bibitem{Mori2002-qi}
+Mori S, Van~Zijl PCM.
+\newblock Fiber tracking: principles and strategies--a technical review.
+\newblock NMR in Biomedicine: An International Journal Devoted to the
+  Development and Application of Magnetic Resonance In Vivo.
+  2002;15(7-8):468--480.
+
+\bibitem{yeatman2012tract}
+Yeatman JD, Dougherty RF, Myall NJ, Wandell BA, Feldman HM.
+\newblock Tract profiles of white matter properties: automating fiber-tract
+  quantification.
+\newblock PloS one. 2012;7(11):e49790.
+
+\bibitem{Jones2005-yq}
+Jones DK, Travis AR, Eden G, Pierpaoli C, Basser PJ.
+\newblock {PASTA}: pointwise assessment of streamline tractography attributes.
+\newblock Magn Reson Med. 2005;53(6):1462--1467.
+
+\bibitem{Bells2011-cf}
+Bells S, Cercignani M, Deoni S, Assaf Y, Pasternak O, Evans C, et~al.
+\newblock Tractometry--comprehensive multi-modal quantitative assessment of
+  white matter along specific tracts.
+\newblock In: Proc. ISMRM. vol. 678; 2011. p.~1.
+
+\bibitem{colby2012}
+Colby JB, Soderberg L, Lebel C, Dinov ID, Thompson PM, Sowell ER.
+\newblock Along-tract statistics allow for enhanced tractography analysis.
+\newblock Neuroimage. 2012;59(4):3227--3242.
+
+\bibitem{ODonnell2009-uu}
+O'Donnell LJ, Westin CF, Golby AJ.
+\newblock Tract-based morphometry for white matter group analysis.
+\newblock Neuroimage. 2009;45(3):832--844.
+
+\bibitem{Nichols2002-zu}
+Nichols TE, Holmes AP.
+\newblock Nonparametric permutation tests for functional neuroimaging: a primer
+  with examples.
+\newblock Hum Brain Mapp. 2002;15(1):1--25.
+
+\bibitem{Nichols2003-yy}
+Nichols T, Hayasaka S.
+\newblock {Controlling the familywise error rate in functional neuroimaging: a
+  comparative review}.
+\newblock Stat Methods Med Res. 2003;12(5):419--446.
+
+\bibitem{chamberland2019dimensionality}
+Chamberland M, Raven EP, Genc S, Duffy K, Descoteaux M, Parker GD, et~al.
+\newblock Dimensionality reduction of diffusion {MRI} measures for improved
+  tractometry of the human brain.
+\newblock NeuroImage. 2019;200:89--100.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2019.06.020}.
+
+\bibitem{huber2018rapid}
+Huber E, Donnelly PM, Rokem A, Yeatman JD.
+\newblock Rapid and widespread white matter plasticity during an intensive
+  reading intervention.
+\newblock Nature communications. 2018;9(1):2260.
+
+\bibitem{dayan2016profilometry}
+Dayan M, Monohan E, Pandya S, Kuceyeski A, Nguyen TD, Raj A, et~al.
+\newblock Profilometry: a new statistical framework for the characterization of
+  white matter pathways, with application to multiple sclerosis.
+\newblock Human brain mapping. 2016;37(3):989--1004.
+
+\bibitem{Murdoch2019-ax}
+Murdoch WJ, Singh C, Kumbier K, Abbasi-Asl R, Yu B.
+\newblock Definitions, methods, and applications in interpretable machine
+  learning.
+\newblock Proc Natl Acad Sci U S A. 2019;116(44):22071--22080.
+
+\bibitem{Breiman2001-uz}
+Breiman L.
+\newblock {Statistical Modeling: The Two Cultures (with comments and a
+  rejoinder by the author)}.
+\newblock Stat Sci. 2001;16(3):199--231.
+
+\bibitem{smith2006tract}
+Smith SM, Jenkinson M, Johansen-Berg H, Rueckert D, Nichols TE, Mackay CE,
+  et~al.
+\newblock Tract-based spatial statistics: voxelwise analysis of multi-subject
+  diffusion data.
+\newblock Neuroimage. 2006;31(4):1487--1505.
+
+\bibitem{yeh2016connectometry}
+Yeh FC, Badre D, Verstynen T.
+\newblock Connectometry: a statistical approach harnessing the analytical
+  potential of the local connectome.
+\newblock Neuroimage. 2016;125:162--171.
+
+\bibitem{Bzdok2020-sd}
+Bzdok D, Engemann D, Thirion B.
+\newblock Inference and Prediction Diverge in Biomedicine.
+\newblock Patterns (N Y). 2020;1(8):100119.
+
+\bibitem{Naselaris2011-ss}
+Naselaris T, Kay KN, Nishimoto S, Gallant JL.
+\newblock Encoding and decoding in {fMRI}.
+\newblock Neuroimage. 2011;56(2):400--410.
+
+\bibitem{Tibshirani1996-qs}
+Tibshirani R.
+\newblock {Regression Shrinkage and Selection via the Lasso}.
+\newblock J R Stat Soc Series B Stat Methodol. 1996;58(1):267--288.
+
+\bibitem{Yuan2006-ky}
+Yuan M, Lin Y.
+\newblock Model selection and estimation in regression with grouped variables.
+\newblock J R Stat Soc Series B Stat Methodol. 2006;68(1):49--67.
+
+\bibitem{simon2013sgl}
+Simon N, Friedman J, Hastie T, Tibshirani R.
+\newblock A sparse-group lasso.
+\newblock Journal of Computational and Graphical Statistics.
+  2013;22(2):231--245.
+
+\bibitem{powell2018local}
+Powell MA, Garcia JO, Yeh FC, Vettel JM, Verstynen T.
+\newblock {Local connectome phenotypes predict social, health, and cognitive
+  factors}.
+\newblock Network Neuroscience. 2018;2(1):86--105.
+\newblock doi:{10.1162/NETN\_a\_00031}.
+
+\bibitem{rasero2021integrating}
+Rasero J, Sentis AI, Yeh FC, Verstynen T.
+\newblock Integrating across neuroimaging modalities boosts prediction accuracy
+  of cognitive ability.
+\newblock PLOS Computational Biology. 2021;17(3):1--25.
+\newblock doi:{10.1371/journal.pcbi.1008347}.
+
+\bibitem{sarica2017corticospinal}
+Sarica A, Cerasa A, Valentino P, Yeatman J, Trotta M, Barone S, et~al.
+\newblock The corticospinal tract profile in amyotrophic lateral sclerosis.
+\newblock Human brain mapping. 2017;38(2):727--739.
+
+\bibitem{van2011upper}
+van~der Graaff MM, Sage CA, Caan MW, Akkerman EM, Lavini C, Majoie CB, et~al.
+\newblock Upper and extra-motoneuron involvement in early motoneuron disease: a
+  diffusion tensor imaging study.
+\newblock Brain. 2011;134(4):1211--1228.
+
+\bibitem{toosy2003diffusion}
+Toosy A, Werring D, Orrell R, Howard R, King M, Barker G, et~al.
+\newblock Diffusion tensor imaging detects corticospinal tract involvement at
+  multiple levels in amyotrophic lateral sclerosis.
+\newblock Journal of Neurology, Neurosurgery \& Psychiatry.
+  2003;74(9):1250--1257.
+
+\bibitem{sarica2014tractography}
+Sarica A, Cerasa A, Vasta R, Perrotta P, Valentino P, Mangone G, et~al.
+\newblock Tractography in amyotrophic lateral sclerosis using a novel
+  probabilistic tool: a study with tract-based reconstruction compared to
+  voxel-based approach.
+\newblock Journal of neuroscience methods. 2014;224:79--87.
+
+\bibitem{sage2007quantitative}
+Sage CA, Peeters RR, G{\"o}rner A, Robberecht W, Sunaert S.
+\newblock Quantitative diffusion tensor imaging in amyotrophic lateral
+  sclerosis.
+\newblock Neuroimage. 2007;34(2):486--499.
+
+\bibitem{sage2009quantitative}
+Sage CA, Van~Hecke W, Peeters R, Sijbers J, Robberecht W, Parizel P, et~al.
+\newblock Quantitative diffusion tensor imaging in amyotrophic lateral
+  sclerosis: revisited.
+\newblock Human brain mapping. 2009;30(11):3657--3675.
+
+\bibitem{karlsborg2004corticospinal}
+Karlsborg M, Rosenbaum S, Wiegell MR, Simonsen H, Larsson HB, Werdelin LM,
+  et~al.
+\newblock {Corticospinal tract degeneration and possible pathogenesis in ALS
+  evaluated by MR diffusion tensor imaging}.
+\newblock Amyotrophic Lateral Sclerosis and Other Motor Neuron Disorders.
+  2004;5(3):136--140.
+
+\bibitem{ellis1999diffusion}
+Ellis C, Simmons A, Jones D, Bland J, Dawson J, Horsfield M, et~al.
+\newblock {Diffusion tensor MRI assesses corticospinal tract damage in ALS}.
+\newblock Neurology. 1999;53(5):1051--1051.
+
+\bibitem{cosottini2005diffusion}
+Cosottini M, Giannelli M, Siciliano G, Lazzarotti G, Michelassi MC, Del~Corona
+  A, et~al.
+\newblock {Diffusion-tensor MR imaging of corticospinal tract in amyotrophic
+  lateral sclerosis and progressive muscular atrophy}.
+\newblock Radiology. 2005;237(1):258--264.
+
+\bibitem{ciccarelli2009investigation}
+Ciccarelli O, Behrens TE, Johansen-Berg H, Talbot K, Orrell RW, Howard RS,
+  et~al.
+\newblock {Investigation of white matter pathology in ALS and PLS using
+  tract-based spatial statistics}.
+\newblock Human brain mapping. 2009;30(2):615--624.
+
+\bibitem{abe2010voxel}
+Abe O, Takao H, Gonoi W, Sasaki H, Murakami M, Kabasawa H, et~al.
+\newblock Voxel-based analysis of the diffusion tensor.
+\newblock Neuroradiology. 2010;52(8):699--710.
+
+\bibitem{Cole2019-rz}
+Cole JH, Marioni RE, Harris SE, Deary IJ.
+\newblock Brain age and other bodily 'ages': implications for neuropsychiatry.
+\newblock Mol Psychiatry. 2019;24(2):266--281.
+
+\bibitem{nelson2019biomarkers}
+Nelson PG, Promislow DEL, Masel J.
+\newblock {Biomarkers for Aging Identified in Cross-sectional Studies Tend to
+  Be Non-causative}.
+\newblock The Journals of Gerontology: Series A. 2019;75(3):466--472.
+\newblock doi:{10.1093/gerona/glz174}.
+
+\bibitem{yeatman2014lifespan}
+Yeatman JD, Wandell BA, Mezer AA.
+\newblock Lifespan maturation and degeneration of human brain white matter.
+\newblock Nature communications. 2014;5:4932.
+
+\bibitem{alexander2017open}
+Alexander LM, Escalera J, Ai L, Andreotti C, Febre K, Mangone A, et~al.
+\newblock An open resource for transdiagnostic research in pediatric mental
+  health and learning disorders.
+\newblock Scientific Data. 2017;4:170181.
+
+\bibitem{shafto2014cambridge}
+Shafto MA, Tyler LK, Dixon M, Taylor JR, Rowe JB, Cusack R, et~al.
+\newblock {The Cambridge Centre for Ageing and Neuroscience (Cam-CAN) study
+  protocol: a cross-sectional, lifespan, multidisciplinary examination of
+  healthy cognitive ageing}.
+\newblock BMC Neurology. 2014;14:204.
+\newblock doi:{https://doi.org/10.1186/s12883-014-0204-1}.
+
+\bibitem{taylor2017cambridge}
+Taylor JR, Williams N, Cusack R, Auer T, Shafto MA, Dixon M, et~al.
+\newblock {The Cambridge Centre for Ageing and Neuroscience (Cam-CAN) data
+  repository: Structural and functional MRI, MEG, and cognitive data from a
+  cross-sectional adult lifespan sample}.
+\newblock NeuroImage. 2017;144:262 -- 269.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2015.09.018}.
+
+\bibitem{jensen2005diffusion}
+Jensen JH, Helpern JA, Ramani A, Lu H, Kaczynski K.
+\newblock Diffusional kurtosis imaging: The quantification of non-gaussian
+  water diffusion by means of magnetic resonance imaging.
+\newblock Magnetic Resonance in Medicine. 2005;53(6):1432--1440.
+\newblock doi:{https://doi.org/10.1002/mrm.20508}.
+
+\bibitem{mcpherson2020single}
+{McPherson} B, Pestilli F.
+\newblock A single-mode associates global patterns of brain network structure
+  and behavior across the human lifespan.
+\newblock bioRxiv. 2020;doi:{10.1101/2020.09.24.312090}.
+
+\bibitem{Richard2018-ux}
+Richard G, Kolsk{\aa}r K, Sanders AM, Kaufmann T, Petersen A, Doan NT, et~al.
+\newblock Assessing distinct patterns of cognitive aging using tissue-specific
+  brain age prediction based on diffusion tensor imaging and brain morphometry.
+\newblock PeerJ. 2018;6:e5908.
+
+\bibitem{simon2013sparse}
+Simon N, Friedman J, Hastie T, Tibshirani R.
+\newblock A sparse-group lasso.
+\newblock Journal of Computational and Graphical Statistics.
+  2013;22(2):231--245.
+
+\bibitem{pinto2020harmonization}
+Pinto MS, Paolella R, Billiet T, Van~Dyck P, Guns PJ, Jeurissen B, et~al.
+\newblock Harmonization of Brain Diffusion MRI: Concepts and Methods.
+\newblock Frontiers in Neuroscience. 2020;14:396.
+\newblock doi:{10.3389/fnins.2020.00396}.
+
+\bibitem{lermausabiaga2019replication}
+Lerma-Usabiaga G, Mukherjee P, Ren Z, Perry ML, Wandell BA.
+\newblock Replication and generalization in applied neuroimaging.
+\newblock NeuroImage. 2019;202:116048.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2019.116048}.
+
+\bibitem{jernigan2016ping}
+Jernigan TL, Brown TT, Hagler DJ Jr, Akshoomoff N, Bartsch H, Newman E, et~al.
+\newblock {The Pediatric Imaging, Neurocognition, and Genetics (PING) Data
+  Repository}.
+\newblock Neuroimage. 2016;124(Pt B):1149--1154.
+
+\bibitem{jernigan2018abcd}
+Jernigan TL, Brown SA, Dowling GJ.
+\newblock {The Adolescent Brain Cognitive Development Study}.
+\newblock J Res Adolesc. 2018;28(1):154--156.
+
+\bibitem{Miller2016-hw}
+Miller KL, Alfaro-Almagro F, Bangerter NK, Thomas DL, Yacoub E, Xu J, et~al.
+\newblock Multimodal population brain imaging in the {UK} {B}iobank prospective
+  epidemiological study.
+\newblock Nat Neurosci. 2016;.
+
+\bibitem{VanEssen2012}
+{Van Essen} DC, Ugurbil K, Auerbach E, Barch D, Behrens TEJ, Bucholz R, et~al.
+\newblock {The Human Connectome Project: A data acquisition perspective}.
+\newblock NeuroImage. 2012;62(4):2222 -- 2231.
+\newblock doi:{http://dx.doi.org/10.1016/j.neuroimage.2012.02.018}.
+
+\bibitem{steinmetz2018distributed}
+Steinmetz N, Zatka-Haas P, Carandini M, Harris K.
+\newblock Distributed correlates of visually-guided behavior across the mouse
+  brain.
+\newblock Nature. 2018; p. in press.
+
+\bibitem{Jun2017-gv}
+Jun JJ, Steinmetz NA, Siegle JH, Denman DJ, Bauza M, Barbarits B, et~al.
+\newblock Fully integrated silicon probes for high-density recording of neural
+  activity.
+\newblock Nature. 2017;551(7679):232--236.
+
+\bibitem{zhou2012}
+Zhou J, Liu J, Narayan VA, Ye J.
+\newblock {Modeling Disease Progression via Fused Sparse Group Lasso}.
+\newblock In: Proceedings of the 18th {ACM} {SIGKDD} International Conference
+  on Knowledge Discovery and Data Mining. KDD '12. New York, NY, USA: ACM;
+  2012. p. 1095--1103.
+
+\bibitem{Rao2014-xm}
+Rao N, Nowak R, Cox C, Rogers T. Classification with Sparse Overlapping Groups;
+  2014.
+
+\bibitem{kruper2021evaluating}
+Kruper J, Yeatman JD, Richie-Halford A, Bloom D, Grotheer M, Caffarra S, et~al.
+\newblock Evaluating the reliability of human brain white matter tractometry.
+\newblock bioRxiv. 2021;doi:{10.1101/2021.02.24.432740}.
+
+\bibitem{yeatman2018browser}
+Yeatman JD, Richie-Halford A, Smith JK, Keshavan A, Rokem A.
+\newblock {A browser-based tool for visualization and analysis of diffusion MRI
+  data}.
+\newblock Nature communications. 2018;9(1):940.
+
+\bibitem{kluyver2016jupyter}
+Kluyver T, Ragan-Kelley B, P{\'e}rez F, Granger BE, Bussonnier M, Frederic J,
+  et~al.
+\newblock {Jupyter Notebooks-a publishing format for reproducible computational
+  workflows.}
+\newblock In: ELPUB; 2016. p. 87--90.
+
+\bibitem{basser1994mr}
+Basser PJ, Mattiello J, LeBihan D.
+\newblock {MR diffusion tensor spectroscopy and imaging}.
+\newblock Biophysical journal. 1994;66(1):259--267.
+
+\bibitem{chang2005restore}
+Chang LC, Jones DK, Pierpaoli C.
+\newblock {RESTORE: robust estimation of tensors by outlier rejection}.
+\newblock Magnetic Resonance in Medicine: An Official Journal of the
+  International Society for Magnetic Resonance in Medicine.
+  2005;53(5):1088--1095.
+
+\bibitem{nipype1}
+Gorgolewski K, Burns CD, Madison C, Clark D, Halchenko YO, Waskom ML, et~al.
+\newblock {Nipype: a flexible, lightweight and extensible neuroimaging data
+  processing framework in Python}.
+\newblock Frontiers in Neuroinformatics. 2011;5:13.
+\newblock doi:{10.3389/fninf.2011.00013}.
+
+\bibitem{nipype2}
+Gorgolewski KJ, Esteban O, Markiewicz CJ, Ziegler E, Ellis DG, Notter MP,
+  et~al.
+\newblock {Nipype}.
+\newblock Software. 2018;doi:{10.5281/zenodo.596855}.
+
+\bibitem{n4}
+Tustison NJ, Avants BB, Cook PA, Zheng Y, Egan A, Yushkevich PA, et~al.
+\newblock {N4ITK: Improved N3 Bias Correction}.
+\newblock IEEE Transactions on Medical Imaging. 2010;29(6):1310--1320.
+\newblock doi:{10.1109/TMI.2010.2046908}.
+
+\bibitem{mni}
+Fonov V, Evans A, McKinstry R, Almli C, Collins D.
+\newblock Unbiased nonlinear average age-appropriate brain templates from birth
+  to adulthood.
+\newblock NeuroImage. 2009;47, Supplement 1:S102.
+\newblock doi:{10.1016/S1053-8119(09)70884-5}.
+
+\bibitem{ants}
+Avants BB, Epstein CL, Grossman M, Gee JC.
+\newblock {Symmetric diffeomorphic image registration with cross-correlation:
+  Evaluating automated labeling of elderly and neurodegenerative brain}.
+\newblock Medical Image Analysis. 2008;12(1):26--41.
+\newblock doi:{10.1016/j.media.2007.06.004}.
+
+\bibitem{fsl_fast}
+Zhang Y, Brady M, Smith S.
+\newblock Segmentation of brain {MR} images through a hidden {M}arkov random
+  field model and the expectation-maximization algorithm.
+\newblock IEEE Transactions on Medical Imaging. 2001;20(1):45--57.
+\newblock doi:{10.1109/42.906424}.
+
+\bibitem{dwidenoise1}
+Veraart J, Novikov DS, Christiaens D, Ades-Aron B, Sijbers J, Fieremans E.
+\newblock Denoising of diffusion {MRI} using random matrix theory.
+\newblock NeuroImage. 2016;142:394--406.
+
+\bibitem{anderssoneddy}
+Andersson JL, Sotiropoulos SN.
+\newblock {An integrated approach to correction for off-resonance effects and
+  subject movement in diffusion MR imaging}.
+\newblock Neuroimage. 2016;125:1063--1078.
+
+\bibitem{eddyrepol}
+Andersson JL, Graham MS, Zsoldos E, Sotiropoulos SN.
+\newblock {Incorporating outlier detection and replacement into a
+  non-parametric framework for movement and distortion correction of diffusion
+  MR images}.
+\newblock Neuroimage. 2016;141:556--572.
+
+\bibitem{topup}
+Andersson JL, Skare S, Ashburner J.
+\newblock How to correct susceptibility distortions in spin-echo echo-planar
+  images: application to diffusion tensor imaging.
+\newblock Neuroimage. 2003;20(2):870--888.
+
+\bibitem{power_fd_dvars}
+Power JD, Mitra A, Laumann TO, Snyder AZ, Schlaggar BL, Petersen SE.
+\newblock {Methods to detect, characterize, and remove motion artifact in
+  resting state fMRI}.
+\newblock NeuroImage. 2014;84(Supplement C):320--341.
+\newblock doi:{10.1016/j.neuroimage.2013.08.048}.
+
+\bibitem{originalcsd}
+Tournier JD, Calamante F, Gadian DG, Connelly A.
+\newblock Direct estimation of the fiber orientation density function from
+  diffusion-weighted {MRI} data using spherical deconvolution.
+\newblock NeuroImage. 2004;23(3):1176--1185.
+
+\bibitem{tournier2008csd}
+Tournier JD, Yeh CH, Calamante F, Cho KH, Connelly A, Lin CP.
+\newblock Resolving crossing fibres using constrained spherical deconvolution:
+  validation using diffusion-weighted imaging phantom data.
+\newblock Neuroimage. 2008;42(2):617--625.
+
+\bibitem{dhollander2019response}
+Dhollander T, Mito R, Raffelt D, Connelly A.
+\newblock Improved white matter response function estimation for 3-tissue
+  constrained spherical deconvolution.
+\newblock In: Proc. Intl. Soc. Mag. Reson. Med; 2019. p. 555.
+
+\bibitem{dhollander2016unsupervised}
+Dhollander T, Raffelt D, Connelly A.
+\newblock Unsupervised 3-tissue response function estimation from single-shell
+  or multi-shell diffusion {MR} data without a co-registered {T1} image.
+\newblock In: ISMRM Workshop on Breaking the Barriers of Diffusion MRI. vol.~5;
+  2016. p.~5.
+
+\bibitem{mrtrix3}
+J-Donald, Smith R, Raffelt D, Tabbara R, Dhollander T, Pietsch M, et~al.
+\newblock {MRtrix3: A fast, flexible and open software framework for medical
+  image processing and visualisation}.
+\newblock NeuroImage. 2019;202:116137.
+
+\bibitem{mtnormalize}
+Raffelt D, Dhollander T, Tournier JD, Tabbara R, Smith RE, Pierre E, et~al.
+\newblock Bias field correction and intensity normalisation for quantitative
+  analysis of apparent fibre density.
+\newblock In: Proc. Intl. Soc. Mag. Reson. Med. vol.~25; 2017. p. 3541.
+
+\bibitem{nilearn}
+Abraham A, Pedregosa F, Eickenberg M, Gervais P, Mueller A, Kossaifi J, et~al.
+\newblock {Machine learning for neuroimaging with scikit-learn}.
+\newblock Frontiers in Neuroinformatics. 2014;8.
+\newblock doi:{10.3389/fninf.2014.00014}.
+
+\bibitem{dipy}
+Garyfallidis E, Brett M, Amirbekian B, Rokem A, Van Der~Walt S, Descoteaux M,
+  et~al.
+\newblock {DIPY, a library for the analysis of diffusion MRI data}.
+\newblock Frontiers in neuroinformatics. 2014;8:8.
+
+\bibitem{basser2000vivo}
+Basser PJ, Pajevic S, Pierpaoli C, Duda J, Aldroubi A.
+\newblock {In vivo fiber tractography using DT-MRI data}.
+\newblock Magnetic resonance in medicine. 2000;44(4):625--632.
+
+\bibitem{wakana2007reproducibility}
+Wakana S, Caprihan A, Panzenboeck MM, Fallon JH, Perry M, Gollub RL, et~al.
+\newblock Reproducibility of quantitative tractography methods applied to
+  cerebral white matter.
+\newblock Neuroimage. 2007;36(3):630--644.
+
+\bibitem{Hua2008-sh}
+Hua K, Zhang J, Wakana S, Jiang H, Li X, Reich DS, et~al.
+\newblock Tract probability maps in stereotaxic spaces: analyses of white
+  matter anatomy and tract-specific quantification.
+\newblock Neuroimage. 2008;39(1):336--347.
+
+\bibitem{gorgolewski2016brain}
+Gorgolewski KJ, Auer T, Calhoun VD, Craddock RC, Das S, Duff EP, et~al.
+\newblock The brain imaging data structure, a format for organizing and
+  describing outputs of neuroimaging experiments.
+\newblock Scientific data. 2016;3(1):1--9.
+
+\bibitem{johnson2007adjusting}
+Johnson WE, Li C, Rabinovic A.
+\newblock Adjusting batch effects in microarray expression data using empirical
+  Bayes methods.
+\newblock Biostatistics. 2007;8(1):118--127.
+
+\bibitem{fortin2018harmonization}
+Fortin JP, Cullen N, Sheline YI, Taylor WD, Aselcioglu I, Cook PA, et~al.
+\newblock Harmonization of cortical thickness measurements across scanners and
+  sites.
+\newblock Neuroimage. 2018;167:104--120.
+
+\bibitem{fortin2017harmonization}
+Fortin JP, Parker D, Tunç B, Watanabe T, Elliott MA, Ruparel K, et~al.
+\newblock Harmonization of multi-site diffusion tensor imaging data.
+\newblock NeuroImage. 2017;161:149--170.
+\newblock doi:{https://doi.org/10.1016/j.neuroimage.2017.08.047}.
+
+\bibitem{nielson2018detecting}
+Nielson DM, Pereira F, Zheng CY, Migineishvili N, Lee JA, Thomas AG, et~al.
+\newblock Detecting and harmonizing scanner differences in the ABCD study -
+  annual release 1.0.
+\newblock bioRxiv. 2018;doi:{10.1101/309260}.
+
+\bibitem{neurocombat_sklearn}
+Pinaya WHL. NeuroCombat-sklearn; 2020.
+\newblock Available from: \url{https://github.com/Warvito/neurocombat_sklearn}.
+
+\bibitem{scikit-learn}
+Pedregosa F, Varoquaux G, Gramfort A, Michel V, Thirion B, Grisel O, et~al.
+\newblock {Scikit-learn: Machine Learning in Python}.
+\newblock Journal of Machine Learning Research. 2011;12:2825--2830.
+
+\bibitem{kaufman2012leakage}
+Kaufman S, Rosset S, Perlich C, Stitelman O.
+\newblock Leakage in data mining: Formulation, detection, and avoidance.
+\newblock ACM Transactions on Knowledge Discovery from Data (TKDD).
+  2012;6(4):15.
+
+\bibitem{tibshirani1996regression}
+Tibshirani R.
+\newblock Regression shrinkage and selection via the lasso.
+\newblock Journal of the Royal Statistical Society Series B (Methodological).
+  1996; p. 267--288.
+
+\bibitem{yuan2006model}
+Yuan M, Lin Y.
+\newblock Model selection and estimation in regression with grouped variables.
+\newblock Journal of the Royal Statistical Society: Series B (Statistical
+  Methodology). 2006;68(1):49--67.
+
+\bibitem{breiman1996bagging}
+Breiman L.
+\newblock Bagging predictors.
+\newblock Machine learning. 1996;24(2):123--140.
+
+\bibitem{nelder1972technique}
+Nelder JA, Wedderburn RWM.
+\newblock Generalized Linear Models.
+\newblock Journal of the Royal Statistical Society Series A (General).
+  1972;135(3):370--384.
+
+\bibitem{harris2020array}
+Harris CR, Millman KJ, van~der Walt SJ, Gommers R, Virtanen P, Cournapeau D,
+  et~al.
+\newblock Array programming with {NumPy}.
+\newblock Nature. 2020;585(7825):357--362.
+\newblock doi:{10.1038/s41586-020-2649-2}.
+
+\bibitem{groupyr}
+{R}ichie {H}alford A, Narayan M, Simon N, Yeatman J, Rokem A.
+\newblock {G}roupyr: {S}parse {G}roup {L}asso in {P}ython.
+\newblock Journal of Open Source Software. 2021;6(58):3024.
+\newblock doi:{10.21105/joss.03024}.
+
+\bibitem{parikh2014proximal}
+Parikh N, Boyd S, et~al.
+\newblock Proximal algorithms.
+\newblock Foundations and Trends in Optimization. 2014;1(3):127--239.
+
+\bibitem{copt}
+Pedregosa F.
+\newblock {C-OPT: composite optimization in Python}; 2018.
+\newblock Available from: \url{http://openopt.github.io/copt/}.
+
+\bibitem{sklearn_api}
+Buitinck L, Louppe G, Blondel M, Pedregosa F, Mueller A, Grisel O, et~al.
+\newblock {API} design for machine learning software: experiences from the
+  scikit-learn project.
+\newblock In: ECML PKDD Workshop: Languages for Data Mining and Machine
+  Learning; 2013. p. 108--122.
+
+\bibitem{scikit_optimize}
+Head T, Kumar M, Nahrstaedt H, Louppe G, Shcherbatyi I.
+  scikit-optimize/scikit-optimize; 2020.
+\newblock Available from: \url{https://doi.org/10.5281/zenodo.4014775}.
+
+\bibitem{mckinney2010data}
+McKinney W, et~al.
+\newblock Data structures for statistical computing in python.
+\newblock In: Proceedings of the 9th Python in Science Conference. vol. 445.
+  Austin, TX; 2010. p. 51--56.
+
+\end{thebibliography}
+
 \section*{Supporting information}
 
-\paragraph{Figure S1: Bundle profiles and regression coefficients for the ALS dataset FA.}
+\paragraph{\replaced{S1 Fig}{Figure S1: Bundle profiles and regression coefficients for the ALS dataset FA.}}
+\label{S1_Fig}
+\added{{\bf Bundle profiles and regression coefficients for the ALS dataset FA.}}
 Diffusion metrics are plotted
@@
 right superior longitudinal fasciculus (SLFR),
-and left superior longitudinal fasciculus (SLFL). We use these acronyms throughout the Supporting Information.
+and left superior longitudinal fasciculus (SLFL).
+\deleted{We use these acronyms throughout the Supporting Information.}
 FA is plotted on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on the twin axis on the right-hand-side. SGL selected
@@
 
-\paragraph*{Figure S2: Bundle profiles and regression coefficients for the ALS dataset MD.} The scale of the $\hat{\beta}$-axis is identical to that used in Figure S1, to facilitate the comparison of the relative importance of each metric.
-
-\paragraph*{Figure S3: Bundle profiles and regression
-coefficients for the WH dataset FA.} In contrast to the ALS classification case,
+\paragraph*{\replaced{S2 Fig.}{Figure S2: Bundle profiles and regression coefficients for the ALS dataset MD.
+The scale of the $\hat{\beta}$-axis is identical to that used in Figure S1, to facilitate the comparison of the relative importance of each metric.}}
+\label{S2_Fig}
+\added{{\bf Bundle profiles and regression coefficients for the ALS dataset MD.}}
+\added{The scale of the $\hat{\beta}$-axis is identical to that used in S1 Fig, to facilitate the comparison of the relative importance of each metric.}
+
+\paragraph*{\replaced{S3 Fig.}{Figure S3: Bundle profiles and regression coefficients for the WH dataset FA.}}
+\label{S3_Fig}
+\added{{\bf Bundle profiles and regression coefficients for the WH dataset FA.}}
+In contrast to the ALS classification case,
 the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting the interpretation that aging is a large and continuous whole-brain process.
 
-\paragraph*{Figure S4: Bundle profiles and regression coefficients for the WH
-dataset MD.} This and Figure S3 demonstrate that SGL behaves much more like the
+\paragraph*{\replaced{S4 Fig.}{Figure S4: Bundle profiles and regression coefficients for the WH dataset MD.}}
+\label{S4_Fig}
+\added{{\bf Bundle profiles and regression coefficients for the WH dataset MD.}}
+This and \replaced{S3 Fig}{Figure S3} demonstrate that SGL behaves much more like the
 lasso than the group lasso, as discussed in the main text. The parsimony pitfall
@@
 
-\paragraph*{Figure S5: FA bundle profiles and $\hat{\beta}$ coefficients for age
-regression in the HBN dataset.} Like the WH dataset, the $\hat{\beta}$
+\paragraph*{\replaced{S5 Fig.}{Figure S5: FA bundle profiles and $\hat{\beta}$ coefficients for age regression in the HBN dataset.}}
+\label{S5_Fig}
+\added{{\bf FA bundle profiles and $\hat{\beta}$ coefficients for age regression in the HBN dataset.}}
+Like the WH dataset, the $\hat{\beta}$
 coefficients are distributed widely through the brain and SGL behaves more like
@@
 
-\paragraph*{Figure S6: MD bundle profiles and $\hat{\beta}$ coefficients for age
-regression in the HBN dataset.} In contrast to the WH results, the bundle
+\paragraph*{\replaced{S6 Fig.}{Figure S6: MD bundle profiles and $\hat{\beta}$ coefficients for age regression in the HBN dataset.}}
+\label{S6_Fig}
+\added{{\bf MD bundle profiles and $\hat{\beta}$ coefficients for age regression in the HBN dataset.}}
+In contrast to the WH results, the bundle
 profiles show different behaviors. For example the SLFL and SLFR bundle profiles
@@
 
-\paragraph*{Figure S7: FA bundle profiles and $\hat{\beta}$ coefficients for age
-regression in the Cam-CAN dataset.} The $\hat{\beta}$ coefficients are
+\paragraph*{\replaced{S7 Fig.}{Figure S7: FA bundle profiles and $\hat{\beta}$ coefficients for age regression in the Cam-CAN dataset.}}
+\label{S7_Fig}
+\added{{\bf FA bundle profiles and $\hat{\beta}$ coefficients for age regression in the Cam-CAN dataset.}}
+The $\hat{\beta}$ coefficients are
 distributed widely through the brain and SGL behaves more like the lasso than
@@
 
-\paragraph*{Figure S8: Mean diffusivity (MD) bundle profiles and $\hat{\beta}$
-coefficients for age regression in the Cam-CAN dataset.}
-
-\paragraph*{Figure S9: Age distributions are similar between the different
-HBN sites.} Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
-
-\paragraph*{Figure S10: FA bundle profiles exhibit strong site differences in the HBN dataset.}
-
-\paragraph*{Figure S11: MD bundle profiles exhibit strong site differences in the HBN dataset.}
-
-\paragraph*{Figure S12: Site differences in FA are eliminated by ComBat harmonization.}
-
-\paragraph*{Figure S13: Site differences in MD are eliminated by ComBat harmonization.}
+\paragraph*{\replaced{S8 Fig.}{Figure S8: Mean diffusivity (MD) bundle profiles and $\hat{\beta}$ coefficients for age regression in the Cam-CAN dataset.}}
+\label{S8_Fig}
+\added{{\bf Mean diffusivity (MD) bundle profiles and $\hat{\beta}$ coefficients for age regression in the Cam-CAN dataset.}}
+
+\paragraph*{\replaced{S9 Fig.}{Figure S9: Age distributions are similar between the different HBN sites.}}
+\label{S9_Fig}
+\added{{\bf Age distributions are similar between the different HBN sites.}}
+Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
+
+\paragraph*{\replaced{S10 Fig.}{Figure S10: FA bundle profiles exhibit strong site differences in the HBN dataset.}}
+\label{S10_Fig}
+\added{{\bf FA bundle profiles exhibit strong site differences in the HBN dataset.}}
+
+\paragraph*{\replaced{S11 Fig.}{Figure S11: MD bundle profiles exhibit strong site differences in the HBN dataset.}}
+\label{S11_Fig}
+\added{{\bf MD bundle profiles exhibit strong site differences in the HBN dataset.}}
+
+\paragraph*{\replaced{S12 Fig.}{Figure S12: Site differences in FA are eliminated by ComBat harmonization.}}
+\label{S12_Fig}
+\added{{\bf Site differences in FA are eliminated by ComBat harmonization.}}
+
+\paragraph*{\replaced{S13 Fig.}{Figure S13: Site differences in MD are eliminated by ComBat harmonization.}}
+\label{S13_Fig}
+\added{{\bf Site differences in MD are eliminated by ComBat harmonization.}}
 

### 2021-06-09 reports/manuscript/supplemental_changes.tex
Move figure captions to the end.
Put figures back in their place.

@@
 
-\section{\added{Data harmonization in the HBN dataset}}
+\section{Data harmonization in the HBN dataset}
 
-\added{\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
+\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC).
 We see strong site differences in both FA and MD profiles.
 Conversely, \cref{fig:hbn-site-age-dist} shows that the age distributions at each site are similar.
-ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.}
+ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.
 
